### 2012-08-14 thesis.tex
Added Yee cell figure.

% Compile with:
% latex --halt-on-error thesis.tex && latex thesis.tex && dvips thesis.dvi && ps2pdf thesis.ps

\documentclass{book}
\usepackage{pstricks}
\usepackage{amsmath}
\newcommand{\E}[2]{\begin{align}#2\end{align}\label{eq:#1}}
\newcommand{\EE}[2]{\begin{subequations}\begin{align}#2\end{align}\label{eq:#1}\end{subequations}}
\newcommand{\curl}{\nabla\times}
\newcommand{\eq}[1]{\eqref{eq:#1}}
\newcommand{\fig}[1]{\ref{fig:#1}}
\begin{document}
\section{Solving $Ax=b$ using MaxwellFDS}
\subsection{Theory}
We need to solve Maxwell's equations, that is,
\EE {maxwell diff}
    {\curl E &= - \mu \frac{\partial H}{\partial t} \\
    \curl H &= J + \epsilon \frac{\partial E}{\partial t}, }
    where $E$, $H$, and $J$ are 
    the electric, magnetic and electric current
    vector fields, respectively,
    $\epsilon$ is the permittivity
    and $\mu$ is the permeability.

Assuming the time dependence $\exp(-i \omega t)$, 
    where $\omega$ is the angular frequency,
    these become
\EE {maxwell harmonic}
    {\curl E &= - i \mu \omega H \\
    \curl H &= J + i \epsilon \omega E,}
    which we can combine to form the time-harmonic wave equation for $E$,
    \E{maxwell wave E}
    {\curl \mu^{-1} \curl E - \epsilon \omega^2 E = -i \omega J,}
    which we will solve using MaxwellFDS.

Note that the alternative wave equation for $H$,
    where we consider the magnetic current source $M$
    instead of $J$,
\E  {maxwell wave H}
    {\curl \epsilon^{-1} \curl H - \mu \omega^2 H = -i \omega M,}
    can also be solved using MaxwellFDS.

\subsection{Numerical}
To solve \eq{maxwell wave E} we discretize our vector fields on the Yee grid
    as shown in \fig{yee grid}.

\begin{figure}[h]\begin{center}
\psset{gridcolor=green, subgridcolor=yellow}
\begin{pspicture}(-2,-2)(7,7)
    \let\psgrid\relax

    % Origin.
    \psdot(0,0) \rput[br](-0.1,0.1){$(0,0,0)$}

    % Principle axes.
    \psline[linestyle=dotted](-1,0)(6,0) \rput(6.3,0){$x$}
    \psline[linestyle=dotted](0,-1)(0,6) \rput(0,6.3){$z$}
    \psline[linestyle=dotted](-0.8,-0.6)(4.8,3.6) \rput(5.05,3.75){$y$}

    % Intermediate axes.
    \psline[linestyle=dotted](0,3)(3,3) % Hy point.
    \psline[linestyle=dotted](3,3)(3,0)

    \psline[linestyle=dotted](0,3)(2.4,4.8) % Hx point.
    \psline[linestyle=dotted](2.4,4.8)(2.4,1.8)

    \psline[linestyle=dotted](2.4,1.8)(5.4,1.8) % Hz point.
    \psline[linestyle=dotted](5.4,1.8)(3,0)

    % E-field vectors.
    \psline{->}(2.6,0)(3.4,0) \rput(3,-0.4){$E_x$}
    \psline{->}(0,2.6)(0,3.4) \rput(-0.4,3){$E_z$}
    \psline{->}(2.1,1.55)(2.7,2.05) \rput(2.05,2.05){$E_z$}

    % H-field vectors.
    \psline{->}(2,4.8)(2.8,4.8) \rput(2.4,5.2){$H_x$}
    \psline{->}(5.4,1.4)(5.4,2.2) \rput(5.8,1.8){$H_z$}
    \psline{->}(2.7,2.75)(3.3,3.25) \rput(2.7,3.3){$H_y$}
\end{pspicture}
\end{center}
\caption{Primitive Yee cell}
\end{figure}

\end{document}

### 2012-08-15 thesis.tex
Getting there...

@@
 
-\documentclass{book}
+\documentclass{article}
 \usepackage{pstricks}
 \usepackage{amsmath}
-\newcommand{\E}[2]{\begin{align}#2\end{align}\label{eq:#1}}
+\newcommand{\E}[2]{\begin{align}#2\label{eq:#1}\end{align}}
 \newcommand{\EE}[2]{\begin{subequations}\begin{align}#2\end{align}\label{eq:#1}\end{subequations}}
@@
 \newcommand{\eq}[1]{\eqref{eq:#1}}
-\newcommand{\fig}[1]{\ref{fig:#1}}
+\newcommand{\fig}[1]{figure~\ref{fig:#1}}
+\newcommand{\MaxwellFDS}{MaxwellFDS }
+\newcommand{\BI}{\begin{itemize}\item}
+\newcommand{\EI}{\end{itemize}}
+\newcommand{\I}{\item}
+\newcommand{\pf}[1]{\frac{\partial}{\partial #1}} % d/d_
+\newcommand{\prim}{\text{prim}}
+\newcommand{\dual}{\text{dual}}
+\newcommand{\mx}{\text{max}}
+\newcommand{\diag}{\text{diag}}
+\title{Harnessing the cloud to understand light: 
+        A whitepaper detailing the \MaxwellFDS core solver}
 \begin{document}
-\section{Solving $Ax=b$ using MaxwellFDS}
-\subsection{Theory}
-We need to solve Maxwell's equations, that is,
+\maketitle
+\tableofcontents
+
+\section*{Introduction}
+\MaxwellFDS is a cloud-powered electromagnetic solver,
+    tailored specifically to the field of nanophotonics.
+\MaxwellFDS stands for Frequency-Domain Solver.
+
+\section{Motivation: why another electromagnetic solver?}
+Although many electromagnetic simulation packages are currently available,
+    we found it necessary, for our own purposes, to create our own.
+Specifically, we desired a simulator which 
+    \BI operates in the frequency-domain, as opposed to the time-domain.
+    \I  scales to multiple high-resolution three-dimensional domains,
+    \I  is readily accessible via Matlab. \EI
+
+\subsection{The advantages of frequency-domain solutions}
+The advantages of solving Maxwell's equations in the  \emph{frequency}-domain 
+    as opposed to simulating them in the \emph{time}-domain include
+    \BI clean excitation of input modes,
+    \I  precise characterization of material dispersion,
+    \I  calculation of figure of merits outside of the simulation,
+    \I  explicit measurement of simulation error, and
+    \I  explicit calculation of eigenmodes. \EI
+
+\subsubsection{Input: clean excitation of modes}
+\subsubsection{Dispersion: precise characterization of frequency-dispersion}
+\subsubsection{Output: complete description of device performance}
+\subsubsection{Error: explicit measurement of simulation error}
+\subsubsection{Eigenmodes: explicit calculation of eigenmodes}
+
+\subsection{The advantages of simulating in the cloud}
+\subsection{The advantages of being built within Matlab}
+
+\section{Harnessing the cloud to understand light}
+\subsection{Accessing }
+
+\section{Solving the electromagnetic wave equation using \MaxwellFDS}
+\subsection{Analytic derivation of the electromagnetic wave equation}
+The electromagnetic wave equation can be derived from 
+    the differential form of Maxwell's equations, that is,
 \EE {maxwell diff}
@@
     {\curl \mu^{-1} \curl E - \epsilon \omega^2 E = -i \omega J,}
-    which we will solve using MaxwellFDS.
+    which \MaxwellFDS solves
 
@@
     {\curl \epsilon^{-1} \curl H - \mu \omega^2 H = -i \omega M,}
-    can also be solved using MaxwellFDS.
+    can also be solved using \MaxwellFDS.
 
-\subsection{Numerical}
-To solve \eq{maxwell wave E} we discretize our vector fields on the Yee grid
-    as shown in \fig{yee grid}.
+\subsection{Numerical discretization of the wave equation}
+\subsubsection{Use of the Yee cell}
+To solve \eq{maxwell wave E} we discretize our vector fields 
+    based on a primitive Yee cell, as shown in \fig{yee cell}. % Ref.
+Similarly to the finite-difference time-domain simulation technique,
+    the use of the Yee cell allows the $\curl$ operators to be well-defined.
 
-\begin{figure}[h]\begin{center}
-\psset{gridcolor=green, subgridcolor=yellow}
-\begin{pspicture}(-2,-2)(7,7)
-    \let\psgrid\relax
-
-    % Origin.
-    \psdot(0,0) \rput[br](-0.1,0.1){$(0,0,0)$}
-
-    % Principle axes.
-    \psline[linestyle=dotted](-1,0)(6,0) \rput(6.3,0){$x$}
-    \psline[linestyle=dotted](0,-1)(0,6) \rput(0,6.3){$z$}
-    \psline[linestyle=dotted](-0.8,-0.6)(4.8,3.6) \rput(5.05,3.75){$y$}
-
-    % Intermediate axes.
-    \psline[linestyle=dotted](0,3)(3,3) % Hy point.
-    \psline[linestyle=dotted](3,3)(3,0)
-
-    \psline[linestyle=dotted](0,3)(2.4,4.8) % Hx point.
-    \psline[linestyle=dotted](2.4,4.8)(2.4,1.8)
-
-    \psline[linestyle=dotted](2.4,1.8)(5.4,1.8) % Hz point.
-    \psline[linestyle=dotted](5.4,1.8)(3,0)
-
-    % E-field vectors.
-    \psline{->}(2.6,0)(3.4,0) \rput(3,-0.4){$E_x$}
-    \psline{->}(0,2.6)(0,3.4) \rput(-0.4,3){$E_z$}
-    \psline{->}(2.1,1.55)(2.7,2.05) \rput(2.05,2.05){$E_z$}
-
-    % H-field vectors.
-    \psline{->}(2,4.8)(2.8,4.8) \rput(2.4,5.2){$H_x$}
-    \psline{->}(5.4,1.4)(5.4,2.2) \rput(5.8,1.8){$H_z$}
-    \psline{->}(2.7,2.75)(3.3,3.25) \rput(2.7,3.3){$H_y$}
-\end{pspicture}
+\begin{figure}[ht]\begin{center}
+    \input{yee-fig.tex}
     \end{center}
-\caption{Primitive Yee cell}
+    \caption{   The primitive Yee cell. 
+                The computational grid is formed by tiling this pattern
+                    in three dimensions such that no two field components
+                    of $E$ or $H$ are co-located. % Ref to Yee.
+                The grid used in \MaxwellFDS has periodic ``wrap-around''
+                    boundary conditions, and 
+                    the relevant distances between adjacent field components
+                    are denoted by $d^\prim_{x,y,z}$ and 
+                    $d^\dual_{x,y,z}$.}
+    \label{fig:yee cell}
 \end{figure}
 
+In this configuration, the $E$, $J$, and $\epsilon$ vector fields
+    are positioned on the $E_{x,y,z}$ locations 
+    while the $H$, $M$ (in the case of \eq{maxwell wave H}) , and $\mu$
+    vector fields are placed on the $H_{x,y,z}$ locations.
+
+To define the distances between adjacent field components,
+    \MaxwellFDS uses the following convention:
+    \BI $d^\prim_{w}$ denotes the distance in the direction $i$
+        between $E_w$ components for $w = x, y, z$, and
+    \I  $d^\dual_{w}$ denotes the distance in the direction $i$
+        between $H_w$ components for $w = x, y, z$. \EI
+This definition allows us to precisely define the numerical derivatives
+    found in the $\curl$ operators.
+
+\subsubsection{Use of a periodic ``wrap-around'' grid}
+\MaxwellFDS features periodic ``wrap-around'' boundary conditions
+    in the definition of the $\curl$ operators in \eq{maxwell wave E}.
+For example, this means that the operation $\pf{x}H_y$ is still well-defined
+    at the $x=0$ boundary as 
+    $(H_y|^{x=0} - H_y|^{x = x_\mx}) / d^\prim_x$.
+
+More specifically, \MaxwellFDS calls the elements 
+    in the Yee cell at $(i,j,k)$ as $E_x(i,j,k)$, $E_y(i,j,k)$, \ldots 
+    and then denotes 
+\BI $d^\prim_x(0)$ as the distance 
+    between $E_x(x_\mx,j,k)$ and $E_x(0,j,k)$,
+\I  $d^\prim_y(0)$ as the distance 
+    between $E_y(i,y_\mx,k)$ and $E_y(i,0,k)$,
+\I  $d^\prim_z(0)$ as the distance 
+    between $E_z(i,j,z_\mx)$ and $E_y(i,j,0)$,
+\I  $d^\dual_x(x_\mx)$ as the distance 
+    between $H_x(x_\mx,j,k)$ and $H_x(0,j,k)$,
+\I  $d^\dual_y(y_\mx)$ as the distance 
+    between $H_y(i,y_\mx,k)$ and $H_y(i,0,k)$, and
+\I  $d^\dual_z(z_\mx)$ as the distance 
+    between $H_z(i,j,z_\mx)$ and $H_y(i,j,0)$. \EI
+
+It should be noted that \MaxwellFDS's strictly periodic grid still
+    allows the use of Bloch periodic, mirror and perfectly-matched layer
+    boundary conditions.
+This is accomplished by setting the $d^{\prim,\dual}$ values to 
+    the appropriate complex values or even $\infty$,
+    both of which \MaxwellFDS is able to understand.
+
+\subsubsection{The wave equation in terms of matrices and vectors}
+With these definitions we now can see how \MaxwellFDS
+    formulates the wave equation in the language of linear algebra.
+Specifically, \MaxwellFDS formulates \eq{maxwell wave E} as
+\E  {maxwell wave E discretized}
+    {(A_1 \diag(\mu^{-1}) A_2 - \omega^2 \diag(\epsilon)) x = b,}
+    where
+    \BI $A_1$ and $A_2$ represent the first and second $\curl$ operators
+        respectively,
+    \I  $x \to E$, and
+    \I  $b \to -i \omega J$. \EI
+
+The vector fields $E$ is converted into vector $x$ as
+\E{}{x = \begin{bmatrix} e_x \\ e_y \\ e_z \end{bmatrix}}
+    where
+\E{}{e_w = \begin{bmatrix} E_w(0,0,0) \\ E_w(1,0,0) \\
+                        \vdots \\ E_w(x_\mx, y_\mx, z_\mx) \end{bmatrix},}
+and so on for all vector fields.
+
 \end{document}

### 2012-08-15 thesis.tex
Closer to finishing MaxwellFDS white paper.

@@
 \subsubsection{Input: clean excitation of modes}
+A clean input excitation is typically quite complex to set up
+    in a time-domain simulation,
+    often requiring an auxiliary simulation to be run in parallel.
+The finite bandwidth of the excitation makes the calculation
+    of the mode profile problematic, while
+    the need to suppress transients requires the use of 
+    long ``build-up'' excitations.
+These difficulties are illustrated in \fig{time domain diagram}
+    where the inputs at the various frequencies of interest
+    must be combined and converted into the time-domain.
+
+However, in a frequency-domain simulation, 
+    since $\omega$ is explicitly defined and has no bandwidth,
+    one can accurately compute the correct input mode.
+Additionally, since one does not need to deal with transient excitations,
+    the input mode can be inserted directly into the simulation
+    without skilled ``tweaking'' on the part of the user,
+    as illustrated in \fig{frequency domain diagram}
+    where each frequency of interest is given it's own simulation.
+
+\begin{figure}[ht]\begin{center}
+\input{tds-fig.tex}
+\caption{The difficulties of working in the time-domain.
+        On the input side, the various input modes must be
+            combined and converted to the time-domain.
+        At the same time, the output measures of performance 
+            must be extracted from the time-domain output
+            while the simulation is still running.}
+\label{fig:time domain diagram}
+\end{center} \end{figure}
+
+\begin{figure}[ht]\begin{center}
+\input{fds-fig.tex}
+\caption{Using a frequency domain solver,
+            the various input modes and output measures
+            are computed independently of one another,
+            greatly simplifying the user's workflow.}
+\label{fig:frequency domain diagram}
+\end{center} \end{figure}
+
 \subsubsection{Dispersion: precise characterization of frequency-dispersion}
+In a similar vein, the explicitness of $\omega$ means that
+    parameters which depend upon frequency can be accurately simulated
+    by simply supplying the correct value of the parameter at the 
+    chosen frequency.
+
+This is in contrast to time-domain solutions,
+    which rely on running integrals to approximate such behavior.
+
 \subsubsection{Output: complete description of device performance}
+An additional advantage to frequency-domain solutions
+    is that all the information concerning the solution
+    is contained in the output field.
+This means that the calculation of figures of merit and 
+    any possible measure of performance happens only
+    after the solver has completed, 
+    as shown in \fig{frequency domain diagram}.
+
+This is in contrast to time-domain simulations,
+    where such calculations must occur as the simulation proceeds, 
+    as shown in \fig{time domain diagram},
+    since the entire field at every point in time cannot be stored in memory.
+
 \subsubsection{Error: explicit measurement of simulation error}
+Yet another advantage of frequency-domain solutions is the ability
+    to explicitly calculate the error in the solution fields,
+    which is impossible to do with time-domain simulations.
+
 \subsubsection{Eigenmodes: explicit calculation of eigenmodes}
+Explicitly calculating the error also allows one 
+    to explicitly calculate eigenmode solutions
+    using frequency-domain solvers.
+This is particularly useful when one is attempting to
+    discriminate between closely spaced modes,
+    which is very difficult using time-domain approaches.
 
 \subsection{The advantages of simulating in the cloud}
+The primary usefulness of the cloud in a simulation context
+    is that it allows one to save both money and time.
+
+\subsubsection{Cloud computing allows for ``free'' parallelism}
+The most fundamental difference in running simulations
+    in a cloud computing environment is its cost structure.
+Specifically, in the cloud, 
+    one is billed based on the amount of computational resources used
+    and the time which one uses those resources.
+In contrast, the cost of simulating on one's own hardware
+    depends most heavily on the amount of hardware needed,
+    at least in most scientific environments.
+
+The disruptive cost structure of cloud environments 
+    has profound effects on scientific workloads 
+    as illustrated in \fig{cloud vs traditional};
+    in essence, allowing scientific workloads access
+    to ``free'' parallelism.
+The parallelism is free in the sense that 
+    the cost of running $N$ jobs sequentially on $1$ computer is equivalent to 
+    the cost of running $N$ jobs in parallel on $N$ computers.
+
+\begin{figure}[ht]\begin{center}
+\input{cloud-fig.tex}
+\caption{The fundamental difference in going to the cloud
+            is that both sequential and parallel workloads
+            cost the same amount of money,
+            since one is billed based on time $\times$ resources.
+        In contrast, simulating on one's own hardware would 
+            mean that parallel workloads are much more expensive
+            since one is billed on resources alone.
+        In essence, therefore, cloud computing allows for 
+            parallelism at no cost.}
+\label{fig:cloud vs traditional}
+\end{center} \end{figure}
+
+\subsubsection{Cloud computing takes care of all messy hardware details}
+A secondary benefit in using cloud computing 
+    is that many details no longer need to be handled such as
+    \BI physically installing, maintaining, and fixing computational hardware,
+    \I  ensuring identical software configurations on every cluster node, and 
+    \I  installing and configuring the cluster networking. \EI
+
+Of course, these conveniences come at the expense of 
+    being able to customize hardware, and networking resources
+    to ideally suit an application's needs.
+However, considering that most scientific folk
+    are not experts in these issues,
+    this can be considered a very small disadvantage.
+
 \subsection{The advantages of being built within Matlab}
+\MaxwellFDS was designed to not only be scalable (in the cloud),
+    but accessible as well.
+For this reason, we have allowed
 
-\section{Harnessing the cloud to understand light}
+\section{Harnessing Amazon's Elastic Compute Cloud} 
 \subsection{Accessing }

### 2012-08-16 thesis.tex
Some updates.

@@
     tailored specifically to the field of nanophotonics.
-\MaxwellFDS stands for Frequency-Domain Solver.
+\MaxwellFDS stands for Frequency-Domain Solver
+    and delivers frequency-domain solutions to the electromagnetic wave equation
+    directly to the Matlab programming environment,
+    and does so in a scalable manner by harnessing the power
+    of the Amazon Elastic Compute Cloud.
+
+In this whitepaper, the core \MaxwellFDS solver is introduced.
 
@@
 \subsection{The advantages of simulating in the cloud}
-The primary usefulness of the cloud in a simulation context
-    is that it allows one to save both money and time.
+Although running scientific workloads in public cloud environments
+    has not yet become the de facto standard,
+    doing so provides many significant advantages.
 
@@
 \subsection{The advantages of being built within Matlab}
-\MaxwellFDS was designed to not only be scalable (in the cloud),
-    but accessible as well.
-For this reason, we have allowed
+The primary advantage of building \MaxwellFDS within Matlab is accessibility.
+
+Often simulation packages are run as stand-alone programs
+    which are controlled either by custom user interfaces
+    or custom input and output file formats.
+The result of this approach, however, is 
+    \BI a steep learning curve for the user,
+    \I  the need to create ``connection'' software
+            in order to link the simulation package with
+            the other packages or environments the user needs, and  
+    \I  increased unreliablility, since the simulation software
+            is inevitably less ``bullet-proof'' than standard
+            platforms such as Matlab. \EI
+
+For these reasons, the core solver of \MaxwellFDS is built
+    \BI to resemble a simple Matlab command,
+    \I  never requires the user to leave the Matlab environment
+            (assuming the user has a valid Amazon Web Services ID). \EI
+
+\MaxwellFDS was built with extreme simplicity in mind,
+    so much so that its core solver is even contained in a single Matlab file,
 

### 2012-08-16 thesis.tex
small

@@
 \section{Harnessing Amazon's Elastic Compute Cloud} 
-\subsection{Accessing }
+In this section, we give an overview of how \MaxwellFDS utilizes
+    the Amazon Elastic Compute Cloud service to 
+    provide nearly unlimited scalability when running electromagnetic simulations.
+
+\subsection{Reserving instances}
+\subsection{Use of spot instances}
+Talk about pricing and how one can be kicked off.
+
+\subsection{Web console for manual monitoring/shutdown}
 

### 2012-08-17 plan/plan.tex
Started on the plan!

\documentclass{book}
\usepackage{amsmath}
% \usepackage{hyperref}

\input ../defs.tex
\newcommand{\T}{^\dagger}
\newcommand{\reals}{{\mbox{\bf R}}}
\newcommand{\comps}{{\mbox{\bf C}}}

\title{Objective-First Nanophotonic Design Plan} 
\author{Jesse Lu}
\begin{document}
\maketitle
\tableofcontents

\chapter{Introduction}
\section{Problem statement}
Our goal is to create a software package 
    to enable the design of nanophotonic devices.
Presently, almost all nanophotonic devices are designed
    by guessing what a good design might look like,
    based on intuition and experience,
    and then optimizing it by trial-and-error.
In contrast, we want to enable the \emph{inverse design}
    of nanophotonic devices;
    that is, to design devices by simply describing the 
    desired performance that it must achieve.

To put things mathematically, we want to create software 
    to solve the following problem,
    \EE {the plan (single mode)}
        {\minimize&  f(x) + g(z) \\
        \subto&     A(z)x - b(z) = 0}
    where 
    \BI $x$ and $z$ are the variables representing 
            the field device our device produces and
            the structure of the device respectively,
    \I  $f(x)$ and $g(z)$ are our \emph{design objectives},
            which tell us the desirable properties 
            that we would like our device to achieve, and
    \I  $A(z)x - b(z)$ is the \emph{physics residual},
            the underlying physical laws which must be met. \EI

In general, we need to consider multiple fields produced 
    by the device.
Our problem statement is then
    \EE {the plan (multi-mode)}
        {\minimize&  \sum_i^N f_i(x_i) + g(z) \\
        \subto&     A_i(z)x_i - b_i(z) = 0,\quad\text{for $i = 1, \ldots, N.$}}

\section{Capabilities of our software}
We have implemented various 
    \emph{optimization paradigms} and \emph{structure parameterizations}
    which a user can arbitrarily combine in order to 
    design nanophotonic devices.

Specifically, the user can choose to work in either
    a \emph{local} or \emph{global} optimization paradigm:
    \BI the local paradigm uses the adjoint method
            to find small changes in the structure which
            will decrease the design objective;
    \I  the global paradigm uses the objective-first method
            to arrive at a structure by forcing
            the design objective to be met from the start. \EI

And the user can also choose between the various structure parameterizations 
    which include density, boundary, 
    continuous, and combinatoric parameterizations.
These parameterizations describe the structure as either
    \BI a material density at every point in space;
    \I  a boundary between objects of different materials;
    \I  a set of continuously variable user-defined parameters; or 
    \I  a combination of user-defined objects. \EI

\chapter{Theory}
\section{Mathematically rigorous statement of the problem}
As previously stated, the problem we want to solve is 
    \EE {rigorous problem statement}
        {\minimize&  \sum_i^N f_i(x_i) + g(z) \\
        \subto&     A_i(z)x_i - b_i(z) = 0,\quad\text{for $i = 1, \ldots, N.$}}
To now be more precise,
    \BI $x_i \in \comps^m$ are the field variables,
    \I  $z \in \reals^n$ is the structure variable,
    \I  $f_i(x_i) \in \comps^m \to \reals$ are the field design objectives,
    \I  $g(z) \in \reals^n \to \reals$ is the structure design objective,
    \I  $A_i(z)x_i - b_i(z)$ are the physics residuals, with
    \I  $A_i(z) \in \comps^{m \times m}$ and
    \I  $b_i(z) \in \comps^m$. \EI

\subsection{Definition of physics residual}
The physics residual corresponds to the electromagnetic wave equation
    \E  {wave equation in E}
        {(\curl \mu^{-1} \curl - \omega^2 \epsilon) E = -i \omega J}
    which is described as $A_i(z)x_i - b_i(z)$ via
    \BI $\curl \mu^{-1} \curl - \omega^2 \epsilon \to A_i(z)$,
    \I  $\epsilon \in z$,
    \I  $E \to x_i$, and
    \I  $-i \omega J \to b_i(z)$. \EI

\subsection{Bi-affine property of the physics residual}
Critically, \eq{wave equation in E} is not only linear in $E$,
    but is also affine in $\epsilon$.
This allows us to form the following relationship,
    \E  {bi-affine}
        {A_i(z)x_i - b_i(z) = B(x_i)z - d(x_i) = 0,}
    which will prove to be very useful.

\subsection{Definition of the field design objective}
Although $f_i(x_i)$ can take on virtually any form,
    we choose to define it very specifically as
    \E  {field design objective definition}
        {f_i(x_i) = \sum_j I_+(|c_{ij}\T x_i| - \alpha_{ij})
            + I_+(\beta_{ij} - |c_{ij}\T x_i|),}
    where $c_{ij} \in \comps^m$ and 
    $I_+$ is the indicator function on nonnegative reals,
    \E{}{I_+(u) = \begin{cases} 0 & u \ge 0, \\ 
                                \infty & u < 0. \end{cases}}

Such a design objective implements the constraints 
    $\alpha_{ij} \le |c_{ij}\T x_i| \le \beta_{ij}$
    which can be interpreted physically as 
    constraining the power emitted into the optical modes
    represented by $c_{ij}$.

\subsection{Choice of the structure design objective}
In contrast to the narrow definition of the field design objective,
    the structure design objective is relatively unconstrained;
    taking on various forms to best suit the needs of
    the structure parameterization in use.

\section{Properties of the problem}
\subsection{nonconvexity}
\subsection{optimality condition}

\section{General strategy to solve the problem}
\subsection{Field update}
Give the \emph{specific} interfaces here. 
What exactly gets input and what does each update output?
\subsection{Structure update}

\end{document}

### 2012-08-29 plan/plan.tex
Updated plan.

@@
 
-\section{Capabilities of our software}
+\section{Capabilities of our software}\label{capabilities of our software}
 We have implemented various 
@@
     \BI $\curl \mu^{-1} \curl - \omega^2 \epsilon \to A_i(z)$,
-    \I  $\epsilon \in z$,
+    \I  $\epsilon \to z$,
     \I  $E \to x_i$, and
@@
 This allows us to form the following relationship,
-    \E  {bi-affine}
+    \E  {bi-affine property}
         {A_i(z)x_i - b_i(z) = B(x_i)z - d(x_i) = 0,}
@@
 \section{Properties of the problem}
-\subsection{nonconvexity}
+We now examine the general mathematical properties 
+    of the stated problem \eq{rigorous problem statement}.
+
+\subsection{Convexity analysis}
+% \subsubsection{Joint non-convexity}
+First we note that, as presented, 
+    \eq{rigorous problem statement} is non-convex 
+    in the variables $x_i$ and $z$. % Ref boyd book
+Not only are the physics residuals $A_i(z)x_i - b_i(z)$ non-convex,
+    but the field design objective, in that it implements the 
+    $ \alpha_{ij} \le |c_{ij}\T x_i| $ constraint, is non-convex as well.
+
+That our problem is non-convex means that it is fundamentally hard to solve
+    because of the existence of multiple local minima.
+Additionally, even if we were to arrive at the global maxima,
+    we would not have a straightforward way to verify global optimality.
+Lastly, fast convergence even to local minima may be difficult
+    because methods such as Newton's method
+    can not be directly applied to non-convex problems.
+
+% \subsubsection{Separable convexity}
+That said, \eq{rigorous problem statement} is \emph{separably convex} 
+    in $x_i$ and $z$ if we ignore the non-convexity
+    in the field design objectives, $f_i(x_i)$, and
+    assume that the structure design objective, $g(z)$, is convex as well.
+This is given because of the bi-affine property
+    of the physics residual, as shown in \eq{bi-affine property}.
+
+The separably convex, or \emph{bi-convex}, properties of our problem
+    open the door for the use of alternating direction algorithms,
+    and specifically the alternating directions 
+    methods of multipliers (ADMM), % Ref. 
+    for the implementation of a global optimization paradigm,
+    as referred to in section \ref{capabilities of our software}.
+Of course, in this context we do not use the term ``global'' rigorously,
+    but only to differentiate it from strategies that rely
+    purely on local information.
+
+Lastly, since our problem is not bi-convex 
+    in the case of non-convex field or structure design objectives,
+    simple extensions to alternating direction algorithms are employed.
+
 \subsection{optimality condition}

### 2012-08-29 fds/fds.tex
Started on the plan!

--- 2012-08-16 thesis.tex
@@
 \usepackage{amsmath}
-\newcommand{\E}[2]{\begin{align}#2\label{eq:#1}\end{align}}
-\newcommand{\EE}[2]{\begin{subequations}\begin{align}#2\end{align}\label{eq:#1}\end{subequations}}
-\newcommand{\curl}{\nabla\times}
-\newcommand{\eq}[1]{\eqref{eq:#1}}
-\newcommand{\fig}[1]{figure~\ref{fig:#1}}
+\input ../defs.tex
 \newcommand{\MaxwellFDS}{MaxwellFDS }
-\newcommand{\BI}{\begin{itemize}\item}
-\newcommand{\EI}{\end{itemize}}
-\newcommand{\I}{\item}
 \newcommand{\pf}[1]{\frac{\partial}{\partial #1}} % d/d_
@@
     \I  calculation of figure of merits outside of the simulation,
+    \I  using a variable-resolution rectangular grid,
     \I  explicit measurement of simulation error, and
@@
     since the entire field at every point in time cannot be stored in memory.
+
+\subsubsection{Grid: efficient, variable-resolution rectangular grid}
+Frequency-domain simulations allow for efficient variable-resolution
+    rectangular grids which are not possible using time-domain simulations.
+
+In time-domain simulations, changing the grid size imposes a large 
+    computational penalty in that the time step of the entire simulation
+    must be reduced in order to satisfy the Courant condition at the
+    point of highest resolution.
+In contrast, a frequency-domain simulation does not even need
+    to consider the idea of a time-step, and 
+    so is free from this constraint.
 
@@
 
-\subsection{Reserving instances}
+\subsection{Instance type used}
+\MaxwellFDS builds a cluster
+    using Amazon's cluster GPU instances (\texttt{cg1.4xlarge}),
+    which each contain two M2050 Nvidia Tesla GPUs.
+Therefore, an $N$-node \MaxwellFDS cluster will contain $2N$ GPUs.
+
+\MaxwellFDS is built on Nvidia Tesla technology in order 
+    to take care of the immense processing power available
+    for parallelizable problems.
+
+Additionally, all of a cluster's instances are launched
+    in a single placement group, % Ref!
+    which allows for faster communication between nodes.
+
 \subsection{Use of spot instances}
-Talk about pricing and how one can be kicked off.
+Because scientific workloads are almost always of a batch nature
+    (e.g. many simulations run at once),
+    \MaxwellFDS takes advantage of Amazone EC2 spot instances
+    in order to drastically lower the cost of using \MaxwellFDS.
+Spot instances cost much less than reserved instances,
+    and can typically be requested in much larger numbers.
+
+To request a spot instance, one must submit a bid price
+    for the desired instance.
+Amazon will then allocate the desired instance for the user
+    as long as the bid price is above the market price.
+If the market price exceeds the bid price,
+    the instance will be shut down and the user will no longer be billed.
+
+Although large fluctuations in market price are not common,
+    \MaxwellFDS uses a large bid price (currently 2 USD) close to the
+    reserved instance price for \texttt{cg1.4xlarge} 
+    in order to ensure that nearly all spot instance bids will be successful.
 
 \subsection{Web console for manual monitoring/shutdown}
+Of course, there is no need to trust what \MaxwellFDS is doing behind the scenes
+    because Amazon provides a web console for monitoring and 
+    manually controlling all instances reserved and in use by the user.
+
+The web console for ec2 can be accessed from \texttt{console.aws.amazon.com}.
+Of particular interest will be ``spot instance requests'' and ``instances''.
 
@@
 
+\subsubsection{Mathematical definition of simulation error}
+From \eq{maxwell wave E discretized} we derive the mathematical expression for 
+    the simulation error which is simply    
+    \E  {maxwell error}
+        {\text{error} = \|Ax-b\|_2 / \|b\|_2,}
+    where $A = A_1 \diag(\mu^{-1}) A_2 - \omega^2 \diag(\epsilon)$.
+
 \end{document}

### 2012-09-21 plan/plan.tex
Added figure.

@@
 % \usepackage{hyperref}
+\usepackage{pstricks}
 
@@
     but is also affine in $\epsilon$.
-This allows us to form the following relationship,
+This allows us to form the extremely useful relationship,
     \E  {bi-affine property}
         {A_i(z)x_i - b_i(z) = B(x_i)z - d(x_i) = 0,}
-    which will prove to be very useful.
+    where $B(x_i) \in \comps^{n \times n}$ and $d(x_i) \in \comps^n$.
 
@@
 
-\subsection{optimality condition}
+\subsection{Optimality condition}
+Based on the problem definition in \eq{rigorous problem statement},
+    we can write down a set of equations that, when met,
+    signal that we have arrived at a locally optimal point.
+Otherwise known as the Karush-Kuhn-Tucker (KKT) conditions, % Ref boyd
+    these are, for \eq{rigorous problem statement},
+    \EE {KKT conditions} % Check how these work out for complex values!!!
+        {|c_{ij}\T x_i| - \beta_{ij} &\le 0, \\
+        \alpha_{ij} - |c_{ij}\T x_i| &\le 0, \\
+        A_i(z)x_i - b_i(z) &= 0, \\
+%         % Lambda dual variables not needed because they do not appear 
+%         % in the last KKT condition.
+%         \lambda_{\alpha ij} &\ge 0, \\ 
+%         \lambda_{\beta ij} &\ge 0, \\
+%         \lambda_{\alpha ij}(|c_{ij}\T x_i| - \beta_{ij}) &= 0, \\
+%         \lambda_{\beta ij}(\alpha_{ij} - |c_{ij}\T x_i|) &= 0, \\
+        \nabla_z g(z) + \sum_i B(x_i)\T \nu_i &= 0,
+        }
+    where $\nu_i \in \comps^n$ are dual variables.
 
 \section{General strategy to solve the problem}
+
+\begin{pspicture}(6,5)(-6,-2)
+\psset{gridcolor=green, subgridcolor=yellow}
+    \let\psgrid\relax
+
+    % Paradigm
+    \rput(0,4.3){optimization paradigm}
+    \psline(-2.2,4)(2.2,4) % top
+    \psline(-2.2,4)(-2.2,2) % left
+    \psline(2.2,4)(2.2,2) % right
+    \psline(-2.2,2)(-1,2)
+    \psline(2.2,2)(1,2)
+    \psline(-1,2.2)(1,2.2)
+    \psline(-1,2)(-1,2.2)
+    \psline(1,2)(1,2.2)
+
+    % Parameterization
+    \psframe(-.8,0.8)(.8,-0.4) 
+    \rput(0,-0.7){\parbox{5cm}{\center structure\\ parameterization}}
+
+    % Arrows
+    \rput[r](-1.9,0.8){into sp}
+    \psline(-1.6,1.8)(-1.6,0.2)
+    \psline{->}(-1.6,0.2)(-1,0.2)
+
+    \rput[l](1.9,0.8){out of sp}
+    \psline(1.6,0.2)(1,0.2)
+    \psline{<-}(1.6,1.8)(1.6,0.2)
+
+    \rput[r](-4.3,3){initial input}
+    \psline{->}(-4,3)(-2.4,3)
+
+    \rput[l](4.3,3){output}
+    \psline{<-}(4,3)(2.4,3)
+\end{pspicture}
+
 \subsection{Field update}

### 2012-09-21 plan/plan.tex
Added caption to figure.

@@
     \BI $x$ and $z$ are the variables representing 
-            the field device our device produces and
-            the structure of the device respectively,
+            the \emph{field} our device produces and
+            the \emph{structure} of the device respectively,
     \I  $f(x)$ and $g(z)$ are our \emph{design objectives},
@@
     which a user can arbitrarily combine in order to 
-    design nanophotonic devices.
+    to solve \eq{the plan (multi-mode)}.
 
@@
 
-And the user can also choose between the various structure parameterizations 
+Also, the user can choose between the various structure parameterizations 
     which include density, boundary, 
@@
     \I  a set of continuously variable user-defined parameters; or 
-    \I  a combination of user-defined objects. \EI
+    \I  a selective combination of user-defined objects. \EI
 
@@
 \subsection{Definition of the field design objective}
-Although $f_i(x_i)$ can take on virtually any form,
+Although the field design objective $f_i(x_i)$ 
+    can take on virtually any form,
     we choose to define it very specifically as
@@
 
+\begin{figure}[ht]\begin{center}
 \begin{pspicture}(6,5)(-6,-2)
@@
     \psframe(-.8,0.8)(.8,-0.4) 
-    \rput(0,-0.7){\parbox{5cm}{\center structure\\ parameterization}}
+    \rput[t](0,-0.6){\parbox{3cm}{\center structure\\ parameterization}}
 
     % Arrows
-    \rput[r](-1.9,0.8){into sp}
+    \rput[r](-4.3,3){$z_\text{guess}$}
+    \psline{->}(-4,3)(-2.4,3)
+
+    \rput[r](-1.9,0.8){$Q(z)$}
     \psline(-1.6,1.8)(-1.6,0.2)
@@
 
-    \rput[l](1.9,0.8){out of sp}
+    \rput[l](1.9,0.8){$\text{argmin}\, Q(z) + g(z)$}
     \psline(1.6,0.2)(1,0.2)
@@
 
-    \rput[r](-4.3,3){initial input}
-    \psline{->}(-4,3)(-2.4,3)
-
-    \rput[l](4.3,3){output}
+    \rput[l](4.3,3){$z_\text{final}$}
     \psline{<-}(4,3)(2.4,3)
 \end{pspicture}
+\caption{Basic layout of our software.
+        At the most basic level, the chosen optimization paradigm 
+            accepts an initial structure $z_\text{guess}$
+            and returns a final, optimized structure $z_\text{final}$.
+        This is accomplished by repeatedly passing quadratic functions $Q(z)$ 
+            to the structure parameterization,
+            which returns an updated structure $z$
+            which minimizes $Q(z) + g(z)$.}
+\label{fig:strategy}
+\end{center} \end{figure}
 

### 2012-11-22 plan/plan.tex
Got the plan going, covered adjoint method.

@@
     to enable the design of nanophotonic devices.
-Presently, almost all nanophotonic devices are designed
-    by guessing what a good design might look like,
-    based on intuition and experience,
-    and then optimizing it by trial-and-error.
-In contrast, we want to enable the \emph{inverse design}
-    of nanophotonic devices;
-    that is, to design devices by simply describing the 
-    desired performance that it must achieve.
+Specifically, our software produces designs for
+    \emph{linear} nanophotonics devices based on
+    \emph{desired coupling strengths} between various optical ports.
+
+% Presently, almost all nanophotonic devices are designed
+%     by guessing what a good design might look like,
+%     based on intuition and experience,
+%     and then optimizing it by trial-and-error.
+% In contrast, we want to enable the \emph{inverse design}
+%     of nanophotonic devices;
+%     that is, to design devices by simply describing the 
+%     desired performance that it must achieve.
 
@@
 
-\section{Capabilities of our software}\label{capabilities of our software}
-We have implemented various 
-    \emph{optimization paradigms} and \emph{structure parameterizations}
-    which a user can arbitrarily combine in order to 
-    to solve \eq{the plan (multi-mode)}.
+\section{Structure of our software}
+In reality, our software package consists of various modules
+    which are designed to be maximally orthogonal.
+The various modules are illustrated in \fig{structure}.
 
-Specifically, the user can choose to work in either
-    a \emph{local} or \emph{global} optimization paradigm:
-    \BI the local paradigm uses the adjoint method
-            to find small changes in the structure which
-            will decrease the design objective;
-    \I  the global paradigm uses the objective-first method
-            to arrive at a structure by forcing
-            the design objective to be met from the start. \EI
+\begin{figure}[ht]\begin{center}
+\begin{pspicture}(6,2.4)(-6,-2)
+\psset{gridcolor=green, subgridcolor=yellow}
+    \let\psgrid\relax
 
-Also, the user can choose between the various structure parameterizations 
-    which include density, boundary, 
-    continuous, and combinatoric parameterizations.
-These parameterizations describe the structure as either
-    \BI a material density at every point in space;
-    \I  a boundary between objects of different materials;
-    \I  a set of continuously variable user-defined parameters; or 
-    \I  a selective combination of user-defined objects. \EI
+    \rput[t](-1.5,1){physics}
+    \psframe(-0.2,0.4)(-2.8,1.4)
+
+    \rput[t](1.5,1){simulation}
+    \psframe(0.2,0.4)(2.8,1.4)
+
+    \psline[linestyle=dashed](-3.2,0.2)(3.2,0.2)
+    \rput[l](3.2,0.2){\parbox{3cm}{\center physics-to-algebra \\ translation layer}}
+    \rput[t](0,-0.4){optimization}
+    \psframe(-1.3,-1)(1.3,0)
+\end{pspicture}
+\caption{Structure of our software. 
+    The physics and simulation modules provide a complete description of the problem.
+    The translation module takes this description and casts it in the language of linear algebra,
+        which the optimization module can then use to produce various designs.}
+\label{fig:structure}
+\end{center} \end{figure}
+
+Although all modules are provided by our software, 
+    the majority of the innovation lies in the optimization module.
+Since the optimization module works entirely in the realm of linear algebra,
+    a translation module is provided in order to cast concepts from electromagnetics into this form.
+Finally, physics and simulation modules are provided 
+    to allow the user to describe the design problem in physical, rather than mathematical terms.
 
@@
 \subsection{Definition of physics residual}
-The physics residual corresponds to the electromagnetic wave equation
+The physics residual, $A_i(z)x_i - b_i(z)$, 
+    corresponds to the electromagnetic wave equation
     \E  {wave equation in E}
         {(\curl \mu^{-1} \curl - \omega^2 \epsilon) E = -i \omega J}
-    which is described as $A_i(z)x_i - b_i(z)$ via
-    \BI $\curl \mu^{-1} \curl - \omega^2 \epsilon \to A_i(z)$,
-    \I  $\epsilon \to z$,
+        via
+    \BI $\curl \mu^{-1} \curl - \omega^2 \epsilon \to A_i(z)$, where $\epsilon$ is a function of $z$,
     \I  $E \to x_i$, and
-    \I  $-i \omega J \to b_i(z)$. \EI
+    \I  $-i \omega J \to b_i(z)$, typically constant with respect to $z$. \EI
 
@@
     \E  {bi-affine property}
-        {A_i(z)x_i - b_i(z) = B(x_i)z - d(x_i) = 0,}
+        {A_i(z)x_i - b_i(z) = B_i(x_i)z - d_i(x_i) = 0,}
     where $B(x_i) \in \comps^{n \times n}$ and $d(x_i) \in \comps^n$.
+   % TODO: Show what B_i and d_i are explicitly.
 
@@
 
-\section{General strategy to solve the problem}
+\chapter{The optimization module}
+
+\section{Capabilities of the module}\label{capabilities of our software}
+We have implemented various 
+    \emph{optimization paradigms} and \emph{structure parameterizations}
+    which a user can arbitrarily combine in order to 
+    to solve \eq{the plan (multi-mode)}.
+
+Specifically, the user can choose to work in either
+    a \emph{local} or \emph{global} optimization paradigm:
+    \BI the local paradigm uses the adjoint method
+            to find small changes in the structure which
+            will decrease the design objective;
+    \I  the global paradigm uses the objective-first method
+            to arrive at a structure by forcing
+            the design objective to be met from the start. \EI
+
+Also, the user can choose between the various structure parameterizations 
+    which include density, boundary, 
+    continuous, and combinatoric parameterizations.
+These parameterizations describe the structure as either
+    \BI a material density at every point in space;
+    \I  a boundary between objects of different materials;
+    \I  a set of continuously variable user-defined parameters; or 
+    \I  a selective combination of user-defined objects. \EI
+
+\section{Structure of the module}
+
+The module is naturally separated into two submodules, 
+    the optimization paradigm (or simply, paradigm) submodule 
+    and the structure parameterization (or simply, structure) submodule.
+The interaction between these two submodules is illustrated in \fig{strategy}.
 
@@
 \end{pspicture}
-\caption{Basic layout of our software.
-        At the most basic level, the chosen optimization paradigm 
+\caption{Basic layout of the module.
+        The optimization paradigm submodule
             accepts an initial structure $z_\text{guess}$
@@
         This is accomplished by repeatedly passing quadratic functions $Q(z)$ 
-            to the structure parameterization,
+            to the structure parameterization module,
             which returns an updated structure $z$
@@
 
-\subsection{Field update}
-Give the \emph{specific} interfaces here. 
-What exactly gets input and what does each update output?
-\subsection{Structure update}
+In essense, a design is achieved via repeated calls to the structure submodule
+    by the paradigm submodule,
+    in which carefully chosen quadratic functions $Q(z)$ are minimized.
+
+\section{The paradigm submodule}
+\subsection{The local optimization paradigm}
+The local optimization paradigm applies the adjoint method to solve \eq{rigorous problem statement}
+    in a manner analogous to the steepest-descent strategy.
+Specifically, we compute the derivative of the total field design objective with respect to $z$,
+    \E{total derivative of field design objective}
+        {\grad_z F = \sum_i^N \grad_z f_i(x_i),}
+    and then pass 
+    \E{}{Q(z) = \frac{1}{2}\norm{z-z_0}^2 + \kappa \grad_z F\cT (z-z_0)}
+    to the structure submodule, for some $\kappa$.
+
+The analogy with a steepest-descent strategy is apparent since 
+    the global minimum of $Q(z)$ can be found via
+    \E{}{\grad_z Q(z) = (z - z_0) + \kappa \grad F = 0,}
+    resulting in 
+    \E{}{z = z_0 - \kappa \grad_z F,}
+    from which we see that the role of $\kappa$ is to determine the step-size 
+    in the direction of steepest-descent.
+
+\subsubsection{Computation of $\grad_z F$}
+The derivatives of the individual field design objectives are found via
+    \E{}{\frac{d}{dz} f_i(x_i) = \frac{\pd f_i}{\pd x_i} \frac{dx_i}{dz}.}
+To obtain ${dx_i}/{dz}$ we first differentiate the corresponding physics residual, 
+    $A_i(z) x_i - b_i(z)$,
+    \E{}{A_i(z) dx_i + dA_i(z) - db_i(z) = A_i(z)dx_i + B_i(x_i)dz,}
+    where $dA_i(z) - db_i(z) = B_i(x_i)dz$ 
+    as a result of the bi-affine property of the physics residual \eq{bi-affine property}.
+
+Assuming that physics is already satisfied, $A_i(z) x_i - b_i(z) = 0$,
+    and that we want to keep the physics residual at 0,
+    the following condition must then be satisfied,
+    \E{}{A_i(z) dx_i = -B_i(x_i) dz}
+    from which we obtain
+    \E{}{\frac{dx}{dz} = -A_i(z)^{-1} B_i(x_i).}
+
+Efficient calculation of $dx/dz$ is almost always impossible since $B_i(x_i) \in \comps^{n \times n}$.
+At the same time, since ${\pd f_i}/{\pd x_i} \in \comps^{1 \times m}$, we instead compute $df_i(x_i)/dz$ via
+    \E{}{\frac{d}{dz} f_i(x_i) = -\frac{\pd f_i}{\pd x_i} A_i(z)^{-1} B_i(x_i) = 
+        -\left(A_i(z)^\cT \frac{\pd f_i}{\pd x_i}^\cT\right)^\cT B_i(x_i)}
+    which requires only one solve of $A_i^\cT$ as opposed to $n$ solves of $A_i$.
+
+\subsubsection{Computation of $\pd f_i(x_i) / \pd x_i$}
+The definition of $f_i(x_i)$ as given in \eq{field design objective definition} is not differentiable 
+    since any deviation away from the power constraints results in $f_i = \infty$.
+In order to make the constraints differentiable, then, 
+    we use the following relaxed indicator function $I^\text{rel}_+$ in place of $I_+$,
+    \E{}{I^\text{rel}_+(u) = \begin{cases} 0 & u \ge 0, \\ 
+                                \frac{1}{a}|u|^p & u < 0, \end{cases}}
+    where $a$ is a normalization factor and $p \in (0, \infty]$. 
+In order to guarantee a well-defined value of $\pd f_i(x_i) / \pd x_i$ even for $p = \infty$,
+    we can let $a = \max_i f_i(x_i)$.
+
+\subsection{The global optimization paradigm}
+
+\section{The structure submodule}
 

### 2012-11-23 plan/plan.tex
Started on global optimization submodule.

@@
 \input ../defs.tex
-\newcommand{\T}{^\dagger}
-\newcommand{\reals}{{\mbox{\bf R}}}
-\newcommand{\comps}{{\mbox{\bf C}}}
 
@@
 \section{Structure of our software}
-In reality, our software package consists of various modules
+Our software package consists of various modules
     which are designed to be maximally orthogonal.
@@
 To now be more precise,
-    \BI $x_i \in \comps^m$ are the field variables,
+    \BI $x_i \in \comps^n$ are the field variables,
     \I  $z \in \reals^n$ is the structure variable,
-    \I  $f_i(x_i) \in \comps^m \to \reals$ are the field design objectives,
+    \I  $f_i(x_i) \in \comps^n \to \reals$ are the field design objectives,
     \I  $g(z) \in \reals^n \to \reals$ is the structure design objective,
     \I  $A_i(z)x_i - b_i(z)$ are the physics residuals, with
-    \I  $A_i(z) \in \comps^{m \times m}$ and
-    \I  $b_i(z) \in \comps^m$. \EI
+    \I  $A_i(z) \in \comps^{n \times n}$ and
+    \I  $b_i(z) \in \comps^n$. \EI
 
@@
         {A_i(z)x_i - b_i(z) = B_i(x_i)z - d_i(x_i) = 0,}
-    where $B(x_i) \in \comps^{n \times n}$ and $d(x_i) \in \comps^n$.
-   % TODO: Show what B_i and d_i are explicitly.
+    where $B(x_i) \in \comps^{n \times n}$, $d(x_i) \in \comps^n$ and
+    \BI $-\omega^2 E \to B_i(x_i)$, 
+    \I  $\curl \mu^{-1} \curl E \to d_i(x_i)$. \EI
 
@@
 \subsection{The global optimization paradigm}
+In contrast to the local paradigm, 
+    the global optimization paradigm utilizes an objective-first strategy
+    in the design process.
+Although such a strategy is not technically global,
+    it is differentiated from local strategies because
+    it strictly enforces all design objectives,
+    even at the expense of non-zero physics residuals.
+
+The optimization paradigm utilizes 
+    the alternating directions method of multipliers\cite{ADMM} (ADMM) optimization technique, 
+    which casts \eq{rigorous problem statement} in terms of the following augmented Lagrangians, 
+    \E{}{\Lag(x, z, y) = \sum_i^N f_i(x_i) + 
+            \frac{\rho}{2} \norm{A_i(z) x_i - b_i(z)}^2 
+            +\real\left[y_i^\cT (A_i(z)x_i-b_i(z))\right] + g(z),}
+    where $\rho$ is a constant scalar and 
+    $y_i$ are dual variables.
+
+ADMM obtains the solutions for $x$ and $z$ via
+    \EE{}{  x_i &\gets \argmin_{x_i} \Lag(x, z, y), \quad i = 1,\ldots,N \\
+            z &\gets \argmin_{z} \Lag(x, z, y), \\
+            y_i &\gets y_i + \rho (A_i(x_i) z - b(x_i)), \quad i = 1,\ldots,N.}
+
+To obtain the correct $Q(z)$ which should be passed to the structure submodule,
+    we use \eq{bi-affine property} to write
+    \E{}{\argmin_z \Lag = \argmin_z g(z) 
+            + \sum_i^N \frac{\rho}{2} \norm{B_i(x_i) z - d(x_i)}^2 
+            + \real\left[ y_i^\cT ( B_i(x_i) z - d_i(x_i))\right]}
+    which means that
+    \E{}{Q(z) = \sum_i^N \frac{\rho}{2} \norm{B_i(x_i) z - d(x_i)}^2 
+            + \real\left[ y_i^\cT ( B_i(x_i) z - d_i(x_i))\right].}
+
+\subsubsection{Computation of $\argmin_{x_i} \Lag$}
+Updating $x_i$, which is left to the paradigm submodule,
+    involves solving $\argmin_{x_i} \Lag(x, z, y)$ for all $i = 1, \ldots, N$.
+This can be accomplished via
+    \E{}{\grad_{x_i}\Lag = \grad_{x_i} f_i(x_i) + }
 
@@
 
+\begin{thebibliography}{99}
+\bibitem{ADMM} Boyd group ADMM paper
+\end{thebibliography}
 \end{document}

### 2012-11-26 plan/plan.tex
Some changes.
Got most of global opt theory done.

@@
     and then pass 
-    \E{}{Q(z) = \frac{1}{2}\norm{z-z_0}^2 + \kappa \grad_z F\cT (z-z_0)}
+    \E{}{Q(z) = \frac{1}{2}\norm{z-z_0}^2 + \kappa \grad_z F^\cT (z-z_0)}
     to the structure submodule, for some $\kappa$.
@@
     which casts \eq{rigorous problem statement} in terms of the following augmented Lagrangians, 
-    \E{}{\Lag(x, z, y) = \sum_i^N f_i(x_i) + 
-            \frac{\rho}{2} \norm{A_i(z) x_i - b_i(z)}^2 
+    \E{}{\Lag(x, z, y) = \sum_i^N f_i(x_i) 
+            + \frac{\rho}{2} \norm{A_i(z) x_i - b_i(z)}^2 
             +\real\left[y_i^\cT (A_i(z)x_i-b_i(z))\right] + g(z),}
     where $\rho$ is a constant scalar and 
-    $y_i$ are dual variables.
+    $y_i$ are dual variables. If we introduce $u_i = y_i / \rho$, then 
+    \E{}{\Lag(x,z,u) = \sum_i^N f_i(x_i)
+            + \frac{\rho}{2} \norm{A_i(z) x_i - b_i(z) + u_i}^2 
+            - \frac{\rho}{2} \norm{u_i}^2 + g(z).}
 
 ADMM obtains the solutions for $x$ and $z$ via
-    \EE{}{  x_i &\gets \argmin_{x_i} \Lag(x, z, y), \quad i = 1,\ldots,N \\
-            z &\gets \argmin_{z} \Lag(x, z, y), \\
-            y_i &\gets y_i + \rho (A_i(x_i) z - b(x_i)), \quad i = 1,\ldots,N.}
+    \EE{}{  x_i &\gets \argmin_{x_i} \Lag(x, z, u), \quad i = 1,\ldots,N \\
+            z &\gets \argmin_{z} \Lag(x, z, u), \\
+            u_i &\gets u_i + (A_i(x_i) z - b(x_i)), \quad i = 1,\ldots,N.}
 
@@
     \E{}{\argmin_z \Lag = \argmin_z g(z) 
-            + \sum_i^N \frac{\rho}{2} \norm{B_i(x_i) z - d(x_i)}^2 
-            + \real\left[ y_i^\cT ( B_i(x_i) z - d_i(x_i))\right]}
+            + \sum_i^N \frac{\rho}{2} \norm{B_i(x_i) z - d(x_i) + u_i}^2}
     which means that
-    \E{}{Q(z) = \sum_i^N \frac{\rho}{2} \norm{B_i(x_i) z - d(x_i)}^2 
-            + \real\left[ y_i^\cT ( B_i(x_i) z - d_i(x_i))\right].}
+    \E{}{Q(z) = \sum_i^N \frac{\rho}{2} \norm{B_i(x_i) z - d(x_i) + u_i}^2}
 
@@
 Updating $x_i$, which is left to the paradigm submodule,
-    involves solving $\argmin_{x_i} \Lag(x, z, y)$ for all $i = 1, \ldots, N$.
-This can be accomplished via
-    \E{}{\grad_{x_i}\Lag = \grad_{x_i} f_i(x_i) + }
+    involves solving $\argmin_{x_i} \Lag(x, z, u)$ via Newton's method for all $i = 1, \ldots, N$.
+This can be accomplished via the gradient with respect to $x_i$
+    \E{}{\grad_{x_i}\Lag(x, z, u) = \grad_{x_i} f_i(x_i)
+                + \rho A_i(z)\T (A_i(z) x_i - b_i(z) + u_i),}
+    as well as the Hessian with respect to $x_i$
+    \E{}{\grad^2_{x_i}\Lag(x, z, u) = \grad^2_{x_i} f_{x_i} + \rho A_i(z)\T A_i(z),}
+    which can be combined to determine the direction of a step in Newton's method,
+    \E{}{\Delta x_i = - \grad^2_{x_i} \Lag^{-1} \grad_{x_i} \Lag.}
+
+Solving $\argmin_{x_i} \Lag(x, z, u)$ from an initial $x_i$ thus proceeds by
+    repeatedly computing $\Delta x_i$ and then performing a line search along that direction,
+    until some convergence criterion is met, typically
+    \E{}{\frac{1}{2} \grad_{x_i}\Lag\T \grad^2_{x_i} \Lag^{-1} \grad_{x_i} \Lag \le \text{error threshold}.}
+
+\subsubsection{Relaxation of $f_i(x_i)$}
+In order to compute $\Delta x_i$ we relax the design objectives, $f_i(x_i)$, to a differentiable, and convex form.
+Specifically, the upper bound constraint is relaxed via
+    \E{}{I_+(\beta_{ij} - |c\T_{ij} x_i|) \to -\frac{1}{t} \ln (\beta_{ij}^2 - \norm{c\T_{ij} x_i}^2),}
+    where $t$ is a real positive scalar. The lower bound constraint is relaxed via
+    \E{}{I_+(|c\T_{ij} x_i| - \alpha_{ij}) \to -\frac{1}{t} \ln (\real[e^{i\phi}c\T_{ij} x_i] - \alpha_{ij}),}
+     where $e^{i\phi}$ is a phase factor on $c\T_{ij} x_i$.
+
+The gradient can now be obtained as
+% \footnote{
+%     \EE{}{\grad_{x_i} f_i(x_i) &= \frac{1}{t(\beta_{ij}^2 - \norm{c\T_{ij} x_i}^2)} c_{ij}c\T_{ij} x_i
+%                             - \frac{1}{t(\real[e^{i\phi} c\T_{ij} x_i] - \alpha_{ij})} e^{i\phi}c_{ij} \\
+%                         &= \frac{1}{t} \left( \frac{c\T_{ij} x_i}{\beta_{ij}^2 - \norm{c\T_{ij} x_i}^2} 
+%                             - \frac{e^{i\phi}}{\real[e^{i\phi} c\T_{ij} x_i] - \alpha_{ij}} \right)
+%                         c_{ij}}
+% 
+%     
+%     \E{}{\grad_{x_i}^2 f_i(x_i) = \frac{1}{t} \left(
+%                 \frac{1}{\beta_{ij} - \norm{c\T_{ij} x_i}^2}
+%                 + \frac{\norm{c\T_{ij} x_i}^2}{(\beta_{ij} - \norm{c\T_{ij} x_i}^2)^2}
+%                 + \frac{1}{(\real[e^{i\phi} c\T_{ij} x_i] - \alpha_{ij})^2} \right)
+%                 c_{ij} c\T_{ij}}}
+
+    \E{}{\grad_{x_i} f_i(x_i) = \frac{s_1}{t} c_{ij}}
+    where
+    \E{}{s_1 = \frac{c\T_{ij} x_i}{\beta_{ij}^2 - \norm{c\T_{ij} x_i}^2} 
+                - \frac{e^{i\phi}}{\real[e^{i\phi} c\T_{ij} x_i] - \alpha_{ij}},}
+    and the Hessian as 
+    \E{}{\grad_{x_i}^2 f_i(x_i) = \frac{s_2}{t} c_{ij} c\T_{ij}}
+    where
+    \E{}{s_2 = \frac{1}{\beta_{ij} - \norm{c\T_{ij} x_i}^2}
+                + \frac{\norm{c\T_{ij} x_i}^2}{(\beta_{ij} - \norm{c\T_{ij} x_i}^2)^2}
+                + \frac{1}{(\real[e^{i\phi} c\T_{ij} x_i] - \alpha_{ij})^2}.}
+
+\subsubsection{Computation of $\Delta x_i$}
+We now show how $\Delta x_i$ may be efficiently computed.
 

### 2012-11-27 plan/plan.tex
Minor.

@@
 
-    \E{}{\grad_{x_i} f_i(x_i) = \frac{s_1}{t} c_{ij}}
+    \E{}{\grad_{x_i} f_i(x_i) = \sum_j \frac{r_j}{t} c_{ij}}
     where
-    \E{}{s_1 = \frac{c\T_{ij} x_i}{\beta_{ij}^2 - \norm{c\T_{ij} x_i}^2} 
+    \E{}{r_j = \frac{c\T_{ij} x_i}{\beta_{ij}^2 - \norm{c\T_{ij} x_i}^2} 
                 - \frac{e^{i\phi}}{\real[e^{i\phi} c\T_{ij} x_i] - \alpha_{ij}},}
     and the Hessian as 
-    \E{}{\grad_{x_i}^2 f_i(x_i) = \frac{s_2}{t} c_{ij} c\T_{ij}}
+    \E{}{\grad_{x_i}^2 f_i(x_i) = \sum_j \frac{s_j}{t} c_{ij} c\T_{ij}}
     where
-    \E{}{s_2 = \frac{1}{\beta_{ij} - \norm{c\T_{ij} x_i}^2}
+    \E{}{s_j = \frac{1}{\beta_{ij} - \norm{c\T_{ij} x_i}^2}
                 + \frac{\norm{c\T_{ij} x_i}^2}{(\beta_{ij} - \norm{c\T_{ij} x_i}^2)^2}

### 2012-11-27 plan/plan.tex
Get computation of delta x_i.

@@
 We now show how $\Delta x_i$ may be efficiently computed.
+First we introduce
+    \E{}{\tilde{c}_i = \frac{1}{\rho t} \sum_j r_j A^{-\cT} c_{ij}}
+    in order to write
+    \E{}{\grad_{x_i} \Lag(x, z, u) = \rho A_i(z)\T(A_i(z)x_i - b_i(z) 
+                            + u_i + \tilde{c}_i).}
+For its part, the Hessian can be simplified using the matrix inversion lemma\footnote{\E{}{ (A + UCV)^{-1} = A^{-1} - A^{-1}U (C^{-1} + V A^{-1} U)^{-1} V A^{-1}}}.
+Coupled with the introduction of 
+    \E{}{\tilde{C}_i = A_i(z)^{-\cT}\begin{bmatrix} 
+                        \sqrt{\frac{s_1}{\rho t}}c_{i1} &
+                        \sqrt{\frac{s_2}{\rho t}}c_{i1} &
+                        \cdots &
+                        \sqrt{\frac{s_{m_i}}{\rho t}}c_{im_i} 
+                        \end{bmatrix}}
+    we can write
+    \E{}{\grad_{x_i}^2 \Lag(x, z, u) = \rho A_i(z)\T (I + \tilde{C}\tilde{C}\T) A_i(z),}
+    and more importantly
+    \E{}{(\grad_{x_i}^2 \Lag(x, z, u))^{-1} = \frac{1}{\rho} A_i(z)^{-1} M A_i(z)^{-\cT},}
+    where
+    \E{}{M = (I + \tilde{C} \tilde{C}\T)^{-1} = 
+            I - \tilde{C} (I + \tilde{C}\T\tilde{C})^{-1} \tilde{C}\T.}
+
+Finally, the expression for $\Delta x_i$ is obtained as
+    \E{}{\Delta x_i = - \grad^2_{x_i} \Lag^{-1} \grad_{x_i} \Lag = 
+        A_i(z)^{-1} M (A_i(z)x_i - b_i(z) + u_i + \tilde{c}_i).}
 

### 2012-12-13 plan/plan.tex
Small correction.

--- 2012-11-27 plan/plan.tex
@@
     \E{}{\frac{d}{dz} f_i(x_i) = -\frac{\pd f_i}{\pd x_i} A_i(z)^{-1} B_i(x_i) = 
-        -\left(A_i(z)^\cT \frac{\pd f_i}{\pd x_i}^\cT\right)^\cT B_i(x_i)}
+        -\left(A_i(z)^{-\cT} \frac{\pd f_i}{\pd x_i}^\cT\right)^\cT B_i(x_i)}
     which requires only one solve of $A_i^\cT$ as opposed to $n$ solves of $A_i$.

### 2012-12-13 plan/adjoint.tex

\documentclass{article}
\usepackage{amsmath}
\usepackage{pstricks}

\input ../defs.tex

\title{Notes on Adjoint Solves using \sc{Maxwell}}
\author{Jesse Lu}
\begin{document}
\maketitle

Maxwell solves $(\curl\mu^{-1}\curl - \omega^2\epsilon)E = i\omega J$, or 
    \E{}{Ax = b,}
    where
    \BI $\curl\mu^{-1}\curl - \omega^2\epsilon \to A$,
    \I  $E \to x$,
    \I  $i\omega J \to b$. \EI
In many cases, however, one requires the solution to the \emph{adjoint} or conjugate-transpose of $A$, namely
    \E{}{A\T y = d.}

To do so, we introduce a diagonal symmetrization matrix, $S$, which has the property
    \E{}{SA = A^T S,}
    and is defined as $S = \text{diag}([ s_x, s_y, s_z])$ where
    \EE{}{  s_x &= s_x^\text{dual} s_y^\text{prim} s_z^\text{prim}, \\
            s_y &= s_x^\text{prim} s_y^\text{dual} s_z^\text{prim}, \\
            s_z &= s_x^\text{prim} s_y^\text{prim} s_z^\text{dual}.}

Using $S$, we perform the following operations on $Ax=b$,
    \EE{}{  SAx &= Sb \\
            A^T Sx &= Sb \\
            A\T S^\ast x^\ast &= S^\ast b^\ast \\
            A\T y &= d,}
    from which we conclude that $y = S^\ast x^\ast$ and $d = S^\ast b^\ast$.

Therefore, in order to solve for $A\T y = d$ given $d$ using Maxwell, we simply compute
    \E{}{y = S^\ast (A^{-1} (S^{-1} d^\ast))^\ast.}

Lastly, we may also consider the case where $\omega$ is an eigenfrequency and $v$ is an eigenmode
    in the simulation domain, then
    \E{}{Av = 0, \quad v \ne 0.}
We simply remark that in this case, a corresponding right eigenvector $w$ may be found via
    \E{}{w = S v}
    since 
    \EE{}{  w^T A &= 0 \\
            v^T S A &= 0 \\
            v^T A^T S &= 0 \\
            S A v &= 0 \\
            Av &= 0.}

\end{document}

### 2012-12-18 plan/plan.tex
Corrected global paradigm math.

@@
     where $t$ is a real positive scalar. The lower bound constraint is relaxed via
-    \E{}{I_+(|c\T_{ij} x_i| - \alpha_{ij}) \to -\frac{1}{t} \ln (\real[e^{i\phi}c\T_{ij} x_i] - \alpha_{ij}),}
-     where $e^{i\phi}$ is a phase factor on $c\T_{ij} x_i$.
+    \E{}{I_+(|c\T_{ij} x_i| - \alpha_{ij}) \to -\frac{1}{t} \ln (\real[e^{-i\phi_{ij}}c\T_{ij} x_i] - \alpha_{ij}),}
+     where $e^{-i\phi_{ij}}$ is a phase factor on $c\T_{ij} x_i$.
+The convention of $\phi_{ij} = \text{angle}(c\T_{ij} x_i)$ is often used
+    to determine $\phi_{ij}$ before optimizing for $x_i$.
 
 The gradient can now be obtained as
-% \footnote{
-%     \EE{}{\grad_{x_i} f_i(x_i) &= \frac{1}{t(\beta_{ij}^2 - \norm{c\T_{ij} x_i}^2)} c_{ij}c\T_{ij} x_i
-%                             - \frac{1}{t(\real[e^{i\phi} c\T_{ij} x_i] - \alpha_{ij})} e^{i\phi}c_{ij} \\
-%                         &= \frac{1}{t} \left( \frac{c\T_{ij} x_i}{\beta_{ij}^2 - \norm{c\T_{ij} x_i}^2} 
-%                             - \frac{e^{i\phi}}{\real[e^{i\phi} c\T_{ij} x_i] - \alpha_{ij}} \right)
-%                         c_{ij}}
-% 
-%     
-%     \E{}{\grad_{x_i}^2 f_i(x_i) = \frac{1}{t} \left(
-%                 \frac{1}{\beta_{ij} - \norm{c\T_{ij} x_i}^2}
-%                 + \frac{\norm{c\T_{ij} x_i}^2}{(\beta_{ij} - \norm{c\T_{ij} x_i}^2)^2}
-%                 + \frac{1}{(\real[e^{i\phi} c\T_{ij} x_i] - \alpha_{ij})^2} \right)
-%                 c_{ij} c\T_{ij}}}
-
-    \E{}{\grad_{x_i} f_i(x_i) = \sum_j \frac{r_j}{t} c_{ij}}
+    \E{}{\grad_{x_i} f_i(x_i) = \sum_j \frac{r_{ij}}{t} c_{ij}}
     where
-    \E{}{r_j = \frac{c\T_{ij} x_i}{\beta_{ij}^2 - \norm{c\T_{ij} x_i}^2} 
-                - \frac{e^{i\phi}}{\real[e^{i\phi} c\T_{ij} x_i] - \alpha_{ij}},}
+    \E{}{r_{ij} = \frac{2c\T_{ij} x_i}{\beta_{ij}^2 - \norm{c\T_{ij} x_i}^2} 
+                - \frac{e^{i\phi_{ij}}}{\real[e^{-i\phi_{ij}} c\T_{ij} x_i] - \alpha_{ij}},}
     and the Hessian as 
-    \E{}{\grad_{x_i}^2 f_i(x_i) = \sum_j \frac{s_j}{t} c_{ij} c\T_{ij}}
+    \E{}{\grad_{x_i}^2 f_i(x_i) = \sum_j \frac{s_{ij}}{t} c_{ij} c\T_{ij}}
     where
-    \E{}{s_j = \frac{1}{\beta_{ij} - \norm{c\T_{ij} x_i}^2}
-                + \frac{\norm{c\T_{ij} x_i}^2}{(\beta_{ij} - \norm{c\T_{ij} x_i}^2)^2}
-                + \frac{1}{(\real[e^{i\phi} c\T_{ij} x_i] - \alpha_{ij})^2}.}
+    \E{}{s_{ij} = \frac{2}{\beta_{ij}^2 - \norm{c\T_{ij} x_i}^2}
+                + \frac{4\norm{c\T_{ij} x_i}^2}{(\beta_{ij}^2 - \norm{c\T_{ij} x_i}^2)^2}
+                + \frac{1}{(\real[e^{-i\phi_{ij}} c\T_{ij} x_i] - \alpha_{ij})^2}.}
 

### 2013-02-15 defense/fig/sprc 2009/technical_paper.tex
Started on new presentation

\documentclass{article}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{tabularx}

\title{Electromagnetic Inverse Design}
\author{Jesse Lu and Jelena Vuckovic}
\date{SPRC 2009 Symposium}

\begin{document}
\maketitle % put the title in
\thispagestyle{empty} % this removes page numbers
\noindent\makebox[\textwidth]{\includegraphics[width=1.6\textwidth]{fig1}}% this is fancy stuff to make a centered, but very wide picture

We develop a method to solve the electromagnetic inverse design problem; that is, to find a dielectric structure that will produce a specified electromagnetic field. Such a method enables the design of non-intuitive, multi-objective photonic components such as small mode-volume or doubly-resonant cavities, broadband waveguide couplers and dispersion-tailored waveguides.

\section*{Problem Challenge}
The electromagnetic inverse design problem is challenging because
\begin{itemize}
\item realistic dielectric structures are typically binary, consisting of only two discrete dielectric materials, and
\item there is no one-to-one correspondence between field profiles and dielectric structures, since certain field profiles are impossible to achieve.
\end{itemize}

\newpage
\section*{Current Progress}
Currently, we have been able to produce two-dimensional proof-of-concept designs including
\begin{itemize}
\item line and ``X'' resonators,
\item degenerate and non-degenerate doubly-resonant cavities, and
\item a single to dual-beam waveguide coupler.
\end{itemize}

\begin{figure}[h!]
\centering
\includegraphics[width=1.0\textwidth]{fig2}
\caption{Magnetic field profile and two-dimensional dielectric structure of a small mode-volume resonator produced by our inverse design method.}
\end{figure}

\end{document}

### 2013-02-15 defense/pres2.tex
Started on new presentation

\documentclass[landscape]{foils}
\usepackage{graphicx}
\usepackage{amsmath}

\input defs.tex
\raggedright
\special{! TeXDict begin /landplus90{true}store end }
\renewcommand{\oursection}[1]{
\foilhead[-1.0cm]{#1}
}
\newcommand{\myfig}[1]{
    \begin{figure}[!h]
    \centerline{\includegraphics[height=6.5cm]{fig/#1.jpg}}
    \end{figure}
}
\newcommand{\medfig}[1]{
    \begin{figure}[!h]
    \centerline{\includegraphics[height=10cm]{fig/#1.jpg}}
    \end{figure}
}
\newcommand{\bigfig}[1]{
    \begin{figure}[!h]
    \centerline{\includegraphics[height=12cm]{fig/#1.jpg}}
    \end{figure}
}
\newcommand{\BI}{\begin{itemize}\item}
\newcommand{\I}{\item}
\newcommand{\EI}{\end{itemize}}

\title{Nanophotonic Computational Design}
\author{Jesse Lu}
\MyLogo{Jesse Lu PhD defense, Jelena Vuckovic group, Stanford University}
\date{February 25, 2013}

% \usepackage{pause}
\usepackage[display]{texpower}

\begin{document}
\setlength{\parskip}{0cm}
\maketitle

% \BIT \itemsep -1pt
% \item motivation
% \item theory
% \item results
% \EIT

\vfill
\newpage

Goal: Show you how to design \emph{any} linear nanophotonic device
\myfig{takeaway}

\pause
\BI Physics Advisory: 
    \begin{quote}CONTAINS INVOLVED MATHEMATICAL CONTENT\end{quote}

\pause
\I  Math Advisory: 
    \begin{quote}CONTAINS INVOLVED NANOPHOTONIC CONTENT\end{quote}
\vfill
\newpage

\oursection{Given a field, can we find its structure?}
\myfig{thedefinition}
\I  Electromagnetic wave equation 
    ($\text{field}\to E$, $\text{structure}\to\epsilon$)
    \BE \nabla\times\mu_0^{-1}\nabla\times E - \omega^2 \epsilon E = 
        -i \omega J \EE

\EI
\end{document}

### 2013-02-18 defense/pres2.tex
Getting there with presentation remake.
Minor.
Getting there...

@@
 \special{! TeXDict begin /landplus90{true}store end }
+\newcommand{\nextpage}{\vfill\newpage}
 \renewcommand{\oursection}[1]{
@@
 }
-\newcommand{\myfig}[1]{
+\newcommand{\myfig}[2]{
+    \begin{figure}[!h]
+    \centerline{\includegraphics[height=#2cm]{fig/#1.jpg}}
+    \end{figure}
+}
+
+\newcommand{\smallfig}[1]{
     \begin{figure}[!h]
@@
 
-\vfill
-\newpage
+\nextpage
 
 Goal: Show you how to design \emph{any} linear nanophotonic device
-\myfig{takeaway}
+\smallfig{takeaway}
+\pause
+\BI Device properties: 
+    \BI Full 3D
+    \I  Compact
+    \I  Efficient
+    \I  Multi-mode 
+    \I  Multi-functional \EI
+\nextpage
 
+\I  Developed by
+    \BI applying (convex) optimization techniques (math)
+    \I  to the area of nanophotonics (physics)
+    \I  and implementing in software (programming) \EI
 \pause
-\BI Physics Advisory: 
+\I  Physics Advisory: 
     \begin{quote}CONTAINS INVOLVED MATHEMATICAL CONTENT\end{quote}
-
 \pause
@@
     \begin{quote}CONTAINS INVOLVED NANOPHOTONIC CONTENT\end{quote}
-\vfill
-\newpage
+\nextpage
 
 \oursection{Given a field, can we find its structure?}
-\myfig{thedefinition}
-\I  Electromagnetic wave equation 
-    ($\text{field}\to E$, $\text{structure}\to\epsilon$)
+\smallfig{my_definition}
+\stepwise{
+\step{\I  Equivalently, find $\epsilon$ (structure) given $E$ (field)
     \BE \nabla\times\mu_0^{-1}\nabla\times E - \omega^2 \epsilon E = 
-        -i \omega J \EE
+        -i \omega J \EE}
+\step{\I  If possible, we can design \emph{any} nanophotonic/optical component!}
+}
+\nextpage
+
+\I Answer: Yes, given $E$ we \emph{can} solve for $\epsilon$ (trivial!)
+    \stepwise{
+    \begin{align*} 
+    \nabla\times\mu_0^{-1}\nabla\times E - \omega^2 \epsilon E &= 
+        -i \omega J \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\\
+    \step{\omega^2 \epsilon E &= \nabla\times\mu_0^{-1}\nabla\times E + 
+        i \omega J }\\
+    \step{\omega^2 E \epsilon &= \nabla\times\mu_0^{-1}\nabla\times E + 
+        i \omega J }\\
+    \step{\epsilon &= (\nabla\times\mu_0^{-1}\nabla\times E + 
+        i \omega J)/ \omega^2 E} 
+    \end{align*}
+    }
+\I  Solving for $\epsilon$ actually way faster than simulation (solving for $E$)!
+\nextpage
+
+\I  Obvious and well-known from a mathematical perspective
+    \BI Pre-requisite (200-level) class in optimization curriculum
+    \I  Not yet taught (I think) in optics/photonics at Stanford \EI
+    \stepwise{\step{
+    \BE
+    \underbrace{\nabla\times\mu_0^{-1}\nabla\times E - \omega^2 \epsilon E = 
+                -i \omega J }_\text{physics}
+    \quad\longrightarrow\quad
+    \underbrace{A(z)x = b}_\text{linear algebra}
+    \EE
+    \begin{align*}
+    E &\to x \\
+    \epsilon &\to z \\
+    \nabla\times\mu_0^{-1}\nabla\times - \omega^2 \epsilon &\to A(z) \\
+    -i\omega J &\to b
+    \end{align*}
+    }
+\step{\I  Key: If $A(z)$ is linear in $z$ then $A(z)x=b$ is as well!}
+    }
 

### 2013-02-18 defense/pres2.tex
Getting there...

@@
     \EE
+    }
+    \step{
     \begin{align*}
@@
 
+\oursection{Direct design of structure in 1D}
+\I  Chose $x$ (field) and solved for $z$ (structure)
+\smallfig{1d_leastsquares}
+\pause
+\I  Perfect performance but unmanufacturable structure
+\nextpage
+
+% \bigfig{1d_regularized}
+\smallfig{1d_regularized_1}
+\smallfig{1d_regularized_2}
+\I  Regularization on $z$ decreases performance 
+\nextpage
+
+\I  We know that there exist $x$ which produce well-behaved $z$
+\I  However, choosing such $x$ is next to impossible
+\I  Therefore, a practical design tool must include $x$-search
+\nextpage
+
+\oursection{Iterative design of structure in 1D}
+\I  
+\I  Insight: Solving for well-behaved $z$ requires fortuitous selection of $x$
+\I  Therefore, vary $x$ in order to allow for well-behaved $z$
+\smallfig{1d_alternate}
+\I  Variation in $x$ allows $z$ to be better behaved
+\nextpage
+
+\I  Alternately solve for $x$ and $z$:
+    \begin{align*} 
+    \minimize_z & \|A(z)x - b\|^2 + \eta_1\|z - z_0\|^2 \\
+    \minimize_x & \|A(z)x - b\|^2 + \eta_0\|x - x_0\|^2 
+    \end{align*}
+\smallfig{1d_alternate}
+
 \EI

### 2013-02-19 defense/pres2.tex
Added feedback from first practice.
Got basic outline down for pres2.

--- 2013-02-18 defense/pres2.tex
@@
 
+\oursection{Introduction}
+\smallfig{optical_networks}
+\BI  Bring the optical network onto a computer chip
+\nextpage
+
+\smallfig{integrated_circuit}
+\I  Currently designed by hand, handful of parameters
+\I  Design by computer, using the full design parameters
+\nextpage
+
+\I  Increasing design complexity requires additional degrees of freedom
+\I  Fortunately, we have a virtually unlimited amount
+\smallfig{des_complexity}
+\I  Include/exclude per pixel gives us $2^{(15^2)} = 2^{225}$ possibilities, 
+    uncountable
+\nextpage
+
 Goal: Show you how to design \emph{any} linear nanophotonic device
@@
 \pause
-\BI Device properties: 
+\I Device properties: 
     \BI Full 3D
@@
 
+\oursection{Direct design of nanophotonic devices}
+\I  Choose $x$ (field) and solve for $z$ (structure)
+\smallfig{1d_leastsquares}
+\I  Perfect performance!\ldots But unmanufacturable structure
+\nextpage
+
+\bigfig{1d_regularized_23}
+\I  Regularization on $z$ decreases performance 
+\nextpage
+
+\I  Conclusion: 
+    \BI Directly solving for $z$ (structure) is easy
+    \I  Solving for manufacturable $z$ is hard \EI
+% \smallfig{1d_regularized_2}
+\I  However, we know that there exist some $x$ (fields) 
+    which produce well-behaved $z$ (structure)
+    \BI But, cannot ask the user to choose such $x$ \EI
+\nextpage
+
+\oursection{Iterative design of nanophotonic devices}
+\I  Key lesson: Nanophotonic design involves 
+    optimizing \emph{both} $x$ (field) and $z$ (structure)
+
+\I  New algorithm: Iteratively solve for $x$ and $z$
+    \begin{align*} 
+    \minimize_z & \|A(z)x - b\|^2 + \eta_0\|z - z_0\|^2 \\
+    \minimize_x & \|A(z)x - b\|^2 + \eta_1\|x - x_0\|^2 
+    \end{align*}
+
+\I  Here, $\eta_{0,1}$ are \emph{regularization} parameters
+\nextpage
+
+\I  Iterative strategy produces $z$ (structure) that 
+    \BI is better behaved
+    \I  more accurately produces $x$ \EI
+\smallfig{1d_alternate}
+\nextpage
+
+\I  We can also put hard limits on $z$
+    \begin{align*} 
+    \minimize_z & \|A(z)x - b\|^2 \\
+    \subto & z_0 \le z \le z_1 \\ \\
+    \minimize_x & \|A(z)x - b\|^2 + \eta_1\|x - x_0\|^2 
+    \end{align*}
+\I  $z_0 \le z \le z_1$ constraint better represents manufacturability constraint
+    \BI Corresponds to a minimum and maximum allowable permittivity ($\epsilon$) \EI
+\nextpage
+
+\smallfig{1d_hardlimit}
+\I  Getting close!
+\nextpage
+
+\I  higher dimensions
+\myfig{2d_circ}{5}
+\myfig{25d_circ}{5}
+\nextpage
+
+\oursection{Objective-first design of nanophotonic devices}
+\I  Next step in our thinking is that for most devices only some parts of the field matter
+\I  waveguiding devices
+\medfig{ob1_wg}
+
+\oursection{Design of 3D nanophotonic devices}
+
 \EI

### 2013-02-19 defense/pres2.tex
Getting there with second pres.

--- 2013-02-18 defense/pres2.tex
@@
 
-Goal: Show you how to design \emph{any} linear nanophotonic device
+\oursection{Introduction}
+\smallfig{optical_networks}
+\BI As information grows, optical networks needed
+    \BI across continents
+    \I  within a datacenter
+    \I  between chips and on-chip \EI
+\nextpage
+
+\I  On-chip optical components are currently designed
+    by tuning a small number of design parameters
+\smallfig{integrated_circuit}
+\pause
+\I  What happens when we use the \emph{full} parameter space
+    for nanophotonic design?
+\nextpage
+
+\I  The full parameter space is \emph{vast}
+\smallfig{des_complexity}
+\I  Include/exclude per pixel gives us $2^{(15^2)} = 2^{225}$ possibilities
+    \BI A virtually uncountable number 
+    \I  Can only be design by a computer \EI
+\nextpage
+
 \smallfig{takeaway}
-\pause
-\BI Device properties: 
-    \BI Full 3D
-    \I  Compact
-    \I  Efficient
-    \I  Multi-mode 
-    \I  Multi-functional \EI
+\I  Our work: Software to design full 3D, multi-mode, and multi-functional
+    linear nanophotonic devices---using the fully available parameter space \pause
+\I  Many of these devices are
+    \BI Completely novel (no previously known designs)
+    \I  Extremely compact (footprints of a few vacuum wavelengths)
+    \I  High efficiency ($>80\%$ transmission) \EI
 \nextpage
@@
 
+\oursection{Direct design of nanophotonic devices}
+\I  Let's try it already! 
+    \BI Choose $x$ (field) 
+    \I  Solve for $z$ (structure) by minimizing the \emph{physics residual},
+        $A(z)x-b$\EI
+    \pause
+    \BE \minimize_z \|A(z)x - b\|^2 \EE
+\pause
+\I  Global minimum where $A(z)x - b = 0$ can be computed in one step
+    \BE \epsilon = (\nabla\times\mu_0^{-1}\nabla\times E + i \omega J)
+                    / \omega^2 E \EE
+    where $\epsilon \to z$
+\nextpage
+
+\I  Choose canonical 1D cavity field for $x$
+\I  Solve for $z$ (structure) and check design fidelity with simulation
+\smallfig{1d_leastsquares}
+\pause
+\I  Result
+    \BI Perfect performance
+    \I  But unmanufacturable structure ($z$ not well-behaved) \EI
+\nextpage
+
+\oursection{Direct design with regularization}
+\I  Direct design ``works'' but not practical
+    \BE \minimize_z \|A(z)x - b\|^2 \EE
+\I  So, let's add a \emph{regularization} term to $z$ and solve the following instead 
+    \BE \minimize_z \|A(z)x - b\|^2 + \eta\|z-z_0\|^2 \EE
+    \BI  $\|z-z_0\|^2$ term keeps $z$ close to $z_0$
+    \I  $\eta$ controls the strength of the regularization \EI
+\I  Solution can still be computed in one step
+\nextpage
+
+\bigfig{1d_regularized_12}
+\I  Unfortunately, regularization on $z$ decreases performance 
+\nextpage
+
+\smallfig{1d_regularized_3}
+    \BE \minimize_z \|A(z)x - b\|^2 + \eta\|z-z_0\|^2 \EE
+\I  Decreased performance a result of non-zero physics residual at optimum
+\nextpage
+
+\I  How to overcome the apparent trade-off between manufacturability ($z$)
+    and performance ($x$)?
+\pause
+\I  Realized that there do exist some $x$ (fields)
+    which result from manufacturable $z$ (structures)
+    \BI These can be produced via simulation
+    \I  However, it's not useful to ask the user to choose such $x$ \EI
+\pause
+\I  Therefore, a \emph{useful} tool would optimize for \emph{both} $x$ and $z$
+\nextpage
+
+\oursection{Iterative design of nanophotonic devices}
+\I  New algorithm: Iteratively solve for $x$ (field) and $z$ (structure)
+    \begin{align*} 
+    \minimize_z & \|A(z)x - b\|^2 + \eta_0\|z - z_0\|^2 \\
+    \minimize_x & \|A(z)x - b\|^2 + \eta_1\|x - x_0\|^2 
+    \end{align*}
+\I  Takes advantage of the \emph{bi-linearity} of the physics residual
+    \BI Jointly solving for $x$ and $z$ is a non-convex problem \EI
+\nextpage
+
+\I  More concisely, we iteratively solve the following
+    \BE \minimize_\text{alternately $x$ then $z$} 
+        \|A(z)x - b\|^2 + \eta_0\|z - z_0\|^2 + \eta_1\|x-x_0\|^2 \EE
+\I  Design process now consists of \emph{multiple} computational steps
+    \BI $\eta_0, \eta_1$ gradually decreased to bring physics residual toward 0 \EI
+\nextpage
+
+\smallfig{1d_alternate}
+\I  Iterative strategy produces $z$ (structure) that 
+    \BI is better behaved
+    \I  more accurately produces $x$ \EI
+\nextpage
+
+\oursection{Iterative design with hard constraints on $z$}
+\I  We can also put hard limits on $z$ (structure)
+    \begin{align*} 
+    \minimize & \|A(z)x - b\|^2 + \eta_1\|x - x_0\|^2\\
+    \subto & z_\text{min} \le z \le z_\text{max}
+    \end{align*}
+\I  $z_\text{min} \le z \le z_\text{max}$ constraint 
+    better represents manufacturability constraint
+    \BI Corresponds to a minimum and maximum allowable permittivity ($\epsilon$) \EI
+\nextpage
+
+\smallfig{1d_hardlimit}
+\I  Final  
+\nextpage
+
+\I  higher dimensions
+\myfig{2d_circ}{5}
+\myfig{25d_circ}{5}
+\nextpage
+
+\oursection{Objective-first design of nanophotonic devices}
+\I  Next step in our thinking is that for most devices only some parts of the field matter
+\I  waveguiding devices
+\medfig{ob1_wg}
+
+\oursection{Design of 3D nanophotonic devices}
+
 \EI

### 2013-02-20 defense/pres2.tex
Getting there...

@@
     \begin{align*} 
-    \minimize_z & \|A(z)x - b\|^2 + \eta_0\|z - z_0\|^2 \\
-    \minimize_x & \|A(z)x - b\|^2 + \eta_1\|x - x_0\|^2 
+    \minimize_z & \|A(z)x - b\|^2 + \eta_0\|z - z_\text{prev}\|^2 \\
+    \minimize_x & \|A(z)x - b\|^2 + \eta_1\|x - x_\text{prev}\|^2 
     \end{align*}
@@
     \BE \minimize_\text{alternately $x$ then $z$} 
-        \|A(z)x - b\|^2 + \eta_0\|z - z_0\|^2 + \eta_1\|x-x_0\|^2 \EE
+        \|A(z)x - b\|^2 + \eta_0\|z - z_\text{prev}\|^2
+                        + \eta_1\|x-x_\text{prev}\|^2 \EE
 \I  Design process now consists of \emph{multiple} computational steps
@@
     \begin{align*} 
-    \minimize & \|A(z)x - b\|^2 + \eta_1\|x - x_0\|^2\\
+    \minimize & \|A(z)x - b\|^2 + \eta_1\|x - x_\text{prev}\|^2\\
     \subto & z_\text{min} \le z \le z_\text{max}
@@
 \smallfig{1d_hardlimit}
-\I  Final  
+\I  Well-behaved, manufacturable $z$ (structure)
+\I  Final $x$ (field) accurately reproduced
+\I  Majority of elements of $z$ are fortuitously at one limit or the other!
 \nextpage
 
-\I  higher dimensions
-\myfig{2d_circ}{5}
-\myfig{25d_circ}{5}
+\I  Can be used to create 2D resonators
+\smallfig{2d_circ}
 \nextpage
 
-\oursection{Objective-first design of nanophotonic devices}
-\I  Next step in our thinking is that for most devices only some parts of the field matter
-\I  waveguiding devices
+\I  3D resonators can be designed using a ``2.5D'' approximation
+\smallfig{25d_circ}
+\nextpage
+
+\oursection{Objective-first design of linear devices}
+\I  Next realization: for linear components, 
+    only certain elements of $x$ (field) matter
+    \BI Specifically, the elements of $x$ at the input/output ports \EI
+    \begin{align*} 
+    \minimize & \|A(z)x - b\|^2 \\
+    \subto & x_\text{boundary} - \hat{x}_\text{boundary} = 0 \\
+        & z_\text{min} \le z \le z_\text{max}
+    \end{align*}
+\I  Instead of regularization term, we force the elements of $x$
+    at the boundary to be equal to the ideal case ($\hat{x}$)
+\nextpage
+
+\I  Applied to the design of 2D waveguide mode couplers
+\smallfig{ob1_explanation}
+\I  Produced designs which exhibited
+    \BI High efficiency ($\sim 98\%$)
+    \I  Small device footprints ($1.5-4$ square vacuum wavelengths) \EI
+\nextpage
+
+\I  Coupler to wide, low-index waveguide
 \medfig{ob1_wg}
+\nextpage
 
-\oursection{Design of 3D nanophotonic devices}
+\I  Coupler from fundamental to second-order waveguide mode
+\medfig{ob1_wg2}
+\nextpage
+
+\oursection{Design of 3D linear nanophotonic devices}
+\I  Finally, enough understanding to tackle the \emph{real} design problem
+\pause
+\I  Goal: Software to design \emph{all} linear nanophotonic devices
+\pause
+    \BI Fully three-dimensional (no approximations)
+    \I  Multi-mode
+    \I  Discrete, manufacturable structure \EI
+\nextpage
+
+\I  Problem: Did not know how to solve $A(z)x - b = 0$ (simulation) in 3D
+    \BI Millions of variables
+    \I  Famously ill-conditioned 
+    \I  No known commercial \emph{solvers} that can handle arbitrary structures \EI
+\pause
+\smallfig{wonseok}
+\I  Fortunately, Wonseok had already solved this problem
+
+\oursection{Maxwell: Light-simulation supercomputer}
+\I  Partnered with Wonseok to develop a cloud-based electromagnetic solver 
+    using Amazon Web Services 
+    \BI GPU-accelerated implementation of Wonseok's algorithm
+    \I  Cluster scales automatically to tens of nodes \EI
+\nextpage
+
+\I  Scalable
+    \BI Far outstrips computing clusters such as Teragrid
+    \I  Can perform multiple solves in parallel, on a single Matlab instance 
+    \I  All computation is performed externally (in the cloud) \EI
+
+\I  Easy to use
+    \BI Installs with a single Matlab command
+    \I  Solves completed with a single Matlab command: \verb+maxwell(...);+ \EI
+
+\I  The key technological enabler ...
 

### 2013-02-20 defense/pres2.tex
Getting there...

@@
     \BI A virtually uncountable number 
-    \I  Can only be design by a computer \EI
+    \I  Can only be leveraged computationally \EI
 \nextpage
@@
 \smallfig{takeaway}
-\I  Our work: Software to design full 3D, multi-mode, and multi-functional
-    linear nanophotonic devices---using the fully available parameter space \pause
+\I  Our work: Software to design 3D linear nanophotonic devices using 
+    the full available parameter space \pause
 \I  Many of these devices are
@@
 
+\I  Called \emph{objective-first} design because the design objective 
+    is prioritized above the physics residual
+    \begin{align*} 
+    \minimize & \|A(z)x - b\|^2 \\
+    \subto & x_\text{boundary} - \hat{x}_\text{boundary} = 0 \\
+        & z_\text{min} \le z \le z_\text{max}
+    \end{align*}
+% \I  In contrast, the typical formulation is 
+%     \begin{align*} 
+%     \minimize & \|x_\text{boundary} - \hat{x}_\text{boundary}\|^2 \\
+%     \subto & A(z)x - b  = 0 \\
+%         & z_\text{min} \le z \le z_\text{max}
+%     \end{align*}
+\nextpage
+
 \I  Applied to the design of 2D waveguide mode couplers
@@
     \I  Multi-mode
-    \I  Discrete, manufacturable structure \EI
+    \I  Discrete, planar, manufacturable structure \EI
 \nextpage
@@
     \I  Cluster scales automatically to tens of nodes \EI
+\smallfig{maxwell}
 \nextpage
@@
 
-\I  The key technological enabler ...
+\I  The key technological enabler in achieving 3D design
+\nextpage
+
+\oursection{3D design: problem statement}
+\begin{align*}
+    \minimize & \sum_i^M \|A_i(z)x_i - b_i\|^2 \\
+    \subto & \alpha_{ij} \le |c_{ij}\T x_i| \le \beta_{ij}, \quad
+        \text{for $i = 1, \ldots, M$ and $j = 1, \ldots, N_i$} \\
+        &   z_\text{min} \le z \le z_\text{max}
+\end{align*}
+\I  $M$ modes with $N_i$ monitored output modes each
+    \BI $b_i$ is the input excitation for each mode
+    \I  $|c_{ij}\T x_i|$ is the field overlap with output mode $c_{ij}$
+    \I  $\alpha_{ij}$ and $\beta_{ij}$ is the design range for the overlap \EI
+\nextpage
+
+\I  Show input and output modes here as explanation of problem statement
+\I  Use 3D model of wgc_te as example.
+\nextpage
 

### 2013-02-20 defense/vis3d/gen/Pradcap.m

@@ -1,0 +1,87 @@
+% [grid] = Pradcap (grid, direction, distance, buffer, gid)
+% direction - zcap, zcapn, zbox, zcenter
+% distance - distance from bottom to set cut off for zcap,box
+% buffer - buffer from PML, should be > PML _thick+2
+% gid - aanlytics with same gid are summed together
+%
+function [grid] = Pradcap(grid,direction,distance,buffer,gid)
+dims = [grid.info.xx grid.info.yy grid.info.zz];
+
+if (strcmp(direction, 'zcap'))
+	ps = [buffer buffer dims(3)-buffer; dims(1)-buffer dims(2)-buffer dims(3)-buffer];
+	grid = Pradplane(grid,ps,'+z',gid);
+	ps = [buffer buffer distance; dims(1)-buffer buffer dims(3)-buffer];
+	grid = Pradplane(grid,ps,'-y',gid);
+	ps = [buffer dims(2)-buffer distance; dims(1)-buffer dims(2)-buffer dims(3)-buffer];
+	grid = Pradplane(grid,ps,'+y',gid);
+	ps = [buffer buffer distance; buffer dims(2)-buffer dims(3)-buffer];
+	grid = Pradplane(grid,ps,'-x',gid);
+	ps = [dims(1)-buffer buffer distance; dims(1)-buffer dims(2)-buffer dims(3)-buffer];
+	grid = Pradplane(grid,ps,'+x',gid);
+elseif(strcmp(direction, 'zcapn'))
+	ps = [buffer buffer buffer; dims(1)-buffer dims(2)-buffer buffer];
+	grid = Pradplane(grid,ps,'-z',gid);
+	ps = [buffer buffer buffer; dims(1)-buffer buffer distance];
+	grid = Pradplane(grid,ps,'-y',gid);
+	ps = [buffer dims(2)-buffer buffer; dims(1)-buffer dims(2)-buffer distance];
+	grid = Pradplane(grid,ps,'+y',gid);
+	ps = [buffer buffer buffer; buffer dims(2)-buffer distance];
+	grid = Pradplane(grid,ps,'-x',gid);
+	ps = [dims(1)-buffer buffer buffer; dims(1)-buffer dims(2)-buffer distance];
+	grid = Pradplane(grid,ps,'+x',gid);
+elseif (strcmp (direction, 'zbox'))
+	ps = [buffer buffer 1; dims(1)-buffer buffer distance];
+        grid = Pradplane(grid,ps,'-y',gid);
[…]

### 2013-02-20 defense/vis3d/gen/changepath.m

@@ -1,0 +1,2 @@
+% just a small script to change path in matlab
+path (path, genpath('../alpha-release'));

### 2013-02-20 defense/vis3d/gen/erbL3.m

@@ -1,0 +1,126 @@
+function [grid] = erbL3 (filename)
+
+% first, create the grid itself
+total_time = 10000;
+tt = total_time;
+gx = 308;
+gy = 212;
+gz = 102;
+grid = create_grid ([gx gy gz], tt);
+Qanaltime = 500;
+pml_thick = 5;
+Siindex = 3.5^2;
+SiNindex = 2.0^2;
+% put in a cylinder of dielectric constant 4
+%[mid0, grid] = new_material (grid, 'simple_dielectric', [1.0]);
+%[mid1, grid] = new_material (grid, 'simple_dielectric', [slabindex]);
+slab = 12/2;
+a = 20;
+r = 6;
+offset = a/2;
+center = [grid.info.xx, grid.info.yy, grid.info.zz]/2;
+grid = draw_slab_corner (grid, [1 1 round(grid.info.zz/2)-slab-slab/2], [grid.info.xx grid.info.yy slab*2.0001], Siindex);
+grid = draw_slab_corner (grid, [1 1 round(grid.info.zz/2)+slab/2], [grid.info.xx grid.info.yy slab], SiNindex);
+count = 0;
+
+p1 = 5;
+p2 = 4;
+x1 = 6;
+x2 = 2;
+y1 = 6;
+y2 = 0;
+di = [1 2 3 0 4	-1 5		0 1 2 3 4 5		-1 0 1 2 3 4]-2 ;
+dj = [7 7 7 7 7 7 7		6 6 6 6 6 6		8 8 8 8 8 8]-7;
+rd = [0 0 0 p1 p1 x1 x1		y1 y1 y1 y1 y1 y1	y1 y1 y1 y1 y1 y1];
+xd = [0 0 0 -p2 p2 -x2 x2	0 0 0 0 0 0		0 0 0 0 0 0];
+yd = [0 0 0 0 0 0 0		-y2 -y2 -y2 -y2 -y2 -y2	y2 y2 y2 y2 y2 y2];
+
+
+fprintf ('cylinders: '); tic
+    for i = -20:20
+        for j = -20:20;
+             centerx = i*a+j*a/2+center(1);
+             centery = round(j*sqrt(3)/2*a)+center(2);
+            if ((centerx > r+pml_thick+1) && (centerx < gx-r-pml_thick-1) && (centery > r+pml_thick+1) && (centery < gy-r-pml_thick-1))
+                count = count + 1;
+		% check if the special guy is in the special thing
[…]

### 2013-02-20 defense/vis3d/gen/field_3D.m

@@ -1,0 +1,73 @@
+% plot the fields in 3D in a pretty way
+function [] = field_3D (epsilon, field, params, T, eps_alpha)
+close all
+field = field{1}.^2 + field{2}.^2 + field{3}.^2;
+dims = my_plot_epsilon (epsilon, 6, 0, eps_alpha);
+% my_plot_field (abs (field), [2, 10, 1, 1.8, 1e-5], 0);
+my_plot_field (abs (field), params, 0);
+my_make_pretty (dims);
+view (T);
+
+
+function [dims] = my_plot_epsilon (A, mat_index, skim, alpha)
+s = skim+1;
+dims = size (A);
+A = A (s:dims(1)-(s+1), s:dims(2)-(s+1), s:dims(3)-(s+1));
+
+order = [2 1 3];
+v = permute (A, order);
+dims = size (v);
+[x y z] = meshgrid (1:dims(2), 1:dims(1), 1:dims(3));
+
+hpatch = patch(isosurface(x,y,z,v, mat_index));
+isonormals(x,y,z,v,hpatch)
+set(hpatch,'FaceAlpha', alpha, 'FaceColor',120*[1 1 1]./255,'EdgeColor','none')
+
+
+
+function [] = my_plot_field (A, params, skim)
+
+if (params(3) <= 0) % fully transparent, don't plot anything
+	return
+end
+% get the colormap
+cmap = colormap ('winter');
+% cmap = cmap (24:64,:); % leave out dark colors
+cmap = cmap(54:-1:10,:);
+cmap = cmap (size (cmap,1):-1:1, :);
+
+% format the values matrix
+A = squeeze(A);
+dims = size(A);
+s = skim+1;
+A = A (s:dims(1)-(s+1), s:dims(2)-(s+1), s:dims(3)-(s+1));
+
+% set the colors and transparencies for different layers
+index = params(2) * params(3).^ (-params(1):0)
+alpha_index = params (4) * params(5) .^ (-params(1):0);
+
+order = [2 1 3];
+v = permute (A, order);
+dims = size (v);
+[x y z] = meshgrid (1:dims(2), 1:dims(1), 1:dims(3));
+
+for cnt = 1 : length (index)
+	hpatch = patch(isosurface(x,y,z,v, index (cnt)));
+	isonormals(x,y,z,v,hpatch)
[…]

### 2013-02-20 defense/vis3d/gen/special_plot.m

@@ -1,0 +1,68 @@
+function [m] = plot_slice_movie (slice, delay, rescale_factor, epsilon, eps_alpha)
+log_on = 0;
+skip = 1;
+skim = 0;
+moviename = 'none';
+dims = size (slice);
+slice = slice (skim+1:dims(1)-skim, skim+1:dims(2)-skim, :);
+
+% alpha_data
+adata = (epsilon-1) ./ max(max(epsilon));
+
+fig = figure;
+if (strcmp (moviename, 'none') == 0)
+	set (fig, 'DoubleBuffer', 'on');
+       % set(gca,'xlim',[-80 80],'ylim',[-80 80],'NextPlot','replace','Visible','off')
+       % set(gca,'NextPlot','replace','Visible','off')
+	%mov=avifile (moviename,'fps',15,'quality',100, 'compression', 'none');
+	movie = 1;
+else
+	movie = 0;
+end
+close all
+d = size (slice);
+% slice=reshape(slice, [d(3) d(2) d(1)]);
+tmax=length(slice(1,1,:));
+if log_on==1
+    cmax=20*log10(max(max(max(abs(slice)))));
+    if (cmax == Inf || cmax == NaN)
+    	cmax = 100;
+	cmax
+    end
+    cmax
+    % cmax = 100;
+    cmin=-200;
+else
+    cmax=max(max(max(abs(slice))))/rescale_factor;
+    cmin=-cmax;
+end
+
+caxis([cmin cmax]);
+% colorbar
+axis([1 length(slice(1,:,1))-1 1 length(slice(:,1,1))]);
+hold on
+cnt = 0;
+for t = 1 : skip : tmax
+    cla
+    cnt = cnt + 1;
+    if log_on==1
+        h = imagesc (20*log10(abs(slice(:,:,t)')));
+    else
+        % h = imagesc (slice(:,:,t)');
+	% h = imagesc (slice(:,:,t)', 'AlphaData', (1-eps_alpha) + eps_alpha*(adata'));
+	h = imagesc (slice(:,:,t)', 'AlphaData', eps_alpha + (1-eps_alpha)*(adata'));
+    end
+    axis equal
+    axis tight
+set (gcf, 'WindowStyle', 'docked');
+	if (movie == 1)
+	% set (h, 'EraseMode', 'xor');
+    m(t)=getframe;
+    % mov=addframe(mov,F);
+    end
+    pause(delay);
+end
+return
+%if (movie == 1)
+%mov=close(mov);
+%end

### 2013-02-20 defense/vis3d/gen/viz_simple.m

@@ -1,0 +1,13 @@
+% simple view of epsilons
+function [] = viz_simple (grid, z, c)
+
+titletext = {'\epsilon_x', '\epsilon_y', '\epsilon_z'};
+for cnt = 1 : length (z)
+	for i = 1 : 3
+		subplot (1, 3, i);
+		imagesc (grid.epsilon{i}(:,:,z(cnt))', c);
+		title ([titletext{i} ' (' num2str(z(cnt)) ')']);
+		axis equal tight
+	end
+	pause
+end

### 2013-02-20 defense/vis3d/vis_3D_epsilon.m

@@ -1,0 +1,33 @@
+function [dims] = vis_3D_epsilon(A, mat_index, skim, alpha)
+    s = skim+1;
+    dims = size (A);
+    A = A(:,dims(2):-1:1,:);
+    A([1:s, dims(1)-(s+1):dims(1)],:,:) = 0;
+    A(:,[1:s, dims(2)-(s+1):dims(2)],:) = 0;
+
+    order = [2 1 3];
+    v = permute (A, order);
+    dims = size (v);
+    [x y z] = meshgrid (1:dims(2), 1:dims(1), 1:dims(3));
+
+    hpatch = patch(isosurface(x,y,z,v, mat_index));
+    isonormals(x,y,z,v,hpatch)
+    set(hpatch,'FaceAlpha', alpha, 'FaceColor',120*[1 1 1]./255,'EdgeColor','none')
+
+    my_make_pretty(dims);
+
+function my_make_pretty (dims)
+    grid on
+    daspect([1,1,1])
+    axis tight
+    camlight left; lighting phong
+    % make it more visually intuitive
+    axis tight
+    axis ([0 dims(2) 0 dims(1) 0 dims(3)]);
+    H = gcf; % get the current figure handle
+    % set (H, 'WindowStyle', 'normal', 'OuterPosition', [100 100 640 480] + [0 0 10 29], 'MenuBar', 'none', 'ToolBar', 'none'); % set the location and size of the window
+    set (H, 'WindowStyle', 'docked');
+    view(0, 45);
+    grid off;
+
+

### 2013-02-21 defense/vis3d/vis_3D_epsilon.m
Added 3D pictures.

@@ -1,4 +1,4 @@
-function [dims] = vis_3D_epsilon(A, mat_index, skim, alpha)
+function vis_3D_epsilon(A, mat_index, skim, alpha)
     s = skim+1;
     dims = size (A);
     A = A(:,dims(2):-1:1,:);
@@ -14,13 +14,16 @@ function [dims] = vis_3D_epsilon(A, mat_index, skim, alpha)
     isonormals(x,y,z,v,hpatch)
     set(hpatch,'FaceAlpha', alpha, 'FaceColor',120*[1 1 1]./255,'EdgeColor','none')
 
-    my_make_pretty(dims);
+    my_make_pretty(dims, alpha);
 
-function my_make_pretty (dims)
+function my_make_pretty (dims, alpha)
+
     grid on
     daspect([1,1,1])
     axis tight
-    camlight left; lighting phong
+    if alpha == 1 % If alpha not equal to 1, don't add lighting
+        camlight left; lighting phong
+    end
     % make it more visually intuitive
     axis tight
     axis ([0 dims(2) 0 dims(1) 0 dims(3)]);
@@ -29,5 +32,6 @@ function my_make_pretty (dims)
     set (H, 'WindowStyle', 'docked');
     view(0, 45);
     grid off;
+    set(gca, 'XTick', [], 'YTick', [], 'ZTick', [], 'Visible', 'off')
 
 

### 2013-02-21 defense/vis3d/visall3D.m

@@ -1,0 +1,25 @@
+function visall3D(vis_dir)
+    d = dir(vis_dir);
+    names = {};
+    for i = 1 : length(d)
+        if d(i).isdir & ~isempty(find(d(i).name ~= '.')) & ...
+                    isempty(strfind(d(i).name, '2D')) & ...
+                    ~isempty(strfind(d(i).name, 'verify'))
+            names{end+1} = d(i).name;
+        end
+    end
+
+    for i = 1 : length(names)
+        try
+            data = load([vis_dir, names{i}, filesep, 'epsz.mat']);
+            epsilon = data.eps_z;
+            close all
+            vis_3D_epsilon(epsilon, 7.25, 0, 1)
+%             if ~isempty(strfind(names{i}, 'fib')) % Need to draw fiber.
+%                 epsilon(:,:,1:41) = 2.25;
+%                 vis_3D_epsilon(epsilon, 2.45, 0, 1);
+%             end
+            print('-dpng', '-r200', [vis_dir, names{i}, filesep, '3D']);
+        end
+    end
+    

### 2013-02-22 defense/pres2.tex
Added fib pics.
Added 3D pictures.

@@
 \oursection{Direct design with regularization}
+\stepwise{
 \I  Direct design ``works'' but not practical
     \BE \minimize_z \|A(z)x - b\|^2 \EE
-\I  So, let's add a \emph{regularization} term to $z$ and solve the following instead 
-    \BE \minimize_z \|A(z)x - b\|^2 + \eta\|z-z_0\|^2 \EE
-    \BI  $\|z-z_0\|^2$ term keeps $z$ close to $z_0$
+\step{\I  So, let's add a \emph{regularization} term to $z$ and solve the following instead 
+    \BE \minimize_z \|A(z)x - b\|^2 + \eta\|z-z_0\|^2 \EE}
+    \step{\BI  $\|z-z_0\|^2$ term keeps $z$ close to $z_0$
     \I  $\eta$ controls the strength of the regularization \EI
-\I  Solution can still be computed in one step
+
+\I  Solution can still be computed in one step}
+}
 \nextpage
@@
 \I  New algorithm: Iteratively solve for $x$ (field) and $z$ (structure)
+    \pause
     \begin{align*} 
@@
     \end{align*}
+    \pause
 \I  Takes advantage of the \emph{bi-linearity} of the physics residual
@@
 \I  We can also put hard limits on $z$ (structure)
+    \pause
     \begin{align*} 
@@
     \end{align*}
+    \pause
 \I  $z_\text{min} \le z \le z_\text{max}$ constraint 
@@
 \oursection{Objective-first design of linear devices}
+\stepwise{
 \I  Next realization: for linear components, 
     only certain elements of $x$ (field) matter
-    \BI Specifically, the elements of $x$ at the input/output ports \EI
+\step{\BI Specifically, the elements of $x$ at the input/output ports \EI}
+\step{
     \begin{align*} 
@@
     \end{align*}
+}
+\step{
 \I  Instead of regularization term, we force the elements of $x$
-    at the boundary to be equal to the ideal case ($\hat{x}$)
+    at the boundary to be equal to the ideal case ($\hat{x}$)}
+}
 \nextpage
@@
     \I  All computation is performed externally (in the cloud) \EI
-
+\pause
 \I  Easy to use
@@
     \I  Solves completed with a single Matlab command: \verb+maxwell(...);+ \EI
-
+\pause
 \I  The key technological enabler in achieving 3D design
@@
 \oursection{3D design: problem statement}
+\stepwise{
+    \step{
 \begin{align*}
@@
 \end{align*}
-\I  $M$ modes with $N_i$ monitored output modes each
-    \BI $b_i$ is the input excitation for each mode
+    }
+\step{
+\I  $M$ modes with $N_i$ monitored output modes each}
+    \step{\BI $b_i$ is the input excitation for each mode
     \I  $|c_{ij}\T x_i|$ is the field overlap with output mode $c_{ij}$
-    \I  $\alpha_{ij}$ and $\beta_{ij}$ is the design range for the overlap \EI
+    \I  $\alpha_{ij}$ and $\beta_{ij}$ is the design range for the overlap \EI}
+}
 \nextpage
 
-\I  Show input and output modes here as explanation of problem statement
-\I  Use 3D model of wgc_te as example.
+\medfig{3D_wgc_te}
+\I  Input mode is excited using current source ($b_i$ or $-i\omega J$)
+\I  Output mode is enforced using overlap integrals
+    ($c_{ij}\T x_i$ or $\int \hat{E_{ij}} E$)
 \nextpage
 
+% \oursection{Structure of 3D designs}
+% \I  250 nm silicon slab surrounded by silica
+
+\I TE mode converter
+\smallfig{takeaway}
+\I  Efficiency: 86.4\%
+\I  Power in rejection mode (transmitted fundamental): 0.7\%
+\I  250 nm silicon slab surrounded by silica
+\newpage
+
+\medfig{3D_wgc_tm}
+\nextpage
+
+\I TM mode converter
+\smallfig{wgc_tm}
+\I  Efficiency: 76.9\%
+\I  Power in rejection mode (transmitted fundamental): 1.0\%
+\newpage
+
+\medfig{3D_spl_modal}
+\nextpage
+
+\I  Spatial mode splitter
+\BI  Efficiency: 88.7\%, 77.4\% (0.27\%, 0.20\%) \EI
+\medfig{spl_modal}
+\newpage
+
+\medfig{3D_spl_tetm}
+\nextpage
+
+\I  TE/TM splitter
+\BI  Efficiency: 87.6\%, 88.8\% (1.06\%, 0.58\%) \EI
+\medfig{spl_tetm}
+\newpage
+
+\medfig{3D_spl_wdm}
+\nextpage
+
+\I  Wavelength splitter
+\BI  Efficiency: 83.2\%, 78.7\% (0.49\%, 1.66\%) \EI
+\medfig{spl_wdm}
+\newpage
+
+\medfig{3D_hub_3x3}
+\nextpage
+
+\I 3x3 hub (88.6\%, 90.6\%, 87.3\% efficiency)
+\bigfig{hub_3x3}
+\newpage
+
+\medfig{3D_hub_4x4}
+\nextpage
+
+\I 4x4 hub
+\bigfig{hub_4x4_eps}
+\newpage
+
+\I Efficiency: 85.9\%, 88.1\%, 85.4\%, 84.3\%
+\bigfig{hub_4x4}
+\newpage
+
+\medfig{3D_hub_2x2x2}
+\nextpage
+
+\I 2x2x2 hub (77.6\%, 73.7\%, 75.7\%, 75.2\% efficiency)
+\bigfig{hub_2x2x2}
+\newpage
+
+\medfig{3D_fib_te}
+\nextpage
+
+\I fiber coupler (51.5\%)
+\medfig{fib_te}
+\newpage
+
+\medfig{3D_fib_pol}
+\nextpage
+
+\I fiber coupler mode splitter (32.6\%, 22.7\%)
+\bigfig{fib_pol}
+\newpage
+
+\medfig{3D_fib_wdm}
+\nextpage
+
+\I fiber coupler wdm (31.6\%, 28.6\%)
+\bigfig{fib_wdm}
+\newpage
 \EI

### 2013-02-23 defense/pres3.tex
Starting on final pres.

--- 2013-02-22 defense/pres2.tex
@@
 \newcommand{\nextpage}{\vfill\newpage}
+
 \renewcommand{\oursection}[1]{
@@
 }
+
+\newcommand{\smalltitle}[1]{
+    \begin{center}{\large #1}\end{center}
+}
+
 \newcommand{\myfig}[2]{
@@
 \maketitle
+\begin{itemize} \itemsep -1pt
+\I  Introduction
+\I  Summary
+\I  Incremental results
+\I  Final result
+\EI
 
@@
 \pause
-\I  What happens when we use the \emph{full} parameter space
-    for nanophotonic design?
+\I  Our idea: Design using \emph{all} available parameters
+    \BI If successful, full-parameter design \emph{guarantees} better devices 
+    \I  i.e. We can do better by using \emph{all} the design parameters \EI
+
 \nextpage
 
-\I  The full parameter space is \emph{vast}
+% \I  The full parameter space for nanophotonic design is \emph{vast}
+% \I  How big is the full design space for nanophotonic devices?
+\I The number of available design parameters for nanophotonic devices
+    is \emph{enormous}
 \smallfig{des_complexity}
+\pause
 \I  Include/exclude per pixel gives us $2^{(15^2)} = 2^{225}$ possibilities
-    \BI A virtually uncountable number 
-    \I  Can only be leveraged computationally \EI
+    \BI $2^{225} = 67$-digit number, uncountable \EI
+\pause
+\I  Realization: Hand-tuning won't work for full-parameter design
 \nextpage
 
+\I  Full-parameter design must be \emph{design-by-description}
+\pause
+\begin{verbatim}
+\\ Human describe here.
+device mux2 
+    in: {freq1, freq2}
+    out1 <= freq1
+    out2 <= freq2
+\end{verbatim}
+\pause
+\smallfig{thesolution}
+\nextpage
+
+\I  Realization: Design-by-description is \emph{extremely powerful}
+\pause
+    \BI The description (or function) of all useful devices is known
+    \I  Therefore, design-by-description will allow us to design \emph{everything} 
+    \EI
+\pause
+\I  Assumes that design-by-description can actually be made to work
+\pause
+\I  Our goal: Make it work
+
+\nextpage
+
+\oursection{Summary}
 \smallfig{takeaway}
@@
     the full available parameter space \pause
+\nextpage
+
 \I  Many of these devices are
@@
     \I  High efficiency ($>80\%$ transmission) \EI
-\nextpage
+\pause
 
@@
 \pause
+
 \I  Physics Advisory: 
     \begin{quote}CONTAINS INVOLVED MATHEMATICAL CONTENT\end{quote}
-\pause
-\I  Math Advisory: 
-    \begin{quote}CONTAINS INVOLVED NANOPHOTONIC CONTENT\end{quote}
 \nextpage

### 2013-02-23 defense/pres3.tex
Getting there...

@@
     \BI The description (or function) of all useful devices is known
-    \I  Therefore, design-by-description will allow us to design \emph{everything} 
+    \I  Therefore, design-by-description enables the design of \emph{everything} 
     \EI
 \pause
-\I  Assumes that design-by-description can actually be made to work
+\I  Assumption: Design-by-description can actually be made to work
 \pause
-\I  Our goal: Make it work
+\I  Our goal: Make it work!
 
@@
 \smallfig{takeaway}
-\I  Our work: Software to design 3D linear nanophotonic devices using 
-    the full available parameter space \pause
+\I  Our work: Designed 3D linear nanophotonic devices
+    \BI Using the full parameter space
+    \I  Using design-by-description \EI
 \nextpage
@@
     \I  Extremely compact (footprints of a few vacuum wavelengths)
-    \I  High efficiency ($>80\%$ transmission) \EI
+    \I  High efficiency ($>80\%$ transmission) 
+    \I  Manufacturable \EI
 \pause
 
-\I  Developed by
+\I  Our approach:
     \BI applying (convex) optimization techniques (math)
@@
 
-\oursection{Given a field, can we find its structure?}
+\oursection{Given a field, can we find its device/structure?}
 \smallfig{my_definition}
@@
     \BE \nabla\times\mu_0^{-1}\nabla\times E - \omega^2 \epsilon E = 
-        -i \omega J \EE}
-\step{\I  If possible, we can design \emph{any} nanophotonic/optical component!}
+        -i \omega J \EE
+where $\epsilon = \vec{\epsilon}(r), E=\vec{E}(r), J = \vec{J}(r)$}
 }
@@
 
-\I Answer: Yes, given $E$ we \emph{can} solve for $\epsilon$ (trivial!)
+\oursection{Given a field, can we find its device/structure?}
+\I  Answer: Yes, given $E$ we \emph{can} solve for $\epsilon$ (trivial!) \\
     \stepwise{
@@
     \end{align*}
+    (Reminder, $\epsilon = \vec{\epsilon}(r), E=\vec{E}(r), J = \vec{J}(r)$)
+\step{
+\I  Solving for $\epsilon$ actually way faster than simulation (solving for $E$)!
 }
-\I  Solving for $\epsilon$ actually way faster than simulation (solving for $E$)!
+
+    }
 \nextpage
@@
 \pause
-\I  Result
-    \BI Perfect performance
-    \I  But unmanufacturable structure ($z$ not well-behaved) \EI
+
+\let\thefootnote\relax\footnotetext{Footnotetext without footnote mark} 
+\I  Result\footnote{Lu et al, Optics Express (2010)}: 
+    Perfect performance, but unmanufacturable structure ($z$)
 \nextpage

### 2013-02-24 defense/pres3.tex
Getting there...

@@
 \usepackage[display]{texpower}
+
+% No mark footnotes.
+\let\thefootnote\relax
 
@@
 
+\footnotetext{J. Lu, J. Vuckovic, Optics Express (2010)}
 \I  Choose canonical 1D cavity field for $x$
@@
 \pause
-
-\let\thefootnote\relax\footnotetext{Footnotetext without footnote mark} 
-\I  Result\footnote{Lu et al, Optics Express (2010)}: 
-    Perfect performance, but unmanufacturable structure ($z$)
+\I  Result: Perfect performance, but unmanufacturable structure ($z$)
 \nextpage
@@
 
-\bigfig{1d_regularized_12}
+\myfig{1d_regularized_12}{11.5}
 \I  Unfortunately, regularization on $z$ decreases performance 
+\footnotetext{J. Lu, J. Vuckovic, Optics Express (2010)}
 \nextpage
@@
 \I  Decreased performance a result of non-zero physics residual at optimum
+\footnotetext{J. Lu, J. Vuckovic, Optics Express (2010)}
 \nextpage
@@
     \I  more accurately produces $x$ \EI
+\footnotetext{J. Lu, J. Vuckovic, Optics Express (2010)}
 \nextpage
@@
 \I  Majority of elements of $z$ are fortuitously at one limit or the other!
+\footnotetext{J. Lu, J. Vuckovic, Optics Express (2010)}
 \nextpage
@@
 \smallfig{2d_circ}
+\footnotetext{J. Lu, J. Vuckovic, Optics Express (2010)}
 \nextpage
@@
 \smallfig{25d_circ}
+\footnotetext{J. Lu, S. Boyd, J. Vuckovic, Optics Express (2011)}
 \nextpage
@@
     \I  Small device footprints ($1.5-4$ square vacuum wavelengths) \EI
+\footnotetext{J. Lu, J. Vuckovic, Optics Express (2012)}
 \nextpage
@@
 \medfig{ob1_wg}
+\footnotetext{J. Lu, J. Vuckovic, Optics Express (2012)}
 \nextpage
@@
 \medfig{ob1_wg2}
+\footnotetext{J. Lu, J. Vuckovic, Optics Express (2012)}
 \nextpage
@@
     \I  Discrete, planar, manufacturable structure \EI
+\footnotetext{D. A. B. Miller, ``All linear optical devices are mode converters,''
+    Optics Express (2012)}
 \nextpage
@@
 \I  Fortunately, Wonseok had already solved this problem
+\footnotetext{W. Shin, S. Fan, ``Choice of the perfectly matched layer boundary condition for frequency-domain Maxwell’s equations solvers,'' J. Comp. Phys. (2012)}
 

### 2013-02-24 defense/pres3.tex
Closer...

@@
 \newcommand{\nextpage}{\vfill\newpage}
-
+\newcommand{\bold}{\textbf}
 \renewcommand{\oursection}[1]{
@@
 }
+\newcommand{\threeDfig}[1]{
+    \begin{figure}[!h]
+    \centerline{\includegraphics[width=20cm]{fig/#1.jpg}}
+    \end{figure}
+}
 \newcommand{\BI}{\begin{itemize}\item}
@@
 \maketitle
-\begin{itemize} \itemsep -1pt
-\I  Introduction
-\I  Summary
-\I  Incremental results
-\I  Final result
-\EI
-
-% \BIT \itemsep -1pt
-% \item motivation
-% \item theory
-% \item results
-% \EIT
-
+% \begin{itemize} \itemsep -1pt
+% \I  Introduction
+% \I  Summary
+% \I  Incremental results
+% \I  Final result
+% \EI
 \nextpage
@@
 \pause
-\I  Our idea: Design using \emph{all} available parameters
+\I  \bold{Our idea}: Design using \emph{all} available parameters
     \BI If successful, full-parameter design \emph{guarantees} better devices 
@@
 \pause
-\I  Realization: Hand-tuning won't work for full-parameter design
+\I  \bold{Realization}: Hand-tuning won't work for full-parameter design
 \nextpage
@@
 
-\I  Realization: Design-by-description is \emph{extremely powerful}
+\I  \bold{Realization}: Design-by-description is \emph{extremely powerful}
 \pause
@@
 \pause
-\I  Assumption: Design-by-description can actually be made to work
+\I  \bold{Assumption}: Design-by-description can actually be made to work
 \pause
-\I  Our goal: Make it work!
+\I  \bold{Our goal}: Make it work!
 
@@
 \smallfig{takeaway}
-\I  Our work: Designed 3D linear nanophotonic devices
+\I  Designed 3D linear nanophotonic devices
     \BI Using the full parameter space
@@
 
-\I  Our approach:
+\I  \bold{Our approach}:
     \BI applying (convex) optimization techniques (math)
@@
 \oursection{Given a field, can we find its device/structure?}
-\I  Answer: Yes, given $E$ we \emph{can} solve for $\epsilon$ (trivial!) \\
+\I  \bold{Answer}: Yes, given $E$ we \emph{can} solve for $\epsilon$ (trivial!) \\
     \stepwise{
@@
     }
-\step{\I  Key: If $A(z)$ is linear in $z$ then $A(z)x=b$ is as well!}
+\step{\I  \bold{Key}: If $A(z)$ is linear in $z$ then $A(z)x=b$ is as well!}
     }
@@
 \pause
-\I  Result: Perfect performance, but unmanufacturable structure ($z$)
+\I  \bold{Result}: Perfect performance, but unmanufacturable structure ($z$)
 \nextpage
@@
 
+\I  \bold{Regularized direct solve result}: decreased performance
 \myfig{1d_regularized_12}{11.5}
-\I  Unfortunately, regularization on $z$ decreases performance 
 \footnotetext{J. Lu, J. Vuckovic, Optics Express (2010)}
@@
 
-\I  How to overcome the apparent trade-off between manufacturability ($z$)
-    and performance ($x$)?
+\I  \bold{Problem}: How to overcome the apparent trade-off 
+    between manufacturability ($z$) and performance ($x$)?
 \pause
@@
 \oursection{Iterative design of nanophotonic devices}
-\I  New algorithm: Iteratively solve for $x$ (field) and $z$ (structure)
+\I  \bold{New algorithm}: Iteratively solve for $x$ (field) and $z$ (structure)
     \pause
@@
 
-\smallfig{1d_alternate}
-\I  Iterative strategy produces $z$ (structure) that 
+\I  \bold{Result of iterative strategy}: $z$ (structure) that 
     \BI is better behaved
     \I  more accurately produces $x$ \EI
+\smallfig{1d_alternate}
 \footnotetext{J. Lu, J. Vuckovic, Optics Express (2010)}
@@
 
+\I  \bold{Result of iterative design with hard constraints on $z$}:
+\BI Well-behaved, manufacturable $z$ (structure)
+\I  Final $x$ (field) accurately reproduced
+\I  Majority of elements of $z$ are fortuitously at one limit or the other \EI
 \smallfig{1d_hardlimit}
-\I  Well-behaved, manufacturable $z$ (structure)
-\I  Final $x$ (field) accurately reproduced
-\I  Majority of elements of $z$ are fortuitously at one limit or the other!
 \footnotetext{J. Lu, J. Vuckovic, Optics Express (2010)}
@@
 
-\I  Can be used to create 2D resonators
+\I  \bold{Extension}: Iterative design can be used to create 2D resonators as well
 \smallfig{2d_circ}
@@
 
-\I  3D resonators can be designed using a ``2.5D'' approximation
+\I  \bold{Extension}: 3D resonators can be designed using a ``2.5D'' approximation
 \smallfig{25d_circ}
+\myfig{25d_approx}{4}
 \footnotetext{J. Lu, S. Boyd, J. Vuckovic, Optics Express (2011)}
@@
     at the boundary to be equal to the ideal case ($\hat{x}$)}
+\footnotetext{D. A. B. Miller, ``All linear optical devices are mode converters,''
+    Optics Express (2012)}
 }
@@
 
-\I  Coupler to wide, low-index waveguide
+\I  \bold{2D objective-first result}: Coupler to wide, low-index waveguide
+    \BI Efficiency: 99.8\%
+    \I  Footprint: 1.5 square vacuum wavelengths \EI
 \medfig{ob1_wg}
@@
 
-\I  Coupler from fundamental to second-order waveguide mode
+\I  \bold{2D objective-first result}: Coupler to second-order waveguide mode
+    \BI Efficiency: 98.0\%
+    \I  Footprint: 1.5 square vacuum wavelengths \EI
 \medfig{ob1_wg2}
@@
 
-\oursection{Design of 3D linear nanophotonic devices}
+\oursection{Final result: Design of 3D linear nanophotonic devices}
 \I  Finally, enough understanding to tackle the \emph{real} design problem
 \pause
-\I  Goal: Software to design \emph{all} linear nanophotonic devices
+\I  \bold{Goal}: Software to design \emph{all} linear nanophotonic devices
 \pause
-    \BI Fully three-dimensional (no approximations)
+    \BI Design-by-description (objective-first)
+    \I  Uses the full parameter space
+    \I  High efficiency
+    \I  Fully three-dimensional (no approximations)
     \I  Multi-mode
     \I  Discrete, planar, manufacturable structure \EI
-\footnotetext{D. A. B. Miller, ``All linear optical devices are mode converters,''
-    Optics Express (2012)}
 \nextpage
 
-\I  Problem: Did not know how to solve $A(z)x - b = 0$ (simulation) in 3D
+\I  \bold{Problem}: Did not know how to solve $A(z)x - b = 0$ (simulation) in 3D
     \BI Millions of variables
@@
 \smallfig{wonseok}
-\I  Fortunately, Wonseok had already solved this problem
+\I  Fortunately, Wonseok Shin (Fan group) had already solved this problem
 \footnotetext{W. Shin, S. Fan, ``Choice of the perfectly matched layer boundary condition for frequency-domain Maxwell’s equations solvers,'' J. Comp. Phys. (2012)}
@@
 \oursection{Maxwell: Light-simulation supercomputer}
-\I  Partnered with Wonseok to develop a cloud-based electromagnetic solver 
-    using Amazon Web Services 
+\I  Partnered with Wonseok to develop electromagnetic solver-as-a-service 
     \BI GPU-accelerated implementation of Wonseok's algorithm
-    \I  Cluster scales automatically to tens of nodes \EI
+    \I  Cluster scales automatically in the cloud (Amazon Web Services)\EI
 \smallfig{maxwell}
@@
 
-\I  Scalable
+\I  Accuracy 
+    \BI Solves the frequency domain problem directly 
+    \I  Allows for precise input excitation and output monitoring \EI
+\pause
+\I  Scalability
     \BI Far outstrips computing clusters such as Teragrid
-    \I  Can perform multiple solves in parallel, on a single Matlab instance 
+    \I  Can perform multiple solves in parallel, from a single Matlab instance 
     \I  All computation is performed externally (in the cloud) \EI
 \pause
-\I  Easy to use
+\I  Ease-of-use
     \BI Installs with a single Matlab command
@@
 \pause
-\I  The key technological enabler in achieving 3D design
+\I  \bold{The key technological enabler in achieving 3D design}
 \nextpage
 
-\oursection{3D design: problem statement}
+\oursection{Final result: Problem statement}
 \stepwise{
@@
 
-\medfig{3D_wgc_te}
+\I  Problem statement in physics language
+\threeDfig{3Db_wgc_te}
 \I  Input mode is excited using current source ($b_i$ or $-i\omega J$)
@@
 
-% \oursection{Structure of 3D designs}
-% \I  250 nm silicon slab surrounded by silica
+\oursection{Final result: Method}
+\footnotetext{S. Boyd et al, Foundations and Trends in Machine Learning (2011)}
+\I  Objective-first problem solved using 
+    alternating directions method of moments (ADMM)
+    \BI Addition of dual variable greatly accelerates convergence \EI
+\pause
+\I  After objective-first solution
+    \BI $z$ is converted to boundary parameterization for manufacturability
+    \I  Steepest-descent used in secondary optimization step \EI
+\pause
+\I  Basic device structure:
+    \BI 250 nm silicon slab surrounded by silica
+    \I  Permittivity: 12.25 (Si), 2.25 (SiO$_2$) \EI
+\nextpage
+
+\oursection{Result 1: Mode converter (TE)}
+\threeDfig{3Db_wgc_te}
+% \I  Converts from fundamental TE (in-plane polarized) mode to 
+%     second-order mode
+\I  Performance description at output waveguide:
+    \BI Power in second-order mode: 90\% to 100\%
+    \I  Power in first-order mode: 0\% to 1\% (rejection) \EI
+\nextpage
 
@@
 
-\medfig{3D_wgc_tm}
+\threeDfig{3Db_wgc_tm}
 \nextpage
@@
 
-\medfig{3D_spl_modal}
+\threeDfig{3Db_spl_modal}
 \nextpage
@@
 
-\medfig{3D_spl_tetm}
+\threeDfig{3Db_spl_tetm}
 \nextpage
@@
 
-\medfig{3D_spl_wdm}
+\threeDfig{3Db_spl_wdm}
 \nextpage
@@
 
-\medfig{3D_hub_3x3}
+\threeDfig{3Db_hub_3x3}
 \nextpage
@@
 
-\medfig{3D_hub_4x4}
+\threeDfig{3Db_hub_4x4}
 \nextpage
@@
 
-\medfig{3D_hub_2x2x2}
+\threeDfig{3Db_hub_2x2x2}
 \nextpage
@@
 
-\medfig{3D_fib_te}
+\threeDfig{3Db_fib_te}
 \nextpage
@@
 
-\medfig{3D_fib_pol}
+\threeDfig{3Db_fib_pol}
 \nextpage
@@
 
-\medfig{3D_fib_wdm}
+\threeDfig{3Db_fib_wdm}
 \nextpage

### 2013-02-24 defense/pres3.tex
Even closer...

@@
     \EI
+\pause
+\I  Also, does not require nanophotonic expertise
 \pause
@@
 
-\I TE mode converter
+\I  Final design, with actual (simulated) field
 \smallfig{takeaway}
-\I  Efficiency: 86.4\%
-\I  Power in rejection mode (transmitted fundamental): 0.7\%
-\I  250 nm silicon slab surrounded by silica
+\I  Efficiency: 86.4\% (rejection: 0.7\%)
+\I  Discrepancy in efficiency likely due to evanescent modes
+\I  3D proof-of-principle for multi-mode on-chip components
+    \BI with \emph{extremely} small device footprints \EI
 \newpage
 
+\oursection{Result 2: Mode converter (TM)}
 \threeDfig{3Db_wgc_tm}
+\I  Analogous to previous result, but with opposite polarization
+\I  Demonstrates that we can work with (multiple) TM modes as well 
 \nextpage
 
-\I TM mode converter
+\I  Efficiency: 76.9\% (rejection: 1.0\%)
 \smallfig{wgc_tm}
-\I  Efficiency: 76.9\%
-\I  Power in rejection mode (transmitted fundamental): 1.0\%
+\I  Lower efficiency likely due to poor confinement of TM-polarized field
+\I  Previously not demonstrated in litterature
 \newpage
 
+\oursection{Result 3: Spatial mode splitter}
 \threeDfig{3Db_spl_modal}
+\I  Key component needed to achieve multi-mode on-chip optics
 \nextpage
 
-\I  Spatial mode splitter
-\BI  Efficiency: 88.7\%, 77.4\% (0.27\%, 0.20\%) \EI
+\I  Efficiency: 88.7\%, 77.4\% (rejection: 0.27\%, 0.20\%)
 \medfig{spl_modal}
+\I  Previous designs in 2D, first design in 3D
+\footnotetext{Y. Jiao, S. Fan, D. A. B.  Miller, Optics Letters (2005)}
 \newpage
 
+\oursection{Result 4: TE/TM splitter}
 \threeDfig{3Db_spl_tetm}
+\I  Shows that both polarizations can be controlled simultaneously
+\I  Never before demonstrated, existence somewhat doubtful
+
 \nextpage
 
-\I  TE/TM splitter
-\BI  Efficiency: 87.6\%, 88.8\% (1.06\%, 0.58\%) \EI
+\I  Efficiency: 87.6\%, 88.8\% (1.06\%, 0.58\%)
 \medfig{spl_tetm}
@@
 
+\oursection{Result 5: Wavelength splitter}
 \threeDfig{3Db_spl_wdm}
+\I  Splits 1550 nm and 1310 nm waveguide modes
+\I  Large wavelength separation allows for small device footprint
 \nextpage
 
-\I  Wavelength splitter
-\BI  Efficiency: 83.2\%, 78.7\% (0.49\%, 1.66\%) \EI
+\I  Efficiency: 83.2\%, 78.7\% (0.49\%, 1.66\%)
 \medfig{spl_wdm}
@@
 
+\oursection{Result 6: 3x3 hub}
 \threeDfig{3Db_hub_3x3}
+\I  Allows for overlapping ``optical traces''
+\I  First demonstration in a single device
 \nextpage
 
-\I 3x3 hub (88.6\%, 90.6\%, 87.3\% efficiency)
+\I  Efficiency: 88.6\%, 90.6\%, 87.3\%
 \bigfig{hub_3x3}
+\I  Rejection modes no longer used for computational efficiency 
 \newpage
 
+\oursection{Result 7: 4x4 hub}
 \threeDfig{3Db_hub_4x4}
+\I  Pop quiz: Can you guess which trace goes where?
 \nextpage
 
-\I 4x4 hub
+\I  Formulate answer as a 4-digit number 
 \bigfig{hub_4x4_eps}
@@
 
-\I Efficiency: 85.9\%, 88.1\%, 85.4\%, 84.3\%
+\I  Efficiency: 85.9\%, 88.1\%, 85.4\%, 84.3\% (Answer: 3241)
 \bigfig{hub_4x4}
@@
 
+\oursection{Result 8: 2x2x2 hub}
 \threeDfig{3Db_hub_2x2x2}
+\I  Demonstrates that switching mechanism can be separately engineered 
+    for different wavelengths (1550 nm and 1310 nm)
+\I  2x2x2 = 2 inputs, 2 outputs, and 2 wavelengths
 \nextpage
 
-\I 2x2x2 hub (77.6\%, 73.7\%, 75.7\%, 75.2\% efficiency)
+\I Efficiency: 77.6\%, 73.7\%, 75.7\%, 75.2\% 
 \bigfig{hub_2x2x2}
@@
 
+\oursection{Result 9: Compact fiber coupler}
 \threeDfig{3Db_fib_te}
+\I  Compact fiber core (2 um) used for computational efficiency
+    \BI Refractive indices of fiber: $n_\text{core} = 1.6$, 
+                                    $n_\text{cladding} = 1.5$ \EI
+\I  Membrane etched halfway to increase out-of-plane symmetry breaking
 \nextpage
 
-\I fiber coupler (51.5\%)
-\medfig{fib_te}
+\I  Efficiency: 51.5\%
+\smallfig{fib_te_short}
+\I  Highest efficiency compact fiber coupler
+\I  Compact: Device combines coupling and focusing functions
 \newpage
 
+\oursection{Result 10: Mode-splitting fiber coupler}
 \threeDfig{3Db_fib_pol}
+\I  Both couples and splits linear and circular polarizations
+    \BI 1310 nm wavelength used to make fiber multi-modal \EI
 \nextpage
 
-\I fiber coupler mode splitter (32.6\%, 22.7\%)
+\I Efficiency: 32.6\%, 22.7\%
 \bigfig{fib_pol}
@@
 
+\oursection{Result 11: Wavelength-splitting fiber coupler}
 \threeDfig{3Db_fib_wdm}
+\I  A fusion of result 9 (fiber coupler) and result 5 (wavelength splitter)
+\I  Shows the power of full-parameter design-by-description
 \nextpage
 
-\I fiber coupler wdm (31.6\%, 28.6\%)
+\I  Efficiency: 31.6\%, 28.6\%
 \bigfig{fib_wdm}
 \newpage
+
+\oursection{Results summary}
+\stepwise{
+\I  Variety of devices suggests all devices possible
+    \BI Converters: both TE and TM polarizations
+    \I  Splitters: spatial, polarization, wavelength
+    \I  Hubs: 3x3, 4x4, 2x2x2
+    \I  Fiber couplers: compact, mode-splitting, wavelength-splitting \EI
+\step{
+\I  Design-by-description is a key enabler
+    \BI All 11 final results achieved in only 3 weeks
+    \I  Of course, 7 years of development and 18 monts of programming\ldots \EI
+}
+\step{
+\I  Individual design runtimes between 8-80 hours
+    \BI Many future speedups possible at all levels \EI
+}}
+
+\oursection{One more thing\ldots}
+\pause
+\medfig{spl_wdm}
+\I  Let's revisit our wavelength splitter 
+\nextpage
+
 \EI

### 2013-02-24 defense/pres3.tex
Almost...

@@
     \BI All 11 final results achieved in only 3 weeks
-    \I  Of course, 7 years of development and 18 monts of programming\ldots \EI
+    \I  Of course, 7 years of development and 18 months of programming\ldots \EI
 }
@@
 \medfig{spl_wdm}
-\I  Let's revisit our wavelength splitter 
+\I  Let's revisit our wavelength splitter (result 5)
 \nextpage
 
+\I  Take original structure and perform a broadband wavelength analysis
+\threeDfig{analysis_spl_only}
+\pause
+\I  Analysis shows that broadband response can be improved
+\I  Already supported by our problem formulation
+    \BI Through the use of ``supermodes'' \EI
+\nextpage
+
+\I  Use 5 modes (instead of 1) at each central wavelength
+\threeDfig{analysis_top}
+\I  \bold{Result}: Use of 5-fold, spectrally-broad supermodes
+    produces broadband response 
+\nextpage
+
+\oursection{Result 12: Broadband wavelength splitter}
+\medfig{top_wdm_comp}
+\I  Broadband design uses original structure as starting point
+\nextpage
+
+\oursection{Result 12-1: Broadband splitter temperature dependence}
+\I  Futher analysis of performance with temperature shift
+\pause
+\I  We use
+    \BI $\Delta n_\text{Si} / \Delta T = 1.85 \cdot 10^{-4} K^{-1}$ 
+    \I  $\Delta n_{\text{SiO}_2} / \Delta T = 0$ \EI
+\pause
+\I  Important since robustness to thermal shift 
+    is critical for practical devices
+\nextpage
+
+\I  \bold{Result}: Stable over $> 900$K thermal shifts
+\threeDfig{analysis_temp_shift2}
+\I  $\Delta T = 905$K point marks refractive index shift from 3.5 to 3.67 (huge!)
+\I  Potentially means that networks with no need for thermal tuning are possible
+    \BI Occurs when thermal robustness $>$ thermal swing \EI
+\nextpage
+
+\oursection{Result 12-2: Broadband splitter fabrication robustness}
+\I  Further analysis of performance with over-/under-etching of the device
+\medfig{top_wdm_overunder}
+\nextpage
+
+\I  \bold{Result}: Stable to $\sim$8 nm over-/under-etch 
+\threeDfig{analysis_fab_shift2}
+\I  Wavelength adjustment not needed in this case
+\I  \bold{Key}: Shows that robustness to variation in wavelength 
+    is a good heuristic for thermal and fabrication robustness
+    \BI Designs using thermal and fabrication supermodes also possible\EI
 \EI

### 2013-02-24 defense/pres3.tex
Basically done with defense presentation.

@@
 % \usepackage{pause}
-\usepackage[display]{texpower}
+\usepackage[display]{texpower} % For presentation
+% \usepackage[printout]{texpower} % For print-out
 
@@
 \threeDfig{3Db_hub_4x4}
-\I  Pop quiz: Can you guess which trace goes where?
+\I  Pop quiz: Can you tell which trace goes where?
 \nextpage
@@
 
-\I  \bold{Result}: Stable over $> 900$K thermal shifts
+\I  \bold{Result}: Stable wavelengths available even up to $905$K shifts!
 \threeDfig{analysis_temp_shift2}
+\pause
 \I  $\Delta T = 905$K point marks refractive index shift from 3.5 to 3.67 (huge!)
+\pause
 \I  Potentially means that networks with no need for thermal tuning are possible
@@
 \I  Wavelength adjustment not needed in this case
+\pause
 \I  \bold{Key}: Shows that robustness to variation in wavelength 
@@
     \BI Designs using thermal and fabrication supermodes also possible\EI
+\nextpage
+
+\I  Robustness likely due to a combination of 
+    small device footprint,
+    broadband wavelength response, and
+    low-intensity field in device
+\medfig{top_wdm}
+\nextpage
+
+\oursection{Conclusion}
+\footnotetext{$^\ast$maybe}
+\I  How to design any$^\ast$ linear multi-mode nanophotonic device
+    \BI using the full parameter space
+    \I  simply by describing its operation \EI
+\pause
+\I  Our method results in designs which are
+    \BI extremely compact
+    \I  manufacturable \EI
+\pause
+\I  Devices can be designed which are robust to
+    \BI wavelength shifts
+    \I  thermal shifts 
+    \I  fabrication error \EI
+\oursection{Acknowledgements}
+\begin{quote}
+Not unto us, O Lord, not unto us, \\
+But to Your name give glory, \\
+Because of Your mercy, \\
+Because of Your truth. (Psalm 115:1)
+\end{quote}
+\stepwise{
+\step{Mom, Dad, }
+\step{Jennifer, }
+\step{Eli, }
+\step{Seth, Lieven, Kelley,}
+\step{Shanhui, Mark,}
+\step{David,}
+\step{Jelena,}
+\step{Stephen,}
+\step{Maria, Yiyang, Szu-lin, Gary,}
+\step{JVgroup,}
+\step{Owen, Paul,}
+\step{Wonseok,}
+\step{Ingrid,}
+\step{Church family,}
+\step{Sandy, Josiah}
+
+\step{\begin{center}Thank you\end{center}}
+}
 \EI

### 2013-02-25 defense/pres3.tex
Final.

@@
 \pause
-\I  Therefore, a \emph{useful} tool would optimize for \emph{both} $x$ and $z$
+\I  \bold{Realization}: A \emph{useful} tool must optimize for \emph{both} $x$ and $z$
 \nextpage
@@
 \I  Output mode is enforced using overlap integrals
-    ($c_{ij}\T x_i$ or $\int \hat{E_{ij}} E$)
+    ($c_{ij}\T x_i$ or $\int \hat{E}_{ij} E$)
 \nextpage
@@
 
+\I  Broadband design still high efficiency 
+\I  Efficiency (1310 nm and 1550 nm): 84.2\%, 82.3\% (0.09\%, 1.41\%)
+\medfig{top_wdm}
+
 \oursection{Result 12-1: Broadband splitter temperature dependence}
@@
 
-\I  \bold{Result}: Stable wavelengths available even up to $905$K shifts!
+\I  \bold{Result}: Stable wavelengths available even up to $\sim1000$K shifts!
 \threeDfig{analysis_temp_shift2}
@@
 \I  Devices can be designed which are robust to
-    \BI wavelength shifts
-    \I  thermal shifts 
+    \BI wavelength and temperature shifts 
     \I  fabrication error \EI

### 2013-02-28 paper/paper.tex
Paper started.

\documentclass[letterpaper,10pt]{article}
\usepackage{graphicx}
\usepackage{opex3}
\usepackage{amsmath,amssymb}
\begin{document}
\title{Nanophotonic Computational Design}
\author{Jesse Lu$^\ast$ and Jelena Vu\v{c}kovi\'{c}}
\address{Stanford University, Stanford, California, USA.}
\email{jesselu@stanford.edu}

\begin{abstract}
In contrast to designing nanophotonic devices 
    by tuning a handful of device parameters, 
    we have developed a computational method 
    which utilizes the full parameter space to design linear nanophotonic devices.
We show that our method may indeed be capable of designing 
    any linear nanophotonic device by demonstrating designed structures which
    are fully three-dimensional and multi-modal,
    exhibit novel functionality,
    have very compact footprints,
    exhibit high efficiency, and
    are manufacturable.
In addition, we also demonstrate the ability to produce structures
    which are strongly robust to wavelength and temperature shift,
    as well as fabrication error.
Critically, we show that our method 
    does not require the user to be a nanophotonic expert or 
    to perform any manual tuning. 
Instead, we are able to design devices 
    solely based on the user's desired performance specification for the device.
\end{abstract}
\ocis{230.75370, 130.3990.}

\begin{thebibliography}{99}
% \bibitem{fibergrating} Y. Tang, Z. Wang, L. Wosinski, U. Westergren, and S. He,
%     ``Highly efficient nonuniform grating coupler for silicon-on-insulator 
%     nanophotonic circuits,''
%     Opt. Lett. \textbf{35}, 1290-1292 (2010).
% \bibitem{ridge}  K. K. Lee, D. R. Lim, L.C. Kimerling, J. Shin, and F. Cerrina, 
%     ``Fabrication of ultralow-loss Si/SiO2 waveguides by roughness reduction,''
%     Opt. Lett. \textbf{26}, 1888-1890 (2001).
% \bibitem{pcslow} Y. A. Vlasov, M. O'Boyle, H. F. Hamann, and S. J. McNab,
%     ``Active control of slow light on a chip with photonic crystal waveguides,''
%     Nature \textbf{438}, 65-69 (2005).
% \bibitem{slotfocus} M. Lipson, 
%     ``Guiding, modulating, and emitting light on 
%     silicon-challenges and opportunities,'' 
%     J. Lightwave Technol. \textbf{23}, 4222-4238 (2005).
% \bibitem{active} J. Van Campenhout, P. Rojo Romeo, P. Regreny, C. Seassal, 
%     D. Van Thourhout, S. Verstuyft, L. Di Cioccio, J.-M. Fedeli, 
%     C. Lagahe, and R. Baets, 
%     ``Electrically pumped InP-based microdisk lasers integrated with a 
%     nanophotonic silicon-on-insulator waveguide circuit,'' 
%     Opt. Express \textbf{15}, 6744-6749 (2007).
% \bibitem{metallic} L. Tang, S. E. Kocabas, S. Latif, A. K. Okyay, 
%     D. S. Ly-Gagnon, K. C. Saraswat, and D. A. B. Miller, 
%     ``Nanometre-scale germanium photodetector enhanced by a 
%     near-infrared dipole antenna,'' 
%     Nature Photonics \textbf{2}, 226-229 (2008).
% % \bibitem{fwadia} V. R. Almeida, R. R. Panepucci, and M. Lipson, 
% %     ``Nanotaper for compact mode conversion,'' 
% %     Opt. Lett. \textbf{28}, 1302-1304 (2003) 
% % \bibitem{wwadia} S. G. Johnson, P. Bienstman,  M. A. Skorobogatiy, 
% %     M. Ibanescu1, E. Lidorikis, and J. D. Joannopoulos,
% %     ``Adiabatic theorem and continuous coupled-mode theory for 
% %     efficient taper transitions in photonic crystals,''
% %     Phys. Rev. E \textbf{66}, 066608 (2002)
% % \bibitem{deriv} F. Wang, J. S. Jensen, O. Sigmund, 
% %     ``Robust topology optimization of photonic crystal waveguides with 
% %     tailored dispersion properties.'' 
% %     J. Opt. Soc. Am. B \textbf{28}, 387-397 (2011)
% % \bibitem{boydbook} S. Boyd, and L. Vandenberghe, 
% %     \emph{Convex Optimization} 
% %     (Cambridge University Press, 2004)
% \bibitem{prevwork} J. Lu, S. Boyd, and J. Vuckovic, 
%     ``Inverse design of a three-dimensional nanophotonic resonator,''
%     Opt. Express \textbf{19}, 10563-10750 (2011). 
% \bibitem{veronis} G. Veronis, and S. Fan, 
%     ``Theoretical investigations of compact couplers between dielectric slab 
%     waveguides and two-dimensional metal-dielectric-metal plasmonic waveguides,'' 
%     Opt. Express \textbf{15}, 1211-1221 (2007).
% \bibitem{yang} R. Yang, R. A. Wahsheh, Z. Lu, and M. A. G. Abushagur, 
%     ``Efficient light coupling between dielectric slot waveguide and plasmonic
%     slot waveguide,'' Opt. Lett. \textbf{35}, 649-651 (2010).
% \bibitem{code} \url{www.github.com/JesseLu/objective-first}
\end{thebibliography}

\section{Introduction}
Currently, almost all nanophotonic components are designed 
    by hand-tuning a small number of parameters 
    (e.g. waveguide widths and gaps, hole and ring sizes).
However, the realization of 
    increasingly complex, dense, and robust on-chip optical networks
    will require utilizing increasing numbers of parameters
    when designing nanophotonic components.

Opening the design space to include many more parameters
    allows for smaller footprint, higher performance devices by definition;
    since original designs are still included in this parameter space.
Unfortunately, the lack of intuition for what such designs might look like and
    the inability to manually search such a large parameter space
    have greatly hindered the ability to employ 
    anything even close to the available parameter space
    for designing nanophotonic components.

For this reason, we have developed and implemented a computational method
    which is able to use the full parameter space 
    to design linear nanophotonic components in three dimensions.
Critically, our method requires no user intervention or manual tuning.
Instead, a \emph{design-by-specification} scheme is used 
    to produce designs based solely on a user's performance specification.

We show that our method can indeed produce designs 
    which are extremely compact, and, at the same time, highly efficient.
Furthermore, we demonstrate that devices with novel functionality
    are easily designed.
We also show that our method can be used to produce designs
    with extreme robustness to wavelength and temperature shift,
    as well as fabrication error.

Lastly, since all our results are produced by simply specifying
    the functionality and performance of the desired device,
    our results suggest that our method may indeed by able
    to design \emph{all} linear nanophotonic devices.

\section{Method}

\section{Results}

\section{Conclusion}

\end{document}

### 2013-03-03 paper/paper.tex
Minor.
Closer

@@
 \usepackage{amsmath,amssymb}
+\input defs.tex
 \begin{document}
@@
 \section{Method}
+% Problem statement 
+In order to produce designs which utilize the full parameter space,
+    and are based solely on the user's performance specification,
+    we formulate the design problem in the following way:
+\begin{subequations}\begin{align}
+    \minimize & \sum_i^M \|A_i(z)x_i - b_i\|^2 \\
+    \subto & \alpha_{ij} \le |c_{ij}\T x_i| \le \beta_{ij}, \quad
+        \text{for $i = 1, \ldots, M$ and $j = 1, \ldots, N_i$} \\
+        &   z_\text{min} \le z \le z_\text{max}
+\end{align} \label{problem}\end{subequations}
+
+The explanation for the various terms in \eqref{problem} follows:
+\begin{enumerate}
+\item 
+    $A_i(z)x_i - b_i$ is the \emph{physics residual} for the $i$th mode.
+    That is to say, $A_i(z)x_i - b_i$ represents the underlying physics
+        of the problem; namely, the electromagnetic wave equation
+        \mbox{$(\nabla\times\mu_0^{-1}\nabla\times - \omega_i^2 \epsilon) E_i 
+            +i \omega_i J_i $}.
+
+    The specific substitutions used in order to transform
+        \BE (\nabla\times\mu_0^{-1}\nabla\times - \omega_i^2 \epsilon) E_i 
+            +i \omega_i J_i  \quad\longrightarrow\quad A_i(z)x_i - b_i \EE
+        are
+    \BI $E_i \to x_i$,
+    \I  $\epsilon \to z$,
+    \I  $\nabla\times\mu_0^{-1}\nabla\times - \omega_i^2 \epsilon \to A_i(z)$, and
+    \I  $ -i\omega_i J_i \to b_i$.  \EI
+
+    In contrast to typical schemes for optimizing physical structures,
+        our formulation actually allows for non-zero physics residuals;
+        which can be deduced since $A_i(z)x_i-b_i=0$ is not a hard constraint.
+    Instead, this formulation is what we call an \emph{objective-first} % Ref
+        formulation in that the \emph{design objective} (explained below)
+        is prioritized above satisfying physics.
+
+\item
+    The (field) design objective consist of 
+        the constraint $\alpha_{ij} \le |c_{ij}\T x_i| \le \beta_{ij}$.
+    Physically, this constraint describes 
+        the performance specification of the device 
+        via a series of field overlap integrals 
+        at various output ports of the device.
+    Specifically, the $c_{ij}\T x_i$ terms represents an overlap integral between
+        the E-field of the $i$th mode ($x_i$)
+        with an E-field of the user's choice ($c_{ij}$),
+        where the additional subscript $j$ allows the user
+        to include multiple such fields.
+
+    The amplitude of the overlap integral is then forced
+
+\end{enumerate}
+% how we solved it
+% Maxwell
 

### 2013-03-03 paper/paper.tex
Working on paper.

@@
 
-\section{Method}
+\section{Problem formulation}
 % Problem statement 
@@
 
-The explanation for the various terms in \eqref{problem} follows:
+The explanation for the various terms in \eq{problem} follows:
 \begin{enumerate}
@@
         to include multiple such fields.
+    The amplitude of the overlap integral is then forced to reside between
+        $\alpha_{ij}$ and $\beta_{ij}$.
 
-    The amplitude of the overlap integral is then forced
+    This mechanism allows the user to express 
+        the desired performance of the device
+        as a combination of field amplitudes in various output field patterns.
+    These outputs would be in response to a predefined input excitation,
+        which is determined by the current excitation $b_i$ ($-i\omega_i J_i$)
+        in the physics residual of each mode.
 
+    As an example of a design objective for some mode 1 
+        a user might choose to have the majority of the output power
+        reside in some output pattern 1,
+        while ensuring that only a small amount of power 
+        be transferred to some output pattern 2.
+    In this case the user would use 
+        $0.9 \le |c_{11}\T x_1| \le 1.0$ for the former.
+        and then $0.0 \le |c_{12}\T x_1| \le 0.01$ for the latter;
+        where $c_{11}$ and $c_{12}$ are representative of 
+        output patterns 1 and 2 respectively.
+
+    Finally, we note again that the design objective in our formulation
+        is actually a hard constraint.
+    This means that it is \emph{always satisfied}, 
+        even to the extent of allowing for an unphysical field 
+        (since the physics residual will not be exactly 0).
+    It is for this reason that we call such a formulation ``objective-first''.
+
+\item 
+    The final term in \eq{problem}, $z_\text{min} \le z \le z_\text{max}$,
+        is the structure design objective.
+    It is used as a relaxation of the binary constraint,
+        $z \in {z_\text{min}, z_\text{max}}$,
+        which would ensure that the final design be composed 
+        of two discrete materials.
 \end{enumerate}
-% how we solved it
-% Maxwell
+
+\section{Method of solution}
+We employed the alternating directions method of multipliers (ADMM) algorithm % Ref!
+    in order to solve \eq{problem}.
+ADMM, at its core, solves \eq{problem} by iteratively solving for 
+    $x_i$, $z$, and a dual variable $u_i$.
 

### 2013-03-03 paper/paper.tex
Finished solution method section draft.

@@
     in order to solve \eq{problem}.
-ADMM, at its core, solves \eq{problem} by iteratively solving for 
+The ADMM algorithm solves \eq{problem} by iteratively solving for 
     $x_i$, $z$, and a dual variable $u_i$.
+
+Since we are working in three dimensions, solving \eq{problem} for $x_i$ 
+    is non-trivial in that it involves millions of variables and
+    requires solving for the ill-conditioned $A_i(z)$ matrix.
+For this reason, we use a home-built
+    finite-difference frequency-domain (FDFD) solver which 
+    implements a hardware-accelerated iterative solver % Ref!
+    on Amazon's Elastic Compute Cloud.
+Critically, our cloud-based solver allows us to scale to solve problems
+    with arbitrarily-large number of modes,
+    with no significant penalty in runtime.
+
+In contrast to solving for $x_i$, solving for $z$ is much simpler since we
+    only consider planar structures;
+    thereby limiting $z$ to have only thousands of variables.
+
+Lastly, in order to arrive at fully discrete, manufacturable structures,
+    we convert $z$ to a boundary parameterization % Ref!
+    and tune our structure using a steepest-descent method.
 

### 2013-03-03 paper/paper.tex
Starting on results.

@@
 \section{Results}
+We demonstrate the effectiveness of our design method 
+    by produce designs for a variety of nanophotonic devices.
+
+All of our results are in three dimensions
+    and consist of a 250 nm etched silicon slab
+    completely surrounded by silica.
+The permittivity values of silicon and silica used
+    were $\epsilon_\text{Si} = 12.25$ and $\epsilon_\text{SiO$_2$} = 2.25$
+    respectively.
+
+Many, if not all, of the produced designs exhibit 
+    novel functionality, high efficiency ($>80\%$), and 
+    very compact footprints of only a few square vacuum wavelengths;
+    while still remaining manufacturable.
+We also show that many devices can be designed
+    to exhibit different functionality for different input excitations.
+Additionally, we show that devices can be designed with large tolerances for
+    errors in wavelength, temperature and fabrication.
+
+% Runtimes for the design process ranged from 8-80 hours 
+%     based on the size of the design space.
+
+\subsection{TE mode converter}
+Our first result was a mode conversion device operating in the TE polarization,
+    which we define as that mode where the primary E-field component
+    of the waveguide mode is polarized in the plane of the structure.
+
+Our performance specification (\fig{3Db_wgc_te}) 
+    for the device was for 90\% to 100\% of the 
+    input power to be transferred from the fundamental waveguide mode,
+    to the second-order waveguide mode.
+At the same time, we specified that no more than 1\% of the input power
+    was to remain in the transmitted fundamental mode.
+
+\myfig{3Db_wgc_te}
+    {Perfomance specification of the TE mode converter.
+    Input mode is the fundamental TE-polarized mode on the left.
+    Primary output mode is the second-order mode on the right.
+    Output power in the transmitted fundamental mode on the right 
+    above 1\% is to be rejected.
+    The structure shown is the final three-dimensional design.
+    }
+
+\myfig{takeaway}
+    {Structure and E-field at the central plane of the device.
+    The conversion efficiency into the second-order mode is 86.4\%,
+    while the power into the rejection mode (fundamental) is 0.7\%.}
 
 \section{Conclusion}
+Conclusion
 

### 2013-03-14 paper/paper.tex
a
Working on paper...

@@
     of the waveguide mode is polarized in the plane of the structure.
+Such a device is significant because 
+    it demonstrates the feasibility of muli-mode on-chip optical networks
+    by showing that high-efficiency mode conversion 
+    can readily be achieved in planar on-chip nanophotonic structures.
+Furthermore, this device also demonstrates that this can be achieved
+    within very small device footprints 
+    ($1.6 \times 2.4$ microns for this device in particular).
 
@@
 
+The performance of the device is shown in \fig{takeaway}.
+The conversion efficiency into the second-order mode is lower
+    than desired (86.4\% as opposed to 90\% to 100\%);
+    this may be due to evanescent modes ``interfering'' 
+    with the output field overlap calculation.
+
 \myfig{takeaway}
@@
 
+\subsection{TM mode converter}
+
+In addition to mode conversion in the TE polarization (E-field in-plane),
+    we show that TM polarization (E-field out-of-plane) mode converters
+    can be designed as well.
+This example shows that full three-dimensional structures 
+    truly are possible,
+    and that no approximations are needed for our method.
+
+Since our method is design-by-specification, 
+    the design of a TM mode converter requires only
+    a small modification to the performance specification of the device;
+    namely the polarization of the input and output modes (\fig{wgc_tm}).
+Specifically, we still design for 
+    $\ge 90\%$ conversion into the second-order mode and 
+    a $\le 1\%$ allowance for the fundamental mode to be transmitted.
+
+\myfig{3Db_wgc_tm}
+    {Perfomance specification of the TM mode converter.
+    Input mode is the fundamental TM-polarized mode on the left.
+    Primary output mode is the second-order mode on the right.
+    Output power in the transmitted fundamental mode on the right 
+    above 1\% is to be rejected.
+    The structure shown is the final three-dimensional design.}
+
+The performance of the device is shown in \fig{wgc_tm}.
+The lower conversion efficiency of 76.9\% in contrast to the TE mode converter
+    may be attributed to the lower confinement of the TM waveguide modes.
+However, good rejection of only 1\% is still achieved.
+
+\myfig{wgc_tm}
+    {Structure and E-field at the central plane of the device.
+    The conversion efficiency into the second-order mode is 76.9\%,
+    while the power into the rejection mode (fundamental) is 1.0\%.}
+
+\subsection{Spatial, polarization, and wavelength splitters}
+Next, we demonstrate the design of nanophotonic waveguide mode splitters.
+Such devices can be used as multiplexors or demultiplexors and
+    are the key component in utilizing a single waveguide to transmit 
+    multiple optical signals.
+
+As a demonstration of the versatility of our method, 
+    we show that it is capable of designing mode splitting devices 
+    based on either the spatial profile, the polarization, or the wavelength
+    of the input modes.
+
 \section{Conclusion}

### 2013-03-15 paper/paper.tex
Slowly getting there.

@@
 %     based on the size of the design space.
-
-\subsection{TE mode converter}
+\subsection{Mode converters}
+\subsubsection{TE mode converter}
 Our first result was a mode conversion device operating in the TE polarization,
@@
     The conversion efficiency into the second-order mode is 86.4\%,
-    while the power into the rejection mode (fundamental) is 0.7\%.}
+    while the power into the rejection mode (fundamental) is 0.7\%.
+    Device footprint is $1.6\times2.4$ microns.}
 
-\subsection{TM mode converter}
+\subsubsection{TM mode converter}
 
@@
     The conversion efficiency into the second-order mode is 76.9\%,
-    while the power into the rejection mode (fundamental) is 1.0\%.}
+    while the power into the rejection mode (fundamental) is 1.0\%.
+    Device footprint is $1.6\times2.4$ microns.}
 
-\subsection{Spatial, polarization, and wavelength splitters}
+\subsection{Splitters}
 Next, we demonstrate the design of nanophotonic waveguide mode splitters.
@@
 
+The performance specification for each device is simply to convert
+    90\% of the input power in a particular input mode into
+    either one of the output modes.
+At the same time, we specify that the transmission into the other output mode 
+    be kept below 1\% of input power.
+
+\subsubsection{Spatial mode splitter}
+We demonstrate what is, to our knowledge, 
+    the first design for a three-dimensional
+    nanophotonic spatial mode splitter.
+Such a device is the key enabler for multi-mode on-chip optical circuits,
+    and we show here that they can be designed to be highly efficient
+    while utilizing a very small device footprint ($2.8\times2.8$ microns). 
+The performance specification is shown in \fig{3Db_spl_modal},
+    and the final results is shown in \fig{spl_modal}.
+
+\myfig{3Db_spl_modal}
+    {Input mode is either the fundamental or second-order
+        TE-polarized mode on the left.
+    Output modes are the fundamental waveguide modes of either output 
+        waveguide on the right.
+    Output power into the desired output arm is specified to be greater than 90\%,
+        while power into the opposing arm is set to below 1\%.}
+\myfig{spl_modal}
+    {The conversion efficiencies into the upper and lower output arms
+        are 88.7\% and 77.4\% respectively, 
+        while the rejection powers for the same modes are 0.27\% and 0.20\%.
+    Device footprint is $2.8\times2.8$ microns.}
+
+\subsubsection{TE/TM splitter}
+In addition to splitting different spatial modes, 
+    we show that different polarization can also be split.
+\Fig{3Db_spl_tetm} shows the performance specification of a 
+    device which is able to separate fundamental TE- and TM-polarized
+    waveguide modes into separate arms.
+The final, verified result is shown in \fig{spl_tetm}.
+
+Not only is this result the first of its kind,
+    it is the first in the device category where a single device
+    is able to control both polarizations within the same device footprint.
+This shows the versatility and broad applicability of our method.
+
+\myfig{3Db_spl_tetm}
+    {Input mode is either the fundamental TE- or TM-polarized 
+        mode on the left.
+    Output power into the desired output arm is specified to be greater than 90\%,
+        while power into the opposing arm is set to below 1\%.}
+\myfig{spl_tetm}
+    {The conversion efficiencies into the upper and lower output arms
+        are 87.6\% and 88.8\% respectively, 
+        while the rejection powers for the same modes are 1.06\% and 0.58\%.
+    Device footprint is $2.8\times2.8$ microns.}
+
+\subsubsection{Wavelength splitter}
+Traditional wavelength splitting devices can also be designed using our method.
+Here, we show that the 1550 nm and 1310 nm wavelengths can be split
+    in a very small device footprint ($2.8\times2.8$ microns).
+\myfig{3Db_spl_wdm}
+    {Input mode is the fundamental TE-polarized mode on the left at 
+        a wavelength of either 1550 nm or 1330 nm.
+    Output modes are the fundamental waveguide modes of either output 
+        waveguide on the right.
+    Output power into the desired output arm is specified to be greater than 90\%,
+        while power into the opposing arm is set to below 1\%.}
+\myfig{spl_wdm}
+    {The conversion efficiencies into the upper and lower output arms
+        are 83.2\% and 78.7\% respectively, 
+        while the rejection powers for the same modes are 0.49\% and 1.66\%.
+    Device footprint is $2.8\times2.8$ microns.}
+
 \section{Conclusion}

### 2013-03-16 paper/paper.tex
Close to finishing draft of paper.

@@
 \subsection{Mode converters}
+
+Our first devices consisted of waveguide mode converters.
+Such devices are simple in that they are single-input, single-output devices.
+At the same time, such a device is significant because 
+    it demonstrates the feasibility of muli-mode on-chip optical networks
+    by showing that high-efficiency mode conversion 
+    can readily be achieved in planar on-chip nanophotonic structures.
+
+We show, through the design of mode converters for both the TE- and TM-polarized
+    waveguide modes, 
+    that our method is indeed fully three-dimensional.
+Additionally, the devices also demonstrate very small device footprints 
+    ($1.6 \times 2.4$ microns for this device in particular).
+
 \subsubsection{TE mode converter}
@@
     of the waveguide mode is polarized in the plane of the structure.
-Such a device is significant because 
-    it demonstrates the feasibility of muli-mode on-chip optical networks
-    by showing that high-efficiency mode conversion 
-    can readily be achieved in planar on-chip nanophotonic structures.
-Furthermore, this device also demonstrates that this can be achieved
-    within very small device footprints 
-    ($1.6 \times 2.4$ microns for this device in particular).
 
@@
 \myfig{takeaway}
-    {Structure and E-field at the central plane of the device.
+    {Structure and E-field at the central plane of the TE mode converter.
     The conversion efficiency into the second-order mode is 86.4\%,
@@
 \myfig{wgc_tm}
-    {Structure and E-field at the central plane of the device.
+    {Structure and E-field at the central plane of the TM mode converter.
     The conversion efficiency into the second-order mode is 76.9\%,
@@
 \myfig{3Db_spl_modal}
-    {Input mode is either the fundamental or second-order
+    {Spatial mode splitter performance specification.
+    Input mode is either the fundamental or second-order
         TE-polarized mode on the left.
@@
 \myfig{spl_modal}
-    {The conversion efficiencies into the upper and lower output arms
+    {Spatial mode splitter final result.
+    The conversion efficiencies into the upper and lower output arms
         are 88.7\% and 77.4\% respectively, 
@@
 \myfig{3Db_spl_tetm}
-    {Input mode is either the fundamental TE- or TM-polarized 
+    {TE/TM splitter performance specification.
+    Input mode is either the fundamental TE- or TM-polarized 
         mode on the left.
@@
 \myfig{spl_tetm}
-    {The conversion efficiencies into the upper and lower output arms
+    {TE/TM splitter final result.
+    The conversion efficiencies into the upper and lower output arms
         are 87.6\% and 88.8\% respectively, 
@@
     in a very small device footprint ($2.8\times2.8$ microns).
+The performance specification is shown in \fig{3Db_spl_wdm}, 
+    and the final result is shown in \fig{spl_wdm}.
 \myfig{3Db_spl_wdm}
-    {Input mode is the fundamental TE-polarized mode on the left at 
+    {Wavelength splitter performance specification.
+    Input mode is the fundamental TE-polarized mode on the left at 
         a wavelength of either 1550 nm or 1330 nm.
@@
 \myfig{spl_wdm}
-    {The conversion efficiencies into the upper and lower output arms
+    {Wavelength splitter final result.
+    The conversion efficiencies into the upper and lower output arms
         are 83.2\% and 78.7\% respectively, 
@@
     Device footprint is $2.8\times2.8$ microns.}
+
+\subsection{Hubs}
+We continue to demonstrate the capabilities of our method
+    by designing multi-input, multi-output devices which we call \emph{hubs}.
+Such devices essentially re-arrange modes in the waveguides,
+    and may be thought of as general cross-connect structures.
+Critically, the successful design of such structures 
+    shows that efficiently routing overlapping signals can be 
+    accomplished in a single layer for nanophotonic circuits.
+
+\subsubsection{3$\times$3 hub}
+We first design a hub with three inputs and outputs.
+The performance specification is shown in \fig{3Db_hub_3x3},
+    and the final result is shown in \fig{hub_3x3}.
+
+\myfig{3Db_hub_3x3}
+    {3$\times$3 hub performance specification.
+    Input and output modes all consist of the fundamental TE-polarized mode.
+    Output power into the desired output arm is specified to be greater than 90\%,
+        no rejection modes are used for computational efficiency.}
+\myfig{hub_3x3}
+    {3$\times$3 hub final result.
+    The conversion efficiencies into the selected output arms
+        are 88.6\%, 90.6\%, and 87.3\% for 
+        input arms 1, 2, and 3 respectively (top to bottom).}
+
+\subsubsection{4$\times$4 hub}
+We extend our previous result to design a hub with four inputs and outputs.
+The performance specification is shown in \fig{3Db_hub_4x4},
+    and the final result is shown in \fig{hub_4x4_comb}.
+
+\myfig{3Db_hub_4x4}
+    {4$\times$4 hub performance specification.
+    Input and output modes all consist of the fundamental TE-polarized mode.
+    Output power into the desired output arm is specified to be greater than 90\%,
+        no rejection modes are used for computational efficiency.}
+\myfig{hub_4x4_comb}
+    {4$\times$4 hub final result.
+    The conversion efficiencies into the selected output arms
+        are 85.9\%, 88.1\%, 85.4\%, and 84.3\% for
+        input arms 1, 2, 3, and 4 respectively (top to bottom).}
+
+\subsubsection{2$\times$2$\times$2 hub}
+We can now design a hub that performs 
+    different switching functions for different wavelengths.
+Specifically, we use two input waveguides, two output waveguides,
+    and two wavelengths (hence the name 2$\times$2$\times$2).
+
+Our performance specification (\fig{3Db_hub_2x2x2}) is
+    to cross-couple the waveguides at the 1310 nm wavelength,
+    but to uncouple the waveguides at the 1550 nm wavelength.
+The final result is shown in \fig{hub_2x2x2}.
+\myfig{3Db_hub_2x2x2}
+    {2$\times$2$\times$2 hub performance specification.
+    Input and output modes all consist of the fundamental TE-polarized mode
+        at either 1550 nm or 1310 nm wavelengths.
+    Output power into the desired output arm is specified to be greater than 80\%,
+        no rejection modes are used for computational efficiency.}
+\myfig{hub_2x2x2}
+    {2$\times$2$\times$2 hub final result.
+    The conversion efficiencies at the 1550 nm wavelength 
+        are 77.6\% and 73.7\% respectively for the top and bottom inputs.
+    At 1310 nm, the respective efficiencies are 75.7\% and 75.2\%.}
+
+\subsection{Fiber couplers}
+The capabilities of our method are further demonstrated
+    in the design of nanophotonic fiber couplers,
+    which couple light from an optical fiber at normal incidence
+    into an in-plane waveguide.
+
+The structure of the optical fibers used was a 2 micron diameter core with 
+    refractive index $n_\text{core} = 1.6$,
+    surrounded by a cladding with refractive index $n_\text{cladding}=1.5$.
+The reduced size of the fiber core was employed in order
+    to keep the device footprint small.
+Additionally, the fiber coupler devices were only etched to half the membrane depth,
+    in order to increase the asymmetry in the device structure.
+
+\subsubsection{Compact fiber coupler}
+We first present the design of a compact fiber coupler.
+Such a device is said to be compact in that the functions
+    of coupling into the plane, and focusing into a narrow waveguide
+    are overlapped in the same device footprint.
+
+Although the performance specification (\fig{3Db_fib_te})
+    desired a coupling efficiency above 90\%,
+    only 51.5\% efficiency was achieved (\fig{fib_te});
+    however, this likely remains the highest efficiency demonstrated
+    in a compact fiber coupler.
+
+\myfig{3Db_fib_te}
+    {Compact fiber coupler performance specification.
+    Input mode consists of the $E_y$-polarized fundamental fiber mode.
+    Output mode is the fundamental TE-polarized mode of the in-plane waveguide.
+    Output power into the desired output arm is specified to be greater than 90\%.}
+\myfig{fib_te}
+    {Compact fiber coupler final result.
+    The conversion efficiency into the in-plane waveguide mode is 51.5\%.}
+
+\subsubsection{Mode-splitting fiber coupler}
+We now continue to show how different functionalities
+    can be incorporated into a single device,
+    by virtue of our design-by-specification scheme.
+
+Here, we show how the functionality of a fiber coupler
+    can be combined with that of a spatial mode splitter.
+Specifically, the performance specification (\fig{3Db_fib_pol})
+    determines that different fiber spatial modes
+    by split into different in-plane nanophotonic waveguides.
+
+The final result (\fig{fib_pol}) has lower efficiencies;
+    however, the result is still useful 
+    in that no device with such a functionality has previously been demonstrated.
+
+\myfig{3Db_fib_pol}
+    {Mode-splitting fiber coupler performance specification.
+    Input mode consists of the fundamental fiber mode or 
+        the third-order, circularly polarized fiber mode.
+    Output mode is the fundamental TE-polarized mode of either in-plane waveguide.
+    Output power into the desired output arm is specified to be greater than 90\%.}
+\myfig{fib_pol}
+    {Mode-splitting fiber coupler final result.
+    The conversion efficiency for the fundamental fiber mode input is 32.6\% 
+        (top plot).
+    The conversion efficiency for the third-order fiber mode input is 22.7\% 
+        (bottom plot).}
+
+\subsubsection{Wavelength-splitting fiber coupler}
+Another example of a functionality-combining device is the wavelength-splitting
+    fiber coupler.
+Here, fiber modes of different wavelengths are coupled in-plane
+    and then split into different nanophotonic waveguides (\fig{3Db_fib_wdm}).
+Once again, efficiencies are low (\fig{fib_wdm}),
+    but no such device has previously been demonstrated.
+
+\myfig{3Db_fib_wdm}
+    {Wavelength-splitting fiber coupler performance specification.
+    Input mode consists of the $E_y$-polarized fundamental fiber mode at either
+        the 1310 nm or 1550 nm wavelengths.
+    Output mode is the fundamental TE-polarized mode of either in-plane waveguide.
+    Output power into the desired output arm is specified to be greater than 90\%.}
+\myfig{fib_wdm}
+    {Wavelength-splitting fiber coupler final result.
+    The conversion efficiency into the in-plane waveguide mode at 1550 nm is 31.6\%.
+    The conversion efficiency into the in-plane waveguide mode at 1310 nm is 28.6\%.}
+
+\subsection{Broadband wavelength splitter}
+We continue to investigate the capabilites of our method
+    by attempting the design of a broadband wavelength splitter.
+
+First, we revisit our wavelength splitter result (\fig{spl_wdm})
+    and perform a broadband analysis, 
+    the results of which are shown in \fig{analysis_spl_only}.
+This analysis reveals that device performance quickly drops off
+    as one moves away from the target wavelengths.
+\myfig{analysis_spl_only}
+    {Broadband analysis of previously design wavelength splitter (\fig{spl_wdm}).
+    Although high-efficiency operation is achieved, 
+    the performance quickly drops off away from the target wavelengths 
+    (denoted by arrows).}
+
+In order to design a broadband wavelength splitter,
+    we modify our performance specification to include multiple target 
+    wavelengths (with identical desired performance) around the 
+    original target wavelengths, as seen in \fig{analysis_top}
+    which reveals that broadband operation has been achieved.
+The final result for the broadband wavelength splitter is shown in \fig{top_wdm}.
+\myfig{analysis_top}
+    {Broadband analysis of broadband wavelength splitter.
+    The addition of multiple target wavelengths (vertical arrows)
+    allows for 
+    high-efficiency operation is achieved across a wide bandwidth.}
+\myfig{top_wdm}
+    {Broadband wavelength splitter final result.}
+\myfig{analysis_temp_shift2}{}
+\myfig{analysis_fab_shift2}{}
+\myfig{top_wdm_overunder}{}
 

### 2013-03-16 paper/paper.tex
Draft done.

@@
 \myfig{top_wdm}
-    {Broadband wavelength splitter final result.}
-\myfig{analysis_temp_shift2}{}
-\myfig{analysis_fab_shift2}{}
-\myfig{top_wdm_overunder}{}
+    {Broadband wavelength splitter final result.
+    The efficiencies at the central target wavelengths of 1550 nm and 1310 nm
+    exceed those of its narrowband counterpart (\fig{spl_wdm}).}
+
+\subsubsection{Temperature-robustness of broadband wavelength splitter}
+We can now perform a temperature analysis of our broadband wavelength splitter,
+    using $\Delta n_\text{Si} / \Delta T = 1.85 \cdot 10^{-4} K^{-1}$ 
+    and $\Delta n_{\text{SiO}_2} / \Delta T = 0$ 
+    (no refractive index shift for silica).
+This analysis, shown in \fig{analysis_temp_shift2},
+    reveals that stable operating points exist
+    over a temperature range of nearly 1000 K.
+Such a result is telling in that it demonstrates
+    that on-chip optical devices can be designed to be \emph{passively} stable
+    to temperature shifts which would typically be present in CPUs,
+    since these are much less than 1000 K.
+\myfig{analysis_temp_shift2}
+    {Temperature analysis of the broadband wavelength splitter.
+    Stable operating points (defined as efficiency $\ge$ 80\%)
+    exist over a temperature shift of 905K.}
+
+\subsubsection{Fabrication-robustness of broadband wavelength splitter}
+A analysis with regard to fabrication-error
+    was also performed on the broadband wavelength splitter.
+The specific fabrication error was a general over- or under-etch
+    of the device (input and output waveguides unaffected).
+\Fig{analysis_fab_shift2} reveals that up to 8 nm of over- or under-etching
+    can be sustained before performance falls below 70\%, at the central
+    operating wavelengths.
+The structural variations at 8 nm of etch error are shown in \fig{top_wdm_overunder}.
+
+\myfig{analysis_fab_shift2}
+    {Analysis of fabrication-error on the performance of the broadband 
+    wavelength splitter.
+    Original central wavelengths are shown to hold greater than 70\% efficiency,
+    in spite of up to 8 nm of over- or under-etch error.}
+\myfig{top_wdm_overunder}
+    {Comparison of under-etched, as-designed, and over-etched structures.
+    Differences are subtle since the pixel size is 40 nm and the
+    fabrication error is 8 nm.}
+
+This result is significant in that it demonstrates
+    that the design of broadband devices
+    seems to be a valid heuristic in the search for 
+    devices which are tolerant to temperature shifts and fabrication error.
+Note, however, that our method, as formulated, is also able to
+    deal with temperature and fabrication shifts explicitly as well;
+    although such results are not demonstrated here.
 
 \section{Conclusion}
-Conclusion
+We have developed and implemented a method to design linear nanophotonic structures
+    which are fully three-dimensional and multi-modal,
+    have very compact footprints,
+    exhibit high efficiency, and
+    are manufacturable.
+We demonstrate this capability by designing various nanophotonic mode converters,
+    splitters, hubs, and fiber couplers.
+Critically, many, if not all, of these devices have never been demonstrated before
+    and are not able to be designed by hand.
+In contrast, our method allows user to easily design such devices
+    by virtue of our design-by-specification scheme.
 
+In addition, we demonstrate the design of a broadband device 
+    which is strongly robust to wavelength and temperature shift,
+    as well as fabrication error.
+We show that such a device has stable operating wavelengths 
+    over temperature shifts as large as 905 K,
+    or over-/under-etching error of up to 8 nm.
+We suggest, based on this design, that wavelength tolerance
+    may be a good heuristic to the design of temperature and fabrication-error
+    tolerant nanophotonic devices.
 \end{document}

### 2013-03-22 paper/paper.tex
Added a bunch of things, paper ready for submission.

@@
 \begin{thebibliography}{99}
+\bibitem{ob1_wg} J. Lu, J. Vuckovic, ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes,'' 
+    Opt. Express \textbf{20}, 7221-7236 (2012)
+\bibitem{admm} S. Boyd, N. Parikh, E. Chu, B. Peleato, and J. Eckstein,
+    ``Distributed Optimization and Statistical Learning via the Alternating Direction Method of Multipliers,''
+    Foundations and Trends in Machine Learning \textbf{3}, 1-122 (2011). 
+\bibitem{wonseok} W. Shin and S. Fan, ``Choice of the perfectly matched layer boundary condition for frequency-domain Maxwell’s equations solvers,''
+    J. of Comp. Phys \textbf{231}, 3406-3431 (2012).
+\bibitem{levelset} S. Osher and R. Fedkiw, \emph{Level Set Methods and Dynamic Implicit Surfaces: 1st Edition} (Springer, 2002).
+\bibitem{2dsplitter} Y. Jiao, S. Fan, and D. A. B. Miller, 
+    ``Demonstrations of systematic photonic crystal design and optimization by low rank adjustment: an extremely compact mode separator'', Opt. Lett. \textbf{30}, 140-142 (2005).
+\bibitem{baets}F. Van Laere, G. Roelkens, M. Ayre, J. Schrauwen, D. Taillaert, D. Van Thourhout, T. F. Krauss, and R. Baets,
+    ``Compact and highly efficient grating couplers between optical fiber and nanophotonic waveguides,''
+    J. of Lightwave Tech. \textbf{25}, 151-156 (2007).
 % \bibitem{fibergrating} Y. Tang, Z. Wang, L. Wosinski, U. Westergren, and S. He,
@@
 Opening the design space to include many more parameters
-    allows for smaller footprint, higher performance devices by definition;
+    allows for smaller footprint, higher performance devices by definition,
     since original designs are still included in this parameter space.
@@
     the inability to manually search such a large parameter space
-    have greatly hindered the ability to employ 
-    anything even close to the available parameter space
-    for designing nanophotonic components.
+    have greatly hindered the ability to achieve this.
 
@@
 
-Lastly, since all our results are produced by simply specifying
+Lastly, all our results are produced by simply specifying
     the functionality and performance of the desired device,
-    our results suggest that our method may indeed by able
+    which suggests that our method may indeed by able
     to design \emph{all} linear nanophotonic devices.
@@
         which can be deduced since $A_i(z)x_i-b_i=0$ is not a hard constraint.
-    Instead, this formulation is what we call an \emph{objective-first} % Ref
+    Instead, this formulation is what we call an \emph{objective-first} \cite{ob1_wg}
         formulation in that the \emph{design objective} (explained below)
@@
     It is used as a relaxation of the binary constraint,
-        $z \in {z_\text{min}, z_\text{max}}$,
+        $z \in \{z_\text{min}, z_\text{max}\}$,
         which would ensure that the final design be composed 
@@
 \section{Method of solution}
-We employed the alternating directions method of multipliers (ADMM) algorithm % Ref!
+We employed the alternating directions method of multipliers (ADMM) algorithm 
+    \cite{admm}
     in order to solve \eq{problem}.
@@
     finite-difference frequency-domain (FDFD) solver which 
-    implements a hardware-accelerated iterative solver % Ref!
+    implements a hardware-accelerated iterative solver\cite{wonseok}
     on Amazon's Elastic Compute Cloud.
@@
 Lastly, in order to arrive at fully discrete, manufacturable structures,
-    we convert $z$ to a boundary parameterization % Ref!
+    we convert $z$ to a boundary parameterization\cite{levelset}
     and tune our structure using a steepest-descent method.
@@
 We demonstrate the effectiveness of our design method 
-    by produce designs for a variety of nanophotonic devices.
+    by producing designs for a variety of nanophotonic devices.
 
 All of our results are in three dimensions
-    and consist of a 250 nm etched silicon slab
+    and are planar structures, consisting of a 250 nm etched silicon slab
     completely surrounded by silica.
@@
 Many, if not all, of the produced designs exhibit 
-    novel functionality, high efficiency ($>80\%$), and 
-    very compact footprints of only a few square vacuum wavelengths;
+    novel functionality, high efficiency, and 
+    very compact footprints of only a few square vacuum wavelengths,
     while still remaining manufacturable.
@@
 At the same time, such a device is significant because 
-    it demonstrates the feasibility of muli-mode on-chip optical networks
+    it demonstrates the feasibility of multi-mode on-chip optical networks
     by showing that high-efficiency mode conversion 
@@
 Additionally, the devices also demonstrate very small device footprints 
-    ($1.6 \times 2.4$ microns for this device in particular).
+    ($1.6 \times 2.4$ microns for this device in particular
+    operating at 1550 nm wavelength).
 
 \subsubsection{TE mode converter}
-Our first result was a mode conversion device operating in the TE polarization,
-    which we define as that mode where the primary E-field component
+Our first result is a mode conversion device operating in the TE polarization,
+    where the primary E-field component
     of the waveguide mode is polarized in the plane of the structure.
 
-Our performance specification (\fig{3Db_wgc_te}) 
-    for the device was for 90\% to 100\% of the 
+Our performance specification (\fig{3Db_wgc_te2}) 
+    for the device was for $\ge90\%$ of the 
     input power to be transferred from the fundamental waveguide mode,
@@
 
-\myfig{3Db_wgc_te}
+\myfig{3Db_wgc_te2}
     {Perfomance specification of the TE mode converter.
@@
     Primary output mode is the second-order mode on the right.
-    Output power in the transmitted fundamental mode on the right 
-    above 1\% is to be rejected.
-    The structure shown is the final three-dimensional design.
+    Output power in the transmitted fundamental mode 
+    should be no more than 1\%.
+    The structure shown is the final three-dimensional design
+    (the same holds for all the following figures in the article).
+%     The x- and y-axes are in the plane of the structure,
+%         with the x-axis is the direction of propagation 
+%         for the input and output waveguides.
+%     As expected, the z-axis is perpendicular to the plane of the structure.
     }
@@
 The conversion efficiency into the second-order mode is lower
-    than desired (86.4\% as opposed to 90\% to 100\%);
-    this may be due to evanescent modes ``interfering'' 
+    than desired (86.4\%). 
+Imperfect conversion may be due to evanescent modes ``interfering'' 
     with the output field overlap calculation.
@@
     while the power into the rejection mode (fundamental) is 0.7\%.
-    Device footprint is $1.6\times2.4$ microns.}
+    Device footprint is $1.6\times2.4$ microns.
+    Operating wavelength is 1550 nm.}
 
@@
     a small modification to the performance specification of the device;
-    namely the polarization of the input and output modes (\fig{wgc_tm}).
+    namely the polarization of the input and output modes (\fig{3Db_wgc_tm}).
 Specifically, we still design for 
@@
 The lower conversion efficiency of 76.9\% in contrast to the TE mode converter
-    may be attributed to the lower confinement of the TM waveguide modes.
+    may be attributed to the lower confinement of the TM waveguide modes 
+    in such thin slabs.
 However, good rejection of only 1\% is still achieved.
@@
 
-\subsection{Splitters}
+\subsection{Mode splitters}
 Next, we demonstrate the design of nanophotonic waveguide mode splitters.
-Such devices can be used as multiplexors or demultiplexors and
+Such devices can be used as multiplexers or demultiplexers and
     are the key component in utilizing a single waveguide to transmit 
@@
 The performance specification for each device is simply to convert
-    90\% of the input power in a particular input mode into
+    more than 90\% of the input power in a particular input mode into
     either one of the output modes.
@@
     the first design for a three-dimensional
-    nanophotonic spatial mode splitter.
+    nanophotonic spatial mode splitter 
+    (previous designs were restricted to two dimensions \cite{2dsplitter}).
 Such a device is the key enabler for multi-mode on-chip optical circuits,
@@
 In addition to splitting different spatial modes, 
-    we show that different polarization can also be split.
+    we show that different polarizations can also be split.
 \Fig{3Db_spl_tetm} shows the performance specification of a 
-    device which is able to separate fundamental TE- and TM-polarized
+    device which is able to separate fundamental TE-polarized ($E_y$ dominant)
+    and TM-polarized ($E_z$ dominant)
     waveguide modes into separate arms.
@@
     {TE/TM splitter performance specification.
-    Input mode is either the fundamental TE- or TM-polarized 
-        mode on the left.
+    Input mode is either the fundamental TE-polarized ($E_y$ dominant, top left)
+    and TM-polarized ($E_z$ dominant, top right).
     Output power into the desired output arm is specified to be greater than 90\%,
@@
     Output modes are the fundamental waveguide modes of either output 
-        waveguide on the right.
+        waveguide on the right;
+        however, the 1550 nm wavelength is directed into the top output, 
+        while the 1310 nm wavelength is directed into the bottom output.
     Output power into the desired output arm is specified to be greater than 90\%,
@@
     Output power into the desired output arm is specified to be greater than 90\%,
-        no rejection modes are used for computational efficiency.}
+        no rejection modes are used for computational efficiency.
+    This hub directs input power from input ports 1, 2, and 3 (from top to bottom)
+    into output ports 2, 3, and 1 respectively.}
 \myfig{hub_3x3}
@@
     Output power into the desired output arm is specified to be greater than 90\%,
-        no rejection modes are used for computational efficiency.}
+        no rejection modes are used for computational efficiency.
+    This hub directs input power from input ports 1, 2, 3, and 4
+    into output ports 3, 2, 4, and 1 respectively.}
 \myfig{hub_4x4_comb}
@@
     Output power into the desired output arm is specified to be greater than 80\%,
-        no rejection modes are used for computational efficiency.}
+        no rejection modes are used for computational efficiency.
+    This hub directs input arms 1 and 2 into output arms 1 and 2 at 1550 nm,
+        but swaps them at 1310 nm.}
 \myfig{hub_2x2x2}
@@
     which couple light from an optical fiber at normal incidence
-    into an in-plane waveguide.
+    into an in-plane waveguide\cite{baets}.
 
@@
     Output mode is the fundamental TE-polarized mode of either in-plane waveguide.
+    The device is designed to couple the fundamental fiber mode into
+        the upper output arm, 
+        while the third-order fiber mode is coupled into the lower output arm.
     Output power into the desired output arm is specified to be greater than 90\%.}
@@
     Output mode is the fundamental TE-polarized mode of either in-plane waveguide.
+    The structure is designed to guide light at the 1550 nm wavelength
+        into the upper output arm,
+        while 1310 nm light is guided into the lower output arm.
     Output power into the desired output arm is specified to be greater than 90\%.}
@@
 \myfig{analysis_top}
-    {Broadband analysis of broadband wavelength splitter.
+    {Broadband analysis of broadband wavelength splitter 
+        (final design shown in \fig{top_wdm}.
     The addition of multiple target wavelengths (vertical arrows)
@@
 Note, however, that our method, as formulated, is also able to
-    deal with temperature and fabrication shifts explicitly as well;
+    deal with temperature and fabrication shifts explicitly as well,
     although such results are not demonstrated here.
@@
 Critically, many, if not all, of these devices have never been demonstrated before
-    and are not able to be designed by hand.
+    and cannot be designed by hand.
 In contrast, our method allows user to easily design such devices
@@
     may be a good heuristic to the design of temperature and fabrication-error
-    tolerant nanophotonic devices.
+    tolerant nanophotonic devices. \\
+
+This work has been supported by the 
+    AFOSR MURI for Complex and Robust On-chip Nanophotonics 
+    (Dr. Gernot Pomrenke), grant number FA9550-09-1-0704.
 \end{document}

### 2013-03-27 defense/intel.tex
Added intel stuff.

--- 2013-02-25 defense/pres3.tex
@@
 \author{Jesse Lu}
-\MyLogo{Jesse Lu PhD defense, Jelena Vuckovic group, Stanford University}
-\date{February 25, 2013}
+\MyLogo{Jesse Lu, Jelena Vuckovic group, Stanford University}
+\date{March 29, 2013}
 
@@
 
-\I  Full-parameter design must be \emph{design-by-description}
+\I  Full-parameter design must be \emph{design-by-specification}
 \pause
 \begin{verbatim}
-\\ Human describe here.
+\\ Human specifiy performance here.
 device mux2 
@@
 
-\I  \bold{Realization}: Design-by-description is \emph{extremely powerful}
+\I  \bold{Realization}: Design-by-specification is \emph{extremely powerful}
 \pause
-    \BI The description (or function) of all useful devices is known
-    \I  Therefore, design-by-description enables the design of \emph{everything} 
+    \BI The specification (or function) of all useful devices is known
+    \I  Therefore, design-by-specification enables the design of \emph{everything} 
     \EI
 \pause
-\I  Also, does not require nanophotonic expertise
-\pause
-\I  \bold{Assumption}: Design-by-description can actually be made to work
-\pause
-\I  \bold{Our goal}: Make it work!
+\smallfig{profs}
+\I  \bold{Approach}: Apply basic optimization concepts to nanophotonic design
 
@@
     \BI Using the full parameter space
-    \I  Using design-by-description \EI
+    \I  Using design-by-specification\EI
 \nextpage
@@
 \pause
-    \BI Design-by-description (objective-first)
+    \BI Design-by-specification (objective-first)
     \I  Uses the full parameter space
@@
 %     second-order mode
-\I  Performance description at output waveguide:
+\I  Performance specification at output waveguide:
     \BI Power in second-order mode: 90\% to 100\%
@@
 
-\I  Efficiency: 88.6\%, 90.6\%, 87.3\%
+\I  Efficiency: 88.6\%, 90.6\%, 87.3\% (Rejection modes no longer used)
 \bigfig{hub_3x3}
-\I  Rejection modes no longer used for computational efficiency 
 \newpage
@@
 \I  A fusion of result 9 (fiber coupler) and result 5 (wavelength splitter)
-\I  Shows the power of full-parameter design-by-description
+\I  Shows the power of full-parameter design-by-specification
 \nextpage
@@
 \step{
-\I  Design-by-description is a key enabler
+\I  Design-by-specification is a key enabler
     \BI All 11 final results achieved in only 3 weeks
@@
     \I  fabrication error \EI
-\oursection{Acknowledgements}
-\begin{quote}
-Not unto us, O Lord, not unto us, \\
-But to Your name give glory, \\
-Because of Your mercy, \\
-Because of Your truth. (Psalm 115:1)
-\end{quote}
-\stepwise{
-\step{Mom, Dad, }
-\step{Jennifer, }
-\step{Eli, }
-\step{Seth, Lieven, Kelley,}
-\step{Shanhui, Mark,}
-\step{David,}
-\step{Jelena,}
-\step{Stephen,}
-\step{Maria, Yiyang, Szu-lin, Gary,}
-\step{JVgroup,}
-\step{Owen, Paul,}
-\step{Wonseok,}
-\step{Ingrid,}
-\step{Church family,}
-\step{Sandy, Josiah}
-
-\step{\begin{center}Thank you\end{center}}
-}
 \EI

### 2013-03-27 thesis/p2/paper1.tex
Added raw papers to be combined into thesis.

\documentclass[10pt,letterpaper]{article}
\usepackage{opex3}
\usepackage{amsmath}
\usepackage{graphicx}

\begin{document}
\title{Inverse design of a three-dimensional nanophotonic resonator}
\author{Jesse Lu, Stephen Boyd, and Jelena Vu\v{c}kovi\'{c}}
\address{Stanford University, \\ Stanford, C.A., 94305}
\email{jesselu@stanford.edu}

\begin{abstract} 
The inverse design of a three-dimensional nanophotonic resonator is presented. The design methodology is computationally fast (10 minutes on a standard desktop workstation) and utilizes a 2.5-dimensional approximation of the full three-dimensional structure. As an example, we employ the proposed method to design a resonator which exhibits a mode volume of $0.32(\lambda/n)^3$ and a quality factor of $7063$. % 8808 35648
\end{abstract}

\ocis{(230.5750) Resonators.} % REPLACE WITH CORRECT OCIS CODES FOR YOUR ARTICLE

%%%%%%%%%%%%%%%%%%%%%%% References %%%%%%%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{99}
\bibitem{miller} D. A. B. Miller, ``Rationale and challenges for optical interconnects to electronic chips,'' Proc. of the IEEE \textbf{88}, 728-749 (2000).
\bibitem{prevwork} J. Lu and J. Vuckovic, ``Inverse design of nanophotonic structures using complementary convex optimization,'' Opt. Express \textbf{18}, 3793-3804 (2010).
\bibitem{inan} U. Inan, A. Inan, \emph{Electromagnetic Waves} (Prentice Hall, 2000), page 296.
\bibitem{yee} K. Yee, ``Numerical solution of initial boundary value problems involving maxwell's equations in isotropic media,'' IEEE Trans. Antennas Propag. Mag. \textbf{14}, 302-307 (1966).
\bibitem{boydbook} S. Boyd and L. Vandenberghe, \emph{Convex Optimization} (Cambridge University Press, 2004).
\bibitem{altdir} S. Boyd, N. Parikh, E. Chu, B. Peleato, and J. Eckstein are preparing a manuscript to be called, ``Distributed Optimization and Statistical Learning via the Alternating Direction Method of Multipliers,'' \verb+http://www.stanford.edu/~boyd/papers/distr_opt_stat_learning_admm.html+. 
\bibitem{cholmod} Y. Chen, T. A. Davis, W. W. Hager, and S. Rajamanickam, ``Algorithm 887: CHOLMOD, supernodal sparse Cholesky factorization and update/downdate,'' ACM Trans. Math. Software \textbf{35}, No. 3, 2009.
\bibitem{cvx} M. Grant and S. Boyd, \emph{CVX: Matlab software for disciplined convex programming}, version 1.21. \verb+http://cvxr.com/cvx+, January 2011.
\bibitem{digitize} D. Englund, I. Fushman, and J. Vuckovic, ``General recipe for designing photonic crystal cavities,'' Opt. Express \textbf{13}, 5961-5975 (2005).
\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%  body  %%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Motivation}
To date, the design of nanophotonic devices has generally involved a lengthy (days, weeks) process in which one perturbs, by trial-and-error, canonical structures such as photonic crystals or waveguide-coupled rings to achieve the desired performance for the device.

Instead, an inverse design method in which the user only specifies the desired electromagnetic field, or characteristics thereof, and then leaves the computer to find a dielectric structure satisfying these requirements, would be a much more intuitive and computationally efficient design strategy. Furthermore, such a method may even be the only feasible option available for the design of more complex multi-wavelength and multi-functional nanophotonic devices needed for on-chip integration\cite{miller}.

\section{2.5-dimensional approximation}
Previously, we demonstrated the inverse design of various nanophotonic devices in two dimensions\cite{prevwork}.
Unfortunately, to directly extend our previous method to full three-dimensional space requires solving for a very large ($\sim 10^7 \times 10^7$) and ill-conditioned matrix, namely that given by the time-harmonic Maxwell's equation in three dimensions, which for the electric ($E$) field is
\begin{align}
\nabla\times\nabla\times E - \mu\omega^2\epsilon E &= 0,\quad\text{where}\label{wave} \\
E &= E(x,y,z).
\end{align}

Therefore, to make our problem more tractable, we formulate a 2.5-dimensional approximation of the electromagnetic fields of a planar three-dimensional nanophotonic device. As shown in Fig.~\ref{approx}a, this involves treating a planar three-dimensional nanophotonic device as a truncated holey fiber with identical dielectric structure. We take advantage of the planar nature of most nanophotonic devices in this way to produce a tractable, computationally-fast method. The $E$-field inside such a holey fiber is expressed as
\begin{equation}
E = E(x,y)e^{-i\beta z},
\end{equation}
where $\beta$ is the wave-vector along the fiber axis. Solving for Eq.~\ref{wave} now requires solving for a much smaller ($\sim 10^5 \times 10^5$) matrix, which can be accomplished using standard linear algebra packages. This simulation technique is thus very similar to a two-dimensional finite-difference frequency-domain solve.

As an example, in Fig.~\ref{approx}b, we compare the 2.5-dimensional electric field against the three-dimensional simulated electric field (at the central plane of the slab), given by a standard finite-difference time-domain (FDTD) software package, for an L3 photonic crystal resonator. We see that with the appropriate choice of $\beta$, which we obtain by fitting a sinusoid to the out-of-plane decay in the three-dimensional FDTD solution, our approximation captures most of the characteristics of the three-dimensional field at the center plane of the slab. 
\begin{figure}[hbt]
\centering\includegraphics[width=\textwidth]{approx}
\caption{(a) For computational feasibility, the resonant fields of a planar nanophotonic device are approximated as those of a truncated holey fiber with identical dielectric structure. (b) An example of our approximation using an L3 photonic crystal resonator. Most of the characteristics of the full three-dimensional field at the center of the slab appear in the approximate solution.}\label{approx}
\end{figure}

In this approximation, converting from a 2.5-dimensional structure to a full three-dimensional structure only requires the correct choice of slab thickness, $t$, since the in-plane values of $\epsilon$ remain the same. To estimate $t$ for the full three-dimensional device, we treat the resonant mode as a guided mode in a slab waveguide surrounded by a cladding of $n=1$. The expression for $t$ is then the thickness of the slab for the lowest-order TE mode of a slab waveguide with effective refractive index $n_\text{eff}$\cite{inan}:
\begin{align}
t &= \frac{2}{\beta}\tan^{-1}\frac{\alpha}{\beta},\label{t} \quad\text{where} \\
\alpha &= \sqrt{k_x^2 - \left(\frac{\omega}{c}\right)^2}, \quad\text{and} \\
k_x &= \sqrt{\left(\frac{n_\text{eff}\omega}{c}\right)^2 - \beta^2}.
\end{align}
Here, $\alpha$ is the wave-vector which determines the evanescent decay of the slab waveguide mode into air, while $k_x$ is an approximated in-plane k-vector. To determine $n_\text{eff}$, the effective refractive index, we use the following approximation,
\begin{equation}
n_\text{eff} = \sqrt{\frac{\|\epsilon E^2\|}{\|E^2\|}}.
\end{equation}
In the above formulation and for the remainder of the manuscript, the norm ($\|\cdot\|$) refers to the 2-norm over the entire grid and is equivalent to the spatial integral $(\int | \cdot |^2 dr)^{1/2}$.

\section{Inverse design method}
\subsection{Original formulation}
In our inverse design method, one proceeds by specifying either the resulting field or its characteristics and then computing a structure which will produce such a field. In this work, we chose to specify the desired field characteristics, namely, small mode-volume and large quality factor. The inverse design problem can then be formulated as,
\begin{align}
\text{minimize} \quad& \frac{\|\epsilon E^2\|}{\text{max}\{\epsilon E^2\}} \label{a1}\\ 
\text{subject to} \quad 
    & \nabla\times\nabla\times E - \mu\omega^2\epsilon E = 0 \label{a2}\\
    & \nabla\cdot\epsilon E = 0 \label{adiv}\\
    & \text{FT}_\text{lightcone}\{E\} = 0, \label{a3} \\
    & \epsilon = \{\epsilon_\text{air}, \epsilon_\text{silicon}\} \label{a4}
\end{align}
where $\epsilon$ and $E$ are the permittivity and electric vector field respectively, defined within the 2.5-dimensional approximation and discretized along a standard Yee grid\cite{yee} with periodic boundary conditions. $\epsilon$ was constrained to be isotropic by only varying $\epsilon_z$ in each cell, and then determining $\epsilon_x$ and $\epsilon_y$ via spatial interpolation. $\text{FT}$ is the two-dimensional Fourier transform.

In this formulation, the minimization objective (Eq.~\ref{a1}) is the mode volume, which we desire to be as small as possible. Similarily, Eq.~\ref{a3} is a constraint on the electric field to produce a large quality factor by forbidding the existence of any Fourier components within the light cone. Eqs.~\ref{a2} and \ref{adiv} are physical constraints that $\epsilon$ and $E$ must satisfy, that is, the wave equation for the 2.5-dimensional fiber mode and the transversality condition. Lastly, Eq.~\ref{a4} is a binary constraint on epsilon, denoting that we only want the structure to be composed of air or silicon.

Although our 2.5-dimensional approximation has reduced the size and complexity of the matrices found in the above formulation, the form of the problem in Eq.~\ref{a1}-\ref{a4} is actually incredibly difficult to solve, if for no other reason that Eq.~\ref{a1}, \ref{a2}, and \ref{a4} are non-convex\cite{boydbook} for joint minimization on both $\epsilon$ and $E$. To make matters worse, the binary constraint in Eq.~\ref{a4} generally results in a problem which is NP-hard\cite{boydbook}. For these reasons, our strategy is to employ an alternating directions scheme\cite{altdir}, in which we break Eq.~\ref{a1}-\ref{a4} into two separate, tractable sub-problems which we then solve iteratively.

\subsection{Alternating directions: field optimization sub-problem}
The first sub-problem in the alternating directions scheme involves optimizing $E$ while holding $\epsilon$ constant,
\begin{align}
\underset{E}{\text{minimize}} \quad& \|\nabla\times\nabla\times E - \mu\omega^2\epsilon E\|
    + \eta \|\epsilon E^2\| \label{b1}\\ 
\text{subject to} \quad 
    & E_\text{center} = 1 \label{bcenter} \\
    & \nabla\cdot\epsilon E = 0 \label{bdiv}\\
    & \text{FT}_\text{lightcone}\{E\} = 0, \label{bQ}
\end{align}
which is a quadratic problem with linear equality constraints, and is easily solved using a standard factor-solve method for sparse matrices\cite{cholmod}.

In this sub-problem, the most significant modification to the original formulation in Eq.~\ref{a1}-\ref{a4} is that the constraint in Eq.~\ref{a2} has been relaxed and moved into the minimization objective (Eq.~\ref{b1}). We will denote this term ($\|\nabla\times\nabla\times E - \mu\omega^2\epsilon E\|$) as the \emph{physics residual}.

At the same time, the term for the mode volume from Eq.~\ref{a1} has also been modified in Eq.~\ref{b1}. We denote this term ($\|\epsilon E^2\|$) as the \emph{design objective}. Note that although the denominator in the original formulation has been removed in order to make the term convex, the present formulation is still equivalent because we fix the $E$-field in the center of the structure (Eq.~\ref{bcenter}), where we want the maximum to occur. Also note that the constraint in Eq.~\ref{bcenter} is crucial in order to avoid the trivial solution $E=0$.

Lastly, the $\eta$ coefficient in Eq.~\ref{b1} allows us to trade-off between the physics residual and the design objective. Thus, in order to achieve a small mode volume, the initial value of $\eta$ is large and is subsequently exponentially reduced once per iteration at all points in the grid in order to bring the physics residual to 0. Furthermore, $\eta$ can also be given a spatial weighting in order to reduce in-plane losses; this strategy was implemented in the results presented here.

\subsection{Alternating directions: structure optimization sub-problem}
The second sub-problem in the alternating directions scheme involves optimizing $\epsilon$ while holding $E$ constant,
\begin{align}
\underset{\epsilon}{\text{minimize}} \quad& \|\nabla\times\nabla\times E - \mu\omega^2\epsilon E\| \label{c1} \\
\text{subject to} \quad 
    & \epsilon_\text{air} \le \epsilon \le \epsilon_\text{silicon}, \label{clim}
\end{align}
which is a quadratic problem with linear inequality constraints and is solved using CVX\cite{cvx}, a convex optimization package for Matlab.

As in the field optimization sub-problem, the physics residual has been relaxed and placed in the minimization objective (Eq.~\ref{c1}). However, we have chosen not to include the design objective term (mode volume). This modification was implemented as a heurestic that seemed to improve the aesthetic quality of the resulting structure.

The second major modification from the original formulation is found in the constraint in Eq.~\ref{clim}. Since the combinatorial problem given by the original constraint in Eq.~\ref{a3} proved to be intractable, the constraint on the values of $\epsilon$ is relaxed to allow for any value in the range from $\epsilon_\text{air}$ to $\epsilon_\text{silicon}$. The sub-problem is now relatively straightforward to solve, although it is very unlikely that one obtains a completely binary structure. In practice various digitization schemes can be implemented\cite{digitize}; however, such schemes were not needed here since a nearly binary structure was produced fortuitously.

\section{Result}
Using the formulations for the field optimization and structure optimization sub-problems presented above, along with our 2.5-dimensional approximation, the inverse design of a planar three-dimensional nanophotonic device is performed.

In order to do so, the frequency, $\omega = 0.16 c/\Delta x$, and the out-of-plane wave vector, $\beta = 0.24 (\Delta x)^{-1}$, are chosen by the user. Here, $\Delta x$ is the grid spacing and $c$ is the speed of light in vacuum. Lastly, an initial dielectric structure consisting entirely of silion, $\epsilon = \epsilon_\text{silicon}$ everywhere on a $160 \times 160$ grid, is used as a starting point---although other initial structures (e.~g.~ air everywhere or random $\epsilon$) yield nearly identical structures in this case.

Having already determined the desired characteristics of our resonator (small mode-volume and large quality factor) in the formulation of the two sub-problems, the inverse design proceeds by alternately solving the field optimization and then the structure optimization sub-problems. That is to say, in every iteration of the algorithm, $E$ is updated to be the solution of Eq.~\ref{b1}-\ref{bQ} and is then plugged into Eq.~\ref{c1}-\ref{clim}, the solution of which becomes the updated value of $\epsilon$. The subsequent iteration then uses the updated $\epsilon$ variable to re-optimize $E$ once again. And the algorithm continues to proceed in this way until the physics residual ($\|\nabla\times\nabla\times E - \mu\omega^2\epsilon E\|$) is reduced to an acceptable value.

\begin{figure}[hbt]
\centering\includegraphics[width=\textwidth]{target}
\caption{The (a) dielectric structure, $\epsilon$, and (b) target field, $E$ ($E_y$ shown only), produced after 75 iterations (10 minutes) on a $160\times 160$ grid. The resulting $\epsilon$ is almost completely binary, and relatively smooth.}\label{target}
\end{figure}
Figs.~\ref{target}a and \ref{target}b are the resulting values of $\epsilon$ and $E$ ($E_y$ shown only), respectively, after 75 iterations of our inverse design method. The entire inverse design process takes only 10 minutes on a standard desktop computer for the $160 \times 160$ grid. An animation of the values of $\epsilon$ and $E_y$ at each iteration of the algorithm is included in the supplementary material.

The values of the physics residual and the design objective (mode volume) at each iteration are shown in Fig.~\ref{progress}. Most importantly, we see that the physics residual seems to converge linearly, indicating that the algorithm is reasonably efficient. The primary factor in determining this rate of convergence is the exponential decrease in $\eta$ (Eq.~\ref{b1}), since as $\eta$ decreases, increasing emphasis is placed on minimizing the physics residual in the field sub-problem.

\begin{figure}[hbt]
\centering\includegraphics[width=\textwidth]{the_prog}
\caption{Value of the physics residual (blue) and design objective, or mode volume, (red) at each iteration. The physics residual seems to exhibit linear convergence, while the mode volume quickly saturates after roughly 25 iterations.}\label{progress}
\end{figure}

\section{Verification} % Find better section name
\subsection{Accuracy}
To evaluate the accuracy of the inverse design method, we compared the field resulting from the iterations (target field) with the actual field of the resulting structure solved by the 2.5-dimensional approximation (2.5D fiber mode) as well as the field of a full three-dimensional FDTD simulation of the resulting structure (full 3D field), as shown in Figs.~\ref{comp} and \ref{xsec}.

As detailed above, the thickness of the corresponding three-dimensional structure is determined by Eq.~\ref{t}, which yielded a value of $8.16 \Delta x$. However, a small sampling of thicknesses in that vicinity resulted in a more accurate thickness of $8.5\Delta x$, which matched the resonant frequency of the target field and 2.5-dimensional fiber mode.
\begin{figure}[hbt]
\centering\includegraphics[width=\textwidth]{compare}
\caption{Comparison ($E_y$) of (a) the target field from the inverse design method (from Fig.~\ref{target}), (b) the actual 2.5-dimensional fiber mode, and (c) the field from the full three-dimensional FDTD simulation. The target field matches well with the full three-dimensional field.}\label{comp}
\end{figure}

\begin{figure}[hbt]
\centering\includegraphics[width=\textwidth]{the_xsec}
\caption{Comparison of the cross sections of the $E_y$ field along the x-axis from the target field (blue), the actual 2.5-dimensional fiber mode (green), and the field from the full three-dimensional FDTD simulation (red). There is some discrepancy between the target field and the full three-dimensional field, but even that is confined to the edges and is only on the order of $\sim 1\%$ of the maximum field amplitude.}\label{xsec}
\end{figure}
Fig.~\ref{comp} plots the $E_y$ component of the target field, 2.5-dimensional fiber mode and the full three-dimensional FDTD field side-by-side. Fig.~\ref{xsec} plots the horizontal cross sections of the magnitudes of the fields on a logarithmic scale. We see that the target field and fiber mode match very well, while there is significantly more discrepancy between the target field and the full three-dimensional field. This is expected with the use of our approximation; however, the error is still relatively small (below 1\% of the maximum field strength) and confined mostly to the edges of the structure.

\subsection{Performance}
The fields from the full three-dimensional FDTD simulation were used to evaluate the performance of the device. The resulting mode volume was $0.32 (\frac{\lambda}{n})^3$ and the total quality factor was 7063. The radiative (out-of-plane) quality factor was 8808 and the in-plane quality factor was 35648.

Fig.~\ref{qcomp} shows the Fourier transforms of the target, fiber and three-dimensional $E_y$ fields taken at the center of the slab. Although there are virtually no field components in the light cone in the case of the target and fiber fields, additional components are present in the full three-dimensional case. This explains why even when leaky radiative components were strictly disallowed in the field optimization sub-problem, the error in the 2.5-dimensional approximation unavoidably introduces some leaky components in the case of the actual three-dimensional structure.

\begin{figure}[hbt]
\centering\includegraphics[width=\textwidth]{qcomp}
\caption{Comparison of the Fourier transforms of the $E_y$ fields of the (a) the target field from the inverse design method, (b) the actual 2.5-dimensional fiber mode, and (c) the field from the full three-dimensional FDTD simulation. The error in our approximation introduces some small additional Fourier components into the light cone.}\label{qcomp}
\end{figure}

\section{Conclusion}
In summary, by using a 2.5-dimension approximation, we demonstrate the inverse design of a three-dimensional nanophotonic resonator. Further development of our method includes applying our inverse method to design three-dimensional devices which support multiple fields at different frequencies. This includes resonant devices such as a multi-wavelength cavity, as well as waveguiding devices such as $N$-port couplers, multiplexers, and grating couplers.\\

This work has been supported in part by the AFOSR MURI for Complex and Robust On-chip Nanophotonics (Dr. Gernot Pomrenke), grant number FA9550-09-1-0704.
\end{document}

### 2013-03-28 thesis/acknowledgement.tex
Starting on thesis...

\prefacesection{Acknowledgement}
body 
\afterpreface

### 2013-03-28 thesis/chapter1.tex
Put together papers.

% \begin{abstract}
% A computationally-fast inverse design method for nanophotonic structures is presented. The method is based on two complementary convex optimization problems which modify the dielectric structure and resonant field respectively. The design of one- and two-dimensional nanophotonic resonators is demonstrated and is shown to require minimal computational resources.
% \end{abstract}
% 
% \begin{thebibliography}{99}
% \bibitem{Yee66} K. Yee, ``Numerical solution of initial boundary value problems involving Maxwell’s equations in isotropic media,'' IEEE Trans. Antennas Propag. Mag. \textbf{14}, 302-307 (1966).
% \bibitem{AB74} M.~Albani and P.~Bernardi, ``A Numerical Method Based on the Discretization of Maxwell Equations in Integral Form,'' IEEE Trans.~Microwave Theory Tech. \textbf{22}, 446-450 (1974).
% \bibitem{GA79} J.~M.~Gerardy and M.~Ausloos, ``Absorption spectrum of clusters of spheres from the general solution of Maxwell's equations. The long-wavelength limit,'' Phys.~Rev.~B \textbf{22}, 4950-4959 (1979).
% \bibitem{Lon09} P. Deotare, M. McCutcheon, I. Frank, M. Khan, M. Loncar, ``High quality factor photonic crystal nanobeam cavities,'' Appl. Phys. Lett. \textbf{94}, 121106 (2009).
% \bibitem{Sch02} J. Vuckovic, M. Loncar, H. Mabuchi, A. Scherer, ``Design of photonic crystal microcavities for cavity QED,'' Phys. Rev. E \textbf{65}, 1-11 (2002).
% \bibitem{Nod05} Y.~Akahane, T.~Asano, B.~Song, S.~Noda, ``Fine-tuned high-Q photonic-crystal nanocavity,'' Opt. Express \textbf{13}, 1202-1214 (2005).
% \bibitem{Lip08} A. Gondarenko, M. Lipson, ``Low modal volume dipole-like dielectric slab resonator,'' Opt. Express \textbf{16}, 17689-17694 (2008).
% \bibitem{SD05} A. Hakansson, J. Sanchez-Dehesa, ``Inverse designed photonic crystal de-multiplex waveguide coupler,'' Opt. Express \textbf{13}, 5440-5449 (2005).
% \bibitem{Sig04} P. Borel, A. Harpøth, L. Frandsen, M. Kristensen, P. Shi, J. Jensen, and O. Sigmund, ``Topology optimization and fabrication of photonic crystal structures,'' Opt. Express \textbf{12}, 1996-2001 (2004).
% \bibitem{Vuc05} D. Englund, I. Fushman, and J. Vuckovic. ``General Recipe for Designing Photonic Crystal Cavities,'' Opt. Express \textbf{12}, 5961–5975 (2005).
% \bibitem{cholmod} \emph{CHOLMOD} software package, accessed via \emph{Matlab}.
% \bibitem{mycomp} Intel Core 2 Quad $2.5$GHz, 8Gb RAM.
% \bibitem{JJ99} S.~G.~Johnson, J.~D.~Joannopoulos, ``Block-iterative frequency-domain methods for Maxwell’s equations in a planewave basis,'' Opt.~Express \textbf{8}, 967-970 (1999).
% \bibitem{BV04} S. Boyd, L. Vandenberghe, \emph{Convex Optimization} (Cambridge University Press, 2004).
% \bibitem{CVX} M. Grant and S. Boyd, \emph{CVX: Matlab software for disciplined convex programming}, \texttt{http://stanford.edu/$\sim$boyd/cvx}, June 2009.
% \bibitem{Hen06} K. Hennessy, C.~Högerle, E.~Hu, A. Badolato, A. Imamoğlu, ``Tuning photonic nanocavities by atomic force microscope nano-oxidation,'' Appl.~Phys.~Lett.~\textbf{89}, 041118 (2006).
% \bibitem{Aka05} B.~-S.~Song, S.~Noda, T.~Asano, Y.~Akahane, ``Ultra-high-Q photonic double-heterostructure nanocavity,'' Nat. Mater. \textbf{4}, 207-210 (2005).
% \bibitem{Riv09} K.~Rivoire, Z.~Lin, F.~Hatami, W.~Ted Masselink, and J.~Vuckovic, ``Second harmonic generation in gallium phosphide photonic crystal nanocavities with ultralow continuous wave pump power,'' Optics Express \textbf{17}, 22609-22615 (2009).
% \end{thebibliography}
% 
\chapter{Direct design}
\section{Introduction}
Numerous numerical methods have been devised to solve Maxwell's equations in both time\cite{Yee66} and frequency\cite{AB74,GA79} domains. We refer to these schemes as direct solvers, since they compute the electric and magnetic fields based on current sources, charge distributions and surrounding dielectric and/or metallic structures. While extremely useful in simulating optical components, using direct methods to design optical components, especially in two or three dimensions,  typically requires an extremely time-consuming direct search in a large parameter space\cite{Lon09,Sch02,Nod05,Lip08,SD05}.

On the other hand, an inverse solver would be much more adept in such design and optimization problems\cite{Sig04,Vuc05}. In this work, we define the inverse problem as that where the electromagnetic field is known, but the surrounding structure is not known. The goal in the inverse problem is, then, to find a dielectric structure that will produce that specific electromagnetic field profile.

We show that one can design nanophotonic resonators by specifying the electromagnetic field and its desirable characteristics (such as cavity quality (Q) factor and/or mode volume) and then using an inverse solver to find the corresponding dielectric structure. We show that the inverse method used is not only computationally-fast, but is also able to optimize for multiple device characteristics and produce multiple resonances, both of which are very difficult using direct methods.

\section{Numerical Setup}
We start from the time-harmonic eigenvalue equation 
\begin{equation}
\nabla \times \epsilon^{-1} \nabla \times H = \left(\frac{\omega}{c}\right)^2 H
\label{trad ev}\end{equation}
where $H$, $\epsilon$, $\omega$ and $c$ are the magnetic field, relative permittivity, resonance frequency and speed of light respectively. To solve the problem numerically, $H$ and $\epsilon$ are discretized in space using the standard Yee cell used in finite difference methods\cite{Yee66}. Also, the curl operators, since they are linear, are represented by the matrix $A$. Eq.~\eqref{trad ev} can now be written as 
\begin{equation}
A Y A x = \xi x
\label{lin ev}\end{equation}
where
\begin{align*}
&A \text{ is the discretized curl operator,} \\
&Y = \text{diag}(\epsilon^{-1}) \text{ is the diagonal matrix representing the dielectric structure,} \\
&x \text{ is a vector representing $H$, and} \\
&\xi =  \left(\frac{\omega}{c}\right)^2. 
\end{align*}
In this form, given $Y$, we can solve the direct problem by computing $x$ using an eigenvalue solver\cite{JJ99}. However, we note that eq.~\eqref{lin ev} is also linear in $Y$, which allows us, if $x$ is held constant, to solve the inverse problem by expressing eq.~\eqref{trad ev} as
\begin{equation}
By = d
\label{inv ls}\end{equation}
where
\begin{align*}
&B = A \cdot \text{diag}(Ax), \\
&d = \xi x\text{, and} \\
&y = 
\begin{bmatrix}
\epsilon_1^{-1} \\ \epsilon_2^{-1} \\ \vdots
\end{bmatrix} \text{ the variable for which we solve.}
\end{align*}
Here, $\text{diag}(Ax)$ is the matrix with the values of $Ax$ along the main diagonal and zeros elsewhere.

\section{Least-Squares Method in 1D}
\subsection{Least-Squares}
\begin{figure}[htbp]\centering
\includegraphics[width=\textwidth]{p1/leastsquares}
\caption{Inverse design of a one-dimensional structure using the unmodified least-squares method. The target field is a sinusoid within a Gaussian envelope. The computed dielectric structure (green area) supports a field (red circles) that exactly matches the target field (blue line). The entire design process is also extremely fast and takes less than $1$ second to complete on a generic desktop computer~\cite{mycomp}. The periodic singularities in the dielectric structure are non-physical and will be addressed later in the article.}
\label{ls pic}\end{figure}
The result of applying this method to a simple one-dimensional problem is shown in Fig.~\ref{ls pic}. A generic least-squares solver~\cite{cholmod} was used to find the dielectric structure, $y$ (green region), that exactly produces the target field, $x$ (blue line), using eq.~\eqref{lin ev}. Using a generic desktop computer, the solution was obtained in less than a second. Then a finite-difference time-domain (FDTD) solver was used to obtain the actual field (red circles) produced by the structure and to verify the accuracy of $y$.

As expected, Fig.~\ref{ls pic} shows that the target field is reproduced exactly by the dielectric structure. However, the resulting structure is full of undesireable singularities. The rest of the section focuses on producing a well-behaved dielectric structure that still reproduces the target field accurately.

\subsection{Regularized Least-Squares}
The simplest way to produce a well-behaved dielectric structure is to add a regularization term to our least-squares problem, 
% \begin{equation}
% \begin{bmatrix} B \\ \sqrt{\eta} I \end{bmatrix} y = \begin{bmatrix} d \\ \sqrt{\eta}y_0 \end{bmatrix}
% \label{regls}\end{equation}
which is equivalent to solving the following optimization problem
\begin{equation}
\minimize_{y}\quad \|By-d\|^2 + \eta\|y-y_0\|^2.
\label{regls alt} \end{equation}
Here $y_0$ represents some initial guess for the dielectric structure, which we want the values of $y$ to stay close to, and $\eta>0$ is a parameter used to trade off fit, i.e. $\|By-d\|^2$, and deviation from $y_0$, i.e. $\|y-y_0\|^2$.

We chose to constrain $\epsilon$ around a constant value of $\epsilon_0 = 10$ and solved the least-squares system for $\eta=10^{-8}$, $10^{-6}$, and $10^{-4}$. The results, each still obtained in under a second, are shown in Fig.~\ref{regls pic} and illustrate the trade-off between constraining $\epsilon$ and accurately reproducing $H$.

\begin{figure}[htbp]\centering
\includegraphics[width=\textwidth]{p1/regularized}
\caption{Inverse design of one-dimensional structures using the regularized least-squares method. The same target field is used as in Fig.~\ref{ls pic}, and the computation time remains below $1$ second. As the regularization parameter, $\eta$, is increased, $\epsilon$ is increasingly constrained to a chosen constant value of $10$. At the same time, the mismatch between target and actual fields increases markedly. This illustrates the apparent trade-off between producing reasonable structures and accurately reproducing a fixed target field.}
\label{regls pic}
\end{figure}

### 2013-03-28 thesis/chapter2.tex
Put together papers.

--- 2013-03-27 thesis/p2/paper1.tex
@@
-\documentclass[10pt,letterpaper]{article}
-\usepackage{opex3}
-\usepackage{amsmath}
-\usepackage{graphicx}
+\chapter{Iterative design}
+\section{Complementary Optimization in 1D}
+\subsection{Motivation for a Complementary Optimization Strategy}
+The fundamental problem in the previous examples is actually not in the methods themselves, but in the improper selection of a target field.
+In fact, it is very difficult to select a suitable target resonant field because not every resonant mode even has a corresponding dielectric structure that is able to reproduce it.
+Furthermore, it is nearly impossible to select a multi-dimensional field which corresponds to a well-behaved, isotropic and discretely-valued $\epsilon$, as would be needed for practical structures.
 
-\begin{document}
-\title{Inverse design of a three-dimensional nanophotonic resonator}
-\author{Jesse Lu, Stephen Boyd, and Jelena Vu\v{c}kovi\'{c}}
-\address{Stanford University, \\ Stanford, C.A., 94305}
-\email{jesselu@stanford.edu}
+For this reason, a successful method must be allowed to either modify the target field, or specify it completely, in which case the user would only determine certain characteristics (e.g.
+mode-volume, Q-factor) that the target field should have.
+The former strategy is developed in both one and two dimensions, while the latter strategy is implemented in Section \ref{sec:2Dbounded} in order to design two-dimensional resonators with discrete values of $\epsilon$.
 
-\begin{abstract} 
-The inverse design of a three-dimensional nanophotonic resonator is presented.
+\subsection{Complementary Optimization}\label{sec:comp}
+We start with the same target field as in the previous examples but we now formulate a method that allows for it to be modified during the design process.
+The formulation chosen is a complementary optimization routine, where we continually alternate between modifying $\epsilon$ to better fit the field, and then modifying the field to better fit $\epsilon$.
+Here, we use the term ``fit'' to mean that either $\epsilon$ or $H$ is solved so that the residual error from eq.~\eqref{trad ev} is minimized.
+Additionally, both iterations are regularized in order to stably approach a solution.
+This algorithm can be summarized as follows,
+\begin{align}
+&\text{choose $x_0$ and $y_0$} \nonumber \\
+&\text{for } i = 1, 2, \ldots \nonumber \\
+&\quad\minimize_{y_i}\quad \|B_{i-1} y_i-d_{i-1}\|^2 + \eta_1\|y_i-y_{i-1}\|^2 \label{comp1}\\
+&\quad\minimize_{x_i}\quad \|A Y_i A x_i - \xi x_{i-1}\|^2 + \eta_2\|x_i-x_{i-1}\|^2 \label{comp2}
+\end{align}
+where $Y_i = \text{diag}(y_i)$, $B_i = A \cdot \text{diag}(A x_i)$ and $d_i = \xi x_i$.
+$\|A Y_i A x_i - \xi x_{i-1}\|^2$ is used instead of $\|A Y_i A x_i - \xi x_{i}\|^2$ to avoid the trivial $x_i = 0$ solution and does not affect the overall accuracy since $x$ changes very slowly.
+
+\begin{figure}[htbp]\centering
+\includegraphics[width=\textwidth]{p1/complementary}
+\caption{Inverse design of a one-dimensional structure using the complementary optimization method.
+The target field in Figs \ref{ls pic} and \ref{regls pic} is used as the initial target field.
+The rates of change for both $\epsilon$ and $H$ are controlled by regularization parameters $\eta_1=10^{-4}$ and $\eta_2=10^{-3}$ respectively.
+The $400$ iterations used to achieve this result took $60$ seconds to compute.
+This method results in a well-behaved $\epsilon$ that actually produces a field very similar to the original target field.
+Interestingly, the formation of a ``steady-state'' periodic structure toward the sides of the structure has emerged.}
+\label{comp pic}
+\end{figure}
+
+Fig.~\ref{comp pic} shows that the complementary optimization algorithm, after $400$ iterations and with the correct choice of regularization parameters $\eta_1$ and $\eta_2$, results in a well-behaved structure that is able to closely reproduce the modified target field.
+Numerically, the least-squares problem must now be solved numerous times, which increases the computational time needed to around $60$ seconds.
+
+\subsection{Complementary Optimization with Bounded $\epsilon$}
+In order to achieve a more practical, discretely-valued dielectric structure, we can impose strict upper- and lower-bounds on $\epsilon$. To this end, we modify our algorithm as such,
+\begin{align}
+&\text{choose $x_0$ and $y_0$} \nonumber \\
+&\text{for } i = 1, 2, \ldots \nonumber \\
+&\quad\minimize_{y_i}\quad \|B_{i-1} y_i-d_{i-1}\|^2 \nonumber \\
+&\quad\text{subject to}\quad \epsilon_\text{max}^{-1} \leq y_i \leq \epsilon_\text{min}^{-1} \label{bc1} \\
+\nonumber \\
+&\quad\minimize_{x_i}\quad \|A Y_i A x_i - \xi x_{i-1}\|^2 + \eta_2\|x_i-x_{i-1}\|^2. \label{bc2}
+\end{align}
+In this algorithm, eq.~\eqref{bc1} is a convex optimization problem\cite{BV04}.
+This allows us to impose hard constraints on $\epsilon$, which in turn allows us to remove the regularization term present in eq.~\eqref{comp1}.
+The \emph{CVX} package\cite{CVX}, a Matlab-based modeling system for convex optimization, is used to solve eq.~\eqref{bc1}, with each iteration of the algorithm now requiring roughly $1$ second of computation time.
+\begin{figure}[htbp]\centering
+\includegraphics[width=\textwidth]{p1/bounded}
+\caption{Inverse design of a one-dimensional structure using the complementary optimization method with bounded $\epsilon$.
+The parameters are identical to those used to produce Fig.~\ref{comp pic} with the exception that only one regularization term is now needed ($\eta_2=10^{-3}$).
+The algorithm was run for $100$ iterations, which took $100$ seconds.
+The structure turns out to be almost completely binary-valued and looks like a periodic structure with tapered duty cycle.
+It produces an actual field which very closely matches the final target field.}
+\label{bounded comp pic}
+\end{figure}
+
+A nearly binary-valued dielectric structure is obtained in Fig.~\ref{bounded comp pic}, which accurately produces the final target field.
+This is very useful for the design of practical structures, since they usually consist of two or three different materials at most.
+Interestingly, although the directly discreteness of $\epsilon$ was not enforced (since that would make the problem non-convex), a discrete, binary-valued structure has still arisen.
+
+\section{Complementary Optimization in 2D}
+\subsection{``S'' Resonator}
+We now demonstrate that the complementary optimization method is versatile and can be scaled to multiple dimensions.
+To ensure that $\epsilon$ is well-behaved we use a point-spread function which does not allow $\epsilon$ to change at a certain point in space without affecting the values surrounding it.
+
+In order to show that our method can produce complex designs, we choose an S-shaped target field which is non-trivial to reproduce.
+The optimization results, using the complementary optimization method from Section \ref{sec:comp}, are shown in Fig.~\ref{S pic}.
+The resulting dielectric structure is continuous, unbounded and contains some singularities (white dots), but the final target and actual fields match up well.
+Also, the computational cost remains quite reasonable; the $50$ iterations needed required only $5$ minutes of computation time.
+The resulting structure is completely unintuitive, and illustrates the kind of new capabilities offered by the inverse design strategy.
+Specifically, that a complex, intricate structure can be designed just by specifying the shape and frequency of a rather simple electromagnetic mode.
+\begin{figure}\centering
+\includegraphics[width=\textwidth]{p1/S}
+\caption{Inverse design of an ``S'' resonator using the complementary optimization method without bounds on $\epsilon$.
+The design was initialized by specifying an initial dielectric structure ($\epsilon=1$ everywhere) and a resonant field in the shape of an ``S''.
+The final dielectric structure was produced after $50$ iterations which took $90$ seconds to complete in total.
+The grid size was $80\times 120$.
+The final dielectric structure is quite unintuive, and yet reproduces the target field surprisingly well.
+This example demonstrates the versatility of the complementary optimization method in producing designs, from very simple specifications, which otherwise could be attained only with considerable difficulty.}
+\label{S pic}
+\end{figure}
+
+\subsection{Multi-Mode Inverse Design}
+The complementary optimization method can also be extended to produce dielectric structures with multiple resonances.
+To do so, multiple initial target fields are specified.
+The dielectric structure is first modified to simultaneously fit all target fields using a multi-objective least-squares method.
+Then each target field is individually modified to fit the structure; and we continue alternating between optimizing $\epsilon$ and $H^{(j)}$ in this way.
+A benefit of this scheme is that only the $\epsilon$ optimization increases in size, so the design process remains computationally tractable, even for several resonant fields.
+This algorithm can be summarized as follows,
+\begin{align}
+&\text{choose $y_0$, $x^{(1)}_0$, $x^{(2)}_0$, \ldots} \nonumber \\
+&\text{for } i = 1, 2, \ldots \nonumber \\
+&\quad\minimize_{y_i}\quad \eta_1\|y_i-y_{i-1}\|^2 + \sum_j \|B^{(j)}_{i-1} y_i-d^{(j)}_{i-1}\|^2  \label{mm1}\\
+&\quad\text{for } j = 1, 2, \ldots \nonumber \\
+&\quad\quad\minimize_{x^{(j)}_i}\quad \|A Y_i A x^{(j)}_i - \xi x^{(j)}_{i-1}\|^2 + \eta_2\|x^{(j)}_i-x^{(j)}_{i-1}\|^2. \label{mm2}
+\end{align}
+The design of an ``X'' resonator with two perpendicular, degenerate modes is shown in Fig.~\ref{X pic}.
+The added complexity increases the total computation time to $5$ minutes for $40$ iterations of the algorithm.
+\begin{figure}\centering
+\includegraphics[width=\textwidth]{p1/X}
+\caption{Inverse design of a doubly-resonant, degenerate ``X'' resonator produced by the complementary optimization method with unbounded $\epsilon$.
+As in Fig.~\ref{S pic} the initial value of $\epsilon$ was $1$ everywhere.
+The two initial target fields used are only slightly perturbed and are very similar to the two final actual target fields.
+Computationally, this design took $5$ minutes to complete on a $120\times 120$ grid and required $40$ iterations.
+This example shows that the complementary optimization strategy can be extended to produce dielectric structures with multiple resonances.
+Such an ``X'' resonator is useful for polarization-entangled single-photon sources for example\cite{Hen06}.}
+\label{X pic}
+\end{figure}
+
+\subsection{Design of Waveguiding Devices}
+The multi-mode inverse design method can also be applied to the design of waveguiding devices such as multiplexers/demultiplexers, waveguide couplers, crossbars and dispersion-tailored waveguides.
+This can be accomplished by treating a waveguiding device as a doubly-degenerate resonator at its operational frequencies and then enforcing opposite symmetries (even/odd or cosine/sine) in the degenerate modes.
+A single-to-dual beam waveguide coupler designed based on Eq.~\eqref{mm1} and \eqref{mm2} is shown in Fig.~\ref{wg pic}, and motivates how one might design other waveguiding devices such as channel-drop filters.
+\begin{figure}[htbp]\centering
+\includegraphics[width=\textwidth]{p1/wg}
+\caption{Inverse design of a single-to-dual beam waveguide coupler using the complementary optimization method without bounds on $\epsilon$.
+Two degenerate modes with opposite symmetry (sine and cosine) are used as target fields.
+Only $4$ iterations ($14$ seconds) are needed to achieve this solution on a $240\times 55$ grid.
+This is a simple demonstration showing that the complementary optimization method can also be extended to design waveguiding devices.}
+\label{wg pic}
+\end{figure}
+In addition to macroscopic waveguiding devices, one should also be able to create novel periodic waveguiding structures.
+For instance, by controlling the frequency of a particular waveguiding mode at each of its $k$-vectors, one could create a waveguide with a customized dispersion characteristic, which would be useful in the design of slow-light waveguides.
+
+\section{Complementary Optimization with Bounded $\epsilon$ in 2D}\label{sec:2Dbounded}
+\subsection{Numerical Method}\label{sec:2Dnum}
+We now use the complementary optimization method to design resonators with discrete, binary $\epsilon$ in two dimensions.
+At the same time, the algorithm is modified so that we no longer specify an initial target field; instead, only an initial dielectric structure and the maximum desired mode volume (i.e.
+mode area in 2D) are specified.
+In addition, the optimization process attempts to maximize the Q-factor.
+Such an algorithm now consists of iteratively solving two convex optimization problems,
+\begin{align}
+&\text{choose $y_0$} \nonumber \\
+&\text{for } i = 1, 2, \ldots \nonumber \\
+&\quad\minimize_{x_i}\quad \|A Y_{i-1} A x_i - \xi x_{i}\|^2 +   \eta \|F x_i\|^2\nonumber \\
+&\quad\text{subject to}\quad (A x_i)^T Y_{i-1} (A x_i) \leq A_\text{mode} \label{be1} \\
+\nonumber \\
+&\quad\minimize_{y_i}\quad \|B_i y_i-d_i\|^2 \nonumber \\
+&\quad\text{subject to}\quad \epsilon_\text{max}^{-1} \leq y_i \leq \epsilon_\text{min}^{-1}. \label{be2} 
+\end{align}
+In this algorithm, the field optimization, Eq.~\eqref{be1}, differs significantly from Eq.~\eqref{bc2}.
+First, the eigenvalue equation term $\|A Y_{i-1} A x_i - \xi x_{i}\|^2$ no longer utilizes $x_{i-1}$.
+Also, a new ``Fourier-minimizing'' term $\|F x_i\|^2$ has been added.
+Here, the row vectors of $F$ consist of the field Fourier components that we do not want incorporated in the final solution.
+The motivation for adding this term is to design high-Q resonators using planar structures, where the Q-factor is limited by out-of-plane losses, and can thus be improved by eliminating field Fourier components that are not localized by total internal reflection (components inside the light cone)~\cite{Vuc05}.
+Lastly, the $(A x_i)^T Y_{i-1} (A x_i)$ term allows us to specify the mode area (mode volume in three dimensions), that we desire for our resonant field.
+This works because the two minimization objectives in Eq.~\eqref{be1} will generally cause the mode area to be as large as possible, which means we always end up with $(A_1 x_i)^T Y_{i-1} (A_1 x_i) = A_\text{mode}$.
+
+The addition of the two new terms in Eq.~\eqref{be1} signifies that the field iteration in our algorithm attempts to do more than to just satisfy Maxwell's equations.
+Rather than only trying to fit the dielectric structure, the resonant field now also minimizes some of its Fourier components while working with a limited mode area.
+
+In contrast with the field optimization given by Eq.~\eqref{be1}, the structure optimization given by Eq.~\eqref{be2} remains identical to the equation in the one-dimensional case, Eq.~\eqref{bc1}, and contains no terms related to notions of Fourier components or mode area.
+In fact, the only objective in the $\epsilon$ optimization is to better fit the field generated from the field optimization.
+This means that in this scheme, the field iteration is leading the structure iteration.
+In other words, Eq.~\eqref{be1} ``looks ahead'' and gradually adapts itself to become a more desirable field, while Eq.~\eqref{be2} just ``follows along''.
+For this reason, this algorithm is unique from the other complementary optimization algorithms previously presented in the article, since in those algorithms both iterations follow one another and eventually ``meet in the middle''.
+
+Finally, in this scheme, we chose to limit the degrees of freedom of both $x_i$ and $y_i$.
+Some components of $x_i$ were fixed at non-zero values and were not allowed to be modified simply to avoid the $x_i = 0$ situation.
+To enhance the aesthetics of the resulting dielectric structure, some components of $y_i$ were frozen as well, which is useful in cases where one would only like to modify the dielectric structure within a waveguide only, for example.
+
+\subsection{Circular Grating Resonator}
+\begin{figure}[htbp]\centering
+\includegraphics[width=\textwidth]{p1/circle}
+\caption{Inverse design of a two-dimensional resonator using the complementary optimization method with strict bounds on $\epsilon$.
+The initial specification is very simple and consists an initial dielectric structure ($\epsilon=12.25$ everywhere), the frequency and mode-volume of the resonance field as well as a weighting factor, $\eta$, to avoid leaky field Fourier components.
+Additionally, the values of $\epsilon$ are only allowed to be modified within a central circular region and must be kept between $1$ and $12.25$.
+After $40$ iterations on a $160 \times 160$ grid, which took $7$ minutes to complete, a discrete structure emerged with excellent match between the predicted ($x_{40}$) and actual fields.
+The structure resembles a circular grating with a bowtie-like central structure for focusing the resonant energy to a single point.}
+\label{circle pic}
+\end{figure}
+Fig.~\ref{circle pic} shows the design of a circular grating resonator using the method from Section \ref{sec:2Dnum}.
+The dielectric structure emerged from a very simple choice of initial structure, namely a constant $\epsilon=12.25$ everywhere.
+The range of $\epsilon$ was limited to be from $1$ to $12.25$, the mode area was set to $5$ and $\eta= 10^{-3}$.
+Central components of $x_i$ were held constant to ensure that an electric dipole in the y-direction was produced in the center of the structure.
+Additionally, the components of $\epsilon$ outside a specified circle were held at a constant $\epsilon=12.25$ for the duration of the design process.
+The entire algorithm was run for $40$ iterations and took $7$ minutes.
+
+After $40$ iterations, we see that a strong binary-valued structure has formed.
+Interestingly, the central bowtie-like structure has emerged from previous geneetic optimization methods as well\cite{Lip08}.
+Note also the extremely small amount of information needed to produce this result: only the frequency and mode area of the resonant field desired, and a trivial intial $\epsilon$.
+The ability to produce a rather advanced design from such a simple problem specification highlights the potential usefulness of inverse methods in the design of novel nanophotonic devices.
+
+\subsection{Beam Resonator}
+The same approach was used to design a beam resonator as shown in Fig.~\ref{line pic}.
+The parameters used in this design are identical to those used for the circular resonator, with the exception that the initial dielectric structure now consists of an unbroken waveguide, and the region where $\epsilon$ can be modified is now confined to the center of the waveguide.
+\begin{figure}[htbp]\centering
+\includegraphics[width=\textwidth]{p1/beam}
+\caption{Inverse design of a beam resonator in two dimensions using the complementary optimization method with bounded $\epsilon$.
+The initial conditions are identical to those for Fig.~\ref{circle pic}, except that the initial dielectric structure is an unbroken waveguide, and $\epsilon$ can only be modified within that waveguide.
+The structure emerged after $40$ iterations on a $320\times 40$ grid, which took $5$ minutes of computation.
+The bowtie-like structure has reappeared in the center.
+Interestingly, the effect of the Fourier term in Eq.~\eqref{be1}, is seen in the outward tapering of the holes.}
+\label{line pic}
+\end{figure}
+
+These two, simple modifications produce a vastly different result as is plainly seen from Fig.~\ref{line pic}.
+Some characteristics remain, such as the two closely spaced holes in the center of the structures which focus the electromagnetic energy to a central point.
+Other features are unique to the beam resonator, such as a gradual outward tapering of hole diameters and size ending in a periodic ``steady-state'' structure, in similar fashion to Fig.~\ref{comp pic}.
+This tapering is a direct result of the Fourier term in Eq.~\eqref{be1} as it leads to a smooth field profile variation and minimization of the components in the light cone that lead to out-of-plane losses\cite{Vuc05,Aka05}.
+
+\section{Conclusions and Outlook}
+In summary, we have introduced and demonstrated a complementary optimization method for the inverse design of nanophotonic resonators as well as waveguiding structures.
+We have demonstrated that, in two dimensions, this method can be used to design non-trivial as well as multi-resonant structures.
+Furthermore, we have shown that by constraining the range of available dielectric constants, the same underlying method can produce binary-valued, discrete dielectric structures.
+
+The methods presented here can readily be extended into three dimensions.
+In essence, the only hurdle is the size of the convex optimization problem for the field optimization.
+Since a full three-dimensional grid often consists of tens of millions of variables, solving the field optimization problem, Eq.~\eqref{be1}, using methods such as LU factorization is no longer computationally tractable.
+Instead, iterative methods such as truncated Newton methods must be employed.
+As it turns out, such iterative methods are especially well suited to this complementary optimization scheme, since they can take advantage of the information in $x_{i-1}$ in order to solve $x_i$ very quickly.
+This is very applicable to our algorithm since the field changes very little from one iteration to the next.
+
+Although solving the field optimization problem is numerically challenging in three dimensions, solving the structure optimization problem, Eq.~\eqref{be2}, in three dimensions is much simpler.
+This is because only structural variations in-plane need to be accounted for planar nanophotonic devices.
+The number of variables in Eq.~\eqref{be2} for both two- and three-dimensional problems is then effectively the same, and the same numerical techniques can be employed to solve both.
+
+A full three-dimensional inverse design method based on complementary optimization would enable the design of novel nanophotonic resonators.
+For instance, a resonator for efficient wavelength-conversion could be designed by creating a structure with multiple well-placed resonant frequencies~\cite{Riv09}.
+Furthermore, effects such as mode overlap and the use of frequency-dependent refractive index materials could be taken into account with such a method.
+
+\subsection*{Acknowledgements}
+This work has been supported in part by the AFOSR MURI for Compex and Robust On-chip Nanophotonics (Dr. Gernot Pomrenke).
+We thank Prof. Stephen Boyd for many fruitful discussions regarding convex optimization.
+
+% 
+% \documentclass[10pt,letterpaper]{article}
+% \usepackage{opex3}
+% \usepackage{amsmath}
+% \usepackage{graphicx}
+% 
+% \begin{document}
+% \title{Inverse design of a three-dimensional nanophotonic resonator}
+% \author{Jesse Lu, Stephen Boyd, and Jelena Vu\v{c}kovi\'{c}}
+% \address{Stanford University, \\ Stanford, C.A., 94305}
+% \email{jesselu@stanford.edu}
+% 
+% 
+% \begin{abstract} 
+% The inverse design of a three-dimensional nanophotonic resonator is presented.
 The design methodology is computationally fast (10 minutes on a standard desktop workstation) and utilizes a 2.5-dimensional approximation of the full three-dimensional structure.
@@
 % 8808 35648
-\end{abstract}
-
-\ocis{(230.5750) Resonators.} % REPLACE WITH CORRECT OCIS CODES FOR YOUR ARTICLE
-
-%%%%%%%%%%%%%%%%%%%%%%% References %%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{thebibliography}{99}
-\bibitem{miller} D. A. B. Miller, ``Rationale and challenges for optical interconnects to electronic chips,'' Proc. of the IEEE \textbf{88}, 728-749 (2000).
-\bibitem{prevwork} J. Lu and J. Vuckovic, ``Inverse design of nanophotonic structures using complementary convex optimization,'' Opt. Express \textbf{18}, 3793-3804 (2010).
-\bibitem{inan} U. Inan, A. Inan, \emph{Electromagnetic Waves} (Prentice Hall, 2000), page 296.
-\bibitem{yee} K. Yee, ``Numerical solution of initial boundary value problems involving maxwell's equations in isotropic media,'' IEEE Trans. Antennas Propag. Mag. \textbf{14}, 302-307 (1966).
-\bibitem{boydbook} S. Boyd and L. Vandenberghe, \emph{Convex Optimization} (Cambridge University Press, 2004).
-\bibitem{altdir} S.
+% \end{abstract}
+% 
+% \ocis{(230.5750) Resonators.} % REPLACE WITH CORRECT OCIS CODES FOR YOUR ARTICLE
+% 
+% %%%%%%%%%%%%%%%%%%%%%%% References %%%%%%%%%%%%%%%%%%%%%%%%%
+% \begin{thebibliography}{99}
+% \bibitem{miller} D. A. B. Miller, ``Rationale and challenges for optical interconnects to electronic chips,'' Proc. of the IEEE \textbf{88}, 728-749 (2000).
+% \bibitem{prevwork} J. Lu and J. Vuckovic, ``Inverse design of nanophotonic structures using complementary convex optimization,'' Opt. Express \textbf{18}, 3793-3804 (2010).
+% \bibitem{inan} U. Inan, A. Inan, \emph{Electromagnetic Waves} (Prentice Hall, 2000), page 296.
+% \bibitem{yee} K. Yee, ``Numerical solution of initial boundary value problems involving maxwell's equations in isotropic media,'' IEEE Trans. Antennas Propag. Mag. \textbf{14}, 302-307 (1966).
+% \bibitem{boydbook} S. Boyd and L. Vandenberghe, \emph{Convex Optimization} (Cambridge University Press, 2004).
+% \bibitem{altdir} S.
 Boyd, N.
@@
 Eckstein are preparing a manuscript to be called, ``Distributed Optimization and Statistical Learning via the Alternating Direction Method of Multipliers,'' \verb+http://www.stanford.edu/~boyd/papers/distr_opt_stat_learning_admm.html+.
-\bibitem{cholmod} Y.
+% \bibitem{cholmod} Y.
 Chen, T.
@@
 3, 2009.
-\bibitem{cvx} M. Grant and S. Boyd, \emph{CVX: Matlab software for disciplined convex programming}, version 1.21. \verb+http://cvxr.com/cvx+, January 2011.
-\bibitem{digitize} D. Englund, I. Fushman, and J. Vuckovic, ``General recipe for designing photonic crystal cavities,'' Opt. Express \textbf{13}, 5961-5975 (2005).
-\end{thebibliography}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%  body  %%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Motivation}
+% \bibitem{cvx} M. Grant and S. Boyd, \emph{CVX: Matlab software for disciplined convex programming}, version 1.21. \verb+http://cvxr.com/cvx+, January 2011.
+% \bibitem{digitize} D. Englund, I. Fushman, and J. Vuckovic, ``General recipe for designing photonic crystal cavities,'' Opt. Express \textbf{13}, 5961-5975 (2005).
+% \end{thebibliography}
+%  
+% %%%%%%%%%%%%%%%%%%%%%%%%%%  body  %%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Begin of 2.5 D (Motivation)}
 To date, the design of nanophotonic devices has generally involved a lengthy (days, weeks) process in which one perturbs, by trial-and-error, canonical structures such as photonic crystals or waveguide-coupled rings to achieve the desired performance for the device.
@@
 \begin{figure}[hbt]
-\centering\includegraphics[width=\textwidth]{approx}
+\centering\includegraphics[width=\textwidth]{p2/approx}
 \caption{(a) For computational feasibility, the resonant fields of a planar nanophotonic device are approximated as those of a truncated holey fiber with identical dielectric structure.
@@
 \begin{figure}[hbt]
-\centering\includegraphics[width=\textwidth]{target}
+\centering\includegraphics[width=\textwidth]{p2/target}
 \caption{The (a) dielectric structure, $\epsilon$, and (b) target field, $E$ ($E_y$ shown only), produced after 75 iterations (10 minutes) on a $160\times 160$ grid.
@@
 \begin{figure}[hbt]
-\centering\includegraphics[width=\textwidth]{the_prog}
+\centering\includegraphics[width=\textwidth]{p2/the_prog}
 \caption{Value of the physics residual (blue) and design objective, or mode volume, (red) at each iteration.
@@
 \begin{figure}[hbt]
-\centering\includegraphics[width=\textwidth]{compare}
+\centering\includegraphics[width=\textwidth]{p2/compare}
 \caption{Comparison ($E_y$) of (a) the target field from the inverse design method (from Fig.~\ref{target}), (b) the actual 2.5-dimensional fiber mode, and (c) the field from the full three-dimensional FDTD simulation.
@@
 \begin{figure}[hbt]
-\centering\includegraphics[width=\textwidth]{the_xsec}
+\centering\includegraphics[width=\textwidth]{p2/the_xsec}
 \caption{Comparison of the cross sections of the $E_y$ field along the x-axis from the target field (blue), the actual 2.5-dimensional fiber mode (green), and the field from the full three-dimensional FDTD simulation (red).
@@
 \begin{figure}[hbt]
-\centering\includegraphics[width=\textwidth]{qcomp}
+\centering\includegraphics[width=\textwidth]{p2/qcomp}
 \caption{Comparison of the Fourier transforms of the $E_y$ fields of the (a) the target field from the inverse design method, (b) the actual 2.5-dimensional fiber mode, and (c) the field from the full three-dimensional FDTD simulation.
@@
 This work has been supported in part by the AFOSR MURI for Complex and Robust On-chip Nanophotonics (Dr. Gernot Pomrenke), grant number FA9550-09-1-0704.
-\end{document}

### 2013-03-28 thesis/chapter3.tex
Put together papers.

% \documentclass[letterpaper,10pt]{article}
% \usepackage{graphicx}
% \usepackage{opex3}
% \usepackage{amsmath,amssymb}
% 
% 
% \begin{document}
% \title{Objective-first design of 
%     high-efficiency, small-footprint couplers between 
%     arbitrary nanophotonic waveguide modes}
% \author{Jesse Lu$^\ast$ and Jelena Vu\v{c}kovi\'{c}}
% \address{Stanford University, Stanford, California, USA.}
% \email{jesselu@stanford.edu}
% 
% \begin{abstract}
% We present an algorithm for designing
%     high efficiency ($\sim$98\%), 
%     small-footprint (1.5-4 square vacuum wavelengths)
%     couplers between arbitrary nanophotonic waveguide modes
%     in two dimensions.
% Our ``objective-first'' method is
%     computationally fast (15 minutes on a single-core personal computer), 
%     requires no trial-and-error, and
%     does not require guessing a good starting design.
% We demonstrate designs for various coupling problems which suggest 
%     that our method allows for the design of any 
%     single-mode, linear optical device.
% \end{abstract}
% \ocis{230.75370, 130.3990.}
% 
% \begin{thebibliography}{99}
% \bibitem{fibergrating} Y. Tang, Z. Wang, L. Wosinski, U. Westergren, and S. He,
%     ``Highly efficient nonuniform grating coupler for silicon-on-insulator 
%     nanophotonic circuits,''
%     Opt. Lett. \textbf{35}, 1290-1292 (2010).
% \bibitem{ridge}  K. K. Lee, D. R. Lim, L.C. Kimerling, J. Shin, and F. Cerrina, 
%     ``Fabrication of ultralow-loss Si/SiO2 waveguides by roughness reduction,''
%     Opt. Lett. \textbf{26}, 1888-1890 (2001).
% \bibitem{pcslow} Y. A. Vlasov, M. O'Boyle, H. F. Hamann, and S. J. McNab,
%     ``Active control of slow light on a chip with photonic crystal waveguides,''
%     Nature \textbf{438}, 65-69 (2005).
% \bibitem{slotfocus} M. Lipson, 
%     ``Guiding, modulating, and emitting light on 
%     silicon-challenges and opportunities,'' 
%     J. Lightwave Technol. \textbf{23}, 4222-4238 (2005).
% \bibitem{active} J. Van Campenhout, P. Rojo Romeo, P. Regreny, C. Seassal, 
%     D. Van Thourhout, S. Verstuyft, L. Di Cioccio, J.-M. Fedeli, 
%     C. Lagahe, and R. Baets, 
%     ``Electrically pumped InP-based microdisk lasers integrated with a 
%     nanophotonic silicon-on-insulator waveguide circuit,'' 
%     Opt. Express \textbf{15}, 6744-6749 (2007).
% \bibitem{metallic} L. Tang, S. E. Kocabas, S. Latif, A. K. Okyay, 
%     D. S. Ly-Gagnon, K. C. Saraswat, and D. A. B. Miller, 
%     ``Nanometre-scale germanium photodetector enhanced by a 
%     near-infrared dipole antenna,'' 
%     Nature Photonics \textbf{2}, 226-229 (2008).
% % \bibitem{fwadia} V. R. Almeida, R. R. Panepucci, and M. Lipson, 
% %     ``Nanotaper for compact mode conversion,'' 
% %     Opt. Lett. \textbf{28}, 1302-1304 (2003) 
% % \bibitem{wwadia} S. G. Johnson, P. Bienstman,  M. A. Skorobogatiy, 
% %     M. Ibanescu1, E. Lidorikis, and J. D. Joannopoulos,
% %     ``Adiabatic theorem and continuous coupled-mode theory for 
% %     efficient taper transitions in photonic crystals,''
% %     Phys. Rev. E \textbf{66}, 066608 (2002)
% % \bibitem{deriv} F. Wang, J. S. Jensen, O. Sigmund, 
% %     ``Robust topology optimization of photonic crystal waveguides with 
% %     tailored dispersion properties.'' 
% %     J. Opt. Soc. Am. B \textbf{28}, 387-397 (2011)
% % \bibitem{boydbook} S. Boyd, and L. Vandenberghe, 
% %     \emph{Convex Optimization} 
% %     (Cambridge University Press, 2004)
% \bibitem{prevwork} J. Lu, S. Boyd, and J. Vuckovic, 
%     ``Inverse design of a three-dimensional nanophotonic resonator,''
%     Opt. Express \textbf{19}, 10563-10750 (2011). 
% \bibitem{veronis} G. Veronis, and S. Fan, 
%     ``Theoretical investigations of compact couplers between dielectric slab 
%     waveguides and two-dimensional metal-dielectric-metal plasmonic waveguides,'' 
%     Opt. Express \textbf{15}, 1211-1221 (2007).
% \bibitem{yang} R. Yang, R. A. Wahsheh, Z. Lu, and M. A. G. Abushagur, 
%     ``Efficient light coupling between dielectric slot waveguide and plasmonic
%     slot waveguide,'' Opt. Lett. \textbf{35}, 649-651 (2010).
% \bibitem{code} \url{www.github.com/JesseLu/objective-first}
% \end{thebibliography}
% 
\chapter{Objective-first design}
\section{Motivation}

% Why is waveguide mode conversion important?
Optical mode conversion, 
    the efficient transfer of photons from one guided mode to another,
    is a fundamental requirement in nanophotonics.
For instance, efficient conversion between waveguides modes
    is essential for:
    \begin{itemize}
        \item Coupling to and from optical fiber\cite{fibergrating}, 
        to communicate with the outside world.
    \item Coupling between various nanophotonic waveguides, 
        since different waveguides are best suited for different applications.
        For example, ridge waveguides seem ideal for 
            low-loss transport\cite{ridge},
            but other waveguides, 
            such as photonic crystal waveguides or slot waveguides,
            may be better suited for slow-light\cite{pcslow} 
            or nonlinear optical devices based on 
            localized field intensities\cite{slotfocus}.
    \item Coupling between different materials systems such as
       passive, active\cite{active}, and metallic\cite{metallic} devices. 
    \end{itemize}
In fact, the problem of converting between nanophotonic modes is essentially
    the function of all linear nanophotonic devices, since
    any linear device is completely characterized by its input and output modes
    and the coupling coefficients between them.

In this paper, we present a method to solve the problem 
    of designing single-mode, linear nanophotonic devices.
We then demonstrate this method by designing coupling structures 
    between various nanophotonic waveguides.
Furthermore, we show that our method 
     does not require a good initial design,
     is computationally fast,
     and can generate high efficiency couplers within a very small footprint. 
% 
% 
% % Why are current solutions insufficient?
% % Brute force
% Of the design strategies currently available,
%     brute-force parameter search is the most often employed 
%     because of its sheer simplicity.
% Although it may be suitable for tuning existing designs,
%     the parameter space for most practical devices is simply too large
%     for such a strategy to be tractable.
% 
% % Adiabatic mode conversion (large devices, symmetry breaking)
% Adiabatic mode conversion strategies have been succesful
%     for certain fiber-waveguide\cite{fwadia} and 
%     waveguide-waveguide\cite{wwadia} couplers,
%     even if the resulting devices often require large footprints.
% However, adiabatic approaches cannot be used in many important cases 
%     such as coupling in the out-of-plane direction, or
%     coupling between modes of opposite symmetry.

% How does your algorithm solve this problem?
% \subsection{Advantages of objective-first design}
\section{Objective-first approach}
% What is objective-first optimization?
Physical structures are typically designed by solving the following problem:
    \begin{subequations}\label{eq:adj}
    \begin{align} 
    \text{decrease} & \quad f(x) \label{eq:adj:obj} \\ 
    \text{subject to} & \quad g(x,p) = 0, \label{eq:adj:con}
    \end{align}
    \end{subequations}
    where $x$ is the field variable and $p$ is the structure variable.
Here, $f(x)$, the \emph{design objective}, 
    calculates the performance of the device 
    (e.g. amount of power lost); 
    while $g(x,p)$ is the underlying physical equation for the system
    (e.g. the electromagnetic wave equation).

In contrast, the objective-first approach solves 
    \begin{subequations}\label{eq:ob1}
    \begin{align} 
    \text{decrease} & \quad \|g(x,p)\|^2 \label{eq:ob1:obj} \\ 
    \text{subject to} & \quad f(x) = 0, \label{eq:ob1:con}
    \end{align}
    \end{subequations}
    where $\|g(x,p)\|^2$ is the \emph{physics residual}.
We term this formulation ``objective-first''
    because the design objective is prioritized even above satisfying physics;
    specifically, we force our design to always exhibit the desired performance
    ($f(x) = 0$), even at the expense of
    not perfectly satisfying the underlying physics which governs its operation.

The motivation behind this formulation is two-fold.
First, this approach allows one to arrive at a locally-optimal design rapidly 
    by allowing $x$ and $p$ to vary independently, 
    as opposed to Eq.~\ref{eq:adj}
    where the value of $x$ is completely dependent on $p$.
Second, it enables an increase in the likelihood of 
    arriving at a high efficiency design
    by forcibly imposing $f(x) = 0$,
    and thereby circumvents any local optima consisting of
    low-performance devices.

% How is it applied to waveguide coupler design?
\section{Objective-first design of waveguide couplers}
We now demonstrate the objective-first approach
    by designing waveguide couplers in two-dimensions.
As such, we do not analyze effects which are only present in full 
    three-dimensional systems, such as out-of-plane losses.
Specifically, we work in the two-dimensional transverse electric mode,
    choosing $H_z$ as the field variable $x$,
    and $\epsilon^{-1}$ (the inverse of the permittivity) 
    as the structure variable $p$.
This results in the following form of the physics residual,
    \begin{equation}
    \|g(x,p)\|^2 = 
    \|g(H_z, \epsilon^{-1})\|^2 = 
    \| \nabla \times \epsilon^{-1} \nabla \times H_z - \mu_0 \omega^2 H_z \|^2,
    \end{equation}
    where $\omega$ is the angular frequency,
    and $\mu_0$ is the permeability of free-space.

In order to produce a method applicable 
    to the design of any linear nanophotonic device,
    we note that its performance
    will be completely characterized by the fields along its boundary,
    and therefore, 
    we choose a boundary-value formulation for the design objective 
    as shown in Fig.~\ref{fig:intro}.
Namely, we first compute the boundary fields needed to obtain
    perfect performance, $H_z^\text{perfect}$,
    and then form the design objective as
    \begin{equation}
    f(x) = f(H_z) = \begin{bmatrix}
        H_z - H_z^\text{perfect} \\
        \frac{\partial H_z}{\partial n} - 
            \frac{\partial H_z^\text{perfect}}{\partial n}
        \end{bmatrix}_\text{boundary}
        = 0,
    \end{equation}
    where $\partial H_z / \partial n$ 
    denotes the spatial derivative in the direction normal to the boundary.

\begin{figure}[htb]
    \centering
    \includegraphics[width=0.8\textwidth]{p3/intro} 
    \caption{Boundary-value formulation of the design objective.
        The values of $H_z^\text{perfect}$, 
            defined along the dashed box surrounding the design area
            (coupling structure), 
            are shown in orange. 
        The values of $H_z^\text{perfect}$ along the top and bottom edges
            of the dashed box are set to zero.
        In this schematic, the fundamental and second-order waveguide modes
            have been chosen as the input and output modes respectively.}
    \label{fig:intro}
\end{figure}

Such a design objective is both extremely simple and widely adaptable 
    to the design of linear nanophotonic devices in general.
On the other hand, such a formulation often prohibits the physics residual 
    from disappearing completely; 
    however, we find that very good device performance is still obtained
    as long as the physics residual is sufficiently small.

Lastly, we employ an alternating directions strategy,
    where both $x$ and $p$ are solved iteratively\cite{prevwork}
    and limit the allowable values of $\epsilon$ to be between
    the permittivity of vacuum and of silicon,
    \begin{equation}
    \epsilon_0 \le \epsilon \le \epsilon_\text{silicon}.
    \end{equation}
Note that a completely binary structure,
    where $\epsilon = \{\epsilon_0, \epsilon_\text{silicon}\}$,
    is needed for manufacturing purposes; this will be pursued in a future work
    along with an analysis of robustness to fabrication imperfections.
That said, the final designs presented here 
    all have significant portions which are already binary.

\subsection{Coupler designs}
We now present five results which suggest our method
    is indeed able to design arbitrary single-mode, linear nanophotonic devices.
These results comprise of couplers between 
    the following nanophotonic waveguides:
    \begin{enumerate}
    \item coupling between waveguides of different refractive index and width
        (Fig.~\ref{fig:fiber});
    \item coupling between waveguide modes of different order and symmetry
        (Fig.~\ref{fig:mode});
    \item coupling between waveguides that confine light 
        using different principles 
        (index guided vs. distributed Bragg reflection guided), 
        i.e., between a slab waveguide and a photonic crystal fiber
        (Fig.~\ref{fig:aircore})
    \item coupling from a dielectric to a plasmonic metal-insulator-metal 
        waveguide (Fig.~\ref{fig:mim}); and
    \item coupling from a dielectric waveguide to a (plasmonic) metal wire
        (Fig.~\ref{fig:wire}).
    \end{enumerate}
All the designs presented are both highly efficient 
    ($\sim 98\%$ coupling efficiency, in contrast to previous designs
    which achieve only $\sim 70\%$ coupling efficiency\cite{veronis,yang})
    and extremely compact 
    (with footprints of only 1.5-4 square vacuum wavelengths).

Note, however, that the small footprint of the designs presented does not 
    imply small, unresolvable feature sizes.
On the other hand, assuming a vacuum wavelength of 1550 nm,
    the smallest possible feature in any of the examples presented is still
    37 nm $\times$ 37 nm (see Fig.~\ref{fig:fiber}, for example),
    as given by the size of a single grid point;
    placing virtually all designs within reach of current-generation lithographic
    systems.

In addition, good starting points were not required; 
    all initial designs were simply $\epsilon = 9$ everywhere
    (a somewhat arbitrary guess, other values work as well).
Finally, only 15 minutes on a single-core personal computer
    were needed to obtain each design.

In the appendix, we further demonstrate the generality of our method
    by presenting several additional examples including
    \begin{enumerate}
    \item coupling between all four modes of a wide dielectric waveguide;
    \item coupling from a wide, low-index waveguide to the output waveguides in 
        Figs~\ref{fig:mode}-\ref{fig:wire}; and
    \item coupling to selected channels of a set of five plasmonic waveguides.
    \end{enumerate}

\begin{figure}[htb]
    \centering
    \includegraphics[width=0.8\textwidth]{p3/1} 
    \caption{Coupler from a narrow, high-index ($\epsilon=12.25$) waveguide to
            a wide, low-index ($\epsilon=2.25$) waveguide. 
        The $H_z^\text{perfect}$ boundary values used as 
            the design objective are shown in the upper-left plots, 
            the generated structure is shown in the upper-right plot, and
            the simulated $H_z$ fields of the device are shown 
            in the bottom two plots.
        The computed efficiency of the coupler is high, $99.8\%$, and
            the device is also extremely compact, 
            convering only $36 \times 76$ grid points,
            where the vacuum wavelength is 42 grid points
            (footprint of $1.55$ square vacuum wavelengths).
        Computation time was 15 minutes on a personal computer.}
    \label{fig:fiber}
\end{figure}
\begin{figure}[htb]
    \centering
    \includegraphics[width=0.8\textwidth]{p3/2} 
    \caption{Coupler that converts the fundamental waveguide mode to the
            second-order waveguide mode.
        This problem is quite difficult since the two modes are of 
            opposite symmetry.
        For example, adiabatic approaches cannot be applied to this case.
        However, our method produces a device 
            (which has the same dimensions and vacuum wavelength as 
            Fig.~\ref{fig:fiber})  
            with a coupling efficiency of $98.0\%$. 
        Computation time was 15 minutes on a personal computer.
        }
    \label{fig:mode}
\end{figure}
\begin{figure}[htb]
    \centering
    \includegraphics[width=0.8\textwidth]{p3/3}
    \caption{Coupler between a dielectric slab waveguide to 
            an air-core waveguide.
        Here, not only are the modes of opposite symmetry,
            but the output waveguide operates on a fundamentally different
            principle (distributed reflection) than the input waveguide 
            (index guided).
        The device still achieves an efficiency of $98.9\%$, demonstrating the
            versatility of our method.
        The vacuum wavelength is 25 grid points, 
            while the device footprint is still $36 \times 76$ grid points
            (footprint of 4.38 square vacuum wavelengths).
        Computation time was 15 minutes on a personal computer.
        }
        \label{fig:aircore}
\end{figure}
\begin{figure}[htb]
    \centering
    \includegraphics[width=0.8\textwidth]{p3/4}
    \caption{Coupler between a dielectric slab waveguide to 
            a plasmonic metal-insulator-metal waveguide.
        The efficiency of the device is $97.5\%$ and 
            has the same wavelength and footprint as the device in
            Fig.~\ref{fig:aircore}.
        Computation time was 15 minutes on a personal computer.
        }
        \label{fig:mim}
\end{figure}
\begin{figure}[htb]
    \centering
    \includegraphics[width=0.8\textwidth]{p3/5}
    \caption{Coupler between a dielectric slab waveguide to 
            a plasmonic wire waveguide.
        The efficiency of the device is $99.1\%$ and 
            has the same wavelength and footprint as the device in
            Fig.~\ref{fig:aircore}.
        Computation time was 15 minutes on a personal computer.
        }
        \label{fig:wire}
\end{figure}
\clearpage

\section{Conclusion}
We develop a fundamentally new approach to designing physical structures,
    which we term ``objective-first'', 
    in that we choose to satisfy the design objective 
    even above satisfying the physical equation which governs its operation.
We then apply this approach to the design of 
    various nanophotonic waveguide couplers,
    and show that our method produces
    high-efficiency designs ($\sim 98\%$ efficiency) 
    in small footprints (1.5-4 square vacuum wavelengths)
    without needing a good starting point.
Furthermore, we suggest that such a methodology may be applicable
    to the design of any single-mode, linear nanophotonic device.\\

This work has been supported by the 
    AFOSR MURI for Complex and Robust On-chip Nanophotonics 
    (Dr. Gernot Pomrenke), grant number FA9550-09-1-0704.
The Matlab code used is available online\cite{code}.
% \clearpage
% \begin{appendix}
\section{Additional mode coupler designs}
In this section, we present additional mode coupler designs.
A wide, high-index waveguide is used at both the input and output ports,
    and all permutations of couplers are fabricated among
    the first four propagating modes.
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\textwidth]{p3/6}
    \caption{
        Coupler from the first-order to the second-order mode 
            of a wide dielectric waveguide.
        Efficiency: $99.3\%$,
        footprint: $1.55$ square vacuum wavelengths.
        }
        % \label{fig:wire}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\textwidth]{p3/7}
    \caption{
        Coupler from the first-order to the third-order mode 
            of a wide dielectric waveguide.
        Efficiency: $98.3\%$,
        footprint: $1.55$ square vacuum wavelengths.
        }
        % \label{fig:wire}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\textwidth]{p3/8}
    \caption{
        Coupler from the first-order to the fourth-order mode 
            of a wide dielectric waveguide.
        Efficiency: $90.6\%$,
        footprint: $1.55$ square vacuum wavelengths.
        }
        % \label{fig:wire}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\textwidth]{p3/9}
    \caption{
        Coupler from the second-order to the third-order mode 
            of a wide dielectric waveguide.
        Efficiency: $96.8\%$,
        footprint: $1.55$ square vacuum wavelengths.
        }
        % \label{fig:wire}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\textwidth]{p3/10}
    \caption{
        Coupler from the second-order to the fourth-order mode 
            of a wide dielectric waveguide.
        Efficiency: $86.3\%$,
        footprint: $1.55$ square vacuum wavelengths.
        }
        % \label{fig:wire}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\textwidth]{p3/11}
    \caption{
        Coupler from the third-order to the fourth-order mode 
            of a wide dielectric waveguide.
        Efficiency: $80.1\%$,
        footprint: $1.55$ square vacuum wavelengths.
        }
        % \label{fig:wire}
\end{figure}
\clearpage
\section{Additional designs with wide, low-index input waveguide}
We now reproduce Figs~\ref{fig:mode}-\ref{fig:wire}
    but instead use a wide, low-index waveguide as the input.
Once again, this is to demonstrate the generality of our method;
    namely, that it can be applied to the design of nearly any
    single-mode, linear nanophotonic device.
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\textwidth]{p3/12}
    \caption{
        Coupler from a wide, low-index waveguide to the
            second-order mode of a narrow, high-index waveguide.
        Efficiency: $96.9\%$,
        footprint: $1.55$ square vacuum wavelengths.
        }
        % \label{fig:wire}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\textwidth]{p3/13}
    \caption{
        Coupler from a wide, low-index waveguide to an 
            ``air-core'' waveguide mode.
        Efficiency: $99.0\%$,
        footprint: $4.38$ square vacuum wavelengths.
        }
        % \label{fig:wire}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\textwidth]{p3/14}
    \caption{
        Coupler from a wide, low-index waveguide to a
            metal-insulator-metal plasmonic waveguide mode.
        Efficiency: $96.7\%$,
        footprint: $4.38$ square vacuum wavelengths.
        }
        % \label{fig:wire}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\textwidth]{p3/15}
    \caption{
        Coupler from a wide, low-index waveguide to a
            plasmonic wire waveguide mode.
        Efficiency: $99.7\%$,
        footprint: $4.38$ square vacuum wavelengths.
        }
        % \label{fig:wire}
\end{figure}
\clearpage

\section{Additional designs with multiple output plasmonic waveguides}
We also present ``selector'' designs where photons are coupled to 
    only one of five possible plasmonic output waveguides.
We demonstrate these selector designs for both metal-insulator-metal and
    metal-wire plasmonic waveguides.
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\textwidth]{p3/16}
    \caption{
        Coupler from a dielectric waveguide to the 
            lowest branch of a set of five plasmonic wire waveguides.
        Efficiency: $94.0\%$,
        footprint: $4.38$ square vacuum wavelengths.
        }
        % \label{fig:wire}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\textwidth]{p3/17}
    \caption{
        Coupler from a dielectric waveguide to the 
            second branch of a set of five plasmonic wire waveguides.
        Efficiency: $97.3\%$,
        footprint: $4.38$ square vacuum wavelengths.
        }
        % \label{fig:wire}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\textwidth]{p3/18}
    \caption{
        Coupler from a dielectric waveguide to the 
            middle branch of a set of five plasmonic wire waveguides.
        Efficiency: $98.5\%$,
        footprint: $4.38$ square vacuum wavelengths.
        }
        % \label{fig:wire}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\textwidth]{p3/19}
    \caption{
        Coupler from a dielectric waveguide to the 
            middle branch of a set of five plasmonic 
            metal-insulator-metal waveguides.
        Efficiency: $97.7\%$,
        footprint: $4.38$ square vacuum wavelengths.
        }
        % \label{fig:wire}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\textwidth]{p3/20}
    \caption{
        Coupler from a dielectric waveguide to the 
            fourth branch of a set of five plasmonic 
            metal-insulator-metal waveguides.
        Efficiency: $95.6\%$,
        footprint: $4.38$ square vacuum wavelengths.
        }
        % \label{fig:wire}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\textwidth]{p3/21}
    \caption{
        Coupler from a dielectric waveguide to the 
            uppermost branch of a set of five plasmonic 
            metal-insulator-metal waveguides.
        Efficiency: $87.5\%$,
        footprint: $4.38$ square vacuum wavelengths.
        }
        % \label{fig:wire}
\end{figure}
\clearpage
% \end{appendix}

### 2013-03-28 thesis/chapter4.tex
Put together papers.

--- 2013-03-22 paper/paper.tex
@@
-\documentclass[letterpaper,10pt]{article}
-\usepackage{graphicx}
-\usepackage{opex3}
-\usepackage{amsmath,amssymb}
-\input defs.tex
-\begin{document}
-\title{Nanophotonic Computational Design}
-\author{Jesse Lu$^\ast$ and Jelena Vu\v{c}kovi\'{c}}
-\address{Stanford University, Stanford, California, USA.}
-\email{jesselu@stanford.edu}
-
-\begin{abstract}
-In contrast to designing nanophotonic devices 
-    by tuning a handful of device parameters, 
-    we have developed a computational method 
-    which utilizes the full parameter space to design linear nanophotonic devices.
-We show that our method may indeed be capable of designing 
-    any linear nanophotonic device by demonstrating designed structures which
-    are fully three-dimensional and multi-modal,
-    exhibit novel functionality,
-    have very compact footprints,
-    exhibit high efficiency, and
-    are manufacturable.
-In addition, we also demonstrate the ability to produce structures
-    which are strongly robust to wavelength and temperature shift,
-    as well as fabrication error.
-Critically, we show that our method 
-    does not require the user to be a nanophotonic expert or 
-    to perform any manual tuning. 
-Instead, we are able to design devices 
-    solely based on the user's desired performance specification for the device.
-\end{abstract}
-\ocis{230.75370, 130.3990.}
-
-\begin{thebibliography}{99}
-\bibitem{ob1_wg} J. Lu, J. Vuckovic, ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes,'' 
-    Opt. Express \textbf{20}, 7221-7236 (2012)
-\bibitem{admm} S. Boyd, N. Parikh, E. Chu, B. Peleato, and J. Eckstein,
-    ``Distributed Optimization and Statistical Learning via the Alternating Direction Method of Multipliers,''
-    Foundations and Trends in Machine Learning \textbf{3}, 1-122 (2011). 
-\bibitem{wonseok} W. Shin and S. Fan, ``Choice of the perfectly matched layer boundary condition for frequency-domain Maxwell’s equations solvers,''
-    J. of Comp. Phys \textbf{231}, 3406-3431 (2012).
-\bibitem{levelset} S. Osher and R. Fedkiw, \emph{Level Set Methods and Dynamic Implicit Surfaces: 1st Edition} (Springer, 2002).
-\bibitem{2dsplitter} Y. Jiao, S. Fan, and D. A. B. Miller, 
-    ``Demonstrations of systematic photonic crystal design and optimization by low rank adjustment: an extremely compact mode separator'', Opt. Lett. \textbf{30}, 140-142 (2005).
-\bibitem{baets}F. Van Laere, G. Roelkens, M. Ayre, J. Schrauwen, D. Taillaert, D. Van Thourhout, T. F. Krauss, and R. Baets,
-    ``Compact and highly efficient grating couplers between optical fiber and nanophotonic waveguides,''
-    J. of Lightwave Tech. \textbf{25}, 151-156 (2007).
-% \bibitem{fibergrating} Y. Tang, Z. Wang, L. Wosinski, U. Westergren, and S. He,
-%     ``Highly efficient nonuniform grating coupler for silicon-on-insulator 
-%     nanophotonic circuits,''
-%     Opt. Lett. \textbf{35}, 1290-1292 (2010).
-% \bibitem{ridge}  K. K. Lee, D. R. Lim, L.C. Kimerling, J. Shin, and F. Cerrina, 
-%     ``Fabrication of ultralow-loss Si/SiO2 waveguides by roughness reduction,''
-%     Opt. Lett. \textbf{26}, 1888-1890 (2001).
-% \bibitem{pcslow} Y. A. Vlasov, M. O'Boyle, H. F. Hamann, and S. J. McNab,
-%     ``Active control of slow light on a chip with photonic crystal waveguides,''
-%     Nature \textbf{438}, 65-69 (2005).
-% \bibitem{slotfocus} M. Lipson, 
-%     ``Guiding, modulating, and emitting light on 
-%     silicon-challenges and opportunities,'' 
-%     J. Lightwave Technol. \textbf{23}, 4222-4238 (2005).
-% \bibitem{active} J. Van Campenhout, P. Rojo Romeo, P. Regreny, C. Seassal, 
-%     D. Van Thourhout, S. Verstuyft, L. Di Cioccio, J.-M. Fedeli, 
-%     C. Lagahe, and R. Baets, 
-%     ``Electrically pumped InP-based microdisk lasers integrated with a 
-%     nanophotonic silicon-on-insulator waveguide circuit,'' 
-%     Opt. Express \textbf{15}, 6744-6749 (2007).
-% \bibitem{metallic} L. Tang, S. E. Kocabas, S. Latif, A. K. Okyay, 
-%     D. S. Ly-Gagnon, K. C. Saraswat, and D. A. B. Miller, 
-%     ``Nanometre-scale germanium photodetector enhanced by a 
-%     near-infrared dipole antenna,'' 
-%     Nature Photonics \textbf{2}, 226-229 (2008).
-% % \bibitem{fwadia} V. R. Almeida, R. R. Panepucci, and M. Lipson, 
-% %     ``Nanotaper for compact mode conversion,'' 
-% %     Opt. Lett. \textbf{28}, 1302-1304 (2003) 
-% % \bibitem{wwadia} S. G. Johnson, P. Bienstman,  M. A. Skorobogatiy, 
-% %     M. Ibanescu1, E. Lidorikis, and J. D. Joannopoulos,
-% %     ``Adiabatic theorem and continuous coupled-mode theory for 
-% %     efficient taper transitions in photonic crystals,''
-% %     Phys. Rev. E \textbf{66}, 066608 (2002)
-% % \bibitem{deriv} F. Wang, J. S. Jensen, O. Sigmund, 
-% %     ``Robust topology optimization of photonic crystal waveguides with 
-% %     tailored dispersion properties.'' 
-% %     J. Opt. Soc. Am. B \textbf{28}, 387-397 (2011)
-% % \bibitem{boydbook} S. Boyd, and L. Vandenberghe, 
-% %     \emph{Convex Optimization} 
-% %     (Cambridge University Press, 2004)
-% \bibitem{prevwork} J. Lu, S. Boyd, and J. Vuckovic, 
-%     ``Inverse design of a three-dimensional nanophotonic resonator,''
-%     Opt. Express \textbf{19}, 10563-10750 (2011). 
-% \bibitem{veronis} G. Veronis, and S. Fan, 
-%     ``Theoretical investigations of compact couplers between dielectric slab 
-%     waveguides and two-dimensional metal-dielectric-metal plasmonic waveguides,'' 
-%     Opt. Express \textbf{15}, 1211-1221 (2007).
-% \bibitem{yang} R. Yang, R. A. Wahsheh, Z. Lu, and M. A. G. Abushagur, 
-%     ``Efficient light coupling between dielectric slot waveguide and plasmonic
-%     slot waveguide,'' Opt. Lett. \textbf{35}, 649-651 (2010).
-% \bibitem{code} \url{www.github.com/JesseLu/objective-first}
-\end{thebibliography}
-
+% \documentclass[letterpaper,10pt]{article}
+% \usepackage{graphicx}
+% \usepackage{opex3}
+% \usepackage{amsmath,amssymb}
+% 
+% 
+% \newcommand{\myfig}[2]{
+%     \begin{figure}[!h]
+%     \begin{centering}
+%     \includegraphics[width=0.8\textwidth]{fig/#1}
+%     \caption{#2}\label{#1}
+%     \end{centering}
+%     \end{figure}
+% }
+% 
+% \newcommand{\Eq}[1]{Eq.~\eqref{#1}}
+% \newcommand{\Fig}[1]{Fig.~\ref{#1}}
+% \newcommand{\eq}[1]{eq.~\eqref{#1}}
+% \newcommand{\fig}[1]{fig.~\ref{#1}}
+% \newcommand{\BI}{\begin{itemize}\item}
+% \newcommand{\I}{\item}
+% \newcommand{\EI}{\end{itemize}}
+% \newcommand{\BEAS}{\begin{eqnarray}}
+% \newcommand{\EEAS}{\end{eqnarray}}
+% % \newcommand{\BEAS}{\begin{IEEEeqnarray}{rl}}
+% % \newcommand{\EEAS}{\end{IEEEeqnarray}}
+% \newcommand{\BSA}{\begin{subequations}\begin{align}}
+% \newcommand{\ESA}{\end{align}\end{subequations}}
+% \newcommand{\BE}{\begin{equation*}}
+% \newcommand{\EE}{\end{equation*}}
+% \newcommand{\BIT}{\begin{itemize}}
+% \newcommand{\EIT}{\end{itemize}}
+% 
+% \newcommand{\eg}{{\it e.g.}}
+% \newcommand{\ie}{{\it i.e.} }
+% 
+% \DeclareMathOperator*{\minimize}{\text{minimize}\quad}
+% \newcommand{\subto}{\text{subject to}\quad}
+% \newcommand{\T}{^\dagger}
+% 
+% 
+% \newcommand{\ones}{\mathbf 1}
+% \newcommand{\reals}{{\mbox{\bf R}}}
+% \newcommand{\comps}{{\mbox{\bf C}}}
+% \newcommand{\integers}{{\mbox{\bf Z}}}
+% \newcommand{\symm}{{\mbox{\bf S}}}  % symmetric matrices
+% 
+% \newcommand{\nullspace}{{\mathcal N}}
+% \newcommand{\range}{{\mathcal R}}
+% \newcommand{\Rank}{\mathop{\bf Rank}}
+% \newcommand{\Tr}{\mathop{\bf Tr}}
+% \newcommand{\diag}{\mathop{\bf diag}}
+% \newcommand{\lambdamax}{{\lambda_{\rm max}}}
+% \newcommand{\lambdamin}{\lambda_{\rm min}}
+% 
+% \newcommand{\Expect}{\mathop{\bf E{}}}
+% \newcommand{\Prob}{\mathop{\bf Prob}}
+% \newcommand{\Co}{{\mathop {\bf Co}}} % convex hull
+% \newcommand{\dist}{\mathop{\bf dist{}}}
+% \newcommand{\argmin}{\mathop{\rm argmin}}
+% \newcommand{\argmax}{\mathop{\rm argmax}}
+% \newcommand{\epi}{\mathop{\bf epi}} % epigraph
+% \newcommand{\Vol}{\mathop{\bf vol}}
+% \newcommand{\dom}{\mathop{\bf dom}} % domain
+% \newcommand{\intr}{\mathop{\bf int}}
+% 
+% \begin{document}
+% 
+% \title{Nanophotonic Computational Design}
+% \author{Jesse Lu$^\ast$ and Jelena Vu\v{c}kovi\'{c}}
+% \address{Stanford University, Stanford, California, USA.}
+% \email{jesselu@stanford.edu}
+% 
+% \begin{abstract}
+% In contrast to designing nanophotonic devices 
+%     by tuning a handful of device parameters, 
+%     we have developed a computational method 
+%     which utilizes the full parameter space to design linear nanophotonic devices.
+% We show that our method may indeed be capable of designing 
+%     any linear nanophotonic device by demonstrating designed structures which
+%     are fully three-dimensional and multi-modal,
+%     exhibit novel functionality,
+%     have very compact footprints,
+%     exhibit high efficiency, and
+%     are manufacturable.
+% In addition, we also demonstrate the ability to produce structures
+%     which are strongly robust to wavelength and temperature shift,
+%     as well as fabrication error.
+% Critically, we show that our method 
+%     does not require the user to be a nanophotonic expert or 
+%     to perform any manual tuning. 
+% Instead, we are able to design devices 
+%     solely based on the user's desired performance specification for the device.
+% \end{abstract}
+% \ocis{230.75370, 130.3990.}
+% 
+% \begin{thebibliography}{99}
+% \bibitem{ob1_wg} J. Lu, J. Vuckovic, ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes,'' 
+%     Opt. Express \textbf{20}, 7221-7236 (2012)
+% \bibitem{admm} S. Boyd, N. Parikh, E. Chu, B. Peleato, and J. Eckstein,
+%     ``Distributed Optimization and Statistical Learning via the Alternating Direction Method of Multipliers,''
+%     Foundations and Trends in Machine Learning \textbf{3}, 1-122 (2011). 
+% \bibitem{wonseok} W. Shin and S. Fan, ``Choice of the perfectly matched layer boundary condition for frequency-domain Maxwell’s equations solvers,''
+%     J. of Comp. Phys \textbf{231}, 3406-3431 (2012).
+% \bibitem{levelset} S. Osher and R. Fedkiw, \emph{Level Set Methods and Dynamic Implicit Surfaces: 1st Edition} (Springer, 2002).
+% \bibitem{2dsplitter} Y. Jiao, S. Fan, and D. A. B. Miller, 
+%     ``Demonstrations of systematic photonic crystal design and optimization by low rank adjustment: an extremely compact mode separator'', Opt. Lett. \textbf{30}, 140-142 (2005).
+% \bibitem{baets}F. Van Laere, G. Roelkens, M. Ayre, J. Schrauwen, D. Taillaert, D. Van Thourhout, T. F. Krauss, and R. Baets,
+%     ``Compact and highly efficient grating couplers between optical fiber and nanophotonic waveguides,''
+%     J. of Lightwave Tech. \textbf{25}, 151-156 (2007).
+% % \bibitem{fibergrating} Y. Tang, Z. Wang, L. Wosinski, U. Westergren, and S. He,
+% %     ``Highly efficient nonuniform grating coupler for silicon-on-insulator 
+% %     nanophotonic circuits,''
+% %     Opt. Lett. \textbf{35}, 1290-1292 (2010).
+% % \bibitem{ridge}  K. K. Lee, D. R. Lim, L.C. Kimerling, J. Shin, and F. Cerrina, 
+% %     ``Fabrication of ultralow-loss Si/SiO2 waveguides by roughness reduction,''
+% %     Opt. Lett. \textbf{26}, 1888-1890 (2001).
+% % \bibitem{pcslow} Y. A. Vlasov, M. O'Boyle, H. F. Hamann, and S. J. McNab,
+% %     ``Active control of slow light on a chip with photonic crystal waveguides,''
+% %     Nature \textbf{438}, 65-69 (2005).
+% % \bibitem{slotfocus} M. Lipson, 
+% %     ``Guiding, modulating, and emitting light on 
+% %     silicon-challenges and opportunities,'' 
+% %     J. Lightwave Technol. \textbf{23}, 4222-4238 (2005).
+% % \bibitem{active} J. Van Campenhout, P. Rojo Romeo, P. Regreny, C. Seassal, 
+% %     D. Van Thourhout, S. Verstuyft, L. Di Cioccio, J.-M. Fedeli, 
+% %     C. Lagahe, and R. Baets, 
+% %     ``Electrically pumped InP-based microdisk lasers integrated with a 
+% %     nanophotonic silicon-on-insulator waveguide circuit,'' 
+% %     Opt. Express \textbf{15}, 6744-6749 (2007).
+% % \bibitem{metallic} L. Tang, S. E. Kocabas, S. Latif, A. K. Okyay, 
+% %     D. S. Ly-Gagnon, K. C. Saraswat, and D. A. B. Miller, 
+% %     ``Nanometre-scale germanium photodetector enhanced by a 
+% %     near-infrared dipole antenna,'' 
+% %     Nature Photonics \textbf{2}, 226-229 (2008).
+% % % \bibitem{fwadia} V. R. Almeida, R. R. Panepucci, and M. Lipson, 
+% % %     ``Nanotaper for compact mode conversion,'' 
+% % %     Opt. Lett. \textbf{28}, 1302-1304 (2003) 
+% % % \bibitem{wwadia} S. G. Johnson, P. Bienstman,  M. A. Skorobogatiy, 
+% % %     M. Ibanescu1, E. Lidorikis, and J. D. Joannopoulos,
+% % %     ``Adiabatic theorem and continuous coupled-mode theory for 
+% % %     efficient taper transitions in photonic crystals,''
+% % %     Phys. Rev. E \textbf{66}, 066608 (2002)
+% % % \bibitem{deriv} F. Wang, J. S. Jensen, O. Sigmund, 
+% % %     ``Robust topology optimization of photonic crystal waveguides with 
+% % %     tailored dispersion properties.'' 
+% % %     J. Opt. Soc. Am. B \textbf{28}, 387-397 (2011)
+% % % \bibitem{boydbook} S. Boyd, and L. Vandenberghe, 
+% % %     \emph{Convex Optimization} 
+% % %     (Cambridge University Press, 2004)
+% % \bibitem{prevwork} J. Lu, S. Boyd, and J. Vuckovic, 
+% %     ``Inverse design of a three-dimensional nanophotonic resonator,''
+% %     Opt. Express \textbf{19}, 10563-10750 (2011). 
+% % \bibitem{veronis} G. Veronis, and S. Fan, 
+% %     ``Theoretical investigations of compact couplers between dielectric slab 
+% %     waveguides and two-dimensional metal-dielectric-metal plasmonic waveguides,'' 
+% %     Opt. Express \textbf{15}, 1211-1221 (2007).
+% % \bibitem{yang} R. Yang, R. A. Wahsheh, Z. Lu, and M. A. G. Abushagur, 
+% %     ``Efficient light coupling between dielectric slot waveguide and plasmonic
+% %     slot waveguide,'' Opt. Lett. \textbf{35}, 649-651 (2010).
+% % \bibitem{code} \url{www.github.com/JesseLu/objective-first}
+% \end{thebibliography}
+\chapter{Final Result}
 \section{Introduction}
@@
     (Dr. Gernot Pomrenke), grant number FA9550-09-1-0704.
-\end{document}
+% \end{document}

### 2013-03-28 thesis/intro.tex
Put together papers.

\chapter{Introduction}
And now for an introduction...

### 2013-03-28 thesis/chapter1.tex
Got direct and regularized chapters done.

@@
 % 
-\chapter{Direct design}
-\section{Introduction}
-Numerous numerical methods have been devised to solve Maxwell's equations in both time\cite{Yee66} and frequency\cite{AB74,GA79} domains.
+\chapter{Direct design}\label{direct}
+% Numerous numerical methods have been devised to solve Maxwell's equations in both time\cite{Yee66} and frequency\cite{AB74,GA79} domains.
 We refer to these schemes as direct solvers, since they compute the electric and magnetic fields based on current sources, charge distributions and surrounding dielectric and/or metallic structures.
 While extremely useful in simulating optical components, using direct methods to design optical components, especially in two or three dimensions,  typically requires an extremely time-consuming direct search in a large parameter space\cite{Lon09,Sch02,Nod05,Lip08,SD05}.
-
-On the other hand, an inverse solver would be much more adept in such design and optimization problems\cite{Sig04,Vuc05}.
+% 
+% On the other hand, an inverse solver would be much more adept in such design and optimization problems\cite{Sig04,Vuc05}.
 In this work, we define the inverse problem as that where the electromagnetic field is known, but the surrounding structure is not known.
 The goal in the inverse problem is, then, to find a dielectric structure that will produce that specific electromagnetic field profile.
+% 
+% We show that one can design nanophotonic resonators by specifying the electromagnetic field and its desirable characteristics (such as cavity quality (Q) factor and/or mode volume) and then using an inverse solver to find the corresponding dielectric structure.
+We show that the inverse method used is not only computationally-fast, but is also able to optimize for multiple device characteristics and produce multiple resonances, both of which are very difficult using direct methods.
+%
 
-We show that one can design nanophotonic resonators by specifying the electromagnetic field and its desirable characteristics (such as cavity quality (Q) factor and/or mode volume) and then using an inverse solver to find the corresponding dielectric structure.
-We show that the inverse method used is not only computationally-fast, but is also able to optimize for multiple device characteristics and produce multiple resonances, both of which are very difficult using direct methods.
+\section{Problem formulation}
+This work was originally sparked by the realization that 
+    the electromagnetic wave equation was not only linear in the field variable,
+    but also in the structure variable.
+Specifically, that
+    \BE \nabla \times \mu_0^{-1} \nabla \times E - \omega^2 \epsilon E = 
+        -i\omega J \label{p1:wave} \EE
+    is \emph{bi-linear} in both $E$ and $\epsilon$.
 
-\section{Numerical Setup}
-We start from the time-harmonic eigenvalue equation 
-\begin{equation}
-\nabla \times \epsilon^{-1} \nabla \times H = \left(\frac{\omega}{c}\right)^2 H
-\label{trad ev}\end{equation}
-where $H$, $\epsilon$, $\omega$ and $c$ are the magnetic field, relative permittivity, resonance frequency and speed of light respectively.
-To solve the problem numerically, $H$ and $\epsilon$ are discretized in space using the standard Yee cell used in finite difference methods\cite{Yee66}.
-Also, the curl operators, since they are linear, are represented by the matrix $A$.
-Eq.~\eqref{trad ev} can now be written as
-\begin{equation}
-A Y A x = \xi x
-\label{lin ev}\end{equation}
-where
-\begin{align*}
-&A \text{ is the discretized curl operator,} \\
-&Y = \text{diag}(\epsilon^{-1}) \text{ is the diagonal matrix representing the dielectric structure,} \\
-&x \text{ is a vector representing $H$, and} \\
-&\xi =  \left(\frac{\omega}{c}\right)^2. 
-\end{align*}
-In this form, given $Y$, we can solve the direct problem by computing $x$ using an eigenvalue solver\cite{JJ99}.
-However, we note that eq.~\eqref{lin ev} is also linear in $Y$, which allows us, if $x$ is held constant, to solve the inverse problem by expressing eq.~\eqref{trad ev} as
-\begin{equation}
-By = d
-\label{inv ls}\end{equation}
-where
-\begin{align*}
-&B = A \cdot \text{diag}(Ax), \\
-&d = \xi x\text{, and} \\
-&y = 
-\begin{bmatrix}
-\epsilon_1^{-1} \\ \epsilon_2^{-1} \\ \vdots
-\end{bmatrix} \text{ the variable for which we solve.}
-\end{align*}
-Here, $\text{diag}(Ax)$ is the matrix with the values of $Ax$ along the main diagonal and zeros elsewhere.
+We now make the following substitution in order to represent \eq{p1:wave}
+    in linear algebra notation:
+    \BI $E \to x$, 
+    \I  $\epsilon \to z$,
+    \I  $\nabla\times\mu_0^{-1}\nabla\times - \omega^2 \epsilon \to A(z)$, and
+    \I  $-i\omega J \to b$. \EI
+The electromagnetic wave equation (\eq{p1:wave}) can now be expressed simply as
+    \BE A(z)x = b, \label{p1:axb} \EE
+    which is not only linear in $x$, but also in $z$, 
+    since $A(z)$ is linear with respect to $z$.
 
-\section{Least-Squares Method in 1D}
-\subsection{Least-Squares}
+The linearity of the electromagnetic wave equation with respect to
+    the structure variable suggests the following direct design method:
+    \begin{enumerate}
+    \item choose the electromagnetic field you wish the structure to produce, and
+    \item solve the electromagnetic wave equation for the structure variable. 
+    \end{enumerate}
+
+In the language of physics, this amounts to computing
+    \BE \epsilon = (\nabla\times\mu_0^{-1}\nabla\times E + 
+        i \omega J)/ \omega^2 E \EE
+    given $E$.
+
+In the language of linear algebra, we have formulated the following problem:
+    \BE \minimize_z \|A(z)x - b\|^2. \label{p1:problem}\EE
+
+\section{Implementation}
+To solve \eq{p1:axb} numerically, $x$ (field) and $z$ (structure) variables
+    are discretized in space using the standard Yee cell 
+    used in finite difference methods\cite{Yee66}. 
+The matrix $A(z)$ is contructed in Matlab and solved using 
+    the standard built-in function.
+Because this implementation was only in 1D,
+    all the computation needed to perform the direct design
+    was completed in under one second 
+    on a standard desktop computer.
+
+For verification purposes, 
+    a finite-difference time-domain (FDTD) solver was used 
+    to obtain the actual field produced by the structure and 
+    to verify the accuracy of the design.
+
+\section{Results}
+We now solve \eq{p1:problem} to design nanophotonic resonators in 1D.
+We use the magnetic field formulation of the electromagnetic equation
+    in the following examples;
+    analogous results for the original $E$-field formulation (\eq{p1:wave})
+    are expected.
+
+The chosen value for the $x$ (field) is a canonical resonator field; 
+    a sinusoid in a Gaussian envelope.
+As the result in fig.~\ref{p1:direct} shows,
+    the direct method is able to perfectly reproduce the target field;
+    however, the resulting structure features
+    periodic singularities which render it unmanufacturable.
+
 \begin{figure}[htbp]\centering
 \includegraphics[width=\textwidth]{p1/leastsquares}
-\caption{Inverse design of a one-dimensional structure using the unmodified least-squares method.
+\caption{Design of a one-dimensional structure using the direct design method.
     The target field is a sinusoid within a Gaussian envelope. 
-The computed dielectric structure (green area) supports a field (red circles) that exactly matches the target field (blue line).
-The entire design process is also extremely fast and takes less than $1$ second to complete on a generic desktop computer~\cite{mycomp}.
-The periodic singularities in the dielectric structure are non-physical and will be addressed later in the article.}
-\label{ls pic}\end{figure}
-The result of applying this method to a simple one-dimensional problem is shown in Fig.~\ref{ls pic}.
-A generic least-squares solver~\cite{cholmod} was used to find the dielectric structure, $y$ (green region), that exactly produces the target field, $x$ (blue line), using eq.~\eqref{lin ev}.
-Using a generic desktop computer, the solution was obtained in less than a second.
-Then a finite-difference time-domain (FDTD) solver was used to obtain the actual field (red circles) produced by the structure and to verify the accuracy of $y$.
+    The computed dielectric structure (green area) supports 
+        a field (red circles) that exactly matches the target field (blue line). 
+    The entire design process is extremely fast and takes less than 
+        $1$ second to complete on a generic desktop computer~\cite{mycomp}. 
+    Unfortunately, the periodic singularities in the dielectric structure 
+        mean that such a structure is unrealizable in practice.}
+\label{p1:direct}\end{figure}
 
-As expected, Fig.~\ref{ls pic} shows that the target field is reproduced exactly by the dielectric structure.
-However, the resulting structure is full of undesireable singularities.
-The rest of the section focuses on producing a well-behaved dielectric structure that still reproduces the target field accurately.
+\chapter{Regularized direct design}\label{regularized}
+\section{Problem formulation}
+The simplest way to produce a well-behaved dielectric structure is 
+    to add a regularization term to our direct formulation (\eq{p1:axb}),
+    \BE \minimize_z \|A(z)x - b\|^2 + \eta \|z - z_0\|^2. \label{reg:problem}\EE
+Here, the regularization term $\eta \|z - z_0\|^2$
+    serves to keep $z$ from straying too far from $z_0$, which we choose.
+The coefficient $\eta$, then, serves as a knob to control the
+    strength of the regularization term.
 
-\subsection{Regularized Least-Squares}
-The simplest way to produce a well-behaved dielectric structure is to add a regularization term to our least-squares problem, 
-% \begin{equation}
-% \begin{bmatrix} B \\ \sqrt{\eta} I \end{bmatrix} y = \begin{bmatrix} d \\ \sqrt{\eta}y_0 \end{bmatrix}
-% \label{regls}\end{equation}
-which is equivalent to solving the following optimization problem
-\begin{equation}
-\minimize_{y}\quad \|By-d\|^2 + \eta\|y-y_0\|^2.
-\label{regls alt} \end{equation}
-Here $y_0$ represents some initial guess for the dielectric structure, which we want the values of $y$ to stay close to, and $\eta>0$ is a parameter used to trade off fit, i.e.
-$\|By-d\|^2$, and deviation from $y_0$, i.e.
-$\|y-y_0\|^2$.
+\section{Implementation}
+\Eq{reg:problem} can still be computed in one step
+    since the regularization term does not add any computational complexity.
+Thus the implementation is only a slight modification
+    from that of chapter~\ref{direct}.
 
-We chose to constrain $\epsilon$ around a constant value of $\epsilon_0 = 10$ and solved the least-squares system for $\eta=10^{-8}$, $10^{-6}$, and $10^{-4}$.
-The results, each still obtained in under a second, are shown in Fig.~\ref{regls pic} and illustrate the trade-off between constraining $\epsilon$ and accurately reproducing $H$.
+\section{Results}
+We chose to constrain the values of $z$ ($\epsilon$) 
+    around a constant value of $z_0, \epsilon_0 = 10$ and 
+    solved \eq{reg:problem} for $\eta=10^{-8}$, $10^{-6}$, and $10^{-4}$;
+    the results of which are shown in fig.~\ref{regls pic}.
+
+Critically, fig.~\ref{regls pic} shows that there seems
+    to be an inherent trade-off between 
+        constraining the structure ($z$) 
+        and accurately reproducing the field ($x$).
 
@@
 \includegraphics[width=\textwidth]{p1/regularized}
-\caption{Inverse design of one-dimensional structures using the regularized least-squares method.
-The same target field is used as in Fig.~\ref{ls pic}, and the computation time remains below $1$ second.
-As the regularization parameter, $\eta$, is increased, $\epsilon$ is increasingly constrained to a chosen constant value of $10$.
-At the same time, the mismatch between target and actual fields increases markedly.
-This illustrates the apparent trade-off between producing reasonable structures and accurately reproducing a fixed target field.}
+\caption{Regularized design of one-dimensional structures. 
+    The same target field is used as in Fig.~\ref{p1:direct}, 
+        and the computation time remains below $1$ second. 
+    As the regularization parameter, $\eta$, is increased, 
+        $\epsilon$ is increasingly constrained to 
+        a chosen constant value of $10$. 
+    At the same time, the mismatch between target and actual fields 
+        increases markedly. 
+    This illustrates the apparent trade-off between 
+        producing reasonable structures and 
+        accurately reproducing a fixed target field.}
 \label{regls pic}

### 2013-03-28 thesis/intro.tex
Getting there with thesis.
Got direct and regularized chapters done.

@@
 \chapter{Introduction}
-And now for an introduction...
+Currently, nanophotonic devices are designed by tuning
+    a handful of design parameters (\fig{integrated_circuit}).
+The goal of this work is nanophotonic design software
+    so that this will no longer be the case.
+\myfig{integrated_circuit}
+    {Examples of hand-tuned nanophotonic devices.
+    Device performance is tuned by varying the sizes of and spacing between
+    a handful of elements (waveguides, resonators, gratings, \ldots).}
+
+Specifically, our goal is to be able to utilize the full parameter space
+    (which is enormous, \fig{des_complexity})
+    to enable compact, high-efficiency designs
+    which may even exhibit novel functionality.
+To achieve this, we have embarked on a quest 
+    to enable nanophotonic \emph{design-by-specification}--that is,
+    software which is able to design a nanophotonic device
+    solely based on the desired performance specification given to it.
+This thesis is a synopsis of the steps that we have taken to achieve this goal.
+\myfig{des_complexity}
+    {The parameter space for nanophotonic design is enormous and largely untapped.
+    Here, we show that, 
+        limited to including or excluding 100 nm square areas,
+        a 1500 nm $\times$ 1500 nm area already contains $2^{225}$ 
+        (an uncountable number) possible designs.}
+
+The organization of this thesis is straightforward: 
+    chapters 2-4 detail the incremental steps in achieving
+    our final result, which is presented in chapter 5.

### 2013-03-28 thesis/chapter2.tex
Getting there for chapter 2.

@@
-\chapter{Iterative design}
-\section{Complementary Optimization in 1D}
-\subsection{Motivation for a Complementary Optimization Strategy}
-The fundamental problem in the previous examples is actually not in the methods themselves, but in the improper selection of a target field.
-In fact, it is very difficult to select a suitable target resonant field because not every resonant mode even has a corresponding dielectric structure that is able to reproduce it.
-Furthermore, it is nearly impossible to select a multi-dimensional field which corresponds to a well-behaved, isotropic and discretely-valued $\epsilon$, as would be needed for practical structures.
+\chapter{Iterative design} \label{iterative}
+% \section{Motivation for a Complementary Optimization Strategy}
+The fundamental problem in the examples 
+    in chapters \ref{direct} and \ref{regularized}
+    is actually not in the methods themselves, 
+    but in the improper selection of a target field. 
+In fact, it is very difficult to select a suitable target field 
+    because not every field even has a manufacturable dielectric structure 
+    that is able to reproduce it. 
+Furthermore, it is nearly impossible to select a multi-dimensional field 
+    which corresponds to a well-behaved, isotropic and 
+    discretely-valued $\epsilon$, 
+    as would be needed for practical structures.
 
-For this reason, a successful method must be allowed to either modify the target field, or specify it completely, in which case the user would only determine certain characteristics (e.g.
-mode-volume, Q-factor) that the target field should have.
-The former strategy is developed in both one and two dimensions, while the latter strategy is implemented in Section \ref{sec:2Dbounded} in order to design two-dimensional resonators with discrete values of $\epsilon$.
+What we realized was that a successful method 
+    must be allowed to modify the target field as well as 
+    its dielectric structure.
+This realization led us to an iterative design strategy for nanophotonic devices.
 
-\subsection{Complementary Optimization}\label{sec:comp}
-We start with the same target field as in the previous examples but we now formulate a method that allows for it to be modified during the design process.
-The formulation chosen is a complementary optimization routine, where we continually alternate between modifying $\epsilon$ to better fit the field, and then modifying the field to better fit $\epsilon$.
-Here, we use the term ``fit'' to mean that either $\epsilon$ or $H$ is solved so that the residual error from eq.~\eqref{trad ev} is minimized.
-Additionally, both iterations are regularized in order to stably approach a solution.
-This algorithm can be summarized as follows,
-\begin{align}
-&\text{choose $x_0$ and $y_0$} \nonumber \\
-&\text{for } i = 1, 2, \ldots \nonumber \\
-&\quad\minimize_{y_i}\quad \|B_{i-1} y_i-d_{i-1}\|^2 + \eta_1\|y_i-y_{i-1}\|^2 \label{comp1}\\
-&\quad\minimize_{x_i}\quad \|A Y_i A x_i - \xi x_{i-1}\|^2 + \eta_2\|x_i-x_{i-1}\|^2 \label{comp2}
-\end{align}
-where $Y_i = \text{diag}(y_i)$, $B_i = A \cdot \text{diag}(A x_i)$ and $d_i = \xi x_i$.
-$\|A Y_i A x_i - \xi x_{i-1}\|^2$ is used instead of $\|A Y_i A x_i - \xi x_{i}\|^2$ to avoid the trivial $x_i = 0$ solution and does not affect the overall accuracy since $x$ changes very slowly.
+\section{Problem formulation}
+We start with the same target field as in the previous examples 
+    but we now allow for it to be modified during the design process. 
+Specifically, we alternate between modifying $z$ (structure) 
+    to better fit $x$ (field), 
+    and then modifying the $x$ (field) to better fit $z$ (structure):
+    \begin{subequations}\begin{align} 
+    \minimize_z & \|A(z)x - b\|^2 + \eta_0\|z - z_\text{prev}\|^2 \\
+    \minimize_x & \|A(z)x - b\|^2 + \eta_1\|x - x_\text{prev}\|^2,
+    \end{align}\end{subequations}
+which can be more succintly expressed as 
+    \BE \minimize_\text{alternately $x$ then $z$} 
+        \|A(z)x - b\|^2 + \eta_0\|z - z_\text{prev}\|^2
+                        + \eta_1\|x-x_\text{prev}\|^2. \label{iterative problem}\EE
+
+In this formulation, both structure ($z$) and field ($x$) variables
+    have regularization terms.
+In order to avoid the performance/manufacturability trade-off 
+    encountered in chapter~\ref{regularized},
+    we decrease the values of $\eta_0$ and $\eta_1$ at each subsequent iteration.
+
+\section{Implementation}
+The most notable implementation difference is that,
+    in contrast to direct design,
+    \eq{iterative problem} must be solved multiple times
+    in order to arrive at a good design.
+Thus, design times now increase from seconds to minutes.
+
+Note that, in order to design two-dimensional structures,
+    \eq{iterative problem} is only modified in the
+    definition of its constituent vectors and matrices,
+    the formulation remains the same.
+
+\section{Results}
+\subsection{1D}
+Fig.~\ref{comp pic} shows that the iterative algorithm, after $400$ iterations and with the correct choice of regularization parameters $\eta_0$ and $\eta_1$, results in a well-behaved structure that is able to closely reproduce the modified target field.
 
@@
 \includegraphics[width=\textwidth]{p1/complementary}
-\caption{Inverse design of a one-dimensional structure using the complementary optimization method.
-The target field in Figs \ref{ls pic} and \ref{regls pic} is used as the initial target field.
-The rates of change for both $\epsilon$ and $H$ are controlled by regularization parameters $\eta_1=10^{-4}$ and $\eta_2=10^{-3}$ respectively.
+\caption{Iterative design of a one-dimensional resonator. 
+    The target field in Figs \ref{p1:direct} and \ref{regls pic} is used as the initial target field.
+The rates of change for both $\epsilon$ and $H$ are controlled by regularization parameters $\eta_0=10^{-4}$ and $\eta_1=10^{-3}$ respectively.
 The $400$ iterations used to achieve this result took $60$ seconds to compute.
@@
 
-Fig.~\ref{comp pic} shows that the complementary optimization algorithm, after $400$ iterations and with the correct choice of regularization parameters $\eta_1$ and $\eta_2$, results in a well-behaved structure that is able to closely reproduce the modified target field.
-Numerically, the least-squares problem must now be solved numerous times, which increases the computational time needed to around $60$ seconds.
+\subsection{2D}
+The iterative design method can also be extended to two dimensions.
+We demonstrate this using an S-shaped target field 
+    which is non-trivial to reproduce. 
+The design result is shown in fig.~\ref{S pic}. 
+    The resulting dielectric structure is continuous, unbounded and 
+    contains very few singularities (white dots), 
+    but the final target and actual fields match up well. 
+Also, the computational cost remains quite reasonable; the $50$ iterations needed required only $5$ minutes of computation time. 
+\begin{figure}\centering
+\includegraphics[width=\textwidth]{p1/S}
+\caption{Iterative design of an ``S'' resonator. 
+The design was initialized by specifying an initial dielectric structure ($\epsilon=1$ everywhere) and a resonant field in the shape of an ``S''. 
+The final dielectric structure was produced after $50$ iterations which took $90$ seconds to complete in total.
+The grid size was $80\times 120$.
+The final dielectric structure is quite unintuive, and yet reproduces the target field surprisingly well.
+This example demonstrates the versatility of the iterative design method in producing designs, from very simple specifications, which otherwise could be attained only with considerable difficulty.}
+\label{S pic}
+\end{figure}
 
-\subsection{Complementary Optimization with Bounded $\epsilon$}
-In order to achieve a more practical, discretely-valued dielectric structure, we can impose strict upper- and lower-bounds on $\epsilon$. To this end, we modify our algorithm as such,
+\chapter{Iterative design with bounded $\epsilon$} \label{bounded}
+\section{Problem formulation}
+In order to achieve a more practical, discretely-valued dielectric structure, we can impose strict upper- and lower-bounds on the structure ($z$). 
+To this end, we can modify \eq{iterative problem} as such,
+    \begin{subequations}
     \begin{align} 
-&\text{choose $x_0$ and $y_0$} \nonumber \\
-&\text{for } i = 1, 2, \ldots \nonumber \\
-&\quad\minimize_{y_i}\quad \|B_{i-1} y_i-d_{i-1}\|^2 \nonumber \\
-&\quad\text{subject to}\quad \epsilon_\text{max}^{-1} \leq y_i \leq \epsilon_\text{min}^{-1} \label{bc1} \\
-\nonumber \\
-&\quad\minimize_{x_i}\quad \|A Y_i A x_i - \xi x_{i-1}\|^2 + \eta_2\|x_i-x_{i-1}\|^2. \label{bc2}
-\end{align}
-In this algorithm, eq.~\eqref{bc1} is a convex optimization problem\cite{BV04}.
+    \minimize & \|A(z)x - b\|^2 + \eta_1\|x - x_\text{prev}\|^2\\
+    \subto & z_\text{min} \le z \le z_\text{max}. 
+    \end{align}\label{bounded problem}
+    \end{subequations}
+Here, the regularization term for $z$ has been replaced by hard constraints
+    on the values that $z$ can take on.
+
+This modification takes us one step closer to producing manufacturable structures,
+    which must be discretely valued.
+
+\section{Implementation} 
+In this algorithm, \eq{bounded problem} is no longer linear in a convex optimization problem\cite{BV04}.
 This allows us to impose hard constraints on $\epsilon$, which in turn allows us to remove the regularization term present in eq.~\eqref{comp1}.
@@
 \section{Complementary Optimization in 2D}
-\subsection{``S'' Resonator}
-We now demonstrate that the complementary optimization method is versatile and can be scaled to multiple dimensions.
-To ensure that $\epsilon$ is well-behaved we use a point-spread function which does not allow $\epsilon$ to change at a certain point in space without affecting the values surrounding it.
-
-In order to show that our method can produce complex designs, we choose an S-shaped target field which is non-trivial to reproduce.
-The optimization results, using the complementary optimization method from Section \ref{sec:comp}, are shown in Fig.~\ref{S pic}.
-The resulting dielectric structure is continuous, unbounded and contains some singularities (white dots), but the final target and actual fields match up well.
-Also, the computational cost remains quite reasonable; the $50$ iterations needed required only $5$ minutes of computation time.
-The resulting structure is completely unintuitive, and illustrates the kind of new capabilities offered by the inverse design strategy.
-Specifically, that a complex, intricate structure can be designed just by specifying the shape and frequency of a rather simple electromagnetic mode.
-\begin{figure}\centering
-\includegraphics[width=\textwidth]{p1/S}
-\caption{Inverse design of an ``S'' resonator using the complementary optimization method without bounds on $\epsilon$.
-The design was initialized by specifying an initial dielectric structure ($\epsilon=1$ everywhere) and a resonant field in the shape of an ``S''.
-The final dielectric structure was produced after $50$ iterations which took $90$ seconds to complete in total.
-The grid size was $80\times 120$.
-The final dielectric structure is quite unintuive, and yet reproduces the target field surprisingly well.
-This example demonstrates the versatility of the complementary optimization method in producing designs, from very simple specifications, which otherwise could be attained only with considerable difficulty.}
-\label{S pic}
-\end{figure}
-
-\subsection{Multi-Mode Inverse Design}
-The complementary optimization method can also be extended to produce dielectric structures with multiple resonances.
-To do so, multiple initial target fields are specified.
-The dielectric structure is first modified to simultaneously fit all target fields using a multi-objective least-squares method.
-Then each target field is individually modified to fit the structure; and we continue alternating between optimizing $\epsilon$ and $H^{(j)}$ in this way.
-A benefit of this scheme is that only the $\epsilon$ optimization increases in size, so the design process remains computationally tractable, even for several resonant fields.
-This algorithm can be summarized as follows,
-\begin{align}
-&\text{choose $y_0$, $x^{(1)}_0$, $x^{(2)}_0$, \ldots} \nonumber \\
-&\text{for } i = 1, 2, \ldots \nonumber \\
-&\quad\minimize_{y_i}\quad \eta_1\|y_i-y_{i-1}\|^2 + \sum_j \|B^{(j)}_{i-1} y_i-d^{(j)}_{i-1}\|^2  \label{mm1}\\
-&\quad\text{for } j = 1, 2, \ldots \nonumber \\
-&\quad\quad\minimize_{x^{(j)}_i}\quad \|A Y_i A x^{(j)}_i - \xi x^{(j)}_{i-1}\|^2 + \eta_2\|x^{(j)}_i-x^{(j)}_{i-1}\|^2. \label{mm2}
-\end{align}
-The design of an ``X'' resonator with two perpendicular, degenerate modes is shown in Fig.~\ref{X pic}.
-The added complexity increases the total computation time to $5$ minutes for $40$ iterations of the algorithm.
-\begin{figure}\centering
-\includegraphics[width=\textwidth]{p1/X}
-\caption{Inverse design of a doubly-resonant, degenerate ``X'' resonator produced by the complementary optimization method with unbounded $\epsilon$.
-As in Fig.~\ref{S pic} the initial value of $\epsilon$ was $1$ everywhere.
-The two initial target fields used are only slightly perturbed and are very similar to the two final actual target fields.
-Computationally, this design took $5$ minutes to complete on a $120\times 120$ grid and required $40$ iterations.
-This example shows that the complementary optimization strategy can be extended to produce dielectric structures with multiple resonances.
-Such an ``X'' resonator is useful for polarization-entangled single-photon sources for example\cite{Hen06}.}
-\label{X pic}
-\end{figure}
-
-\subsection{Design of Waveguiding Devices}
-The multi-mode inverse design method can also be applied to the design of waveguiding devices such as multiplexers/demultiplexers, waveguide couplers, crossbars and dispersion-tailored waveguides.
-This can be accomplished by treating a waveguiding device as a doubly-degenerate resonator at its operational frequencies and then enforcing opposite symmetries (even/odd or cosine/sine) in the degenerate modes.
-A single-to-dual beam waveguide coupler designed based on Eq.~\eqref{mm1} and \eqref{mm2} is shown in Fig.~\ref{wg pic}, and motivates how one might design other waveguiding devices such as channel-drop filters.
-\begin{figure}[htbp]\centering
-\includegraphics[width=\textwidth]{p1/wg}
-\caption{Inverse design of a single-to-dual beam waveguide coupler using the complementary optimization method without bounds on $\epsilon$.
-Two degenerate modes with opposite symmetry (sine and cosine) are used as target fields.
-Only $4$ iterations ($14$ seconds) are needed to achieve this solution on a $240\times 55$ grid.
-This is a simple demonstration showing that the complementary optimization method can also be extended to design waveguiding devices.}
-\label{wg pic}
-\end{figure}
-In addition to macroscopic waveguiding devices, one should also be able to create novel periodic waveguiding structures.
-For instance, by controlling the frequency of a particular waveguiding mode at each of its $k$-vectors, one could create a waveguide with a customized dispersion characteristic, which would be useful in the design of slow-light waveguides.
-
-\section{Complementary Optimization with Bounded $\epsilon$ in 2D}\label{sec:2Dbounded}
 \subsection{Numerical Method}\label{sec:2Dnum}

### 2013-03-28 thesis/chapter2.tex
Working on bounded results.

@@
 \section{Implementation} 
-In this algorithm, \eq{bounded problem} is no longer linear in a convex optimization problem\cite{BV04}.
-This allows us to impose hard constraints on $\epsilon$, which in turn allows us to remove the regularization term present in eq.~\eqref{comp1}.
-The \emph{CVX} package\cite{CVX}, a Matlab-based modeling system for convex optimization, is used to solve eq.~\eqref{bc1}, with each iteration of the algorithm now requiring roughly $1$ second of computation time.
+In this algorithm, \eq{bounded problem} is no longer linear in $z$
+    but is still convex\cite{BV04}.
+For this reason, the \emph{CVX} package\cite{CVX}, 
+    a Matlab-based modeling system for convex optimization, 
+    is now used to solve \eq{bounded problem} for $z$.
+
+\section{Results}
+\subsection{1D}
+Once again, we attempt the design of a one-dimensional resonator
+    and find thata nearly binary-valued dielectric structure is obtained,
+    as seen in fig.~\ref{bounded comp pic}.
+Note that the the directly discreteness of $z$ was not enforced (since that would make the problem non-convex); 
+    however, a discrete, binary-valued structure arose fortuitously. 
+Critically, this dielectric structure accurately produces the final target field.
+
 \begin{figure}[htbp]\centering
 \includegraphics[width=\textwidth]{p1/bounded}
-\caption{Inverse design of a one-dimensional structure using the complementary optimization method with bounded $\epsilon$.
+\caption{Iterative design of a one-dimensional structure with bounded $\epsilon$. 
     The parameters are identical to those used to produce Fig.~\ref{comp pic} with the exception that only one regularization term is now needed ($\eta_2=10^{-3}$).
@@
 
-A nearly binary-valued dielectric structure is obtained in Fig.~\ref{bounded comp pic}, which accurately produces the final target field.
-This is very useful for the design of practical structures, since they usually consist of two or three different materials at most.
-Interestingly, although the directly discreteness of $\epsilon$ was not enforced (since that would make the problem non-convex), a discrete, binary-valued structure has still arisen.
+\subsection{2D}
 
-\section{Complementary Optimization in 2D}
-\subsection{Numerical Method}\label{sec:2Dnum}
 We now use the complementary optimization method to design resonators with discrete, binary $\epsilon$ in two dimensions.

### 2013-03-29 thesis/chapter2.tex
Chapter 2 draft done.

@@
 We now use the complementary optimization method to design resonators with discrete, binary $\epsilon$ in two dimensions.
-At the same time, the algorithm is modified so that we no longer specify an initial target field; instead, only an initial dielectric structure and the maximum desired mode volume (i.e.
-mode area in 2D) are specified.
-In addition, the optimization process attempts to maximize the Q-factor.
-Such an algorithm now consists of iteratively solving two convex optimization problems,
-\begin{align}
-&\text{choose $y_0$} \nonumber \\
-&\text{for } i = 1, 2, \ldots \nonumber \\
-&\quad\minimize_{x_i}\quad \|A Y_{i-1} A x_i - \xi x_{i}\|^2 +   \eta \|F x_i\|^2\nonumber \\
-&\quad\text{subject to}\quad (A x_i)^T Y_{i-1} (A x_i) \leq A_\text{mode} \label{be1} \\
-\nonumber \\
-&\quad\minimize_{y_i}\quad \|B_i y_i-d_i\|^2 \nonumber \\
-&\quad\text{subject to}\quad \epsilon_\text{max}^{-1} \leq y_i \leq \epsilon_\text{min}^{-1}. \label{be2} 
-\end{align}
-In this algorithm, the field optimization, Eq.~\eqref{be1}, differs significantly from Eq.~\eqref{bc2}.
-First, the eigenvalue equation term $\|A Y_{i-1} A x_i - \xi x_{i}\|^2$ no longer utilizes $x_{i-1}$.
-Also, a new ``Fourier-minimizing'' term $\|F x_i\|^2$ has been added.
-Here, the row vectors of $F$ consist of the field Fourier components that we do not want incorporated in the final solution.
-The motivation for adding this term is to design high-Q resonators using planar structures, where the Q-factor is limited by out-of-plane losses, and can thus be improved by eliminating field Fourier components that are not localized by total internal reflection (components inside the light cone)~\cite{Vuc05}.
-Lastly, the $(A x_i)^T Y_{i-1} (A x_i)$ term allows us to specify the mode area (mode volume in three dimensions), that we desire for our resonant field.
-This works because the two minimization objectives in Eq.~\eqref{be1} will generally cause the mode area to be as large as possible, which means we always end up with $(A_1 x_i)^T Y_{i-1} (A_1 x_i) = A_\text{mode}$.
 
-The addition of the two new terms in Eq.~\eqref{be1} signifies that the field iteration in our algorithm attempts to do more than to just satisfy Maxwell's equations.
-Rather than only trying to fit the dielectric structure, the resonant field now also minimizes some of its Fourier components while working with a limited mode area.
+Fig.~\ref{circle pic} shows the design of a circular grating resonator. 
+The dielectric structure emerged from a very simple choice of initial structure, 
+    namely a constant $\epsilon=12.25$ everywhere. 
+The range of $\epsilon$ was limited to be from $1$ to $12.25$.
+Additionally, the components of $\epsilon$ outside a specified circle 
+    were held at a constant $\epsilon=12.25$ 
+    for the duration of the design process. 
+The entire algorithm was run for $40$ iterations and took $7$ minutes.
+Interestingly, the central bowtie-like structure has emerged 
+    from previous genetic optimization methods as well\cite{Lip08}.
 
-In contrast with the field optimization given by Eq.~\eqref{be1}, the structure optimization given by Eq.~\eqref{be2} remains identical to the equation in the one-dimensional case, Eq.~\eqref{bc1}, and contains no terms related to notions of Fourier components or mode area.
-In fact, the only objective in the $\epsilon$ optimization is to better fit the field generated from the field optimization.
-This means that in this scheme, the field iteration is leading the structure iteration.
-In other words, Eq.~\eqref{be1} ``looks ahead'' and gradually adapts itself to become a more desirable field, while Eq.~\eqref{be2} just ``follows along''.
-For this reason, this algorithm is unique from the other complementary optimization algorithms previously presented in the article, since in those algorithms both iterations follow one another and eventually ``meet in the middle''.
-
-Finally, in this scheme, we chose to limit the degrees of freedom of both $x_i$ and $y_i$.
-Some components of $x_i$ were fixed at non-zero values and were not allowed to be modified simply to avoid the $x_i = 0$ situation.
-To enhance the aesthetics of the resulting dielectric structure, some components of $y_i$ were frozen as well, which is useful in cases where one would only like to modify the dielectric structure within a waveguide only, for example.
-
-\subsection{Circular Grating Resonator}
 \begin{figure}[htbp]\centering
 \includegraphics[width=\textwidth]{p1/circle}
-\caption{Inverse design of a two-dimensional resonator using the complementary optimization method with strict bounds on $\epsilon$.
-The initial specification is very simple and consists an initial dielectric structure ($\epsilon=12.25$ everywhere), the frequency and mode-volume of the resonance field as well as a weighting factor, $\eta$, to avoid leaky field Fourier components.
-Additionally, the values of $\epsilon$ are only allowed to be modified within a central circular region and must be kept between $1$ and $12.25$.
+\caption{Iterative design of a two-dimensional resonator 
+            with hard constraints on $\epsilon$.
+    The values of $\epsilon$ are only allowed to be modified within a central circular region and must be kept between $1$ and $12.25$. 
     After $40$ iterations on a $160 \times 160$ grid, which took $7$ minutes to complete, a discrete structure emerged with excellent match between the predicted ($x_{40}$) and actual fields. 
@@
 \end{figure}
-Fig.~\ref{circle pic} shows the design of a circular grating resonator using the method from Section \ref{sec:2Dnum}.
-The dielectric structure emerged from a very simple choice of initial structure, namely a constant $\epsilon=12.25$ everywhere.
-The range of $\epsilon$ was limited to be from $1$ to $12.25$, the mode area was set to $5$ and $\eta= 10^{-3}$.
-Central components of $x_i$ were held constant to ensure that an electric dipole in the y-direction was produced in the center of the structure.
-Additionally, the components of $\epsilon$ outside a specified circle were held at a constant $\epsilon=12.25$ for the duration of the design process.
-The entire algorithm was run for $40$ iterations and took $7$ minutes.
 
-After $40$ iterations, we see that a strong binary-valued structure has formed.
-Interestingly, the central bowtie-like structure has emerged from previous geneetic optimization methods as well\cite{Lip08}.
-Note also the extremely small amount of information needed to produce this result: only the frequency and mode area of the resonant field desired, and a trivial intial $\epsilon$.
-The ability to produce a rather advanced design from such a simple problem specification highlights the potential usefulness of inverse methods in the design of novel nanophotonic devices.
+The same approach was used to design a beam resonator 
+    as shown in Fig.~\ref{line pic}. 
+The parameters used in this design are identical 
+    to those used for the circular resonator, 
+    with the exception that the initial dielectric structure 
+    now consists of an unbroken waveguide, 
+    and the region where $\epsilon$ can be modified is now confined 
+    to the center of the waveguide.
 
-\subsection{Beam Resonator}
-The same approach was used to design a beam resonator as shown in Fig.~\ref{line pic}.
-The parameters used in this design are identical to those used for the circular resonator, with the exception that the initial dielectric structure now consists of an unbroken waveguide, and the region where $\epsilon$ can be modified is now confined to the center of the waveguide.
 \begin{figure}[htbp]\centering
 \includegraphics[width=\textwidth]{p1/beam}
-\caption{Inverse design of a beam resonator in two dimensions using the complementary optimization method with bounded $\epsilon$.
-The initial conditions are identical to those for Fig.~\ref{circle pic}, except that the initial dielectric structure is an unbroken waveguide, and $\epsilon$ can only be modified within that waveguide.
-The structure emerged after $40$ iterations on a $320\times 40$ grid, which took $5$ minutes of computation.
-The bowtie-like structure has reappeared in the center.
-Interestingly, the effect of the Fourier term in Eq.~\eqref{be1}, is seen in the outward tapering of the holes.}
+\caption{Iterative design of a beam resonator in two dimensions 
+        with bounded $\epsilon$. 
+    The initial conditions are identical to those for Fig.~\ref{circle pic}, 
+        except that the initial dielectric structure is an unbroken waveguide, 
+        and $\epsilon$ can only be modified within that waveguide. 
+    The structure emerged after $40$ iterations on a $320\times 40$ grid, 
+        which took $5$ minutes of computation. 
+    The bowtie-like structure has reappeared in the center.}
 \label{line pic}
 \end{figure}
-
-These two, simple modifications produce a vastly different result as is plainly seen from Fig.~\ref{line pic}.
-Some characteristics remain, such as the two closely spaced holes in the center of the structures which focus the electromagnetic energy to a central point.
-Other features are unique to the beam resonator, such as a gradual outward tapering of hole diameters and size ending in a periodic ``steady-state'' structure, in similar fashion to Fig.~\ref{comp pic}.
-This tapering is a direct result of the Fourier term in Eq.~\eqref{be1} as it leads to a smooth field profile variation and minimization of the components in the light cone that lead to out-of-plane losses\cite{Vuc05,Aka05}.
-
-\section{Conclusions and Outlook}
-In summary, we have introduced and demonstrated a complementary optimization method for the inverse design of nanophotonic resonators as well as waveguiding structures.
-We have demonstrated that, in two dimensions, this method can be used to design non-trivial as well as multi-resonant structures.
-Furthermore, we have shown that by constraining the range of available dielectric constants, the same underlying method can produce binary-valued, discrete dielectric structures.
-
-The methods presented here can readily be extended into three dimensions.
-In essence, the only hurdle is the size of the convex optimization problem for the field optimization.
-Since a full three-dimensional grid often consists of tens of millions of variables, solving the field optimization problem, Eq.~\eqref{be1}, using methods such as LU factorization is no longer computationally tractable.
-Instead, iterative methods such as truncated Newton methods must be employed.
-As it turns out, such iterative methods are especially well suited to this complementary optimization scheme, since they can take advantage of the information in $x_{i-1}$ in order to solve $x_i$ very quickly.
-This is very applicable to our algorithm since the field changes very little from one iteration to the next.
-
-Although solving the field optimization problem is numerically challenging in three dimensions, solving the structure optimization problem, Eq.~\eqref{be2}, in three dimensions is much simpler.
-This is because only structural variations in-plane need to be accounted for planar nanophotonic devices.
-The number of variables in Eq.~\eqref{be2} for both two- and three-dimensional problems is then effectively the same, and the same numerical techniques can be employed to solve both.
-
-A full three-dimensional inverse design method based on complementary optimization would enable the design of novel nanophotonic resonators.
-For instance, a resonator for efficient wavelength-conversion could be designed by creating a structure with multiple well-placed resonant frequencies~\cite{Riv09}.
-Furthermore, effects such as mode overlap and the use of frequency-dependent refractive index materials could be taken into account with such a method.
-
-\subsection*{Acknowledgements}
-This work has been supported in part by the AFOSR MURI for Compex and Robust On-chip Nanophotonics (Dr. Gernot Pomrenke).
-We thank Prof. Stephen Boyd for many fruitful discussions regarding convex optimization.
 
@@
 % %%%%%%%%%%%%%%%%%%%%%%%%%%  body  %%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Begin of 2.5 D (Motivation)}
-To date, the design of nanophotonic devices has generally involved a lengthy (days, weeks) process in which one perturbs, by trial-and-error, canonical structures such as photonic crystals or waveguide-coupled rings to achieve the desired performance for the device.
-
-Instead, an inverse design method in which the user only specifies the desired electromagnetic field, or characteristics thereof, and then leaves the computer to find a dielectric structure satisfying these requirements, would be a much more intuitive and computationally efficient design strategy.
+% \section{Begin of 2.5 D (Motivation)}
+% To date, the design of nanophotonic devices has generally involved a lengthy (days, weeks) process in which one perturbs, by trial-and-error, canonical structures such as photonic crystals or waveguide-coupled rings to achieve the desired performance for the device.
+% 
+% Instead, an inverse design method in which the user only specifies the desired electromagnetic field, or characteristics thereof, and then leaves the computer to find a dielectric structure satisfying these requirements, would be a much more intuitive and computationally efficient design strategy.
 Furthermore, such a method may even be the only feasible option available for the design of more complex multi-wavelength and multi-functional nanophotonic devices needed for on-chip integration\cite{miller}.
-
-\section{2.5-dimensional approximation}
-Previously, we demonstrated the inverse design of various nanophotonic devices in two dimensions\cite{prevwork}.
+% 
+\subsection{2.5D}
+% \section{2.5-dimensional approximation}
 Unfortunately, to directly extend our previous method to full three-dimensional space requires solving for a very large ($\sim 10^7 \times 10^7$) and ill-conditioned matrix, namely that given by the time-harmonic Maxwell's equation in three dimensions, which for the electric ($E$) field is
@@
 \end{equation}
-In the above formulation and for the remainder of the manuscript, the norm ($\|\cdot\|$) refers to the 2-norm over the entire grid and is equivalent to the spatial integral $(\int | \cdot |^2 dr)^{1/2}$.
+% In the above formulation and for the remainder of the manuscript, the norm ($\|\cdot\|$) refers to the 2-norm over the entire grid and is equivalent to the spatial integral $(\int | \cdot |^2 dr)^{1/2}$.
 
-\section{Inverse design method}
-\subsection{Original formulation}
-In our inverse design method, one proceeds by specifying either the resulting field or its characteristics and then computing a structure which will produce such a field.
+% 
+% In our inverse design method, one proceeds by specifying either the resulting field or its characteristics and then computing a structure which will produce such a field.
 In this work, we chose to specify the desired field characteristics, namely, small mode-volume and large quality factor.
 The inverse design problem can then be formulated as,
-\begin{align}
-\text{minimize} \quad& \frac{\|\epsilon E^2\|}{\text{max}\{\epsilon E^2\}} \label{a1}\\ 
-\text{subject to} \quad 
-    & \nabla\times\nabla\times E - \mu\omega^2\epsilon E = 0 \label{a2}\\
-    & \nabla\cdot\epsilon E = 0 \label{adiv}\\
-    & \text{FT}_\text{lightcone}\{E\} = 0, \label{a3} \\
-    & \epsilon = \{\epsilon_\text{air}, \epsilon_\text{silicon}\} \label{a4}
-\end{align}
-where $\epsilon$ and $E$ are the permittivity and electric vector field respectively, defined within the 2.5-dimensional approximation and discretized along a standard Yee grid\cite{yee} with periodic boundary conditions.
+% \begin{align}
+% \text{minimize} \quad& \frac{\|\epsilon E^2\|}{\text{max}\{\epsilon E^2\}} \label{a1}\\ 
+% \text{subject to} \quad 
+%     & \nabla\times\nabla\times E - \mu\omega^2\epsilon E = 0 \label{a2}\\
+%     & \nabla\cdot\epsilon E = 0 \label{adiv}\\
+%     & \text{FT}_\text{lightcone}\{E\} = 0, \label{a3} \\
+%     & \epsilon = \{\epsilon_\text{air}, \epsilon_\text{silicon}\} \label{a4}
+% \end{align}
+% where $\epsilon$ and $E$ are the permittivity and electric vector field respectively, defined within the 2.5-dimensional approximation and discretized along a standard Yee grid\cite{yee} with periodic boundary conditions.
 $\epsilon$ was constrained to be isotropic by only varying $\epsilon_z$ in each cell, and then determining $\epsilon_x$ and $\epsilon_y$ via spatial interpolation.
 $\text{FT}$ is the two-dimensional Fourier transform.
-
-In this formulation, the minimization objective (Eq.~\ref{a1}) is the mode volume, which we desire to be as small as possible.
+% 
+% In this formulation, the minimization objective (Eq.~\ref{a1}) is the mode volume, which we desire to be as small as possible.
 Similarily, Eq.~\ref{a3} is a constraint on the electric field to produce a large quality factor by forbidding the existence of any Fourier components within the light cone.
@@
 Lastly, Eq.~\ref{a4} is a binary constraint on epsilon, denoting that we only want the structure to be composed of air or silicon.
-
-Although our 2.5-dimensional approximation has reduced the size and complexity of the matrices found in the above formulation, the form of the problem in Eq.~\ref{a1}-\ref{a4} is actually incredibly difficult to solve, if for no other reason that Eq.~\ref{a1}, \ref{a2}, and \ref{a4} are non-convex\cite{boydbook} for joint minimization on both $\epsilon$ and $E$.
+% 
+% Although our 2.5-dimensional approximation has reduced the size and complexity of the matrices found in the above formulation, the form of the problem in Eq.~\ref{a1}-\ref{a4} is actually incredibly difficult to solve, if for no other reason that Eq.~\ref{a1}, \ref{a2}, and \ref{a4} are non-convex\cite{boydbook} for joint minimization on both $\epsilon$ and $E$.
 To make matters worse, the binary constraint in Eq.~\ref{a4} generally results in a problem which is NP-hard\cite{boydbook}.
 For these reasons, our strategy is to employ an alternating directions scheme\cite{altdir}, in which we break Eq.~\ref{a1}-\ref{a4} into two separate, tractable sub-problems which we then solve iteratively.
-
-\subsection{Alternating directions: field optimization sub-problem}
-The first sub-problem in the alternating directions scheme involves optimizing $E$ while holding $\epsilon$ constant,
-\begin{align}
-\underset{E}{\text{minimize}} \quad& \|\nabla\times\nabla\times E - \mu\omega^2\epsilon E\|
-    + \eta \|\epsilon E^2\| \label{b1}\\ 
-\text{subject to} \quad 
-    & E_\text{center} = 1 \label{bcenter} \\
-    & \nabla\cdot\epsilon E = 0 \label{bdiv}\\
-    & \text{FT}_\text{lightcone}\{E\} = 0, \label{bQ}
-\end{align}
-which is a quadratic problem with linear equality constraints, and is easily solved using a standard factor-solve method for sparse matrices\cite{cholmod}.
-
-In this sub-problem, the most significant modification to the original formulation in Eq.~\ref{a1}-\ref{a4} is that the constraint in Eq.~\ref{a2} has been relaxed and moved into the minimization objective (Eq.~\ref{b1}).
+% 
+% \subsection{Alternating directions: field optimization sub-problem}
+% The first sub-problem in the alternating directions scheme involves optimizing $E$ while holding $\epsilon$ constant,
+% \begin{align}
+% \underset{E}{\text{minimize}} \quad& \|\nabla\times\nabla\times E - \mu\omega^2\epsilon E\|
+%     + \eta \|\epsilon E^2\| \label{b1}\\ 
+% \text{subject to} \quad 
+%     & E_\text{center} = 1 \label{bcenter} \\
+%     & \nabla\cdot\epsilon E = 0 \label{bdiv}\\
+%     & \text{FT}_\text{lightcone}\{E\} = 0, \label{bQ}
+% \end{align}
+% which is a quadratic problem with linear equality constraints, and is easily solved using a standard factor-solve method for sparse matrices\cite{cholmod}.
+% 
+% In this sub-problem, the most significant modification to the original formulation in Eq.~\ref{a1}-\ref{a4} is that the constraint in Eq.~\ref{a2} has been relaxed and moved into the minimization objective (Eq.~\ref{b1}).
 We will denote this term ($\|\nabla\times\nabla\times E - \mu\omega^2\epsilon E\|$) as the \emph{physics residual}.
-
-At the same time, the term for the mode volume from Eq.~\ref{a1} has also been modified in Eq.~\ref{b1}.
+% 
+% At the same time, the term for the mode volume from Eq.~\ref{a1} has also been modified in Eq.~\ref{b1}.
 We denote this term ($\|\epsilon E^2\|$) as the \emph{design objective}.
@@
 Also note that the constraint in Eq.~\ref{bcenter} is crucial in order to avoid the trivial solution $E=0$.
-
-Lastly, the $\eta$ coefficient in Eq.~\ref{b1} allows us to trade-off between the physics residual and the design objective.
+% 
+% Lastly, the $\eta$ coefficient in Eq.~\ref{b1} allows us to trade-off between the physics residual and the design objective.
 Thus, in order to achieve a small mode volume, the initial value of $\eta$ is large and is subsequently exponentially reduced once per iteration at all points in the grid in order to bring the physics residual to 0.
 Furthermore, $\eta$ can also be given a spatial weighting in order to reduce in-plane losses; this strategy was implemented in the results presented here.
-
-\subsection{Alternating directions: structure optimization sub-problem}
-The second sub-problem in the alternating directions scheme involves optimizing $\epsilon$ while holding $E$ constant,
-\begin{align}
-\underset{\epsilon}{\text{minimize}} \quad& \|\nabla\times\nabla\times E - \mu\omega^2\epsilon E\| \label{c1} \\
-\text{subject to} \quad 
-    & \epsilon_\text{air} \le \epsilon \le \epsilon_\text{silicon}, \label{clim}
-\end{align}
-which is a quadratic problem with linear inequality constraints and is solved using CVX\cite{cvx}, a convex optimization package for Matlab.
-
-As in the field optimization sub-problem, the physics residual has been relaxed and placed in the minimization objective (Eq.~\ref{c1}).
+% 
+% 
+% \subsection{Alternating directions: structure optimization sub-problem}
+% The second sub-problem in the alternating directions scheme involves optimizing $\epsilon$ while holding $E$ constant,
+% \begin{align}
+% \underset{\epsilon}{\text{minimize}} \quad& \|\nabla\times\nabla\times E - \mu\omega^2\epsilon E\| \label{c1} \\
+% \text{subject to} \quad 
+%     & \epsilon_\text{air} \le \epsilon \le \epsilon_\text{silicon}, \label{clim}
+% \end{align}
+% which is a quadratic problem with linear inequality constraints and is solved using CVX\cite{cvx}, a convex optimization package for Matlab.
+% 
+% As in the field optimization sub-problem, the physics residual has been relaxed and placed in the minimization objective (Eq.~\ref{c1}).
 However, we have chosen not to include the design objective term (mode volume).
 This modification was implemented as a heurestic that seemed to improve the aesthetic quality of the resulting structure.
-
-The second major modification from the original formulation is found in the constraint in Eq.~\ref{clim}.
+% 
+% The second major modification from the original formulation is found in the constraint in Eq.~\ref{clim}.
 Since the combinatorial problem given by the original constraint in Eq.~\ref{a3} proved to be intractable, the constraint on the values of $\epsilon$ is relaxed to allow for any value in the range from $\epsilon_\text{air}$ to $\epsilon_\text{silicon}$.
@@
 In practice various digitization schemes can be implemented\cite{digitize}; however, such schemes were not needed here since a nearly binary structure was produced fortuitously.
-
-\section{Result}
-Using the formulations for the field optimization and structure optimization sub-problems presented above, along with our 2.5-dimensional approximation, the inverse design of a planar three-dimensional nanophotonic device is performed.
+% 
+% \section{Result}
+Using \eq{iterative problem}, along with our 2.5-dimensional approximation, the iterative design of a planar three-dimensional nanophotonic device is performed.
 
@@
 Lastly, an initial dielectric structure consisting entirely of silion, $\epsilon = \epsilon_\text{silicon}$ everywhere on a $160 \times 160$ grid, is used as a starting point---although other initial structures (e.~g.~ air everywhere or random $\epsilon$) yield nearly identical structures in this case.
-
-Having already determined the desired characteristics of our resonator (small mode-volume and large quality factor) in the formulation of the two sub-problems, the inverse design proceeds by alternately solving the field optimization and then the structure optimization sub-problems.
-That is to say, in every iteration of the algorithm, $E$ is updated to be the solution of Eq.~\ref{b1}-\ref{bQ} and is then plugged into Eq.~\ref{c1}-\ref{clim}, the solution of which becomes the updated value of $\epsilon$.
-The subsequent iteration then uses the updated $\epsilon$ variable to re-optimize $E$ once again.
-And the algorithm continues to proceed in this way until the physics residual ($\|\nabla\times\nabla\times E - \mu\omega^2\epsilon E\|$) is reduced to an acceptable value.
 
@@
 The entire inverse design process takes only 10 minutes on a standard desktop computer for the $160 \times 160$ grid.
-An animation of the values of $\epsilon$ and $E_y$ at each iteration of the algorithm is included in the supplementary material.
 
-The values of the physics residual and the design objective (mode volume) at each iteration are shown in Fig.~\ref{progress}.
+% The values of the physics residual and the design objective (mode volume) at each iteration are shown in Fig.~\ref{progress}.
 Most importantly, we see that the physics residual seems to converge linearly, indicating that the algorithm is reasonably efficient.
 The primary factor in determining this rate of convergence is the exponential decrease in $\eta$ (Eq.~\ref{b1}), since as $\eta$ decreases, increasing emphasis is placed on minimizing the physics residual in the field sub-problem.
-
-\begin{figure}[hbt]
-\centering\includegraphics[width=\textwidth]{p2/the_prog}
-\caption{Value of the physics residual (blue) and design objective, or mode volume, (red) at each iteration.
+% 
+% \begin{figure}[hbt]
+% \centering\includegraphics[width=\textwidth]{p2/the_prog}
+% \caption{Value of the physics residual (blue) and design objective, or mode volume, (red) at each iteration.
 The physics residual seems to exhibit linear convergence, while the mode volume quickly saturates after roughly 25 iterations.}\label{progress}
-\end{figure}
-
-\section{Verification} % Find better section name
-\subsection{Accuracy}
-To evaluate the accuracy of the inverse design method, we compared the field resulting from the iterations (target field) with the actual field of the resulting structure solved by the 2.5-dimensional approximation (2.5D fiber mode) as well as the field of a full three-dimensional FDTD simulation of the resulting structure (full 3D field), as shown in Figs.~\ref{comp} and \ref{xsec}.
+% \end{figure}
+% 
+To evaluate the accuracy of our 2.5D approximation, we compared the field resulting from the iterations (target field) with the actual field of the resulting structure solved by the 2.5-dimensional approximation (2.5D fiber mode) as well as the field of a full three-dimensional FDTD simulation of the resulting structure (full 3D field), as shown in Figs.~\ref{comp} and \ref{xsec}.
 
@@
 This is expected with the use of our approximation; however, the error is still relatively small (below 1\% of the maximum field strength) and confined mostly to the edges of the structure.
-
-\subsection{Performance}
-The fields from the full three-dimensional FDTD simulation were used to evaluate the performance of the device.
+% 
+% \subsection{Performance}
+% The fields from the full three-dimensional FDTD simulation were used to evaluate the performance of the device.
 The resulting mode volume was $0.32 (\frac{\lambda}{n})^3$ and the total quality factor was 7063.
 The radiative (out-of-plane) quality factor was 8808 and the in-plane quality factor was 35648.
-
-Fig.~\ref{qcomp} shows the Fourier transforms of the target, fiber and three-dimensional $E_y$ fields taken at the center of the slab.
+% 
+% Fig.~\ref{qcomp} shows the Fourier transforms of the target, fiber and three-dimensional $E_y$ fields taken at the center of the slab.
 Although there are virtually no field components in the light cone in the case of the target and fiber fields, additional components are present in the full three-dimensional case.
 This explains why even when leaky radiative components were strictly disallowed in the field optimization sub-problem, the error in the 2.5-dimensional approximation unavoidably introduces some leaky components in the case of the actual three-dimensional structure.
-
-\begin{figure}[hbt]
-\centering\includegraphics[width=\textwidth]{p2/qcomp}
-\caption{Comparison of the Fourier transforms of the $E_y$ fields of the (a) the target field from the inverse design method, (b) the actual 2.5-dimensional fiber mode, and (c) the field from the full three-dimensional FDTD simulation.
+% 
+% \begin{figure}[hbt]
+% \centering\includegraphics[width=\textwidth]{p2/qcomp}
+% \caption{Comparison of the Fourier transforms of the $E_y$ fields of the (a) the target field from the inverse design method, (b) the actual 2.5-dimensional fiber mode, and (c) the field from the full three-dimensional FDTD simulation.
 The error in our approximation introduces some small additional Fourier components into the light cone.}\label{qcomp}
-\end{figure}
-
-\section{Conclusion}
-In summary, by using a 2.5-dimension approximation, we demonstrate the inverse design of a three-dimensional nanophotonic resonator.
+% \end{figure}
+% 
+% \section{Conclusion}
+% In summary, by using a 2.5-dimension approximation, we demonstrate the inverse design of a three-dimensional nanophotonic resonator.
 Further development of our method includes applying our inverse method to design three-dimensional devices which support multiple fields at different frequencies.
 This includes resonant devices such as a multi-wavelength cavity, as well as waveguiding devices such as $N$-port couplers, multiplexers, and grating couplers.\\
-
-This work has been supported in part by the AFOSR MURI for Complex and Robust On-chip Nanophotonics (Dr. Gernot Pomrenke), grant number FA9550-09-1-0704.
+%

### 2013-03-29 thesis/appendix1.tex
Did chap3.

--- 2013-03-28 thesis/chapter3.tex
@@
-% \documentclass[letterpaper,10pt]{article}
-% \usepackage{graphicx}
-% \usepackage{opex3}
-% \usepackage{amsmath,amssymb}
-% 
-% 
-% \begin{document}
-% \title{Objective-first design of 
-%     high-efficiency, small-footprint couplers between 
-%     arbitrary nanophotonic waveguide modes}
-% \author{Jesse Lu$^\ast$ and Jelena Vu\v{c}kovi\'{c}}
-% \address{Stanford University, Stanford, California, USA.}
-% \email{jesselu@stanford.edu}
-% 
-% \begin{abstract}
-% We present an algorithm for designing
-%     high efficiency ($\sim$98\%), 
-%     small-footprint (1.5-4 square vacuum wavelengths)
-%     couplers between arbitrary nanophotonic waveguide modes
-%     in two dimensions.
-% Our ``objective-first'' method is
-%     computationally fast (15 minutes on a single-core personal computer), 
-%     requires no trial-and-error, and
-%     does not require guessing a good starting design.
-% We demonstrate designs for various coupling problems which suggest 
-%     that our method allows for the design of any 
-%     single-mode, linear optical device.
-% \end{abstract}
-% \ocis{230.75370, 130.3990.}
-% 
-% \begin{thebibliography}{99}
-% \bibitem{fibergrating} Y. Tang, Z. Wang, L. Wosinski, U. Westergren, and S. He,
-%     ``Highly efficient nonuniform grating coupler for silicon-on-insulator 
-%     nanophotonic circuits,''
-%     Opt. Lett. \textbf{35}, 1290-1292 (2010).
-% \bibitem{ridge}  K. K. Lee, D. R. Lim, L.C. Kimerling, J. Shin, and F. Cerrina, 
-%     ``Fabrication of ultralow-loss Si/SiO2 waveguides by roughness reduction,''
-%     Opt. Lett. \textbf{26}, 1888-1890 (2001).
-% \bibitem{pcslow} Y. A. Vlasov, M. O'Boyle, H. F. Hamann, and S. J. McNab,
-%     ``Active control of slow light on a chip with photonic crystal waveguides,''
-%     Nature \textbf{438}, 65-69 (2005).
-% \bibitem{slotfocus} M. Lipson, 
-%     ``Guiding, modulating, and emitting light on 
-%     silicon-challenges and opportunities,'' 
-%     J. Lightwave Technol. \textbf{23}, 4222-4238 (2005).
-% \bibitem{active} J. Van Campenhout, P. Rojo Romeo, P. Regreny, C. Seassal, 
-%     D. Van Thourhout, S. Verstuyft, L. Di Cioccio, J.-M. Fedeli, 
-%     C. Lagahe, and R. Baets, 
-%     ``Electrically pumped InP-based microdisk lasers integrated with a 
-%     nanophotonic silicon-on-insulator waveguide circuit,'' 
-%     Opt. Express \textbf{15}, 6744-6749 (2007).
-% \bibitem{metallic} L. Tang, S. E. Kocabas, S. Latif, A. K. Okyay, 
-%     D. S. Ly-Gagnon, K. C. Saraswat, and D. A. B. Miller, 
-%     ``Nanometre-scale germanium photodetector enhanced by a 
-%     near-infrared dipole antenna,'' 
-%     Nature Photonics \textbf{2}, 226-229 (2008).
-% % \bibitem{fwadia} V. R. Almeida, R. R. Panepucci, and M. Lipson, 
-% %     ``Nanotaper for compact mode conversion,'' 
-% %     Opt. Lett. \textbf{28}, 1302-1304 (2003) 
-% % \bibitem{wwadia} S. G. Johnson, P. Bienstman,  M. A. Skorobogatiy, 
-% %     M. Ibanescu1, E. Lidorikis, and J. D. Joannopoulos,
-% %     ``Adiabatic theorem and continuous coupled-mode theory for 
-% %     efficient taper transitions in photonic crystals,''
-% %     Phys. Rev. E \textbf{66}, 066608 (2002)
-% % \bibitem{deriv} F. Wang, J. S. Jensen, O. Sigmund, 
-% %     ``Robust topology optimization of photonic crystal waveguides with 
-% %     tailored dispersion properties.'' 
-% %     J. Opt. Soc. Am. B \textbf{28}, 387-397 (2011)
-% % \bibitem{boydbook} S. Boyd, and L. Vandenberghe, 
-% %     \emph{Convex Optimization} 
-% %     (Cambridge University Press, 2004)
-% \bibitem{prevwork} J. Lu, S. Boyd, and J. Vuckovic, 
-%     ``Inverse design of a three-dimensional nanophotonic resonator,''
-%     Opt. Express \textbf{19}, 10563-10750 (2011). 
-% \bibitem{veronis} G. Veronis, and S. Fan, 
-%     ``Theoretical investigations of compact couplers between dielectric slab 
-%     waveguides and two-dimensional metal-dielectric-metal plasmonic waveguides,'' 
-%     Opt. Express \textbf{15}, 1211-1221 (2007).
-% \bibitem{yang} R. Yang, R. A. Wahsheh, Z. Lu, and M. A. G. Abushagur, 
-%     ``Efficient light coupling between dielectric slot waveguide and plasmonic
-%     slot waveguide,'' Opt. Lett. \textbf{35}, 649-651 (2010).
-% \bibitem{code} \url{www.github.com/JesseLu/objective-first}
-% \end{thebibliography}
-% 
-\chapter{Objective-first design}
-\section{Motivation}
-
-% Why is waveguide mode conversion important?
-Optical mode conversion, 
-    the efficient transfer of photons from one guided mode to another,
-    is a fundamental requirement in nanophotonics.
-For instance, efficient conversion between waveguides modes
-    is essential for:
-    \begin{itemize}
-        \item Coupling to and from optical fiber\cite{fibergrating}, 
-        to communicate with the outside world.
-    \item Coupling between various nanophotonic waveguides, 
-        since different waveguides are best suited for different applications.
-        For example, ridge waveguides seem ideal for 
-            low-loss transport\cite{ridge},
-            but other waveguides, 
-            such as photonic crystal waveguides or slot waveguides,
-            may be better suited for slow-light\cite{pcslow} 
-            or nonlinear optical devices based on 
-            localized field intensities\cite{slotfocus}.
-    \item Coupling between different materials systems such as
-       passive, active\cite{active}, and metallic\cite{metallic} devices. 
-    \end{itemize}
-In fact, the problem of converting between nanophotonic modes is essentially
-    the function of all linear nanophotonic devices, since
-    any linear device is completely characterized by its input and output modes
-    and the coupling coefficients between them.
-
-In this paper, we present a method to solve the problem 
-    of designing single-mode, linear nanophotonic devices.
-We then demonstrate this method by designing coupling structures 
-    between various nanophotonic waveguides.
-Furthermore, we show that our method 
-     does not require a good initial design,
-     is computationally fast,
-     and can generate high efficiency couplers within a very small footprint. 
-% 
-% 
-% % Why are current solutions insufficient?
-% % Brute force
-% Of the design strategies currently available,
-%     brute-force parameter search is the most often employed 
-%     because of its sheer simplicity.
-% Although it may be suitable for tuning existing designs,
-%     the parameter space for most practical devices is simply too large
-%     for such a strategy to be tractable.
-% 
-% % Adiabatic mode conversion (large devices, symmetry breaking)
-% Adiabatic mode conversion strategies have been succesful
-%     for certain fiber-waveguide\cite{fwadia} and 
-%     waveguide-waveguide\cite{wwadia} couplers,
-%     even if the resulting devices often require large footprints.
-% However, adiabatic approaches cannot be used in many important cases 
-%     such as coupling in the out-of-plane direction, or
-%     coupling between modes of opposite symmetry.
-
-% How does your algorithm solve this problem?
-% \subsection{Advantages of objective-first design}
-\section{Objective-first approach}
-% What is objective-first optimization?
-Physical structures are typically designed by solving the following problem:
-    \begin{subequations}\label{eq:adj}
-    \begin{align} 
-    \text{decrease} & \quad f(x) \label{eq:adj:obj} \\ 
-    \text{subject to} & \quad g(x,p) = 0, \label{eq:adj:con}
-    \end{align}
-    \end{subequations}
-    where $x$ is the field variable and $p$ is the structure variable.
-Here, $f(x)$, the \emph{design objective}, 
-    calculates the performance of the device 
-    (e.g. amount of power lost); 
-    while $g(x,p)$ is the underlying physical equation for the system
-    (e.g. the electromagnetic wave equation).
-
-In contrast, the objective-first approach solves 
-    \begin{subequations}\label{eq:ob1}
-    \begin{align} 
-    \text{decrease} & \quad \|g(x,p)\|^2 \label{eq:ob1:obj} \\ 
-    \text{subject to} & \quad f(x) = 0, \label{eq:ob1:con}
-    \end{align}
-    \end{subequations}
-    where $\|g(x,p)\|^2$ is the \emph{physics residual}.
-We term this formulation ``objective-first''
-    because the design objective is prioritized even above satisfying physics;
-    specifically, we force our design to always exhibit the desired performance
-    ($f(x) = 0$), even at the expense of
-    not perfectly satisfying the underlying physics which governs its operation.
-
-The motivation behind this formulation is two-fold.
-First, this approach allows one to arrive at a locally-optimal design rapidly 
-    by allowing $x$ and $p$ to vary independently, 
-    as opposed to Eq.~\ref{eq:adj}
-    where the value of $x$ is completely dependent on $p$.
-Second, it enables an increase in the likelihood of 
-    arriving at a high efficiency design
-    by forcibly imposing $f(x) = 0$,
-    and thereby circumvents any local optima consisting of
-    low-performance devices.
-
-% How is it applied to waveguide coupler design?
-\section{Objective-first design of waveguide couplers}
-We now demonstrate the objective-first approach
-    by designing waveguide couplers in two-dimensions.
-As such, we do not analyze effects which are only present in full 
-    three-dimensional systems, such as out-of-plane losses.
-Specifically, we work in the two-dimensional transverse electric mode,
-    choosing $H_z$ as the field variable $x$,
-    and $\epsilon^{-1}$ (the inverse of the permittivity) 
-    as the structure variable $p$.
-This results in the following form of the physics residual,
-    \begin{equation}
-    \|g(x,p)\|^2 = 
-    \|g(H_z, \epsilon^{-1})\|^2 = 
-    \| \nabla \times \epsilon^{-1} \nabla \times H_z - \mu_0 \omega^2 H_z \|^2,
-    \end{equation}
-    where $\omega$ is the angular frequency,
-    and $\mu_0$ is the permeability of free-space.
-
-In order to produce a method applicable 
-    to the design of any linear nanophotonic device,
-    we note that its performance
-    will be completely characterized by the fields along its boundary,
-    and therefore, 
-    we choose a boundary-value formulation for the design objective 
-    as shown in Fig.~\ref{fig:intro}.
-Namely, we first compute the boundary fields needed to obtain
-    perfect performance, $H_z^\text{perfect}$,
-    and then form the design objective as
-    \begin{equation}
-    f(x) = f(H_z) = \begin{bmatrix}
-        H_z - H_z^\text{perfect} \\
-        \frac{\partial H_z}{\partial n} - 
-            \frac{\partial H_z^\text{perfect}}{\partial n}
-        \end{bmatrix}_\text{boundary}
-        = 0,
-    \end{equation}
-    where $\partial H_z / \partial n$ 
-    denotes the spatial derivative in the direction normal to the boundary.
-
-\begin{figure}[htb]
-    \centering
-    \includegraphics[width=0.8\textwidth]{p3/intro} 
-    \caption{Boundary-value formulation of the design objective.
-        The values of $H_z^\text{perfect}$, 
-            defined along the dashed box surrounding the design area
-            (coupling structure), 
-            are shown in orange. 
-        The values of $H_z^\text{perfect}$ along the top and bottom edges
-            of the dashed box are set to zero.
-        In this schematic, the fundamental and second-order waveguide modes
-            have been chosen as the input and output modes respectively.}
-    \label{fig:intro}
-\end{figure}
-
-Such a design objective is both extremely simple and widely adaptable 
-    to the design of linear nanophotonic devices in general.
-On the other hand, such a formulation often prohibits the physics residual 
-    from disappearing completely; 
-    however, we find that very good device performance is still obtained
-    as long as the physics residual is sufficiently small.
-
-Lastly, we employ an alternating directions strategy,
-    where both $x$ and $p$ are solved iteratively\cite{prevwork}
-    and limit the allowable values of $\epsilon$ to be between
-    the permittivity of vacuum and of silicon,
-    \begin{equation}
-    \epsilon_0 \le \epsilon \le \epsilon_\text{silicon}.
-    \end{equation}
-Note that a completely binary structure,
-    where $\epsilon = \{\epsilon_0, \epsilon_\text{silicon}\}$,
-    is needed for manufacturing purposes; this will be pursued in a future work
-    along with an analysis of robustness to fabrication imperfections.
-That said, the final designs presented here 
-    all have significant portions which are already binary.
-
-\subsection{Coupler designs}
-We now present five results which suggest our method
-    is indeed able to design arbitrary single-mode, linear nanophotonic devices.
-These results comprise of couplers between 
-    the following nanophotonic waveguides:
-    \begin{enumerate}
-    \item coupling between waveguides of different refractive index and width
-        (Fig.~\ref{fig:fiber});
-    \item coupling between waveguide modes of different order and symmetry
-        (Fig.~\ref{fig:mode});
-    \item coupling between waveguides that confine light 
-        using different principles 
-        (index guided vs. distributed Bragg reflection guided), 
-        i.e., between a slab waveguide and a photonic crystal fiber
-        (Fig.~\ref{fig:aircore})
-    \item coupling from a dielectric to a plasmonic metal-insulator-metal 
-        waveguide (Fig.~\ref{fig:mim}); and
-    \item coupling from a dielectric waveguide to a (plasmonic) metal wire
-        (Fig.~\ref{fig:wire}).
-    \end{enumerate}
-All the designs presented are both highly efficient 
-    ($\sim 98\%$ coupling efficiency, in contrast to previous designs
-    which achieve only $\sim 70\%$ coupling efficiency\cite{veronis,yang})
-    and extremely compact 
-    (with footprints of only 1.5-4 square vacuum wavelengths).
-
-Note, however, that the small footprint of the designs presented does not 
-    imply small, unresolvable feature sizes.
-On the other hand, assuming a vacuum wavelength of 1550 nm,
-    the smallest possible feature in any of the examples presented is still
-    37 nm $\times$ 37 nm (see Fig.~\ref{fig:fiber}, for example),
-    as given by the size of a single grid point;
-    placing virtually all designs within reach of current-generation lithographic
-    systems.
-
-In addition, good starting points were not required; 
-    all initial designs were simply $\epsilon = 9$ everywhere
-    (a somewhat arbitrary guess, other values work as well).
-Finally, only 15 minutes on a single-core personal computer
-    were needed to obtain each design.
-
-In the appendix, we further demonstrate the generality of our method
-    by presenting several additional examples including
-    \begin{enumerate}
-    \item coupling between all four modes of a wide dielectric waveguide;
-    \item coupling from a wide, low-index waveguide to the output waveguides in 
-        Figs~\ref{fig:mode}-\ref{fig:wire}; and
-    \item coupling to selected channels of a set of five plasmonic waveguides.
-    \end{enumerate}
-
-\begin{figure}[htb]
-    \centering
-    \includegraphics[width=0.8\textwidth]{p3/1} 
-    \caption{Coupler from a narrow, high-index ($\epsilon=12.25$) waveguide to
-            a wide, low-index ($\epsilon=2.25$) waveguide. 
-        The $H_z^\text{perfect}$ boundary values used as 
-            the design objective are shown in the upper-left plots, 
-            the generated structure is shown in the upper-right plot, and
-            the simulated $H_z$ fields of the device are shown 
-            in the bottom two plots.
-        The computed efficiency of the coupler is high, $99.8\%$, and
-            the device is also extremely compact, 
-            convering only $36 \times 76$ grid points,
-            where the vacuum wavelength is 42 grid points
-            (footprint of $1.55$ square vacuum wavelengths).
-        Computation time was 15 minutes on a personal computer.}
-    \label{fig:fiber}
-\end{figure}
-\begin{figure}[htb]
-    \centering
-    \includegraphics[width=0.8\textwidth]{p3/2} 
-    \caption{Coupler that converts the fundamental waveguide mode to the
-            second-order waveguide mode.
-        This problem is quite difficult since the two modes are of 
-            opposite symmetry.
-        For example, adiabatic approaches cannot be applied to this case.
-        However, our method produces a device 
-            (which has the same dimensions and vacuum wavelength as 
-            Fig.~\ref{fig:fiber})  
-            with a coupling efficiency of $98.0\%$. 
-        Computation time was 15 minutes on a personal computer.
-        }
-    \label{fig:mode}
-\end{figure}
-\begin{figure}[htb]
-    \centering
-    \includegraphics[width=0.8\textwidth]{p3/3}
-    \caption{Coupler between a dielectric slab waveguide to 
-            an air-core waveguide.
-        Here, not only are the modes of opposite symmetry,
-            but the output waveguide operates on a fundamentally different
-            principle (distributed reflection) than the input waveguide 
-            (index guided).
-        The device still achieves an efficiency of $98.9\%$, demonstrating the
-            versatility of our method.
-        The vacuum wavelength is 25 grid points, 
-            while the device footprint is still $36 \times 76$ grid points
-            (footprint of 4.38 square vacuum wavelengths).
-        Computation time was 15 minutes on a personal computer.
-        }
-        \label{fig:aircore}
-\end{figure}
-\begin{figure}[htb]
-    \centering
-    \includegraphics[width=0.8\textwidth]{p3/4}
-    \caption{Coupler between a dielectric slab waveguide to 
-            a plasmonic metal-insulator-metal waveguide.
-        The efficiency of the device is $97.5\%$ and 
-            has the same wavelength and footprint as the device in
-            Fig.~\ref{fig:aircore}.
-        Computation time was 15 minutes on a personal computer.
-        }
-        \label{fig:mim}
-\end{figure}
-\begin{figure}[htb]
-    \centering
-    \includegraphics[width=0.8\textwidth]{p3/5}
-    \caption{Coupler between a dielectric slab waveguide to 
-            a plasmonic wire waveguide.
-        The efficiency of the device is $99.1\%$ and 
-            has the same wavelength and footprint as the device in
-            Fig.~\ref{fig:aircore}.
-        Computation time was 15 minutes on a personal computer.
-        }
-        \label{fig:wire}
-\end{figure}
-\clearpage
-
-\section{Conclusion}
-We develop a fundamentally new approach to designing physical structures,
-    which we term ``objective-first'', 
-    in that we choose to satisfy the design objective 
-    even above satisfying the physical equation which governs its operation.
-We then apply this approach to the design of 
-    various nanophotonic waveguide couplers,
-    and show that our method produces
-    high-efficiency designs ($\sim 98\%$ efficiency) 
-    in small footprints (1.5-4 square vacuum wavelengths)
-    without needing a good starting point.
-Furthermore, we suggest that such a methodology may be applicable
-    to the design of any single-mode, linear nanophotonic device.\\
-
-This work has been supported by the 
-    AFOSR MURI for Complex and Robust On-chip Nanophotonics 
-    (Dr. Gernot Pomrenke), grant number FA9550-09-1-0704.
-The Matlab code used is available online\cite{code}.
-% \clearpage
-% \begin{appendix}
+\chapter{Additional objective-first results}\label{ob-1 additional}
 \section{Additional mode coupler designs}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{p3/6}
+    \includegraphics[width=\textwidth]{p3/6}
     \caption{
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{p3/7}
+    \includegraphics[width=\textwidth]{p3/7}
     \caption{
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{p3/8}
+    \includegraphics[width=\textwidth]{p3/8}
     \caption{
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{p3/9}
+    \includegraphics[width=\textwidth]{p3/9}
     \caption{
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{p3/10}
+    \includegraphics[width=\textwidth]{p3/10}
     \caption{
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{p3/11}
+    \includegraphics[width=\textwidth]{p3/11}
     \caption{
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{p3/12}
+    \includegraphics[width=\textwidth]{p3/12}
     \caption{
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{p3/13}
+    \includegraphics[width=\textwidth]{p3/13}
     \caption{
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{p3/14}
+    \includegraphics[width=\textwidth]{p3/14}
     \caption{
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{p3/15}
+    \includegraphics[width=\textwidth]{p3/15}
     \caption{
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{p3/16}
+    \includegraphics[width=\textwidth]{p3/16}
     \caption{
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{p3/17}
+    \includegraphics[width=\textwidth]{p3/17}
     \caption{
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{p3/18}
+    \includegraphics[width=\textwidth]{p3/18}
     \caption{
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{p3/19}
+    \includegraphics[width=\textwidth]{p3/19}
     \caption{
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{p3/20}
+    \includegraphics[width=\textwidth]{p3/20}
     \caption{
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{p3/21}
+    \includegraphics[width=\textwidth]{p3/21}
     \caption{

### 2013-03-29 thesis/appendix2.tex
Did chap3.

\chapter{Metamaterial-like objective-first results}\label{ob-1 meta}

### 2013-03-29 thesis/chapter3.tex
Did chap3.

@@
 %     near-infrared dipole antenna,'' 
-%     Nature Photonics \textbf{2}, 226-229 (2008).
+%     Nature Photonics \textbf{2}, 226-229 (2).
 % % \bibitem{fwadia} V. R. Almeida, R. R. Panepucci, and M. Lipson, 
@@
 % 
-\chapter{Objective-first design}
-\section{Motivation}
-
-% Why is waveguide mode conversion important?
-Optical mode conversion, 
-    the efficient transfer of photons from one guided mode to another,
-    is a fundamental requirement in nanophotonics.
-For instance, efficient conversion between waveguides modes
-    is essential for:
-    \begin{itemize}
-        \item Coupling to and from optical fiber\cite{fibergrating}, 
-        to communicate with the outside world.
-    \item Coupling between various nanophotonic waveguides, 
-        since different waveguides are best suited for different applications.
-        For example, ridge waveguides seem ideal for 
-            low-loss transport\cite{ridge},
-            but other waveguides, 
-            such as photonic crystal waveguides or slot waveguides,
-            may be better suited for slow-light\cite{pcslow} 
-            or nonlinear optical devices based on 
-            localized field intensities\cite{slotfocus}.
-    \item Coupling between different materials systems such as
-       passive, active\cite{active}, and metallic\cite{metallic} devices. 
-    \end{itemize}
-In fact, the problem of converting between nanophotonic modes is essentially
-    the function of all linear nanophotonic devices, since
-    any linear device is completely characterized by its input and output modes
-    and the coupling coefficients between them.
-
-In this paper, we present a method to solve the problem 
-    of designing single-mode, linear nanophotonic devices.
-We then demonstrate this method by designing coupling structures 
-    between various nanophotonic waveguides.
-Furthermore, we show that our method 
-     does not require a good initial design,
-     is computationally fast,
-     and can generate high efficiency couplers within a very small footprint. 
+\chapter{Objective-first design} \label{ob-1}
+% 
+% % Why is waveguide mode conversion important?
+% Optical mode conversion, 
+%     the efficient transfer of photons from one guided mode to another,
+%     is a fundamental requirement in nanophotonics.
+% For instance, efficient conversion between waveguides modes
+%     is essential for:
+%     \begin{itemize}
+%         \item Coupling to and from optical fiber\cite{fibergrating}, 
+%         to communicate with the outside world.
+%     \item Coupling between various nanophotonic waveguides, 
+%         since different waveguides are best suited for different applications.
+%         For example, ridge waveguides seem ideal for 
+%             low-loss transport\cite{ridge},
+%             but other waveguides, 
+%             such as photonic crystal waveguides or slot waveguides,
+%             may be better suited for slow-light\cite{pcslow} 
+%             or nonlinear optical devices based on 
+%             localized field intensities\cite{slotfocus}.
+%     \item Coupling between different materials systems such as
+%        passive, active\cite{active}, and metallic\cite{metallic} devices. 
+%     \end{itemize}
+% In fact, the problem of converting between nanophotonic modes is essentially
+%     the function of all linear nanophotonic devices, since
+%     any linear device is completely characterized by its input and output modes
+%     and the coupling coefficients between them.
+% 
+% In this paper, we present a method to solve the problem 
+%     of designing single-mode, linear nanophotonic devices.
+% We then demonstrate this method by designing coupling structures 
+%     between various nanophotonic waveguides.
+% Furthermore, we show that our method 
+%      does not require a good initial design,
+%      is computationally fast,
+%      and can generate high efficiency couplers within a very small footprint. 
 % 
@@
 % \subsection{Advantages of objective-first design}
-\section{Objective-first approach}
-% What is objective-first optimization?
-Physical structures are typically designed by solving the following problem:
-    \begin{subequations}\label{eq:adj}
+% \section{Objective-first approach}
+% % What is objective-first optimization?
+% Physical structures are typically designed by solving the following problem:
+%     \begin{subequations}\label{eq:adj}
+%     \begin{align} 
+%     \text{decrease} & \quad f(x) \label{eq:adj:obj} \\ 
+%     \text{subject to} & \quad g(x,p) = 0, \label{eq:adj:con}
+%     \end{align}
+%     \end{subequations}
+%     where $x$ is the field variable and $p$ is the structure variable.
+% Here, $f(x)$, the \emph{design objective}, 
+%     calculates the performance of the device 
+%     (e.g. amount of power lost); 
+%     while $g(x,p)$ is the underlying physical equation for the system
+%     (e.g. the electromagnetic wave equation).
+% 
+% In contrast, the objective-first approach solves 
+%     \begin{subequations}\label{eq:ob1}
+%     \begin{align} 
+%     \text{decrease} & \quad \|g(x,p)\|^2 \label{eq:ob1:obj} \\ 
+%     \text{subject to} & \quad f(x) = 0, \label{eq:ob1:con}
+%     \end{align}
+%     \end{subequations}
+%     where $\|g(x,p)\|^2$ is the \emph{physics residual}.
+% We term this formulation ``objective-first''
+%     because the design objective is prioritized even above satisfying physics;
+%     specifically, we force our design to always exhibit the desired performance
+%     ($f(x) = 0$), even at the expense of
+%     not perfectly satisfying the underlying physics which governs its operation.
+% 
+% The motivation behind this formulation is two-fold.
+% First, this approach allows one to arrive at a locally-optimal design rapidly 
+%     by allowing $x$ and $p$ to vary independently, 
+%     as opposed to Eq.~\ref{eq:adj}
+%     where the value of $x$ is completely dependent on $p$.
+% Second, it enables an increase in the likelihood of 
+%     arriving at a high efficiency design
+%     by forcibly imposing $f(x) = 0$,
+%     and thereby circumvents any local optima consisting of
+%     low-performance devices.
+% 
+% How is it applied to waveguide coupler design?
+\section{Problem formulation}
+Our next realization was that,
+    for linear nanophotonic devices,
+    only certain portions of the electromagnetic field were relevant 
+    to device performance--namely the boundary fields
+    at the input and output ports of the device.
+This realization motivated the following problem formulation:
+    \begin{subequations}
     \begin{align} 
-    \text{decrease} & \quad f(x) \label{eq:adj:obj} \\ 
-    \text{subject to} & \quad g(x,p) = 0, \label{eq:adj:con}
-    \end{align}
+    \minimize & \|A(z)x - b\|^2 \\
+    \subto & x_\text{boundary} - \hat{x}_\text{boundary} = 0 \\
+        & z_\text{min} \le z \le z_\text{max},
+    \end{align} \label{ob1 problem}
     \end{subequations}
-    where $x$ is the field variable and $p$ is the structure variable.
-Here, $f(x)$, the \emph{design objective}, 
-    calculates the performance of the device 
-    (e.g. amount of power lost); 
-    while $g(x,p)$ is the underlying physical equation for the system
-    (e.g. the electromagnetic wave equation).
-
-In contrast, the objective-first approach solves 
-    \begin{subequations}\label{eq:ob1}
-    \begin{align} 
-    \text{decrease} & \quad \|g(x,p)\|^2 \label{eq:ob1:obj} \\ 
-    \text{subject to} & \quad f(x) = 0, \label{eq:ob1:con}
-    \end{align}
-    \end{subequations}
-    where $\|g(x,p)\|^2$ is the \emph{physics residual}.
-We term this formulation ``objective-first''
-    because the design objective is prioritized even above satisfying physics;
-    specifically, we force our design to always exhibit the desired performance
-    ($f(x) = 0$), even at the expense of
-    not perfectly satisfying the underlying physics which governs its operation.
-
-The motivation behind this formulation is two-fold.
-First, this approach allows one to arrive at a locally-optimal design rapidly 
-    by allowing $x$ and $p$ to vary independently, 
-    as opposed to Eq.~\ref{eq:adj}
-    where the value of $x$ is completely dependent on $p$.
-Second, it enables an increase in the likelihood of 
-    arriving at a high efficiency design
-    by forcibly imposing $f(x) = 0$,
-    and thereby circumvents any local optima consisting of
-    low-performance devices.
-
-% How is it applied to waveguide coupler design?
-\section{Objective-first design of waveguide couplers}
-We now demonstrate the objective-first approach
-    by designing waveguide couplers in two-dimensions.
-As such, we do not analyze effects which are only present in full 
-    three-dimensional systems, such as out-of-plane losses.
-Specifically, we work in the two-dimensional transverse electric mode,
-    choosing $H_z$ as the field variable $x$,
-    and $\epsilon^{-1}$ (the inverse of the permittivity) 
-    as the structure variable $p$.
-This results in the following form of the physics residual,
-    \begin{equation}
-    \|g(x,p)\|^2 = 
-    \|g(H_z, \epsilon^{-1})\|^2 = 
-    \| \nabla \times \epsilon^{-1} \nabla \times H_z - \mu_0 \omega^2 H_z \|^2,
-    \end{equation}
-    where $\omega$ is the angular frequency,
-    and $\mu_0$ is the permeability of free-space.
-
-In order to produce a method applicable 
-    to the design of any linear nanophotonic device,
-    we note that its performance
-    will be completely characterized by the fields along its boundary,
-    and therefore, 
-    we choose a boundary-value formulation for the design objective 
-    as shown in Fig.~\ref{fig:intro}.
-Namely, we first compute the boundary fields needed to obtain
-    perfect performance, $H_z^\text{perfect}$,
-    and then form the design objective as
-    \begin{equation}
-    f(x) = f(H_z) = \begin{bmatrix}
-        H_z - H_z^\text{perfect} \\
-        \frac{\partial H_z}{\partial n} - 
-            \frac{\partial H_z^\text{perfect}}{\partial n}
-        \end{bmatrix}_\text{boundary}
-        = 0,
-    \end{equation}
-    where $\partial H_z / \partial n$ 
-    denotes the spatial derivative in the direction normal to the boundary.
+    which replaces the field regularization term from \eq{iterative problem}
+    with the hard constraint $x_\text{boundary} - \hat{x}_\text{boundary} = 0$.
+This constraint forces the field at the device boundary ($x_\text{boundary}$)
+    to be equal to that of an ideal device ($\hat{x}_\text{boundary}$),
+    as shown in fig.~\ref{p3/intro}.
+We call this type of formulation ``objective-first''
+    since the performance of the device is prioritized above
+    the physicality of the device.
 
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{p3/intro} 
+    \includegraphics[width=\textwidth]{p3/intro} 
     \caption{Boundary-value formulation of the design objective.
@@
 \end{figure}
-
+%\section{Objective-first design of waveguide couplers}
+% We now demonstrate the objective-first approach
+%     by designing waveguide couplers in two-dimensions.
+% As such, we do not analyze effects which are only present in full 
+%     three-dimensional systems, such as out-of-plane losses.
+% Specifically, we work in the two-dimensional transverse electric mode,
+%     choosing $H_z$ as the field variable $x$,
+%     and $\epsilon^{-1}$ (the inverse of the permittivity) 
+%     as the structure variable $p$.
+% This results in the following form of the physics residual,
+%     \begin{equation}
+%     \|g(x,p)\|^2 = 
+%     \|g(H_z, \epsilon^{-1})\|^2 = 
+%     \| \nabla \times \epsilon^{-1} \nabla \times H_z - \mu_0 \omega^2 H_z \|^2,
+%     \end{equation}
+%     where $\omega$ is the angular frequency,
+%     and $\mu_0$ is the permeability of free-space.
+% 
+% In order to produce a method applicable 
+%     to the design of any linear nanophotonic device,
+%     we note that its performance
+%     will be completely characterized by the fields along its boundary,
+%     and therefore, 
+%     we choose a boundary-value formulation for the design objective 
+%     as shown in Fig.~\ref{fig:intro}.
+% Namely, we first compute the boundary fields needed to obtain
+%     perfect performance, $H_z^\text{perfect}$,
+%     and then form the design objective as
+%     \begin{equation}
+%     f(x) = f(H_z) = \begin{bmatrix}
+%         H_z - H_z^\text{perfect} \\
+%         \frac{\partial H_z}{\partial n} - 
+%             \frac{\partial H_z^\text{perfect}}{\partial n}
+%         \end{bmatrix}_\text{boundary}
+%         = 0,
+%     \end{equation}
+%     where $\partial H_z / \partial n$ 
+%     denotes the spatial derivative in the direction normal to the boundary.
+% 
+% \begin{figure}[htb]
+%     \centering
+%     \includegraphics[width=\textwidth]{p3/intro} 
+%     \caption{Boundary-value formulation of the design objective.
+%         The values of $H_z^\text{perfect}$, 
+%             defined along the dashed box surrounding the design area
+%             (coupling structure), 
+%             are shown in orange. 
+%         The values of $H_z^\text{perfect}$ along the top and bottom edges
+%             of the dashed box are set to zero.
+%         In this schematic, the fundamental and second-order waveguide modes
+%             have been chosen as the input and output modes respectively.}
+%     \label{fig:intro}
+% \end{figure}
+%     
 Such a design objective is both extremely simple and widely adaptable 
@@
 
-Lastly, we employ an alternating directions strategy,
-    where both $x$ and $p$ are solved iteratively\cite{prevwork}
+\section{Implementation}
+We employ an alternating directions strategy,
+    where both $x$ and $z$ are solved iteratively
     and limit the allowable values of $\epsilon$ to be between
@@
     where $\epsilon = \{\epsilon_0, \epsilon_\text{silicon}\}$,
-    is needed for manufacturing purposes; this will be pursued in a future work
-    along with an analysis of robustness to fabrication imperfections.
+    is needed for manufacturing purposes.
 That said, the final designs presented here 
@@
 
-\subsection{Coupler designs}
-We now present five results which suggest our method
+\section{Results}
+We now demonstrate the objective-first approach
+    by designing waveguide couplers in two-dimensions.
+As such, we do not analyze effects which are only present in full 
+    three-dimensional systems, such as out-of-plane losses.
+Specifically, we work in the two-dimensional transverse electric mode,
+    choosing $H_z$ as the field variable $x$,
+    and $\epsilon^{-1}$ (the inverse of the permittivity) 
+    as the structure variable $z$.
+
+Specifically, we present five results which suggest our method
     is indeed able to design arbitrary single-mode, linear nanophotonic devices.
@@
 
-In the appendix, we further demonstrate the generality of our method
+In appendix~\ref{ob-1 additional}, we further demonstrate the generality of our method
     by presenting several additional examples including
@@
 
+Furthermore, appendix~\ref{ob-1 meta} contains designs for metamaterial-like
+    devices.
+
 \begin{figure}[htb]
     \centering
-    \includegraphics[width=0.8\textwidth]{p3/1} 
+    \includegraphics[width=\textwidth]{p3/1} 
     \caption{Coupler from a narrow, high-index ($\epsilon=12.25$) waveguide to
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{p3/2} 
+    \includegraphics[width=\textwidth]{p3/2} 
     \caption{Coupler that converts the fundamental waveguide mode to the
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{p3/3}
+    \includegraphics[width=\textwidth]{p3/3}
     \caption{Coupler between a dielectric slab waveguide to 
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{p3/4}
+    \includegraphics[width=\textwidth]{p3/4}
     \caption{Coupler between a dielectric slab waveguide to 
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{p3/5}
+    \includegraphics[width=\textwidth]{p3/5}
     \caption{Coupler between a dielectric slab waveguide to 
@@
 \end{figure}
-\clearpage
-
-\section{Conclusion}
-We develop a fundamentally new approach to designing physical structures,
-    which we term ``objective-first'', 
-    in that we choose to satisfy the design objective 
-    even above satisfying the physical equation which governs its operation.
-We then apply this approach to the design of 
-    various nanophotonic waveguide couplers,
-    and show that our method produces
-    high-efficiency designs ($\sim 98\%$ efficiency) 
-    in small footprints (1.5-4 square vacuum wavelengths)
-    without needing a good starting point.
-Furthermore, we suggest that such a methodology may be applicable
-    to the design of any single-mode, linear nanophotonic device.\\
-
-This work has been supported by the 
-    AFOSR MURI for Complex and Robust On-chip Nanophotonics 
-    (Dr. Gernot Pomrenke), grant number FA9550-09-1-0704.
-The Matlab code used is available online\cite{code}.
+% 
+% \section{Conclusion}
+% We develop a fundamentally new approach to designing physical structures,
+%     which we term ``objective-first'', 
+%     in that we choose to satisfy the design objective 
+%     even above satisfying the physical equation which governs its operation.
+% We then apply this approach to the design of 
+%     various nanophotonic waveguide couplers,
+%     and show that our method produces
+%     high-efficiency designs ($\sim 98\%$ efficiency) 
+%     in small footprints (1.5-4 square vacuum wavelengths)
+%     without needing a good starting point.
+% Furthermore, we suggest that such a methodology may be applicable
+%     to the design of any single-mode, linear nanophotonic device.\\
+% 
+% This work has been supported by the 
+%     AFOSR MURI for Complex and Robust On-chip Nanophotonics 
+%     (Dr. Gernot Pomrenke), grant number FA9550-09-1-0704.
+% The Matlab code used is available online\cite{code}.
 % \clearpage
 % \begin{appendix}
-\section{Additional mode coupler designs}
-In this section, we present additional mode coupler designs.
-A wide, high-index waveguide is used at both the input and output ports,
-    and all permutations of couplers are fabricated among
-    the first four propagating modes.
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.8\textwidth]{p3/6}
-    \caption{
-        Coupler from the first-order to the second-order mode 
-            of a wide dielectric waveguide.
-        Efficiency: $99.3\%$,
-        footprint: $1.55$ square vacuum wavelengths.
-        }
-        % \label{fig:wire}
-\end{figure}
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.8\textwidth]{p3/7}
-    \caption{
-        Coupler from the first-order to the third-order mode 
-            of a wide dielectric waveguide.
-        Efficiency: $98.3\%$,
-        footprint: $1.55$ square vacuum wavelengths.
-        }
-        % \label{fig:wire}
-\end{figure}
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.8\textwidth]{p3/8}
-    \caption{
-        Coupler from the first-order to the fourth-order mode 
-            of a wide dielectric waveguide.
-        Efficiency: $90.6\%$,
-        footprint: $1.55$ square vacuum wavelengths.
-        }
-        % \label{fig:wire}
-\end{figure}
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.8\textwidth]{p3/9}
-    \caption{
-        Coupler from the second-order to the third-order mode 
-            of a wide dielectric waveguide.
-        Efficiency: $96.8\%$,
-        footprint: $1.55$ square vacuum wavelengths.
-        }
-        % \label{fig:wire}
-\end{figure}
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.8\textwidth]{p3/10}
-    \caption{
-        Coupler from the second-order to the fourth-order mode 
-            of a wide dielectric waveguide.
-        Efficiency: $86.3\%$,
-        footprint: $1.55$ square vacuum wavelengths.
-        }
-        % \label{fig:wire}
-\end{figure}
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.8\textwidth]{p3/11}
-    \caption{
-        Coupler from the third-order to the fourth-order mode 
-            of a wide dielectric waveguide.
-        Efficiency: $80.1\%$,
-        footprint: $1.55$ square vacuum wavelengths.
-        }
-        % \label{fig:wire}
-\end{figure}
-\clearpage
-\section{Additional designs with wide, low-index input waveguide}
-We now reproduce Figs~\ref{fig:mode}-\ref{fig:wire}
-    but instead use a wide, low-index waveguide as the input.
-Once again, this is to demonstrate the generality of our method;
-    namely, that it can be applied to the design of nearly any
-    single-mode, linear nanophotonic device.
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.8\textwidth]{p3/12}
-    \caption{
-        Coupler from a wide, low-index waveguide to the
-            second-order mode of a narrow, high-index waveguide.
-        Efficiency: $96.9\%$,
-        footprint: $1.55$ square vacuum wavelengths.
-        }
-        % \label{fig:wire}
-\end{figure}
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.8\textwidth]{p3/13}
-    \caption{
-        Coupler from a wide, low-index waveguide to an 
-            ``air-core'' waveguide mode.
-        Efficiency: $99.0\%$,
-        footprint: $4.38$ square vacuum wavelengths.
-        }
-        % \label{fig:wire}
-\end{figure}
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.8\textwidth]{p3/14}
-    \caption{
-        Coupler from a wide, low-index waveguide to a
-            metal-insulator-metal plasmonic waveguide mode.
-        Efficiency: $96.7\%$,
-        footprint: $4.38$ square vacuum wavelengths.
-        }
-        % \label{fig:wire}
-\end{figure}
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.8\textwidth]{p3/15}
-    \caption{
-        Coupler from a wide, low-index waveguide to a
-            plasmonic wire waveguide mode.
-        Efficiency: $99.7\%$,
-        footprint: $4.38$ square vacuum wavelengths.
-        }
-        % \label{fig:wire}
-\end{figure}
-\clearpage
-
-\section{Additional designs with multiple output plasmonic waveguides}
-We also present ``selector'' designs where photons are coupled to 
-    only one of five possible plasmonic output waveguides.
-We demonstrate these selector designs for both metal-insulator-metal and
-    metal-wire plasmonic waveguides.
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.8\textwidth]{p3/16}
-    \caption{
-        Coupler from a dielectric waveguide to the 
-            lowest branch of a set of five plasmonic wire waveguides.
-        Efficiency: $94.0\%$,
-        footprint: $4.38$ square vacuum wavelengths.
-        }
-        % \label{fig:wire}
-\end{figure}
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.8\textwidth]{p3/17}
-    \caption{
-        Coupler from a dielectric waveguide to the 
-            second branch of a set of five plasmonic wire waveguides.
-        Efficiency: $97.3\%$,
-        footprint: $4.38$ square vacuum wavelengths.
-        }
-        % \label{fig:wire}
-\end{figure}
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.8\textwidth]{p3/18}
-    \caption{
-        Coupler from a dielectric waveguide to the 
-            middle branch of a set of five plasmonic wire waveguides.
-        Efficiency: $98.5\%$,
-        footprint: $4.38$ square vacuum wavelengths.
-        }
-        % \label{fig:wire}
-\end{figure}
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.8\textwidth]{p3/19}
-    \caption{
-        Coupler from a dielectric waveguide to the 
-            middle branch of a set of five plasmonic 
-            metal-insulator-metal waveguides.
-        Efficiency: $97.7\%$,
-        footprint: $4.38$ square vacuum wavelengths.
-        }
-        % \label{fig:wire}
-\end{figure}
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.8\textwidth]{p3/20}
-    \caption{
-        Coupler from a dielectric waveguide to the 
-            fourth branch of a set of five plasmonic 
-            metal-insulator-metal waveguides.
-        Efficiency: $95.6\%$,
-        footprint: $4.38$ square vacuum wavelengths.
-        }
-        % \label{fig:wire}
-\end{figure}
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.8\textwidth]{p3/21}
-    \caption{
-        Coupler from a dielectric waveguide to the 
-            uppermost branch of a set of five plasmonic 
-            metal-insulator-metal waveguides.
-        Efficiency: $87.5\%$,
-        footprint: $4.38$ square vacuum wavelengths.
-        }
-        % \label{fig:wire}
-\end{figure}
-\clearpage
-% \end{appendix}

### 2013-03-29 thesis/appendix3.tex
Added chapter 4 and appendix 3.

--- 2012-12-18 plan/plan.tex
@@
-\documentclass{book}
-\usepackage{amsmath}
-% \usepackage{hyperref}
-\usepackage{pstricks}
-
-\input ../defs.tex
-
-\title{Objective-First Nanophotonic Design Plan} 
-\author{Jesse Lu}
-\begin{document}
-\maketitle
-\tableofcontents
-
-\chapter{Introduction}
-\section{Problem statement}
-Our goal is to create a software package 
-    to enable the design of nanophotonic devices.
-Specifically, our software produces designs for
-    \emph{linear} nanophotonics devices based on
-    \emph{desired coupling strengths} between various optical ports.
-
-% Presently, almost all nanophotonic devices are designed
-%     by guessing what a good design might look like,
-%     based on intuition and experience,
-%     and then optimizing it by trial-and-error.
-% In contrast, we want to enable the \emph{inverse design}
-%     of nanophotonic devices;
-%     that is, to design devices by simply describing the 
-%     desired performance that it must achieve.
-
-To put things mathematically, we want to create software 
-    to solve the following problem,
-    \EE {the plan (single mode)}
-        {\minimize&  f(x) + g(z) \\
-        \subto&     A(z)x - b(z) = 0}
-    where 
-    \BI $x$ and $z$ are the variables representing 
-            the \emph{field} our device produces and
-            the \emph{structure} of the device respectively,
-    \I  $f(x)$ and $g(z)$ are our \emph{design objectives},
-            which tell us the desirable properties 
-            that we would like our device to achieve, and
-    \I  $A(z)x - b(z)$ is the \emph{physics residual},
-            the underlying physical laws which must be met. \EI
-
-In general, we need to consider multiple fields produced 
-    by the device.
-Our problem statement is then
-    \EE {the plan (multi-mode)}
-        {\minimize&  \sum_i^N f_i(x_i) + g(z) \\
-        \subto&     A_i(z)x_i - b_i(z) = 0,\quad\text{for $i = 1, \ldots, N.$}}
-
-\section{Structure of our software}
-Our software package consists of various modules
-    which are designed to be maximally orthogonal.
-The various modules are illustrated in \fig{structure}.
-
-\begin{figure}[ht]\begin{center}
-\begin{pspicture}(6,2.4)(-6,-2)
-\psset{gridcolor=green, subgridcolor=yellow}
-    \let\psgrid\relax
-
-    \rput[t](-1.5,1){physics}
-    \psframe(-0.2,0.4)(-2.8,1.4)
-
-    \rput[t](1.5,1){simulation}
-    \psframe(0.2,0.4)(2.8,1.4)
-
-    \psline[linestyle=dashed](-3.2,0.2)(3.2,0.2)
-    \rput[l](3.2,0.2){\parbox{3cm}{\center physics-to-algebra \\ translation layer}}
-    \rput[t](0,-0.4){optimization}
-    \psframe(-1.3,-1)(1.3,0)
-\end{pspicture}
-\caption{Structure of our software. 
-    The physics and simulation modules provide a complete description of the problem.
-    The translation module takes this description and casts it in the language of linear algebra,
-        which the optimization module can then use to produce various designs.}
-\label{fig:structure}
-\end{center} \end{figure}
-
-Although all modules are provided by our software, 
-    the majority of the innovation lies in the optimization module.
-Since the optimization module works entirely in the realm of linear algebra,
-    a translation module is provided in order to cast concepts from electromagnetics into this form.
-Finally, physics and simulation modules are provided 
-    to allow the user to describe the design problem in physical, rather than mathematical terms.
-
-\chapter{Theory}
-\section{Mathematically rigorous statement of the problem}
+\renewcommand{\EE}[2]{\begin{subequations}\begin{align}#2\end{align}\label{eq:#1}\end{subequations}}
+\chapter{Mathematical details of nanophotonic computational design method} 
+\label{maths}
 As previously stated, the problem we want to solve is 
@@
 To now be more precise,
-    \BI $x_i \in \comps^n$ are the field variables,
-    \I  $z \in \reals^n$ is the structure variable,
-    \I  $f_i(x_i) \in \comps^n \to \reals$ are the field design objectives,
-    \I  $g(z) \in \reals^n \to \reals$ is the structure design objective,
+    \BI $x_i \in \comps^m$ are the field variables,
+    \I  $z \in \comps^n$ is the structure variable,
+    \I  $f_i(x_i) \in \comps^m \to \reals$ are the field design objectives,
+    \I  $g(z) \in \comps^n \to \reals$ is the structure design objective,
     \I  $A_i(z)x_i - b_i(z)$ are the physics residuals, with
@@
 
-\subsection{Definition of physics residual}
+\section{Definition of physics residual}
 The physics residual, $A_i(z)x_i - b_i(z)$, 
@@
         via
-    \BI $\curl \mu^{-1} \curl - \omega^2 \epsilon \to A_i(z)$, where $\epsilon$ is a function of $z$,
+    \BI $\curl \mu^{-1} \curl - \omega^2 \epsilon \to A_i(z)$, % where $\epsilon$ is a function of $z$,
+    \I  $\epsilon \to S_i z + \epsilon_{\text{const}, i}$,
     \I  $E \to x_i$, and
@@
 
-\subsection{Bi-affine property of the physics residual}
+\section{Bi-affine property of the physics residual}
 Critically, \eq{wave equation in E} is not only linear in $E$,
@@
         {A_i(z)x_i - b_i(z) = B_i(x_i)z - d_i(x_i) = 0,}
-    where $B(x_i) \in \comps^{n \times n}$, $d(x_i) \in \comps^n$ and
+    where $B(x_i) \in \comps^{m \times n}$, $d(x_i) \in \comps^n$ and
     \BI  $-\omega^2 E \to B_i(x_i)$, 
@@
 
-\subsection{Definition of the field design objective}
+\section{Definition of the field design objective}
 Although the field design objective $f_i(x_i)$ 
@@
 
-\subsection{Choice of the structure design objective}
-In contrast to the narrow definition of the field design objective,
-    the structure design objective is relatively unconstrained;
-    taking on various forms to best suit the needs of
-    the structure parameterization in use.
+\section{Choice of the structure design objective}
+The form of the structure design objective consists of two parts,
+    \BI a structure parameterization function 
+        $m(p) \in \reals^l \to \comps^n$, and 
+    \I  a parameter weighting function $w(p)\in \reals^l \to \reals$. \EI
+Both use the variable $p$ which allows us 
+    to cast $z$ into arbitrary parameters of our choice.
+Together, the general form of the structure design objective is
+    \E  {structure design objective definition}
+        {g(z) = I_0(z - m(p)) + w(p),}
+    where $I_0$ is the indicator function on the set containing only $0$,
+    \E{}{I_0(u) = \begin{cases} 0 & u = 0, \\ 
+                                \infty & \text{otherwise.} \end{cases}}
+An alternative interpretation of \eq{structure design objective definition} 
+    is that it implements a hard constraint on $z$ 
+    via the parameterization function $m(z)$,
+    as well as a soft constraint on $z$ 
+    via the weighting function $w(z)$.
 
-\section{Properties of the problem}
-We now examine the general mathematical properties 
-    of the stated problem \eq{rigorous problem statement}.
+Additionally, constraints on the elements of $p$ include either
+    a bounded continuous range of allowable values, or
+    a finite set of discrete allowable values.
 
-\subsection{Convexity analysis}
-% \subsubsection{Joint non-convexity}
+\section{Convexity analysis}
+% \subsection{Joint non-convexity}
 First we note that, as presented, 
@@
 
-% \subsubsection{Separable convexity}
+% \subsection{Separable convexity}
 That said, \eq{rigorous problem statement} is \emph{separably convex} 
@@
     methods of multipliers (ADMM), % Ref. 
-    for the implementation of a global optimization paradigm,
-    as referred to in section \ref{capabilities of our software}.
+    for the implementation of a ``global'' optimization paradigm,
 Of course, in this context we do not use the term ``global'' rigorously,
@@
 
-\subsection{Optimality condition}
-Based on the problem definition in \eq{rigorous problem statement},
-    we can write down a set of equations that, when met,
-    signal that we have arrived at a locally optimal point.
-Otherwise known as the Karush-Kuhn-Tucker (KKT) conditions, % Ref boyd
-    these are, for \eq{rigorous problem statement},
-    \EE {KKT conditions} % Check how these work out for complex values!!!
-        {|c_{ij}\T x_i| - \beta_{ij} &\le 0, \\
-        \alpha_{ij} - |c_{ij}\T x_i| &\le 0, \\
-        A_i(z)x_i - b_i(z) &= 0, \\
-%         % Lambda dual variables not needed because they do not appear 
-%         % in the last KKT condition.
-%         \lambda_{\alpha ij} &\ge 0, \\ 
-%         \lambda_{\beta ij} &\ge 0, \\
-%         \lambda_{\alpha ij}(|c_{ij}\T x_i| - \beta_{ij}) &= 0, \\
-%         \lambda_{\beta ij}(\alpha_{ij} - |c_{ij}\T x_i|) &= 0, \\
-        \nabla_z g(z) + \sum_i B(x_i)\T \nu_i &= 0,
-        }
-    where $\nu_i \in \comps^n$ are dual variables.
+% \section{Optimality condition}
+% Based on the problem definition in \eq{rigorous problem statement},
+%     we can write down a set of equations that, when met,
+%     signal that we have arrived at a locally optimal point.
+% Otherwise known as the Karush-Kuhn-Tucker (KKT) conditions, % Ref boyd
+%     these are, for \eq{rigorous problem statement},
+%     \EE {KKT conditions} % Check how these work out for complex values!!!
+%         {|c_{ij}\T x_i| - \beta_{ij} &\le 0, \\
+%         \alpha_{ij} - |c_{ij}\T x_i| &\le 0, \\
+%         A_i(z)x_i - b_i(z) &= 0, \\
+% %         % Lambda dual variables not needed because they do not appear 
+% %         % in the last KKT condition.
+% %         \lambda_{\alpha ij} &\ge 0, \\ 
+% %         \lambda_{\beta ij} &\ge 0, \\
+% %         \lambda_{\alpha ij}(|c_{ij}\T x_i| - \beta_{ij}) &= 0, \\
+% %         \lambda_{\beta ij}(\alpha_{ij} - |c_{ij}\T x_i|) &= 0, \\
+%         \nabla_z g(z) + \sum_i B(x_i)\T \nu_i &= 0,
+%         }
+%     where $\nu_i \in \comps^n$ are dual variables.
+%
 
-\chapter{The optimization module}
+% \chapter{The optimization module}
 
-\section{Capabilities of the module}\label{capabilities of our software}
+\section{Capabilities of the optimization software}
 We have implemented various 
-    \emph{optimization paradigms} and \emph{structure parameterizations}
+    \emph{optimization paradigms} and \emph{structure updates}
     which a user can arbitrarily combine in order to 
@@
 
-Also, the user can choose between the various structure parameterizations 
-    which include density, boundary, 
-    continuous, and combinatoric parameterizations.
-These parameterizations describe the structure as either
-    \BI a material density at every point in space;
-    \I  a boundary between objects of different materials;
-    \I  a set of continuously variable user-defined parameters; or 
-    \I  a selective combination of user-defined objects. \EI
-
-\section{Structure of the module}
+% In addition, the user can choose between \emph{continuous} or \emph{discrete}
+%     structure updates:
+%     \BI a continuous update constrains the values of $p$
+%         to be within a continous, bounded range; on the other hand,
+%     \I  a discrete update constrains the values of $p$ 
+%         within a finite set of allowable values. \EI
+% 
+\section{Structure of the software}
 
@@
     and the structure parameterization (or simply, structure) submodule.
-The interaction between these two submodules is illustrated in \fig{strategy}.
+% The interaction between these two submodules is illustrated in \fig{strategy}.
 
-\begin{figure}[ht]\begin{center}
-\begin{pspicture}(6,5)(-6,-2)
-\psset{gridcolor=green, subgridcolor=yellow}
-    \let\psgrid\relax
-
-    % Paradigm
-    \rput(0,4.3){optimization paradigm}
-    \psline(-2.2,4)(2.2,4) % top
-    \psline(-2.2,4)(-2.2,2) % left
-    \psline(2.2,4)(2.2,2) % right
-    \psline(-2.2,2)(-1,2)
-    \psline(2.2,2)(1,2)
-    \psline(-1,2.2)(1,2.2)
-    \psline(-1,2)(-1,2.2)
-    \psline(1,2)(1,2.2)
-
-    % Parameterization
-    \psframe(-.8,0.8)(.8,-0.4) 
-    \rput[t](0,-0.6){\parbox{3cm}{\center structure\\ parameterization}}
-
-    % Arrows
-    \rput[r](-4.3,3){$z_\text{guess}$}
-    \psline{->}(-4,3)(-2.4,3)
-
-    \rput[r](-1.9,0.8){$Q(z)$}
-    \psline(-1.6,1.8)(-1.6,0.2)
-    \psline{->}(-1.6,0.2)(-1,0.2)
-
-    \rput[l](1.9,0.8){$\text{argmin}\, Q(z) + g(z)$}
-    \psline(1.6,0.2)(1,0.2)
-    \psline{<-}(1.6,1.8)(1.6,0.2)
-
-    \rput[l](4.3,3){$z_\text{final}$}
-    \psline{<-}(4,3)(2.4,3)
-\end{pspicture}
-\caption{Basic layout of the module.
-        The optimization paradigm submodule
-            accepts an initial structure $z_\text{guess}$
-            and returns a final, optimized structure $z_\text{final}$.
-        This is accomplished by repeatedly passing quadratic functions $Q(z)$ 
-            to the structure parameterization module,
-            which returns an updated structure $z$
-            which minimizes $Q(z) + g(z)$.}
-\label{fig:strategy}
-\end{center} \end{figure}
-
+% \begin{figure}[ht]\begin{center}
+% \begin{pspicture}(6,5)(-6,-2)
+% \psset{gridcolor=green, subgridcolor=yellow}
+%     \let\psgrid\relax
+% 
+%     % Paradigm
+%     \rput(0,4.3){optimization paradigm}
+%     \psline(-2.2,4)(2.2,4) % top
+%     \psline(-2.2,4)(-2.2,2) % left
+%     \psline(2.2,4)(2.2,2) % right
+%     \psline(-2.2,2)(-1,2)
+%     \psline(2.2,2)(1,2)
+%     \psline(-1,2.2)(1,2.2)
+%     \psline(-1,2)(-1,2.2)
+%     \psline(1,2)(1,2.2)
+% 
+%     % Parameterization
+%     \psframe(-.8,0.8)(.8,-0.4) 
+%     % \rput[t](0,-0.6){\parbox{3cm}{\center structure\\ update}}
+%     \rput[t](0,-0.6){structure update}
+% 
+%     % Arrows
+%     \rput[r](-4.3,3){$z_\text{init}$}
+%     \psline{->}(-4,3)(-2.4,3)
+% 
+%     \rput[r](-1.9,0.8){$Q(z)$}
+%     \psline(-1.6,1.8)(-1.6,0.2)
+%     \psline{->}(-1.6,0.2)(-1,0.2)
+% 
+%     \rput[l](1.9,0.8){$\argmin Q(z) + g(z)$}
+%     \psline(1.6,0.2)(1,0.2)
+%     \psline{<-}(1.6,1.8)(1.6,0.2)
+% 
+% 
+%     \rput[l](4.3,3){$z_\text{final}$}
+%     \psline{<-}(4,3)(2.4,3)
+% \end{pspicture}
+% \caption{Basic layout of the module.
+%         The optimization paradigm submodule
+%             accepts an initial structure $z_\text{init}$
+%             and returns a final, optimized structure $z_\text{final}$.
+%         This is accomplished by repeatedly passing quadratic functions $Q(z)$ 
+%             to the structure update submodule,
+%             which returns an updated structure $z$
+%             which minimizes $Q(z) + g(z)$.}
+% \label{fig:strategy}
+% \end{center} \end{figure}
+% 
 In essense, a design is achieved via repeated calls to the structure submodule
@@
 
-\section{The paradigm submodule}
-\subsection{The local optimization paradigm}
+\section{The local optimization paradigm}
 The local optimization paradigm applies the adjoint method to solve \eq{rigorous problem statement}
@@
 
-\subsubsection{Computation of $\grad_z F$}
+\subsection{Computation of $\grad_z F$}
 The derivatives of the individual field design objectives are found via
@@
 
-Efficient calculation of $dx/dz$ is almost always impossible since $B_i(x_i) \in \comps^{n \times n}$.
+Efficient calculation of $dx_i/dz$ is almost always impossible since $B_i(x_i) \in \comps^{n \times n}$.
 At the same time, since ${\pd f_i}/{\pd x_i} \in \comps^{1 \times m}$, we instead compute $df_i(x_i)/dz$ via
@@
 
-\subsubsection{Computation of $\pd f_i(x_i) / \pd x_i$}
+\subsection{Computation of $\pd f_i(x_i) / \pd x_i$}
 The definition of $f_i(x_i)$ as given in \eq{field design objective definition} is not differentiable 
@@
 
-\subsection{The global optimization paradigm}
+\section{The global optimization paradigm}
 In contrast to the local paradigm, 
@@
 
-\subsubsection{Computation of $\argmin_{x_i} \Lag$}
+\subsection{Computation of $\argmin_{x_i} \Lag$}
 Updating $x_i$, which is left to the paradigm submodule,
@@
 
-\subsubsection{Relaxation of $f_i(x_i)$}
+\subsection{Relaxation of $f_i(x_i)$}
 In order to compute $\Delta x_i$ we relax the design objectives, $f_i(x_i)$, to a differentiable, and convex form.
@@
 
-\subsubsection{Computation of $\Delta x_i$}
+\subsection{Computation of $\Delta x_i$}
 We now show how $\Delta x_i$ may be efficiently computed.
@@
                             + u_i + \tilde{c}_i).}
-For its part, the Hessian can be simplified using the matrix inversion lemma\footnote{\E{}{ (A + UCV)^{-1} = A^{-1} - A^{-1}U (C^{-1} + V A^{-1} U)^{-1} V A^{-1}}}.
+For its part, the Hessian can be simplified using the matrix inversion lemma\footnote{$(A + UCV)^{-1} = A^{-1} - A^{-1}U (C^{-1} + V A^{-1} U)^{-1} V A^{-1}$}.
 Coupled with the introduction of 
@@
 \section{The structure submodule}
+% \subsection{The continuous structure update}
+A continuous structure update scheme solves
+    \E  {structure submodule primary equation}
+        {\argmin Q(z) + g(z)}
+    by limiting the allowable values of $p$
+    in \eq{structure design objective definition} to a continuous range
+    of real values.
 
-\begin{thebibliography}{99}
-\bibitem{ADMM} Boyd group ADMM paper
-\end{thebibliography}
-\end{document}
+If both $m(p)$ and $w(p)$ are linear, 
+    then \eq{structure submodule primary equation} is convex
+    and can be solved using CVX.
+
+On the other hand, if this is not the case, 
+    then \eq{structure submodule primary equation}
+    is solved using a gradient-descent method.
+
+% 
+% \subsection{The discrete structure update}
+% A discrete structure update scheme solves 
+%     \eq{structure submodule primary equation}
+%     while limiting the range of $p$ to a finite set of discrete values.
+% 
+% In the special case where both $m(p)$ and $w(p)$, as well as $Q(z)$
+%     are all linear and diagonal,
+%     then \eq{structure submodule primary equation} may be solved trivially.
+% Naturally, this is a very unique case and requires some amount 
+%     of care to set up on the user's part.
+% 
+% In general, \eq{structure submodule primary equation} is solved 
+%     using a greedy algorithm where the most beneficial change
+%     in a single element of $p$ is taken until no beneficial steps remain.
+%
+
+% 
+% \begin{thebibliography}{99}
+% \bibitem{ADMM} Boyd group ADMM paper
+% \end{thebibliography}
+% \end{document}

### 2013-03-29 thesis/chapter4.tex
Added chapter 4 and appendix 3.

@@
 % \end{thebibliography}
-\chapter{Final Result}
-\section{Introduction}
-Currently, almost all nanophotonic components are designed 
-    by hand-tuning a small number of parameters 
-    (e.g. waveguide widths and gaps, hole and ring sizes).
-However, the realization of 
-    increasingly complex, dense, and robust on-chip optical networks
-    will require utilizing increasing numbers of parameters
-    when designing nanophotonic components.
-
-Opening the design space to include many more parameters
-    allows for smaller footprint, higher performance devices by definition,
-    since original designs are still included in this parameter space.
-Unfortunately, the lack of intuition for what such designs might look like and
-    the inability to manually search such a large parameter space
-    have greatly hindered the ability to achieve this.
-
-For this reason, we have developed and implemented a computational method
-    which is able to use the full parameter space 
-    to design linear nanophotonic components in three dimensions.
-Critically, our method requires no user intervention or manual tuning.
-Instead, a \emph{design-by-specification} scheme is used 
-    to produce designs based solely on a user's performance specification.
-
-We show that our method can indeed produce designs 
-    which are extremely compact, and, at the same time, highly efficient.
-Furthermore, we demonstrate that devices with novel functionality
-    are easily designed.
-We also show that our method can be used to produce designs
-    with extreme robustness to wavelength and temperature shift,
+\chapter{Nanophotonic computational design} \label{final}
+% \section{Introduction}
+% Currently, almost all nanophotonic components are designed 
+%     by hand-tuning a small number of parameters 
+%     (e.g. waveguide widths and gaps, hole and ring sizes).
+% However, the realization of 
+%     increasingly complex, dense, and robust on-chip optical networks
+%     will require utilizing increasing numbers of parameters
+%     when designing nanophotonic components.
+% 
+% Opening the design space to include many more parameters
+%     allows for smaller footprint, higher performance devices by definition,
+%     since original designs are still included in this parameter space.
+% Unfortunately, the lack of intuition for what such designs might look like and
+%     the inability to manually search such a large parameter space
+%     have greatly hindered the ability to achieve this.
+% 
+% For this reason, we have developed and implemented a computational method
+%     which is able to use the full parameter space 
+%     to design linear nanophotonic components in three dimensions.
+% Critically, our method requires no user intervention or manual tuning.
+% Instead, a \emph{design-by-specification} scheme is used 
+%     to produce designs based solely on a user's performance specification.
+% 
+% We show that our method can indeed produce designs 
+%     which are extremely compact, and, at the same time, highly efficient.
+% Furthermore, we demonstrate that devices with novel functionality
+%     are easily designed.
+% We also show that our method can be used to produce designs
+%     with extreme robustness to wavelength and temperature shift,
+%     as well as fabrication error.
+% 
+% Lastly, all our results are produced by simply specifying
+%     the functionality and performance of the desired device,
+%     which suggests that our method may indeed by able
+%     to design \emph{all} linear nanophotonic devices.
+% 
+\section{Problem formulation}
+We now develop a method which may indeed be capable of designing 
+    linear nanophotonic device which
+    are fully three-dimensional and multi-modal,
+    exhibit novel functionality,
+    have very compact footprints,
+    exhibit high efficiency, and
+    are manufacturable.
+In addition, we also demonstrate the ability to produce structures
+    which are strongly robust to wavelength and temperature shift,
     as well as fabrication error.
 
-Lastly, all our results are produced by simply specifying
-    the functionality and performance of the desired device,
-    which suggests that our method may indeed by able
-    to design \emph{all} linear nanophotonic devices.
-
-\section{Problem formulation}
-% Problem statement 
 In order to produce designs which utilize the full parameter space,
     and are based solely on the user's performance specification,
-    we formulate the design problem in the following way:
+    we use the following final formulation:
 \begin{subequations}\begin{align}
@@
         which can be deduced since $A_i(z)x_i-b_i=0$ is not a hard constraint.
-    Instead, this formulation is what we call an \emph{objective-first} \cite{ob1_wg}
+    Instead, this formulation is what also an \emph{objective-first} \cite{ob1_wg}
         formulation in that the \emph{design objective} (explained below)
@@
 
-\section{Method of solution}
+\section{Implementation}
 We employed the alternating directions method of multipliers (ADMM) algorithm 
@@
     and tune our structure using a steepest-descent method.
+
+The mathematical details of our implementation are given 
+    in appendix~\ref{maths}
 
@@
 
-\section{Conclusion}
-We have developed and implemented a method to design linear nanophotonic structures
-    which are fully three-dimensional and multi-modal,
-    have very compact footprints,
-    exhibit high efficiency, and
-    are manufacturable.
-We demonstrate this capability by designing various nanophotonic mode converters,
-    splitters, hubs, and fiber couplers.
-Critically, many, if not all, of these devices have never been demonstrated before
-    and cannot be designed by hand.
-In contrast, our method allows user to easily design such devices
-    by virtue of our design-by-specification scheme.
-
-In addition, we demonstrate the design of a broadband device 
-    which is strongly robust to wavelength and temperature shift,
-    as well as fabrication error.
-We show that such a device has stable operating wavelengths 
-    over temperature shifts as large as 905 K,
-    or over-/under-etching error of up to 8 nm.
-We suggest, based on this design, that wavelength tolerance
-    may be a good heuristic to the design of temperature and fabrication-error
-    tolerant nanophotonic devices. \\
-
-This work has been supported by the 
-    AFOSR MURI for Complex and Robust On-chip Nanophotonics 
-    (Dr. Gernot Pomrenke), grant number FA9550-09-1-0704.
+% \section{Conclusion}
+% We have developed and implemented a method to design linear nanophotonic structures
+%     which are fully three-dimensional and multi-modal,
+%     have very compact footprints,
+%     exhibit high efficiency, and
+%     are manufacturable.
+% We demonstrate this capability by designing various nanophotonic mode converters,
+%     splitters, hubs, and fiber couplers.
+% Critically, many, if not all, of these devices have never been demonstrated before
+%     and cannot be designed by hand.
+% In contrast, our method allows user to easily design such devices
+%     by virtue of our design-by-specification scheme.
+% 
+% In addition, we demonstrate the design of a broadband device 
+%     which is strongly robust to wavelength and temperature shift,
+%     as well as fabrication error.
+% We show that such a device has stable operating wavelengths 
+%     over temperature shifts as large as 905 K,
+%     or over-/under-etching error of up to 8 nm.
+% We suggest, based on this design, that wavelength tolerance
+%     may be a good heuristic to the design of temperature and fabrication-error
+%     tolerant nanophotonic devices. \\
+% 
 % \end{document}

### 2013-03-29 thesis/intro.tex
Added chapter 4 and appendix 3.

@@
 The organization of this thesis is straightforward: 
-    chapters 2-4 detail the incremental steps in achieving
-    our final result, which is presented in chapter 5.
+    chapters \ref{direct}-\ref{ob-1} detail the incremental steps in achieving
+    our final result, which is presented in chapter \ref{final}.

### 2013-04-02 thesis/appendix2.tex
Added meta and fixed references.

@@
-\chapter{Metamaterial-like objective-first results}\label{ob-1 meta}
+% Custom figures.
+% \newcommand{\myfig}[2]{\begin{figure}[!h]\includegraphics[width=0.95\textwidth]{fig/#1.jpg}\caption{#2}\label{fig:#1}\end{figure}}
+\renewcommand{\myfig}[2]{
+    \begin{figure}[!h]\begin{center}
+    \includegraphics[width=\textwidth]{meta/fig/#1}\caption{#2}\label{fig:#1}
+    \end{center}\end{figure}}
+% \newcommand{\myfiglarge}[2]{\begin{figure}[!h]\begin{center}\includegraphics[width=0.95\textwidth]{fig/#1}\caption{#2}\label{fig:#1}\end{center}\end{figure}}
+% \newcommand{\myfigthree}[2]{\begin{figure}[!h]\begin{center}\includegraphics[width=0.73\textwidth]{fig/#1}\caption{#2}\label{fig:#1}\end{center}\end{figure}}
+
+\newcommand{\ER}[1]{\eqref{eq:#1}}
+\newcommand{\SR}[1]{Section~\ref{sec:#1}}
+\newcommand{\sR}[1]{section~\ref{sec:#1}}
+\newcommand{\FR}[1]{Figure~\ref{fig:#1}}
+\newcommand{\fR}[1]{figure~\ref{fig:#1}}
+
+\chapter[Design of optical cloaks and mimics]{Objective-first design of optical cloaks and mimics}\label{ob-1 meta}
+------------------------------------------------------%
+\section{Optical Cloak Design}
+%---------------------------------------------------------%    
+We now extend the applicability of our method
+    to the design of metamaterial devices which operate in free-space.
+In particular,
+    we adapt the waveguide coupler algorithm to the 
+    to the design of optical cloaks.
+
+% %---------------------------------------------------------%
+% \subsection{Application of the Objective-first Strategy}
+% %---------------------------------------------------------%
+
+Adapting the method used in chapter~\ref{ob-1} to the design of optical cloaks
+    really only requires one to change the simulation environment
+    to allow for free-space modes.
+This is accomplished by modifying the upper and lower boundaries
+    of the simulation domain from absorbing boundary conditions
+    to periodic boundary conditions,
+    which allows for plane-wave modes to propagate without loss
+    until reaching the left or right boundaries,
+    where absorbing boundary conditions are still maintained.
+
+In terms of the design objective, 
+    we allow the device to span the entire height of the simulation domain,
+    and thus consider only the leftmost and rightmost planes as boundary values.
+Specifically, for this section the input and output modes are plane waves
+    with normal incidence, 
+    as can be expected for good cloaking devices.
+The achieved results all yield high efficiency,
+    although we note that the cloaking effect is only measured
+    for a specific input mode.
+That is to say, just as the waveguide couplers previously designed
+    were single-mode devices,
+    so the cloaks designed in this section are also ``single-mode'' cloaks.
+An additional modification, as compared to chapter~\ref{ob-1}, is that
+    we now prevent the structure from being modified in certain areas
+    which contain the object to be cloaked.
+Each design is run for 400 iterations
+    with a uniform initial value of $p = 1/9$ for the structure
+    (where the structure is allowed to vary),
+    and the range of $p$ is limited to $1/12.25 \le p \le 1$,
+    implying a dielectric cloak.
+
+%---------------------------------------------------------%
+\subsection{Anti-reflection Coating}
+%---------------------------------------------------------%
+
+As a first example,
+    we attempt to design the simplest and most elementary ``cloaking'' device available,
+    which, we argue, is a simple anti-reflection coating;
+    in which case the object to be cloaked is nothing more than
+    the interface between two dielectric materials.
+In this case we use the interface between air and silicon, as shown in \FR{cloak/c1}
+\myfig{cloak/c1}{Anti-reflection coating.
+                Efficiency: 99.99\%,
+                device footprint: $60 \times 100$ grid points,
+                wavelength: 63 grid points.}
+
+Unsurprisingly for such a simple case, 
+    we achieve a very high efficiency device.
+Note also that the efficiency of the device can be deduced by eye,
+    based on the absence of reflections or standing waves 
+    in bottom two plots of \FR{cloak/c1}.
+
+%---------------------------------------------------------%
+\subsection{Wrap-around Cloak}
+%---------------------------------------------------------%
+
+Next, we design a cloak for a plasmonic cylinder,
+    which is quite effective at scattering light
+    as can be seen from \FR{cloak/c6},
+    where we show that the uncloaked cylnder,
+    although subwavelength in size, scatters
+    the majority of light away from the desire output (plane-wave) mode.
+\myfig{cloak/c6}{Plasmonic cylinder to be cloaked. 
+                68.5\% of light is diverted away from the desired output mode.}
+
+In designing the wrap-around cloak,
+    we allow the structure to vary at all points within the design area
+    except in the immediate vicinity of the plasmonic cylinder.
+Application of the objective-first strategy results
+    in an efficient (greater than 99\%) device as seen in \FR{cloak/c2}.
+\myfig{cloak/c2}{Wrap-around cloak.
+                Efficiency: 99.99\%,
+                device footprint: $60 \times 100$ grid points,
+                wavelength: 42 grid points.}
+Note that our cloak employs only isotropic, non-magnetic materials,
+    and at the same time it is specific to a particular input
+    and to a particular object.
+That is to say, it is a single-frequency, single-mode, and single-object 
+    cloaking device.
+
+%---------------------------------------------------------%
+\subsection{Open-channel Cloak}
+%---------------------------------------------------------%
+
+With a simple modification, from the previous example,
+    we can design a cloak which features an open channel
+    to the exterior electromagnetic environment (\FR{cloak/c4}).
+This simple modification creates an air gap that
+    connects the cylinder to the outside world
+    both from the front and back and
+    may be useful in the case where one would like to
+    remove or replace the cloaked object.
+
+\myfig{cloak/c4}{Open-channel cloak.
+                Efficiency: 99.8\%,
+                device footprint: $60 \times 100$ grid points,
+                wavelength: 42 grid points.}
+Such a design is still very efficient (greater than 99\% efficiency)
+    and demonstrates the usefulness of the objective-first strategy
+    in cases where other methods, such as transformation optics,
+    may require use of the entire space around the object
+    to be cloaked.
+
+%---------------------------------------------------------%
+\subsection{Channeling Cloak}
+%---------------------------------------------------------%
+
+Our last cloaking example replaces the plasmonic cylinder 
+    with a thin metallic wall in which a sub-wavelength channel is etched.
+Such a metallic wall is very effective at blocking incoming light
+    (as can be seen from \FR{cloak/c7} where more than 99\%
+    of the incoming light is blocked) 
+    because of its large negative permittivity ($\epsilon = -20$),
+    meaning that any cloaking device would be forced to channel
+    all the input light into a very small aperture
+    and then to flatten that light out into a plane wave again.
+\myfig{cloak/c7}{Metallic wall with sub-wavelength channel to be cloaked.
+                99.9\% of the light is blocked from the desired output plane-wave.}
+
+Once again, our method is able to produce a design with efficiency greater
+    than 99\%, as shown in \FR{cloak/c5}.
+\myfig{cloak/c5}{Channeling cloak.
+                Efficiency: 99.9\%,
+                device footprint: $60 \times 100$ grid points,
+                wavelength: 42 grid points.}
+
+%---------------------------------------------------------%
+\section{Optical Mimic Design}
+\label{sec:mimic}
+%---------------------------------------------------------%
+
+We now apply our objective-first strategy to the design of optical mimics.
+We define an optical mimic to be a linear nanophotonic device which 
+    mimics the output field of another device.
+In this sense optical mimics are anti-cloaks;
+    where cloaks strive to make an object's electromagnetic presence vanish,
+    mimics strive to implement an object's presence without that 
+    object actually being there.
+
+As such, the design of optical mimics provides a tantalyzing approach
+    to the realization of practical metamaterial devices.
+That is to say, if one can reliably produce practical optical mimics,
+    then producing metamaterials can be accomplished by 
+    simply producing an optical mimic of that material.
+In a more general sense, 
+    designing optical mimics is really just a recasting of the thrust of 
+    the objective-first design strategy in its purest form:
+    the design of a nanophotonic device based purely 
+    on the electromagnetic fields one wishes to produce.
+As such, devices which perform well-known optical functions
+    (e.g. focusing, lithography) can also be designed.
+
+% %---------------------------------------------------------%
+% \subsection{Application of the Objective-first Strategy}
+% %---------------------------------------------------------%                    
+%                 
+The objective-first design of optical mimics proceeds in virtually
+    an identical way to the design of optical cloaks,
+    the only difference being that the output modes are 
+    specifically chosen to be those that produce the desired function.
+For most of the examples provided, the input illumination is still an incident plane wave.
+Lastly, instead of measuring efficiency, 
+    we measure the relative error of the simulated field
+    against that of a perfect target field
+    at a relevant plane some distance away from the device.
+The location of this plane is identified as a dotted line in the subsequent figures.
+
+%---------------------------------------------------------%
+\subsection{Plasmonic Cylinder Mimic}
+%---------------------------------------------------------%
+
+Our first design is simply to mimic the plasmonic cylinder 
+    which we cloaked in the previous section.
+\FR{mimic/m1} shows the result of the design.
+
+The final structure is shown in the upper right plot,
+    while the ideal field and the simulated field
+    are shown in the middle and bottom plots.
+Note that the ideal field is cut off to emphasize 
+    the fields to the right of the device (the output fields).
+Also, the magnitude of the fields are compared at the 
+    dotted black line at which point the relative error
+    is also calculated.
+For this simple, initial mimic, the simulated field
+    quite closely imitates that produced by a single plasmonic cylinder (8.1\% error)
+
+    \myfig{mimic/m1}{Plasmonic cylinder mimic (see \FR{cloak/c6} for the original object). 
+                Error: 8.1\%,
+                device footprint: $40 \times 120$ grid points,
+                wavelength: 42 grid points.}
+\clearpage
+
+%---------------------------------------------------------%
+\subsection{Diffraction-limited Lens Mimic}
+%---------------------------------------------------------%
+
+We now design a mimic for a typical diffraction-limited lens.
+In this case, the object which we wish to mimic does not require simulation
+    since the fields of a lens can be readily computed.
+For the three figures below, 
+    the computed ideal fields are shown as the target fields.
+
+\FR{mimic/m3} shows the mimic of a lens with relatively moderate focusing. 
+In such a lens, the focusing action is gradual and easily discernible
+    by eye.
+The computed error in this case is 12.0\%.
+
+In constrast, \FR{mimic/m4} and \FR{mimic/m5} are both mimics of
+    a lens with a smaller half-wavelength spot size.
+Such a lens is much harder to design, 
+    because of the high-frequency spatial components involved;
+    and yet, we show that an objective-first strategy can 
+    produce successful designs (5.6\% and 1.4\% error)
+    and that this is achievable at both shorter and longer focal depths.
+\myfig{mimic/m3}{Full-width-half-max at focus: 1.5 $\lambda$,
+                focus depth: 100 grid points.
+                Error: 12.0\%,
+                device footprint: $40 \times 120$ grid points (1.6 $\lambda$ thick),
+                wavelength: 25 grid points.}
+
+\myfig{mimic/m4}{Full-width-half-max at focus: 0.5 $\lambda$,
+                focus depth: 50 grid points.
+                Error: 5.6\%,
+                device footprint: $40 \times 120$ grid points (1.6 $\lambda$ thick),
+                wavelength: 25 grid points.}
+\myfig{mimic/m5}{Full-width-half-max at focus: 0.5 $\lambda$,
+                focus depth: 150 grid points.
+                Error: 1.4\%,
+                device footprint: $40 \times 120$ grid points (1.6 $\lambda$ thick),
+                wavelength: 25 grid points.}
+\clearpage
+
+%---------------------------------------------------------%
+\subsection{Sub-diffraction Lens Mimic}
+%---------------------------------------------------------%
+
+Our method is now employed to mimic the effect of a sub-diffraction lens.
+Since such a lens can be created using a negative-index material \cite{pendry}
+    this mimic can be viewed as an imitation of a negative-index material,
+    in that the following device recreates the sub-diffraction target-field 
+    at the output plane (dotted line)
+    when illuminated by the same target field at the input of the device.
+In other words,
+    this device is an image-specific sub-diffraction imager,
+    which is another way of saying that it is a single-mode imager.
+\myfig{mimic/m2}{Sub-diffraction lens mimic.
+                The target field has a full-width half-maximum of 0.14 $\lambda$.
+                Error: 28.6\%,
+                device footprint: $60 \times 120$ grid points (1.43 $\lambda$ thick),
+                wavelength: 42 grid points.}
+
+As \FR{mimic/m2} shows,
+   we are able to recreate the target field at the output,
+   albeit with higher error (28.6\%).
+Although the error in this example is larger,
+    the field produced by the device has a full-width half-maximum
+    nearly equal to that of the target field.
+
+Note that the target field is created simply by placing 
+    the imaging field at the output plane.
+Also note that, as expected, 
+    the output field decays very quickly since,
+    for such a deeply subwavelength field,
+    it is composed primarily of evanescently decaying modes.
+
+%---------------------------------------------------------%
+\subsection{Sub-diffraction Optical Mask}
+%---------------------------------------------------------%
+
+Lastly, we extend the idea of a sub-diffraction lens mimic
+    one step further and
+    design a sub-diffraction optical mask.
+Such a device takes a plane wave as its input and
+    produces a sub-diffraction image at its output plane.
+Of course, akin to its lens counterpart,
+    this output plane must lie within the near-field 
+    of the device (specifically, two computational cells away)
+    because of its sub-wavelength nature.
+    \FR{mimic/m6} shows the design of a simple mask which 
+    successfully produces three peaks at its output
+    with an error of 19.8\%.
+\myfig{mimic/m6}{Sub-diffraction optical mask.
+                The three central peaks in the target field are each
+                separated by 0.28 $\lambda$.
+                Error: 19.8\%,
+                device footprint: $40 \times 120$ grid points,
+                wavelength: 25 grid points.}

### 2013-04-02 thesis/appendix3.tex
Added meta and fixed references.

@@
+\renewcommand{\eq}[1]{eq.~\eqref{eq:#1}}
 \renewcommand{\EE}[2]{\begin{subequations}\begin{align}#2\end{align}\label{eq:#1}\end{subequations}}
-\chapter{Mathematical details of nanophotonic computational design method} 
+\chapter[Computational design mathematics]{Mathematical details of nanophotonic computational design method} 
 \label{maths}
@@
     which a user can arbitrarily combine in order to 
-    to solve \eq{the plan (multi-mode)}.
+    to solve \eq{rigorous problem statement}.
 

### 2013-04-02 thesis/chapter3.tex
Added meta and fixed references.

@@
     to be equal to that of an ideal device ($\hat{x}_\text{boundary}$),
-    as shown in fig.~\ref{p3/intro}.
+    as shown in fig.~\ref{fig:intro}.
 We call this type of formulation ``objective-first''

### 2013-04-16 thesis/appendix2.tex
Added bibliography and fixed citations.

@@
 Our method is now employed to mimic the effect of a sub-diffraction lens.
-Since such a lens can be created using a negative-index material \cite{pendry}
+Since such a lens can be created using a negative-index material \cite{Pendry00}
     this mimic can be viewed as an imitation of a negative-index material,

### 2013-04-16 thesis/appendix3.tex
Added bibliography and fixed citations.

@@
 The optimization paradigm utilizes 
-    the alternating directions method of multipliers\cite{ADMM} (ADMM) optimization technique, 
+    the alternating directions method of multipliers\cite{Boyd11} (ADMM) optimization technique, 
     which casts \eq{rigorous problem statement} in terms of the following augmented Lagrangians, 

### 2013-04-16 thesis/bibliography.tex
Added bibliography and fixed citations.

\begin{thebibliography}{99}

\bibitem{Boyd04} S. Boyd, L. Vandenberghe, \emph{Convex Optimization} (Cambridge University Press, 2004).

\bibitem{Boyd11} S. Boyd, N. Parikh, E. Chu, B. Peleato, and J. Eckstein,
    ``Distributed Optimization and Statistical Learning via the Alternating Direction Method of Multipliers,''
    Foundations and Trends in Machine Learning \textbf{3}, 1-122 (2011).

\bibitem{Gond08} A. Gondarenko, M. Lipson, ``Low modal volume dipole-like dielectric slab resonator,'' Opt. Express \textbf{16}, 17689-17694 (2008).

\bibitem{Grant09} M. Grant and S. Boyd, \emph{CVX: Matlab software for disciplined convex programming}, \texttt{http://stanford.edu/$\sim$boyd/cvx}, June 2009.

\bibitem{Inan00} U. Inan, A. Inan, \emph{Electromagnetic Waves} (Prentice Hall, 2000), page 296.

\bibitem{Jiao05} Y. Jiao, S. Fan, and D. A. B. Miller, 
    ``Demonstrations of systematic photonic crystal design and optimization by low rank adjustment: an extremely compact mode separator'', Opt. Lett. \textbf{30}, 140-142 (2005).

\bibitem{Laere07}F. Van Laere, G. Roelkens, M. Ayre, J. Schrauwen, D. Taillaert, D. Van Thourhout, T. F. Krauss, and R. Baets,
    ``Compact and highly efficient grating couplers between optical fiber and nanophotonic waveguides,''
    J. of Lightwave Tech. \textbf{25}, 151-156 (2007).

\bibitem{Lu10} J. Lu and J. Vuckovic, ``Inverse design of nanophotonic structures using complementary convex optimization,'' Opt. Express \textbf{18}, 3793-3804 (2010).

\bibitem{Lu11} J. Lu, S. Boyd, and J. Vuckovic, 
    ``Inverse design of a three-dimensional nanophotonic resonator,''
    Opt. Express \textbf{19}, 10563-10750 (2011).

\bibitem{Lu12} J. Lu, J. Vuckovic, ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes,'' 
    Opt. Express \textbf{20}, 7221-7236 (2012)

\bibitem{Lu13} J. Lu, J. Vuckovic, ``Nanophotonic computational design,'' \emph{under review}.

\bibitem{Miller12} D. A. B. Miller, "All linear optical devices are mode converters," Opt. Express \textbf{20}, 23985-23993 (2012)

\bibitem{Osher02} S. Osher and R. Fedkiw, \emph{Level Set Methods and Dynamic Implicit Surfaces: 1st Edition} (Springer, 2002).

\bibitem{Pendry00} J. B. Pendry, ``Negative refraction makes a perfect lens,''
    Physical Review Letters, \textbf{85}, 3966-3969 (2000).

\bibitem{Shin12} W. Shin and S. Fan, ``Choice of the perfectly matched layer boundary condition for frequency-domain Maxwell’s equations solvers,''
    J. of Comp. Phys \textbf{231}, 3406-3431 (2012).

\bibitem{Veronis07} G. Veronis, and S. Fan, 
    ``Theoretical investigations of compact couplers between dielectric slab 
    waveguides and two-dimensional metal-dielectric-metal plasmonic waveguides,'' 
    Opt. Express \textbf{15}, 1211-1221 (2007).

\bibitem{Yang10} R. Yang, R. A. Wahsheh, Z. Lu, and M. A. G. Abushagur, 
    ``Efficient light coupling between dielectric slot waveguide and plasmonic
    slot waveguide,'' Opt. Lett. \textbf{35}, 649-651 (2010).

\bibitem{Yee66} K. Yee, ``Numerical solution of initial boundary value problems involving Maxwell’s equations in isotropic media,'' IEEE Trans. Antennas Propag. Mag. \textbf{14}, 302-307 (1966).

% 
% \bibitem{SD05} A. Hakansson, J. Sanchez-Dehesa, ``Inverse designed photonic crystal de-multiplex waveguide coupler,'' Opt. Express \textbf{13}, 5440-5449 (2005).
% 
% \bibitem{AB74} M.~Albani and P.~Bernardi, ``A Numerical Method Based on the Discretization of Maxwell Equations in Integral Form,'' IEEE Trans.~Microwave Theory Tech. \textbf{22}, 446-450 (1974).
% 
% \bibitem{GA79} J.~M.~Gerardy and M.~Ausloos, ``Absorption spectrum of clusters of spheres from the general solution of Maxwell's equations. The long-wavelength limit,'' Phys.~Rev.~B \textbf{22}, 4950-4959 (1979).
% 
% \bibitem{Lon09} P. Deotare, M. McCutcheon, I. Frank, M. Khan, M. Loncar, ``High quality factor photonic crystal nanobeam cavities,'' Appl. Phys. Lett. \textbf{94}, 121106 (2009).
% 
% \bibitem{Sch02} J. Vuckovic, M. Loncar, H. Mabuchi, A. Scherer, ``Design of photonic crystal microcavities for cavity QED,'' Phys. Rev. E \textbf{65}, 1-11 (2002).
% 
% \bibitem{Nod05} Y.~Akahane, T.~Asano, B.~Song, S.~Noda, ``Fine-tuned high-Q photonic-crystal nanocavity,'' Opt. Express \textbf{13}, 1202-1214 (2005).
% 
% 
% \bibitem{Sig04} P. Borel, A. Harpøth, L. Frandsen, M. Kristensen, P. Shi, J. Jensen, and O. Sigmund, ``Topology optimization and fabrication of photonic crystal structures,'' Opt. Express \textbf{12}, 1996-2001 (2004).
% 
% \bibitem{Vuc05} D. Englund, I. Fushman, and J. Vuckovic. ``General Recipe for Designing Photonic Crystal Cavities,'' Opt. Express \textbf{12}, 5961–5975 (2005).
% 
% \bibitem{cholmod} \emph{CHOLMOD} software package, accessed via \emph{Matlab}.
% 
% \bibitem{mycomp} Intel Core 2 Quad $2.5$GHz, 8Gb RAM.
% 
% \bibitem{JJ99} S.~G.~Johnson, J.~D.~Joannopoulos, ``Block-iterative frequency-domain methods for Maxwell’s equations in a planewave basis,'' Opt.~Express \textbf{8}, 967-970 (1999).
% 
% \bibitem{Hen06} K. Hennessy, C.~Högerle, E.~Hu, A. Badolato, A. Imamoğlu, ``Tuning photonic nanocavities by atomic force microscope nano-oxidation,'' Appl.~Phys.~Lett.~\textbf{89}, 041118 (2006).
% 
% \bibitem{Aka05} B.~-S.~Song, S.~Noda, T.~Asano, Y.~Akahane, ``Ultra-high-Q photonic double-heterostructure nanocavity,'' Nat. Mater. \textbf{4}, 207-210 (2005).
% 
% \bibitem{Riv09} K.~Rivoire, Z.~Lin, F.~Hatami, W.~Ted Masselink, and J.~Vuckovic, ``Second harmonic generation in gallium phosphide photonic crystal nanocavities with ultralow continuous wave pump power,'' Optics Express \textbf{17}, 22609-22615 (2009).
% 
% \bibitem{miller} D. A. B. Miller, ``Rationale and challenges for optical interconnects to electronic chips,'' Proc. of the IEEE \textbf{88}, 728-749 (2000).
% 
% \bibitem{yee} K. Yee, ``Numerical solution of initial boundary value problems involving maxwell's equations in isotropic media,'' IEEE Trans. Antennas Propag. Mag. \textbf{14}, 302-307 (1966).
% 
% \bibitem{boydbook} S. Boyd and L. Vandenberghe, \emph{Convex Optimization} (Cambridge University Press, 2004).
% 
% \bibitem{altdir} S. Boyd, N. Parikh, E. Chu, B. Peleato, and J. Eckstein are preparing a manuscript to be called, ``Distributed Optimization and Statistical Learning via the Alternating Direction Method of Multipliers,'' \url{www.stanford.edu/~boyd/papers/distr_opt_stat_learning_admm.html}. 
% 
% \bibitem{cholmod} Y. Chen, T. A. Davis, W. W. Hager, and S. Rajamanickam, ``Algorithm 887: CHOLMOD, supernodal sparse Cholesky factorization and update/downdate,'' ACM Trans. Math. Software \textbf{35}, No. 3, 2009.
% 
% \bibitem{cvx} M. Grant and S. Boyd, \emph{CVX: Matlab software for disciplined convex programming}, version 1.21. \url{cvxr.com/cvx}, January 2011.
% 
% \bibitem{fibergrating} Y. Tang, Z. Wang, L. Wosinski, U. Westergren, and S. He,
%     ``Highly efficient nonuniform grating coupler for silicon-on-insulator 
%     nanophotonic circuits,''
%     Opt. Lett. \textbf{35}, 1290-1292 (2010).
% 
% \bibitem{ridge}  K. K. Lee, D. R. Lim, L.C. Kimerling, J. Shin, and F. Cerrina, 
%     ``Fabrication of ultralow-loss Si/SiO2 waveguides by roughness reduction,''
%     Opt. Lett. \textbf{26}, 1888-1890 (2001).
% 
% \bibitem{pcslow} Y. A. Vlasov, M. O'Boyle, H. F. Hamann, and S. J. McNab,
%     ``Active control of slow light on a chip with photonic crystal waveguides,''
%     Nature \textbf{438}, 65-69 (2005).
% 
% \bibitem{slotfocus} M. Lipson, 
%     ``Guiding, modulating, and emitting light on 
%     silicon-challenges and opportunities,'' 
%     J. Lightwave Technol. \textbf{23}, 4222-4238 (2005).
% 
% \bibitem{active} J. Van Campenhout, P. Rojo Romeo, P. Regreny, C. Seassal, 
%     D. Van Thourhout, S. Verstuyft, L. Di Cioccio, J.-M. Fedeli, 
%     C. Lagahe, and R. Baets, 
%     ``Electrically pumped InP-based microdisk lasers integrated with a 
%     nanophotonic silicon-on-insulator waveguide circuit,'' 
%     Opt. Express \textbf{15}, 6744-6749 (2007).
% 
% \bibitem{metallic} L. Tang, S. E. Kocabas, S. Latif, A. K. Okyay, 
%     D. S. Ly-Gagnon, K. C. Saraswat, and D. A. B. Miller, 
%     ``Nanometre-scale germanium photodetector enhanced by a 
%     near-infrared dipole antenna,'' 
%     Nature Photonics \textbf{2}, 226-229 (2).
% 
% % \bibitem{fwadia} V. R. Almeida, R. R. Panepucci, and M. Lipson, 
% %     ``Nanotaper for compact mode conversion,'' 
% %     Opt. Lett. \textbf{28}, 1302-1304 (2003) 
% % \bibitem{wwadia} S. G. Johnson, P. Bienstman,  M. A. Skorobogatiy, 
% %     M. Ibanescu1, E. Lidorikis, and J. D. Joannopoulos,
% %     ``Adiabatic theorem and continuous coupled-mode theory for 
% %     efficient taper transitions in photonic crystals,''
% %     Phys. Rev. E \textbf{66}, 066608 (2002)
% % \bibitem{deriv} F. Wang, J. S. Jensen, O. Sigmund, 
% %     ``Robust topology optimization of photonic crystal waveguides with 
% %     tailored dispersion properties.'' 
% %     J. Opt. Soc. Am. B \textbf{28}, 387-397 (2011)
% % \bibitem{boydbook} S. Boyd, and L. Vandenberghe, 
% %     \emph{Convex Optimization} 
% %     (Cambridge University Press, 2004)
% 
%
% %
% 
% 
% \bibitem{baets}F. Van Laere, G. Roelkens, M. Ayre, J. Schrauwen, D. Taillaert, D. Van Thourhout, T. F. Krauss, and R. Baets,
%     ``Compact and highly efficient grating couplers between optical fiber and nanophotonic waveguides,''
% 
\end{thebibliography}

### 2013-04-16 thesis/chapter1.tex
Added bibliography and fixed citations.

@@
 \section{Results}
-We now solve \eq{p1:problem} to design nanophotonic resonators in 1D.
+We now solve \eq{p1:problem} to design nanophotonic resonators in 1D\cite{Lu10}.
 We use the magnetic field formulation of the electromagnetic equation
@@
     The entire design process is extremely fast and takes less than 
-        $1$ second to complete on a generic desktop computer~\cite{mycomp}. 
+        $1$ second to complete on a generic desktop computer.
     Unfortunately, the periodic singularities in the dielectric structure 
@@
     solved \eq{reg:problem} for $\eta=10^{-8}$, $10^{-6}$, and $10^{-4}$;
-    the results of which are shown in fig.~\ref{regls pic}.
+    the results of which are shown in fig.~\ref{regls pic}\cite{Lu10}.
 

### 2013-04-16 thesis/chapter2.tex
Added bibliography and fixed citations.

@@
 \subsection{1D}
-Fig.~\ref{comp pic} shows that the iterative algorithm, after $400$ iterations and with the correct choice of regularization parameters $\eta_0$ and $\eta_1$, results in a well-behaved structure that is able to closely reproduce the modified target field.
+Fig.~\ref{comp pic} shows that the iterative algorithm, after $400$ iterations and with the correct choice of regularization parameters $\eta_0$ and $\eta_1$, results in a well-behaved structure that is able to closely reproduce the modified target field\cite{Lu10}.
 
@@
 \subsection{2D}
-The iterative design method can also be extended to two dimensions.
+The iterative design method can also be extended to two dimensions\cite{Lu10}.
 We demonstrate this using an S-shaped target field 
@@
 In this algorithm, \eq{bounded problem} is no longer linear in $z$
-    but is still convex\cite{BV04}.
-For this reason, the \emph{CVX} package\cite{CVX}, 
+    but is still convex\cite{Boyd04}.
+For this reason, the \emph{CVX} package\cite{Grant09}, 
     a Matlab-based modeling system for convex optimization, 
@@
 Once again, we attempt the design of a one-dimensional resonator
-    and find thata nearly binary-valued dielectric structure is obtained,
-    as seen in fig.~\ref{bounded comp pic}.
+    and find that a nearly binary-valued dielectric structure is obtained,
+    as seen in fig.~\ref{bounded comp pic}\cite{Lu10}.
 Note that the the directly discreteness of $z$ was not enforced (since that would make the problem non-convex); 
@@
 
-We now use the complementary optimization method to design resonators with discrete, binary $\epsilon$ in two dimensions.
+We now use the complementary optimization method to design resonators with discrete, binary $\epsilon$ in two dimensions\cite{Lu10}.
 
@@
 Interestingly, the central bowtie-like structure has emerged 
-    from previous genetic optimization methods as well\cite{Lip08}.
+    from previous genetic optimization methods as well\cite{Gond08}.
 
@@
 
-Therefore, to make our problem more tractable, we formulate a 2.5-dimensional approximation of the electromagnetic fields of a planar three-dimensional nanophotonic device.
+Therefore, to make our problem more tractable, we formulate a 2.5-dimensional approximation of the electromagnetic fields of a planar three-dimensional nanophotonic device\cite{Lu11}.
 As shown in Fig.~\ref{approx}a, this involves treating a planar three-dimensional nanophotonic device as a truncated holey fiber with identical dielectric structure.
@@
 Solving for Eq.~\ref{wave} now requires solving for a much smaller ($\sim 10^5 \times 10^5$) matrix, which can be accomplished using standard linear algebra packages.
-This simulation technique is thus very similar to a two-dimensional finite-difference frequency-domain solve.
+This simulation technique is thus very similar to a two-dimensional finite-difference frequency-domain solver.
 
@@
 To estimate $t$ for the full three-dimensional device, we treat the resonant mode as a guided mode in a slab waveguide surrounded by a cladding of $n=1$.
-The expression for $t$ is then the thickness of the slab for the lowest-order TE mode of a slab waveguide with effective refractive index $n_\text{eff}$\cite{inan}:
+The expression for $t$ is then the thickness of the slab for the lowest-order TE mode of a slab waveguide with effective refractive index $n_\text{eff}$\cite{Inan00}:
 \begin{align}
@@
 % \section{Result}
-Using \eq{iterative problem}, along with our 2.5-dimensional approximation, the iterative design of a planar three-dimensional nanophotonic device is performed.
+Using \eq{iterative problem}, along with our 2.5-dimensional approximation, the iterative design of a planar three-dimensional nanophotonic device is performed\cite{Lu11}.
 

### 2013-04-16 thesis/chapter3.tex
Added bibliography and fixed citations.

@@
 Such a design objective is both extremely simple and widely adaptable 
-    to the design of linear nanophotonic devices in general.
+    to the design of linear nanophotonic devices in general\cite{Miller12}.
 On the other hand, such a formulation often prohibits the physics residual 
@@
 Specifically, we present five results which suggest our method
-    is indeed able to design arbitrary single-mode, linear nanophotonic devices.
+    is indeed able to design arbitrary single-mode, linear nanophotonic devices\cite{Lu12}.
 These results comprise of couplers between 
@@
     ($\sim 98\%$ coupling efficiency, in contrast to previous designs
-    which achieve only $\sim 70\%$ coupling efficiency\cite{veronis,yang})
+    which achieve only $\sim 70\%$ coupling efficiency\cite{Veronis07,Yang10})
     and extremely compact 

### 2013-04-16 thesis/chapter4.tex
Added bibliography and fixed citations.

@@
 We now develop a method which may indeed be capable of designing 
-    linear nanophotonic device which
+    linear nanophotonic devices which
     are fully three-dimensional and multi-modal,
@@
         which can be deduced since $A_i(z)x_i-b_i=0$ is not a hard constraint.
-    Instead, this formulation is what also an \emph{objective-first} \cite{ob1_wg}
+    Instead, this formulation is what also an \emph{objective-first} \cite{Lu12}
         formulation in that the \emph{design objective} (explained below)
@@
 We employed the alternating directions method of multipliers (ADMM) algorithm 
-    \cite{admm}
+    \cite{Boyd11}
     in order to solve \eq{problem}.
@@
     finite-difference frequency-domain (FDFD) solver which 
-    implements a hardware-accelerated iterative solver\cite{wonseok}
+    implements a hardware-accelerated iterative solver\cite{Shin12}
     on Amazon's Elastic Compute Cloud.
@@
 Lastly, in order to arrive at fully discrete, manufacturable structures,
-    we convert $z$ to a boundary parameterization\cite{levelset}
+    we convert $z$ to a boundary parameterization\cite{Osher02}
     and tune our structure using a steepest-descent method.
@@
 We demonstrate the effectiveness of our design method 
-    by producing designs for a variety of nanophotonic devices.
+    by producing designs for a variety of nanophotonic devices\cite{Lu13}.
 
@@
     nanophotonic spatial mode splitter 
-    (previous designs were restricted to two dimensions \cite{2dsplitter}).
+    (previous designs were restricted to two dimensions \cite{Jiao05}).
 Such a device is the key enabler for multi-mode on-chip optical circuits,
@@
     which couple light from an optical fiber at normal incidence
-    into an in-plane waveguide\cite{baets}.
+    into an in-plane waveguide\cite{Laere07}.
 

### 2013-04-16 thesis/appendix2.tex
Draft done.

@@
 \chapter[Design of optical cloaks and mimics]{Objective-first design of optical cloaks and mimics}\label{ob-1 meta}
-------------------------------------------------------%
+% ------------------------------------------------------%
 \section{Optical Cloak Design}
 %---------------------------------------------------------%    
-We now extend the applicability of our method
+We now further extend the applicability of the objective-first method
+    (chapter~\ref{ob-1})
     to the design of metamaterial devices which operate in free-space.

### 2013-04-16 thesis/chapter1.tex
Draft done.

@@
     is \emph{bi-linear} in both $E$ and $\epsilon$.
+Practically, this meant that solving for $\epsilon$ should be rather straightforward,
+    since we already now how to solve linear systems in general.
 
-We now make the following substitution in order to represent \eq{p1:wave}
-    in linear algebra notation:
+The language of linear algebra will make itself very useful
+    in eventually formulating our problem correctly and generally.
+To this end, we now make the following substitution in order to represent \eq{p1:wave}
+    in such linear algebra notation:
     \BI $E \to x$, 
@@
 The electromagnetic wave equation (\eq{p1:wave}) can now be expressed simply as
-    \BE A(z)x = b, \label{p1:axb} \EE
-    which is not only linear in $x$, but also in $z$, 
+    \BE A(z)x = b. \label{p1:axb} \EE
+We note once again that \eq{p1:wave} is not only linear in $x$, but also in $z$, 
     since $A(z)$ is linear with respect to $z$.
@@
 
-In the language of physics, this amounts to computing
+In the language of physics, this amounts to a very simple computation;
+    namely,
     \BE \epsilon = (\nabla\times\mu_0^{-1}\nabla\times E + 
         i \omega J)/ \omega^2 E \EE
-    given $E$.
+    given $E$!
 
-In the language of linear algebra, we have formulated the following problem:
+In the language of linear algebra, the problem is formulation as follows:
     \BE \minimize_z \|A(z)x - b\|^2. \label{p1:problem}\EE
@@
 \section{Problem formulation}
-The simplest way to produce a well-behaved dielectric structure is 
+We were previously quite excited to learn that solving for 
+    a dielectric structure ($\epsilon$ or $z$) given 
+    its electromagnetic field ($E$ or $x$) is actually quite simple,
+    but generally results in unrealizable structures.
+Along these lines, we also knew that the simplest way 
+    to produce a well-behaved dielectric structure is 
     to add a regularization term to our direct formulation (\eq{p1:axb}),
@@
 \section{Implementation}
-\Eq{reg:problem} can still be computed in one step
+Fortunately, \eq{reg:problem} can still be computed in one step
     since the regularization term does not add any computational complexity.
@@
 
-Critically, fig.~\ref{regls pic} shows that there seems
-    to be an inherent trade-off between 
+Although our results seemed promising in producing well-behaved
+    dielectric structures;
+    critically, fig.~\ref{regls pic} shows that there seems
+    to be an unavoidable trade-off between 
     constraining the structure ($z$) 

### 2013-04-16 thesis/chapter2.tex
Draft done.

@@
 % \section{Motivation for a Complementary Optimization Strategy}
-The fundamental problem in the examples 
+Having started off with the exciting realization that one could easily 
+    solve for $z$ ($\epsilon$), we quickly ran into 
+    the problem revealed in fig.~\ref{regls pic}.
+It now seemed that a structure that was both well-behaved and high-performance
+    might not be possible!
+
+Further thought led us to conclude that
+    the fundamental problem in the examples 
     in chapters \ref{direct} and \ref{regularized}
@@
     but in the improper selection of a target field. 
-In fact, it is very difficult to select a suitable target field 
+In fact, we realizaed thtat it is very difficult to select a suitable target field 
     because not every field even has a manufacturable dielectric structure 
@@
 \section{Problem formulation}
-We start with the same target field as in the previous examples 
+The problem formulation for our iterative design strategy
+    starts with the same target field as in the previous examples,
     but we now allow for it to be modified during the design process. 
@@
 \section{Implementation}
-The most notable implementation difference is that,
+In terms of implementation,
+    the most notable implementation difference is that,
     in contrast to direct design,
@@
 
-Note that, in order to design two-dimensional structures,
+Since this strategy started to produce more successful results,
+    we shifted from one-dimensional structures to two-dimensional structures.
+In terms of implementation, we note that 
+    in order to design higher-dimensional structures,
     \eq{iterative problem} is only modified in the
@@
 \subsection{1D}
-Fig.~\ref{comp pic} shows that the iterative algorithm, after $400$ iterations and with the correct choice of regularization parameters $\eta_0$ and $\eta_1$, results in a well-behaved structure that is able to closely reproduce the modified target field\cite{Lu10}.
+Fig.~\ref{comp pic} shows that the iterative algorithm, after $400$ iterations and with the correct choice of regularization parameters $\eta_0$ and $\eta_1$, 
+    indeed results in a well-behaved structure that is able to closely reproduce the modified target field\cite{Lu10}!
 
@@
 \section{Problem formulation}
-In order to achieve a more practical, discretely-valued dielectric structure, we can impose strict upper- and lower-bounds on the structure ($z$). 
-To this end, we can modify \eq{iterative problem} as such,
+Having achieved a measure of success with the iterative design strategy
+    outlined in the previous chapter,
+    we strove 
+    to achieve a more practical, discretely-valued dielectric structure. 
+To do this, we imposed strict upper- and lower-bounds on the structure variable $z$. 
+To this end, we modified \eq{iterative problem} as such,
     \begin{subequations}
@@
 
-This modification takes us one step closer to producing manufacturable structures,
-    which must be discretely valued.
+\section{Implementation} 
+In this formulation, \eq{bounded problem} is no longer linear in $z$
+    but is still convex\cite{Boyd04}.
 
-\section{Implementation} 
-In this algorithm, \eq{bounded problem} is no longer linear in $z$
-    but is still convex\cite{Boyd04}.
-For this reason, the \emph{CVX} package\cite{Grant09}, 
+Practically, this means that although it is no longer absolutely trivial
+    to solve \eq{bounded problem} for $z$, it can still be done reliably.
+By reliably, we mean that since \eq{bounded problem} is still convex in $z$,
+    there exists a single local optimum (which is also the global optimum)
+    and that there also exists software which can efficiently
+    discover this globally optimum point.
+
+Specifically, the \emph{CVX} package\cite{Grant09}, 
     a Matlab-based modeling system for convex optimization, 
-    is now used to solve \eq{bounded problem} for $z$.
+    is the software we used to solve \eq{bounded problem} for $z$.
 

### 2013-04-16 thesis/intro.tex
Draft done.

--- 2013-03-28 thesis/intro.tex
@@
 \chapter{Introduction}
-And now for an introduction...
+The twenty-first century has rightly been called the ``information age'',
+    as advances in computation have resulted in an explosion
+    in the amount of information created and communicated on a daily basis.
+
+The underlying communication fabric and key technological enabler
+    of our information age has been the high-bandwidth, long-distance
+    communication capability afforded by the optical network.
+
+First used to communicate between cities and across continents,
+    optical networks are now needed to simply communicate across rooms (datacenters)
+    because of the ballooning information creation and communication
+    abilities of single computers.
+As our appetite for information continues to grow,
+    the optical network will be used for even shorter distances
+    such as chip-to-chip and even core-to-core communication.
+The focus of this work is the design of nanophotonic components
+    to enable such future on-chip optical networks.
+
+Currently, on-chip networks consist of devices
+    which are designed by tuning
+    a handful of design parameters (\fig{integrated_circuit}).
+Much progress has been made on this front;
+    however, we note that the available design space is largely untouched (\fig{des_complexity}).
+
+\myfig{integrated_circuit}
+    {Examples of hand-tuned nanophotonic devices.
+    Device performance is tuned by varying the sizes of and spacing between
+    a handful of elements (waveguides, resonators, gratings, \ldots).}
+
+To be precise, the motivation for this works stems from the twin realizations that
+    \begin{enumerate}
+    \item the fabrication of on-chip optical networks in semiconductor 
+    foundries enables virtually unlimited design complexity at no additional 
+    fabrication cost, and
+    \item component performance can only benefit by the addition and
+    consideration of these additional degrees of freedom.
+    \end{enumerate}
+The goal of this work, then, is to be able to take advantage
+    of the full available parameter space to design nanophotonic devices.
+
+\myfig{des_complexity}
+    {The parameter space for nanophotonic design is enormous and largely untapped.
+    Here, we show that, 
+        limited to including or excluding 100 nm square areas,
+        a 1500 nm $\times$ 1500 nm area already contains $2^{225}$ 
+        (an uncountable number) possible designs.}
+
+Along this line of reasoning
+    we expect to be able to produce devices which
+    \BI have very compact footprints,
+    \I  exhibit high efficiency performance,
+    \I  are multi-modal in their operation,
+    \I  are robust to shifts in wavelength and temperature,
+    \I  are robust to fabrication error,
+    \I  may even demonstrate novel, never-before-seen functionality. \EI
+Our final result (chapter~\ref{final}) indeed demonstrates
+    manufacturable, three-dimensional nanophotonic devices which
+    exhibit these properties.
+
+Of course, in this regime, the hand-tuning of parameters 
+    is no longer a tractable strategy.
+Instead, we use a \emph{design-by-specification} strategy
+    which simply means that our software produces nanophotonic designs
+    based solely based on the desired performance specification given to it,
+    and requires no intermediate hand tuning.
+
+We note, lastly, that the design-by-specification strategy
+    is unusually powerful in the sense that \emph{all} useful nanophotonic devices
+    can be designed in this way.
+Indeed, the apparent ease with which we are able to produce designs seems
+    to lend one to this conclusion.
+
+The organization of this thesis is straightforward: 
+    chapters \ref{direct}-\ref{ob-1} detail the incremental steps in achieving
+    our final result, which is presented in chapter \ref{final}.
+Futhermore, each section is broken into three major sections:
+    \begin{description}
+    \item[Problem formulation] where we show how we cast the design problem
+        in incrementally more sophisticated mathematics.
+    \item[Implementation] where we note how the formulated problem 
+        was solved computationally.
+    \item[Results] where we demonstrate the abilities (and weaknesses)
+        of each formulation.
+    \end{description}
+
+Additionally, appendices~\ref{ob-1 additional} and \ref{ob-1 meta} 
+    contain numerous examples of devices designed using our
+    so-called ``objective-first'' design formulation.
+Appendix~\ref{maths} contains the nitty-gritty mathematics
+    that was used to implement our final design tool, 
+    as outlined in chapter~\ref{final}.
+This appendix will be most useful to any wishing to reproduce our work.

### 2013-05-07 paper/paper.tex
Got the export to work.
evising paper.

@@
 \usepackage{amsmath,amssymb}
-\input defs.tex
+
+\newcommand{\myfig}[2]{
+    \begin{figure}[!h]
+    \begin{centering}
+    \includegraphics[width=0.8\textwidth]{fig/#1}
+    \caption{#2}\label{#1}
+    \end{centering}
+    \end{figure}
+}
+
+\newcommand{\Eq}[1]{Eq.~\eqref{#1}}
+\newcommand{\Fig}[1]{Fig.~\ref{#1}}
+\newcommand{\eq}[1]{eq.~\eqref{#1}}
+\newcommand{\fig}[1]{fig.~\ref{#1}}
+\newcommand{\BI}{\begin{itemize}\item}
+\newcommand{\I}{\item}
+\newcommand{\EI}{\end{itemize}}
+\newcommand{\BEAS}{\begin{eqnarray}}
+\newcommand{\EEAS}{\end{eqnarray}}
+% \newcommand{\BEAS}{\begin{IEEEeqnarray}{rl}}
+% \newcommand{\EEAS}{\end{IEEEeqnarray}}
+\newcommand{\BSA}{\begin{subequations}\begin{align}}
+\newcommand{\ESA}{\end{align}\end{subequations}}
+\newcommand{\BE}{\begin{equation*}}
+\newcommand{\EE}{\end{equation*}}
+\newcommand{\BIT}{\begin{itemize}}
+\newcommand{\EIT}{\end{itemize}}
+
+\newcommand{\eg}{{\it e.g.}}
+\newcommand{\ie}{{\it i.e.} }
+
+\DeclareMathOperator*{\minimize}{\text{minimize}\quad}
+\newcommand{\subto}{\text{subject to}\quad}
+\newcommand{\T}{^\dagger}
+
+\newcommand{\ones}{\mathbf 1}
+\newcommand{\reals}{{\mbox{\bf R}}}
+\newcommand{\comps}{{\mbox{\bf C}}}
+\newcommand{\integers}{{\mbox{\bf Z}}}
+\newcommand{\symm}{{\mbox{\bf S}}}  % symmetric matrices
+
+\newcommand{\nullspace}{{\mathcal N}}
+\newcommand{\range}{{\mathcal R}}
+\newcommand{\Rank}{\mathop{\bf Rank}}
+\newcommand{\Tr}{\mathop{\bf Tr}}
+\newcommand{\diag}{\mathop{\bf diag}}
+\newcommand{\lambdamax}{{\lambda_{\rm max}}}
+\newcommand{\lambdamin}{\lambda_{\rm min}}
+
+\newcommand{\Expect}{\mathop{\bf E{}}}
+\newcommand{\Prob}{\mathop{\bf Prob}}
+\newcommand{\Co}{{\mathop {\bf Co}}} % convex hull
+\newcommand{\dist}{\mathop{\bf dist{}}}
+\newcommand{\argmin}{\mathop{\rm argmin}}
+\newcommand{\argmax}{\mathop{\rm argmax}}
+\newcommand{\epi}{\mathop{\bf epi}} % epigraph
+\newcommand{\Vol}{\mathop{\bf vol}}
+\newcommand{\dom}{\mathop{\bf dom}} % domain
+\newcommand{\intr}{\mathop{\bf int}}
+
 \begin{document}
+
 \title{Nanophotonic Computational Design}
@@
 \begin{thebibliography}{99}
+\bibitem{lipson} 
+    A. Gondarenko, and M. Lipson, 
+    ``Low modal volume dipole-like dielectric slab resonator,'' 
+    Opt. Express \textbf{16} 17689-17694 (2008).  
+\bibitem{yablo} C.-Y. Kao, S. Osher, and E. Yablonovitch, 
+    ``Maximizing band gaps in two-dimensional photonic crystals by using level set methods,'' Appl. Phys. B \textbf{81}, 235-244 (2005).
+\bibitem{levi}
+    P. Seliger, M. Mahvash, C. Wang, and A. Levi,
+    ''Optimization of aperiodic dielectric structures,''
+    J. Appl. Phys. \textbf{100}, 34310-6 (2006).
+\bibitem{johnson} A. Oskooi, A. Mutapcic, S. Noda, J. D. Joannopoulos, S. P. Boyd, and S. G. Johnson, 
+    ``Robust optimization of adiabatic tapers for coupling to slow-light photonic-crystal waveguides,'' Opt. Express \textbf{20}, 21558-21575 (2012).
+\bibitem{sigmund1} Y. Elesin, B. S. Lazarov, J. S. Jensen, O. Sigmund, 
+    ``Design of robust and efficient photonic switches using topology optimization,''
+    Photonics and Nanostructures - Fundamentals and Applications \textbf{10}, 
+    153–165 (2012).
+\bibitem{jameson} L. Martinelli, and A. Jameson, 
+    ``Computational Aerodynamics: Solvers and Shape Optimization,''
+    J. Heat Transfer \textbf{135}, 011002 (2013).
+\bibitem{bendsoe} M. P. Bendsoe, O. Sigmund,
+    ``Material interpolation schemes in topology optimization,''
+    Archive of Applied Mechanics \textbf{69}, 635-654 (1999).
+\bibitem{miller} D. A. B. Miller, 
+    ``All linear optical devices are mode converters,'' 
+    Opt. Express \textbf{20}, 23985-23993 (2012).
 \bibitem{ob1_wg} J. Lu, J. Vuckovic, ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes,'' 
@@
     ``Demonstrations of systematic photonic crystal design and optimization by low rank adjustment: an extremely compact mode separator'', Opt. Lett. \textbf{30}, 140-142 (2005).
+\bibitem{mode1} J.
+Castro, D.
+F.
+Geraghty, S.
+Honkanen, C.
+M.
+Greiner, D.
+Iazikov, and T.
+W.
+Mossberg, ``Demonstration of mode conversion using anti-symmetric waveguide Bragg gratings,'' Opt.
+Express \textbf{13}, 4180-4184 (2005).
+\bibitem{mode2} E. Khoo, A. Liu, and J. Wu, ``Nonuniform photonic crystal taper for high-efficiency mode coupling,'' Opt. Express \textbf{13}, 7748-7759 (2005).
+\bibitem{mode3} P.
+Sanchis, J.
+Marti, J.
+Blasco, A.
+Martinez, and A.
+Garcia, ``Mode matching technique for highly efficient coupling between dielectric waveguides and planar photonic crystal circuits,'' Opt.
+Express \textbf{10}, 1391-1397 (2002).
+\bibitem{forchel} T. D. Happ, M. Kamp, and A. Forchel, 
+    ``Photonic crystal tapers for ultracompact mode conversion,'' 
+    Opt. Lett. \textbf{26}, 1102-1104 (2001) 
 \bibitem{baets}F. Van Laere, G. Roelkens, M. Ayre, J. Schrauwen, D. Taillaert, D. Van Thourhout, T. F. Krauss, and R. Baets,
@@
     J. of Lightwave Tech. \textbf{25}, 151-156 (2007).
-% \bibitem{fibergrating} Y. Tang, Z. Wang, L. Wosinski, U. Westergren, and S. He,
-%     ``Highly efficient nonuniform grating coupler for silicon-on-insulator 
-%     nanophotonic circuits,''
-%     Opt. Lett. \textbf{35}, 1290-1292 (2010).
-% \bibitem{ridge}  K. K. Lee, D. R. Lim, L.C. Kimerling, J. Shin, and F. Cerrina, 
-%     ``Fabrication of ultralow-loss Si/SiO2 waveguides by roughness reduction,''
-%     Opt. Lett. \textbf{26}, 1888-1890 (2001).
-% \bibitem{pcslow} Y. A. Vlasov, M. O'Boyle, H. F. Hamann, and S. J. McNab,
-%     ``Active control of slow light on a chip with photonic crystal waveguides,''
-%     Nature \textbf{438}, 65-69 (2005).
-% \bibitem{slotfocus} M. Lipson, 
-%     ``Guiding, modulating, and emitting light on 
-%     silicon-challenges and opportunities,'' 
-%     J. Lightwave Technol. \textbf{23}, 4222-4238 (2005).
-% \bibitem{active} J. Van Campenhout, P. Rojo Romeo, P. Regreny, C. Seassal, 
-%     D. Van Thourhout, S. Verstuyft, L. Di Cioccio, J.-M. Fedeli, 
-%     C. Lagahe, and R. Baets, 
-%     ``Electrically pumped InP-based microdisk lasers integrated with a 
-%     nanophotonic silicon-on-insulator waveguide circuit,'' 
-%     Opt. Express \textbf{15}, 6744-6749 (2007).
-% \bibitem{metallic} L. Tang, S. E. Kocabas, S. Latif, A. K. Okyay, 
-%     D. S. Ly-Gagnon, K. C. Saraswat, and D. A. B. Miller, 
-%     ``Nanometre-scale germanium photodetector enhanced by a 
-%     near-infrared dipole antenna,'' 
-%     Nature Photonics \textbf{2}, 226-229 (2008).
-% % \bibitem{fwadia} V. R. Almeida, R. R. Panepucci, and M. Lipson, 
-% %     ``Nanotaper for compact mode conversion,'' 
-% %     Opt. Lett. \textbf{28}, 1302-1304 (2003) 
-% % \bibitem{wwadia} S. G. Johnson, P. Bienstman,  M. A. Skorobogatiy, 
-% %     M. Ibanescu1, E. Lidorikis, and J. D. Joannopoulos,
-% %     ``Adiabatic theorem and continuous coupled-mode theory for 
-% %     efficient taper transitions in photonic crystals,''
-% %     Phys. Rev. E \textbf{66}, 066608 (2002)
-% % \bibitem{deriv} F. Wang, J. S. Jensen, O. Sigmund, 
-% %     ``Robust topology optimization of photonic crystal waveguides with 
-% %     tailored dispersion properties.'' 
-% %     J. Opt. Soc. Am. B \textbf{28}, 387-397 (2011)
-% % \bibitem{boydbook} S. Boyd, and L. Vandenberghe, 
-% %     \emph{Convex Optimization} 
-% %     (Cambridge University Press, 2004)
-% \bibitem{prevwork} J. Lu, S. Boyd, and J. Vuckovic, 
-%     ``Inverse design of a three-dimensional nanophotonic resonator,''
-%     Opt. Express \textbf{19}, 10563-10750 (2011). 
-% \bibitem{veronis} G. Veronis, and S. Fan, 
-%     ``Theoretical investigations of compact couplers between dielectric slab 
-%     waveguides and two-dimensional metal-dielectric-metal plasmonic waveguides,'' 
-%     Opt. Express \textbf{15}, 1211-1221 (2007).
-% \bibitem{yang} R. Yang, R. A. Wahsheh, Z. Lu, and M. A. G. Abushagur, 
-%     ``Efficient light coupling between dielectric slot waveguide and plasmonic
-%     slot waveguide,'' Opt. Lett. \textbf{35}, 649-651 (2010).
-% \bibitem{code} \url{www.github.com/JesseLu/objective-first}
+\bibitem{robust1} F.
+Wang, J.
+S.
+Jensen, and O.
+Sigmund, ``Robust topology optimization of photonic crystal waveguides with tailored dispersion properties,'' J.
+Opt.
+Soc.
+Am.
+B \textbf{28}, 387-397 (2011).
 \end{thebibliography}
@@
     when designing nanophotonic components.
+
+Increasingly sophisticated optimization strategies for 
+    specific nanophotonic devices have been developed;
+    ranging from the use of genetic algorithms\cite{lipson},
+    level-set methods\cite{yablo}, 
+    tweaking the size and shape of specific canonical gemetric shapes\cite{levi,johnson},
+    and even utilizing the full parameter space\cite{sigmund1}.
+
+    \cite{jameson}
+    \cite{bendsoe}
 

### 2013-05-07 paper/paper.tex
Revision sent to Jelena.

@@
     Archive of Applied Mechanics \textbf{69}, 635-654 (1999).
+\bibitem{ob1_wg} J. Lu, J. Vuckovic, ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes,'' 
+    Opt. Express \textbf{20}, 7221-7236 (2012)
 \bibitem{miller} D. A. B. Miller, 
@@
     Opt. Express \textbf{20}, 23985-23993 (2012).
-\bibitem{ob1_wg} J. Lu, J. Vuckovic, ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes,'' 
-    Opt. Express \textbf{20}, 7221-7236 (2012)
 \bibitem{admm} S. Boyd, N. Parikh, E. Chu, B. Peleato, and J. Eckstein,
@@
 
-Increasingly sophisticated optimization strategies for 
-    specific nanophotonic devices have been developed;
-    ranging from the use of genetic algorithms\cite{lipson},
-    level-set methods\cite{yablo}, 
-    tweaking the size and shape of specific canonical gemetric shapes\cite{levi,johnson},
-    and even utilizing the full parameter space\cite{sigmund1}.
-
-    \cite{jameson}
-    \cite{bendsoe}
-
 Opening the design space to include many more parameters
@@
 
-For this reason, we have developed and implemented a computational method
-    which is able to use the full parameter space 
+To this end, increasingly sophisticated optimization strategies for 
+    specific nanophotonic devices have been developed
+    which are able to search this parameter space.
+These range from the use of genetic algorithms\cite{lipson},
+    level-set methods\cite{yablo}, 
+    and the optimization of specific geometric parameters\cite{levi,johnson}.
+Additionally, much success has been attained\cite{sigmund1}
+    through the use of topological design methods that
+    have traditionally been applied in other fields\cite{jameson,bendsoe}.
+
+In this work, we have endeavored to extend the current art
+    by developing and implementing a general computational method
+    for nanophotonic design which extends across all linear nanophotonic devices.
+Specifically, our method uses the full parameter space 
     to design linear nanophotonic components in three dimensions.
@@
 Lastly, all our results are produced by simply specifying
-    the functionality and performance of the desired device,
-    which suggests that our method may indeed by able
+    the functionality and performance of the desired linear device
+    in terms of mode conversion\cite{miller}.
+The variety of successful designs presented 
+    suggests that our method may indeed by able
     to design \emph{all} linear nanophotonic devices.
@@
         output patterns 1 and 2 respectively.
+
+    We note that although the performance description of nearly all
+        linear devices can be specified using such a constraint,
+        the constraint itself is \emph{not} linear (neither is it convex).
+    Other performance objectives are indeed possible which are nonlinear 
+        and nonconvex (such as optimizing for energy density or Q-factor)---convex 
+        objectives would be straightforward to implement,
+        while some non-convex objectives would require clever heurestics.
 
@@
     operating at 1550 nm wavelength).
+Lastly, our devices convert between modes of opposing symmetry.
+
+This is in contrast to prior art\cite{mode1,mode2,mode3,forchel},
+    which is largely limited to two-dimensional designs,
+    where mode-coupling is between same-symmetry modes,
+    and devices are often larger in the transverse direction
+    because of the need for photonic crystal mirrors.
 
@@
     desired a coupling efficiency above 90\%,
-    only 51.5\% efficiency was achieved (\fig{fib_te});
-    however, this likely remains the highest efficiency demonstrated
-    in a compact fiber coupler.
+    only 51.5\% efficiency was achieved (\fig{fib_te}).
 
@@
 The specific fabrication error was a general over- or under-etch
-    of the device (input and output waveguides unaffected).
+    of the device (input and output waveguides unaffected)\cite{robust1}.
 \Fig{analysis_fab_shift2} reveals that up to 8 nm of over- or under-etching

### 2013-05-20 paper/export/paper.tex
Got the export to work.
Final update for paper.

--- 2013-03-22 paper/paper.tex
@@
 \usepackage{amsmath,amssymb}
-\input defs.tex
+
+\newcommand{\myfig}[2]{
+    \begin{figure}[!h]
+    \begin{centering}
+    \includegraphics[width=0.8\textwidth]{#1}
+    \caption{#2}\label{#1}
+    \end{centering}
+    \end{figure}
+}
+
+\newcommand{\Eq}[1]{Eq.~\eqref{#1}}
+\newcommand{\Fig}[1]{Fig.~\ref{#1}}
+\newcommand{\eq}[1]{Eq.~\eqref{#1}}
+\newcommand{\fig}[1]{Fig.~\ref{#1}}
+\newcommand{\BI}{\begin{itemize}\item}
+\newcommand{\I}{\item}
+\newcommand{\EI}{\end{itemize}}
+\newcommand{\BEAS}{\begin{eqnarray}}
+\newcommand{\EEAS}{\end{eqnarray}}
+% \newcommand{\BEAS}{\begin{IEEEeqnarray}{rl}}
+% \newcommand{\EEAS}{\end{IEEEeqnarray}}
+\newcommand{\BSA}{\begin{subequations}\begin{align}}
+\newcommand{\ESA}{\end{align}\end{subequations}}
+\newcommand{\BE}{\begin{equation*}}
+\newcommand{\EE}{\end{equation*}}
+\newcommand{\BIT}{\begin{itemize}}
+\newcommand{\EIT}{\end{itemize}}
+
+\newcommand{\eg}{{\it e.g.}}
+\newcommand{\ie}{{\it i.e.} }
+
+\DeclareMathOperator*{\minimize}{\text{minimize}\quad}
+\newcommand{\subto}{\text{subject to}\quad}
+\newcommand{\T}{^\dagger}
+
+\newcommand{\ones}{\mathbf 1}
+\newcommand{\reals}{{\mbox{\bf R}}}
+\newcommand{\comps}{{\mbox{\bf C}}}
+\newcommand{\integers}{{\mbox{\bf Z}}}
+\newcommand{\symm}{{\mbox{\bf S}}}  % symmetric matrices
+
+\newcommand{\nullspace}{{\mathcal N}}
+\newcommand{\range}{{\mathcal R}}
+\newcommand{\Rank}{\mathop{\bf Rank}}
+\newcommand{\Tr}{\mathop{\bf Tr}}
+\newcommand{\diag}{\mathop{\bf diag}}
+\newcommand{\lambdamax}{{\lambda_{\rm max}}}
+\newcommand{\lambdamin}{\lambda_{\rm min}}
+
+\newcommand{\Expect}{\mathop{\bf E{}}}
+\newcommand{\Prob}{\mathop{\bf Prob}}
+\newcommand{\Co}{{\mathop {\bf Co}}} % convex hull
+\newcommand{\dist}{\mathop{\bf dist{}}}
+\newcommand{\argmin}{\mathop{\rm argmin}}
+\newcommand{\argmax}{\mathop{\rm argmax}}
+\newcommand{\epi}{\mathop{\bf epi}} % epigraph
+\newcommand{\Vol}{\mathop{\bf vol}}
+\newcommand{\dom}{\mathop{\bf dom}} % domain
+\newcommand{\intr}{\mathop{\bf int}}
+
 \begin{document}
-\title{Nanophotonic Computational Design}
+
+\title{Nanophotonic computational design}
 \author{Jesse Lu$^\ast$ and Jelena Vu\v{c}kovi\'{c}}
-\address{Stanford University, Stanford, California, USA.}
+\address{Ginzton Laboratory, Stanford University, Stanford, California, USA.}
 \email{jesselu@stanford.edu}
@@
 \end{abstract}
-\ocis{230.75370, 130.3990.}
+\ocis{350.4238 (Nanophotonics); 350.3950 (Micro-optics).}
 
 \begin{thebibliography}{99}
-\bibitem{ob1_wg} J. Lu, J. Vuckovic, ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes,'' 
+\bibitem{lipson} 
+    A. Gondarenko and M. Lipson, 
+    ``Low modal volume dipole-like dielectric slab resonator,'' 
+    Opt. Express \textbf{16} 17689-17694 (2008).  
+\bibitem{yablo} C.-Y. Kao, S. Osher, and E. Yablonovitch, 
+    ``Maximizing band gaps in two-dimensional photonic crystals by using level set methods,'' Appl. Phys. B \textbf{81}, 235-244 (2005).
+\bibitem{levi}
+    P. Seliger, M. Mahvash, C. Wang, and A. Levi,
+    ''Optimization of aperiodic dielectric structures,''
+    J. Appl. Phys. \textbf{100}, 34310-6 (2006).
+\bibitem{johnson} A. Oskooi, A. Mutapcic, S. Noda, J. D. Joannopoulos, S. P. Boyd, and S. G. Johnson, 
+    ``Robust optimization of adiabatic tapers for coupling to slow-light photonic-crystal waveguides,'' Opt. Express \textbf{20}, 21558-21575 (2012).
+\bibitem{sigmund1} Y. Elesin, B. S. Lazarov, J. S. Jensen, O. Sigmund, 
+    ``Design of robust and efficient photonic switches using topology optimization,''
+    Photonics and Nanostructures - Fundamentals and Applications \textbf{10}, 
+    153–165 (2012).
+\bibitem{jameson} L. Martinelli and A. Jameson, 
+    ``Computational aerodynamics: solvers and shape optimization,''
+    J. Heat Transfer \textbf{135}, 011002 (2013).
+\bibitem{bendsoe} M. P. Bendsoe and O. Sigmund,
+    ``Material interpolation schemes in topology optimization,''
+    Archive of Applied Mechanics \textbf{69}, 635-654 (1999).
+\bibitem{ob1_wg} J. Lu and J. Vuckovic, ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes,'' 
     Opt. Express \textbf{20}, 7221-7236 (2012)
+\bibitem{miller} D. A. B. Miller, 
+    ``All linear optical devices are mode converters,'' 
+    Opt. Express \textbf{20}, 23985-23993 (2012).
 \bibitem{admm} S. Boyd, N. Parikh, E. Chu, B. Peleato, and J. Eckstein,
-    ``Distributed Optimization and Statistical Learning via the Alternating Direction Method of Multipliers,''
+    ``Distributed optimization and statistical learning via the alternating direction method of multipliers,''
     Foundations and Trends in Machine Learning \textbf{3}, 1-122 (2011). 
@@
 
-For this reason, we have developed and implemented a computational method
-    which is able to use the full parameter space 
+To this end, increasingly sophisticated optimization strategies for 
+    specific nanophotonic devices have been developed
+    which are able to search this parameter space.
+These range from the use of genetic algorithms\cite{lipson},
+    level-set methods\cite{yablo}, 
+    and the optimization of specific geometric parameters \cite{levi,johnson}.
+Additionally, much success has been attained\cite{sigmund1}
+    through the use of topological design methods that
+    have traditionally been applied in other fields \cite{jameson,bendsoe}.
+
+In this work, we have endeavored to extend the current art
+    by developing and implementing a general computational method
+    for nanophotonic design which extends across all linear nanophotonic devices.
+Specifically, our method uses the full parameter space 
     to design linear nanophotonic components in three dimensions.
@@
 Lastly, all our results are produced by simply specifying
-    the functionality and performance of the desired device,
-    which suggests that our method may indeed by able
+    the functionality and performance of the desired linear device
+    in terms of mode conversion \cite{miller}.
+The variety of successful designs presented 
+    suggests that our method may indeed by able
     to design \emph{all} linear nanophotonic devices.
@@
         which can be deduced since $A_i(z)x_i-b_i=0$ is not a hard constraint.
-    Instead, this formulation is what we call an \emph{objective-first} \cite{ob1_wg}
+    Instead, this formulation is what we call an \emph{objective-first}\cite{ob1_wg}
         formulation in that the \emph{design objective} (explained below)
@@
     which couple light from an optical fiber at normal incidence
-    into an in-plane waveguide\cite{baets}.
+    into an in-plane waveguide \cite{baets}.
 
@@
 The specific fabrication error was a general over- or under-etch
-    of the device (input and output waveguides unaffected).
+    of the device (input and output waveguides unaffected) \cite{robust1}.
 \Fig{analysis_fab_shift2} reveals that up to 8 nm of over- or under-etching
@@
 
+\section{Acknowledgments}
 This work has been supported by the 

### 2013-05-20 paper/paper.tex
Final update for paper.

@@
 \newcommand{\Fig}[1]{Fig.~\ref{#1}}
-\newcommand{\eq}[1]{eq.~\eqref{#1}}
-\newcommand{\fig}[1]{fig.~\ref{#1}}
+\newcommand{\eq}[1]{Eq.~\eqref{#1}}
+\newcommand{\fig}[1]{Fig.~\ref{#1}}
 \newcommand{\BI}{\begin{itemize}\item}
@@
 
-\title{Nanophotonic Computational Design}
+\title{Nanophotonic computational design}
 \author{Jesse Lu$^\ast$ and Jelena Vu\v{c}kovi\'{c}}
-\address{Stanford University, Stanford, California, USA.}
+\address{Ginzton Laboratory, Stanford University, Stanford, California, USA.}
 \email{jesselu@stanford.edu}
@@
 \end{abstract}
-\ocis{230.75370, 130.3990.}
+\ocis{350.4238 (Nanophotonics); 350.3950 (Micro-optics).}
 
@@
 \bibitem{lipson} 
-    A. Gondarenko, and M. Lipson, 
+    A. Gondarenko and M. Lipson, 
     ``Low modal volume dipole-like dielectric slab resonator,'' 
@@
     153–165 (2012).
-\bibitem{jameson} L. Martinelli, and A. Jameson, 
-    ``Computational Aerodynamics: Solvers and Shape Optimization,''
+\bibitem{jameson} L. Martinelli and A. Jameson, 
+    ``Computational aerodynamics: solvers and shape optimization,''
     J. Heat Transfer \textbf{135}, 011002 (2013).
-\bibitem{bendsoe} M. P. Bendsoe, O. Sigmund,
+\bibitem{bendsoe} M. P. Bendsoe and O. Sigmund,
     ``Material interpolation schemes in topology optimization,''
     Archive of Applied Mechanics \textbf{69}, 635-654 (1999).
-\bibitem{ob1_wg} J. Lu, J. Vuckovic, ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes,'' 
+\bibitem{ob1_wg} J. Lu and J. Vuckovic, ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes,'' 
     Opt. Express \textbf{20}, 7221-7236 (2012)
@@
 \bibitem{admm} S. Boyd, N. Parikh, E. Chu, B. Peleato, and J. Eckstein,
-    ``Distributed Optimization and Statistical Learning via the Alternating Direction Method of Multipliers,''
+    ``Distributed optimization and statistical learning via the alternating direction method of multipliers,''
     Foundations and Trends in Machine Learning \textbf{3}, 1-122 (2011). 
@@
     level-set methods\cite{yablo}, 
-    and the optimization of specific geometric parameters\cite{levi,johnson}.
+    and the optimization of specific geometric parameters \cite{levi,johnson}.
 Additionally, much success has been attained\cite{sigmund1}
     through the use of topological design methods that
-    have traditionally been applied in other fields\cite{jameson,bendsoe}.
+    have traditionally been applied in other fields \cite{jameson,bendsoe}.
 
@@
     the functionality and performance of the desired linear device
-    in terms of mode conversion\cite{miller}.
+    in terms of mode conversion \cite{miller}.
 The variety of successful designs presented 
@@
 The specific fabrication error was a general over- or under-etch
-    of the device (input and output waveguides unaffected)\cite{robust1}.
+    of the device (input and output waveguides unaffected) \cite{robust1}.
 \Fig{analysis_fab_shift2} reveals that up to 8 nm of over- or under-etching

### 2013-05-24 thesis/bibliography.tex
Thesis revision (from Jelena's comments) almost done.
Just need conclusion.

@@
 \begin{thebibliography}{99}
+
+\bibitem{pic1} 
+    Qianfan Xu, Bradley Schmidt, Sameer Pradhan, and Michal Lipson,
+    ``Micrometre-scale silicon electro-optic modulator,''
+    Nature \textbf{435}, 325-327 (2005).
+
+\bibitem{pic2}
+    Jie Sun, Erman Timurdogan, Ami Yaacobi, Ehsan Shah Hosseini, and Michael R. Watts,
+    ``Large-scale nanophotonic phased array,''
+    Nature \textbf{493}, 195-199 (2013).
+
+\bibitem{lipson} 
+    A. Gondarenko and M. Lipson, 
+    ``Low modal volume dipole-like dielectric slab resonator,'' 
+    Opt. Express \textbf{16}, 17689-17694 (2008).
+
+\bibitem{yablo} C.-Y. Kao, S. Osher, and E. Yablonovitch, 
+    ``Maximizing band gaps in two-dimensional photonic crystals by using level set methods,'' Appl. Phys. B \textbf{81}, 235-244 (2005).
+
+\bibitem{levi}
+    P. Seliger, M. Mahvash, C. Wang, and A. Levi,
+    ''Optimization of aperiodic dielectric structures,''
+    J. Appl. Phys. \textbf{100}, 34310-6 (2006).
+
+\bibitem{johnson} A. Oskooi, A. Mutapcic, S. Noda, J. D. Joannopoulos, S. P. Boyd, and S. G. Johnson, 
+    ``Robust optimization of adiabatic tapers for coupling to slow-light photonic-crystal waveguides,'' Opt. Express \textbf{20}, 21558-21575 (2012).
+
+\bibitem{sigmund1} Y. Elesin, B. S. Lazarov, J. S. Jensen, O. Sigmund, 
+    ``Design of robust and efficient photonic switches using topology optimization,''
+    Photonics and Nanostructures - Fundamentals and Applications \textbf{10}, 
+    153–165 (2012).
+
+\bibitem{jameson} L. Martinelli and A. Jameson, 
+    ``Computational aerodynamics: solvers and shape optimization,''
+    J. Heat Transfer \textbf{135}, 011002 (2013).
+
+\bibitem{bendsoe} M. P. Bendsoe and O. Sigmund,
+    ``Material interpolation schemes in topology optimization,''
+    Archive of Applied Mechanics \textbf{69}, 635-654 (1999).
 
@@
 \bibitem{Lu12} J. Lu, J. Vuckovic, ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes,'' 
-    Opt. Express \textbf{20}, 7221-7236 (2012)
+    Opt. Express \textbf{20}, 7221-7236 (2012).
 
-\bibitem{Lu13} J. Lu, J. Vuckovic, ``Nanophotonic computational design,'' \emph{under review}.
+\bibitem{Lu13} J. Lu, J. Vuckovic, ``Nanophotonic computational design,'' 
+    Opt. Express \textbf{21}, 13351-13367 (2013).
 
@@
     Opt. Express \textbf{15}, 1211-1221 (2007).
+
+\bibitem{robust1} F.
+Wang, J.
+S.
+Jensen, and O.
+Sigmund, ``Robust topology optimization of photonic crystal waveguides with tailored dispersion properties,'' J.
+Opt.
+Soc.
+Am.
+B \textbf{28}, 387-397 (2011).
 

### 2013-05-24 thesis/chapter1.tex
Thesis revision (from Jelena's comments) almost done.
Just need conclusion.

@@
     but also in the structure variable.
-Specifically, that
+Specifically, that both $E$ and $\epsilon$ are \emph{bi-linear} in
+    the electromagnetic wave equation which is
     \BE \nabla \times \mu_0^{-1} \nabla \times E - \omega^2 \epsilon E = 
-        -i\omega J \label{p1:wave} \EE
-    is \emph{bi-linear} in both $E$ and $\epsilon$.
+        -i\omega J, \label{p1:wave} \EE
+    where
+    \BI $E$ is the electric-field,
+    \I  $J$ is the excitation current density,
+    \I  $\omega$ is the angular frequency,
+    \I  $\mu_0$ is the permeability of vacuum, and
+    \I  $\epsilon$ is the space-dependent permittivity. \EI
 Practically, this meant that solving for $\epsilon$ should be rather straightforward,
@@
 We were previously quite excited to learn that solving for 
-    a dielectric structure ($\epsilon$ or $z$) given 
-    its electromagnetic field ($E$ or $x$) is actually quite simple,
+    a dielectric structure ($\epsilon$, i.e.~$z$) given 
+    its electromagnetic field ($E$, i.e.~$x$) is actually quite simple,
     but generally results in unrealizable structures.
@@
 Although our results seemed promising in producing well-behaved
-    dielectric structures;
-    critically, fig.~\ref{regls pic} shows that there seems
+    dielectric structures,
+    fig.~\ref{regls pic} shows that there seems
     to be an unavoidable trade-off between 

### 2013-05-24 thesis/chapter2.tex
Thesis revision (from Jelena's comments) almost done.
Just need conclusion.

@@
     but in the improper selection of a target field. 
-In fact, we realizaed thtat it is very difficult to select a suitable target field 
+In fact, we realized thtat it is very difficult to select a suitable target field 
     because not every field even has a manufacturable dielectric structure 
@@
 Fig.~\ref{comp pic} shows that the iterative algorithm, after $400$ iterations and with the correct choice of regularization parameters $\eta_0$ and $\eta_1$, 
-    indeed results in a well-behaved structure that is able to closely reproduce the modified target field\cite{Lu10}!
+    indeed results in a well-behaved structure that is able to closely reproduce the modified target field\cite{Lu10}.
 
@@
 
-\subsection{2D}
+\subsection{Iterative design in 2D}
 The iterative design method can also be extended to two dimensions\cite{Lu10}.
@@
 % 
-\subsection{2.5D}
+\subsection{Iterative design in 2.5D}
 % \section{2.5-dimensional approximation}
@@
 \alpha &= \sqrt{k_x^2 - \left(\frac{\omega}{c}\right)^2}, \quad\text{and} \\
-k_x &= \sqrt{\left(\frac{n_\text{eff}\omega}{c}\right)^2 - \beta^2}.
+k_x &= \sqrt{\left(\frac{n_\text{eff}\omega}{c}\right)^2 - \beta^2},
 \end{align}
-Here, $\alpha$ is the wave-vector which determines the evanescent decay of the slab waveguide mode into air, while $k_x$ is an approximated in-plane k-vector.
+Here, $\alpha$ is the wave-vector which determines the evanescent decay of the slab waveguide mode into air, while $k_x$ is an approximated in-plane k-vector, and $x$ is the speed of light.
 To determine $n_\text{eff}$, the effective refractive index, we use the following approximation,

### 2013-05-24 thesis/chapter3.tex
Thesis revision (from Jelena's comments) almost done.
Just need conclusion.

@@
 % 
-\chapter{Objective-first design} \label{ob-1}
+\chapter{Objective-first design in 2D} \label{ob-1}
 % 
@@
     \end{enumerate}
-All the designs presented are both highly efficient 
+All designs presented are both highly efficient 
     ($\sim 98\%$ coupling efficiency, in contrast to previous designs

### 2013-05-24 thesis/chapter4.tex
Thesis revision (from Jelena's comments) almost done.
Just need conclusion.

@@
 % \end{thebibliography}
-\chapter{Nanophotonic computational design} \label{final}
+\chapter{Nanophotonic computational design in 3D} \label{final}
 % \section{Introduction}
@@
 \section{Problem formulation}
-We now develop a method which may indeed be capable of designing 
+In this central chapter of this work, 
+    we present a method which may indeed be capable of designing 
     linear nanophotonic devices which
@@
 
+    We note that although the performance description of nearly all
+        linear devices can be specified using such a constraint,
+        the constraint itself is \emph{not} linear (neither is it convex).
+    Other performance objectives are indeed possible which are nonlinear 
+        and nonconvex (such as optimizing for energy density or Q-factor)---convex 
+        objectives would be straightforward to implement,
+        while some non-convex objectives would require clever heurestics.
+
     Finally, we note again that the design objective in our formulation
@@
 
-All of our results are in three dimensions
+\emph{All of our results are in three dimensions
     and are planar structures, consisting of a 250 nm etched silicon slab
-    completely surrounded by silica.
+    completely surrounded by silica.}
 The permittivity values of silicon and silica used
@@
     {Perfomance specification of the TE mode converter.
-    Input mode is the fundamental TE-polarized mode on the left.
-    Primary output mode is the second-order mode on the right.
-    Output power in the transmitted fundamental mode 
+    Input mode is the fundamental TE-polarized mode on the top-left.
+    Primary output mode is the second-order mode on the top-right.
+    Output power in the transmitted fundamental mode (bottom-right) 
     should be no more than 1\%.
@@
     {Perfomance specification of the TM mode converter.
-    Input mode is the fundamental TM-polarized mode on the left.
-    Primary output mode is the second-order mode on the right.
-    Output power in the transmitted fundamental mode on the right 
-    above 1\% is to be rejected.
+    Input mode is the fundamental TM-polarized mode on the top-left.
+    Primary output mode is the second-order mode on the top-right.
+    Output power in the transmitted fundamental mode on the bottom-right 
+    should be under 1\%.
     The structure shown is the final three-dimensional design.}
@@
         input arms 1, 2, 3, and 4 respectively (top to bottom).}
+\clearpage
 
@@
     At 1310 nm, the respective efficiencies are 75.7\% and 75.2\%.}
+\clearpage
 

### 2013-05-24 thesis/conclusion.tex
Thesis revision (from Jelena's comments) almost done.
Just need conclusion.

\chapter{Conclusion and future work}\label{conclusion}

### 2013-05-24 thesis/intro.tex
Thesis revision (from Jelena's comments) almost done.
Just need conclusion.

@@
     which are designed by tuning
-    a handful of design parameters (\fig{integrated_circuit}).
+    a handful of design parameters\cite{pic1,pic2} (\fig{integrated_circuit}).
 Much progress has been made on this front;
@@
 \myfig{integrated_circuit}
-    {Examples of hand-tuned nanophotonic devices.
+    {Examples of hand-tuned nanophotonic devices\cite{pic1,pic2}.
     Device performance is tuned by varying the sizes of and spacing between
@@
     \end{enumerate}
+Unfortunately, the lack of intuition for what such designs might look like and
+    the inability to manually search such a large parameter space
+    have greatly hindered the ability to achieve a full-parameter space design.
 The goal of this work, then, is to be able to take advantage
@@
 
-Along this line of reasoning
-    we expect to be able to produce devices which
+Previously, design algorithms featuring a large number of parameters
+    have been applied to the design of individual devices.
+These range from the use of genetic algorithms\cite{lipson},
+    level-set methods\cite{yablo}, 
+    and the optimization of specific geometric parameters\cite{levi,johnson}
+    to design nanophotonic devices.
+Additionally, much success in this field has been attained\cite{sigmund1}
+    through the use of topological design methods that
+    have traditionally been applied in other fields \cite{jameson,bendsoe}.
+
+Built upon this prior art,
+    this work's aim is to produce a design method 
+    that not only produces designs for a single device,
+    but for a wide range of devices.
+Specifically,
+    we desired to be able to produce devices which
     \BI have very compact footprints,
@@
 
-Of course, in this regime, the hand-tuning of parameters 
-    is no longer a tractable strategy.
-Instead, we use a \emph{design-by-specification} strategy
+Not only was a large parameter space used to achieve such designs,
+    but we employed a \emph{design-by-specification} strategy
     which simply means that our software produces nanophotonic designs
-    based solely based on the desired performance specification given to it,
+    based solely on the desired performance specification given to it,
     and requires no intermediate hand tuning.
-
-We note, lastly, that the design-by-specification strategy
+We note that such a design-by-specification strategy
     is unusually powerful in the sense that \emph{all} useful nanophotonic devices
@@
 This appendix will be most useful to any wishing to reproduce our work.
+
+The work presented here is based on the following publications:
+\begin{itemize}
+\item chapters~\ref{direct}-\ref{bounded}: ``Inverse design of nanophotonic structures using complementary convex optimization,'' Opt. Express (2010),
+\item chapter~\ref{bounded}:
+    ``Inverse design of a three-dimensional nanophotonic resonator,''
+    Opt. Express (2011), 
+\item chapter~\ref{ob-1}: ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes,'' 
+    Opt. Express (2012),
+\item chapter~\ref{final}: ``Nanophotonic computational design,'' Opt. Express (2013).
+\end{itemize}

### 2013-05-25 thesis/appendix3.tex
Draft done.
Ready to submit thesis to committee.

@@
 \label{maths}
-As previously stated, the problem we want to solve is 
+As previously stated (chapter~\ref{final}), the problem we want to solve is 
     \EE {rigorous problem statement}
@@
 
-\section{The structure submodule}
-% \subsection{The continuous structure update}
-A continuous structure update scheme solves
-    \E  {structure submodule primary equation}
-        {\argmin Q(z) + g(z)}
-    by limiting the allowable values of $p$
-    in \eq{structure design objective definition} to a continuous range
-    of real values.
-
-If both $m(p)$ and $w(p)$ are linear, 
-    then \eq{structure submodule primary equation} is convex
-    and can be solved using CVX.
-
-On the other hand, if this is not the case, 
-    then \eq{structure submodule primary equation}
-    is solved using a gradient-descent method.
-
+% \section{The structure submodule}
+% % \subsection{The continuous structure update}
+% A continuous structure update scheme solves
+%     \E  {structure submodule primary equation}
+%         {\argmin Q(z) + g(z)}
+%     by limiting the allowable values of $p$
+%     in \eq{structure design objective definition} to a continuous range
+%     of real values.
+% 
+% If both $m(p)$ and $w(p)$ are linear, 
+%     then \eq{structure submodule primary equation} is convex
+%     and can be solved using CVX.
+% 
+% On the other hand, if this is not the case, 
+%     then \eq{structure submodule primary equation}
+%     is solved using a gradient-descent method.
+% 
 % 

### 2013-05-25 thesis/conclusion.tex
Ready to submit thesis to committee.

@@
 \chapter{Conclusion and future work}\label{conclusion}
+
+We have presented a general design method
+    for linear nanophotonic devices,
+    as well as the intermediary results, difficulties, and realizations
+    that enabled us to achieve this final result.
+
+The ability to design essentially \emph{any} linear nanophotonic device
+    simply by specifying its desired performance
+    is a simple, powerful, and necessary tool for future 
+    on-chip networks.
+As such, this work represents only an existence proof
+    that such computational capabilities are possible 
+    and can be achieved.
+Specifically, that it is possible to design nanophotonic devices which
+    \BI are fully three-dimensional,
+    \I  are manufacturable,
+    \I  have very compact footprints,
+    \I  exhibit high efficiency performance,
+    \I  are multi-modal in their operation,
+    \I  are robust to shifts in wavelength and temperature,
+    \I  are robust to fabrication error,
+    \I  demonstrate novel, never-before-seen functionality, \EI
+    simply by giving a computer a design specification for the device.
+
+In this vein, there exist numerous opportunities 
+    to \emph{vastly} improve and extend the work we have presented.
+
+\section{Additional fabrication constraints}
+Improving the ease of manufacturability of optimized designs
+    is an area where many gains should be realized.
+
+While our final results are considered to be within
+    the current limits of nanofabrication,
+    they are by no means \emph{easy} to manufacture.
+Additional or modified optimization steps
+    where the structure is constrained to simple shapes (e.g.~circles only)
+    or where the minimum feature size is maximized
+    would significantly boost the manufacturability of the resulting designs.
+
+Such capability is actually already implemented (though not utilized), 
+    to a large extent,
+    in the final method presented in chapter~\ref{final},
+    in that $g(z)$ in eq.~\eqref{eq:rigorous problem statement}
+    can incorporate arbitrary constraints on the structure.
+Additionally, the parameterization of the structure can be modified
+    to describe the position and size of simple, 
+    rather than arbitrary, shapes.
+
+\section{Exploration of the solution space}
+Our final result, and indeed nearly all of our results,
+    were achieved utilizing simple initial structures
+    of uniform permittivity.
+This was chosen for simplicity of implementation,
+    and to show that working designs could still be achieved
+    from completely non-functional initial structures.
+At the same time, because of the non-convex nature of our problem,
+    we expect different initial structures to arrive at different designs;
+    an aspect that we have yet to explore at all.
+
+For this reason, 
+    an investigation into the various methods and choices of initial structures 
+    would be a necessary and useful pursuit.
+Additional parameters, such as the size and shape of the optimization area,
+    should also be modified in an attempt to understand their effect
+    on produced designs.
+
+In theory, such investigations should not be computationally demanding
+    since one could execute multiple design runs with different initial conditions
+    in an embarrassingly parallel manner.
+Practically, however, the speed of the underlying simulation engine
+    can dictate whether or not this is feasible in a research environment.
+
+\section{Enhanced simulation capabilities}
+Solving for the matrix corresponding to the electromagnetic wave equation
+    is the primary computational burden of our method.
+Therefore, simulation code which is faster, and can handle larger, higher
+    resolution grids
+    has a direct and significant impact on the design capabilities of our method.
+
+Currently, although our use of the method described in \cite{Shin12} seems optimal,
+    improvements (whether in algorithm or implementation)
+    should be eagerly investigated.
+Just as the currently used method was the key technology in achieving 
+    the final results presented here,
+    a new advance in the capabilities of the simulation engine
+    may very well be the stepping stone
+    to an entirely new set of capabilities.

### 2013-05-28 thesis/intro.tex
Ready to submit thesis to committee.
Minor correction (from Jelena).

@@
     \I  are robust to fabrication error,
-    \I  may even demonstrate novel, never-before-seen functionality. \EI
+    \I  demonstrate novel, never-before-seen functionality. \EI
 Our final result (chapter~\ref{final}) indeed demonstrates
@@
     our final result, which is presented in chapter \ref{final}.
-Futhermore, each section is broken into three major sections:
+Futhermore, each chapter is broken into three major sections:
     \begin{description}
@@
 \begin{itemize}
-\item chapters~\ref{direct}-\ref{bounded}: ``Inverse design of nanophotonic structures using complementary convex optimization,'' Opt. Express (2010),
-\item chapter~\ref{bounded}:
+\item chapters~\ref{direct}-\ref{bounded}: J. Lu and J. Vuckovic, ``Inverse design of nanophotonic structures using complementary convex optimization,'' Opt. Express \textbf{18}, 3793-3804 (2010),
+\item chapter~\ref{bounded}: J. Lu, S. Boyd, and J. Vuckovic, 
     ``Inverse design of a three-dimensional nanophotonic resonator,''
-    Opt. Express (2011), 
-\item chapter~\ref{ob-1}: ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes,'' 
-    Opt. Express (2012),
-\item chapter~\ref{final}: ``Nanophotonic computational design,'' Opt. Express (2013).
+    Opt. Express \textbf{19}, 10563-10750 (2011),
+\item chapter~\ref{ob-1}: J. Lu, J. Vuckovic, ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes,'' 
+    Opt. Express \textbf{20}, 7221-7236 (2012),
+\item chapter~\ref{final}: J. Lu, J. Vuckovic, ``Nanophotonic computational design,'' 
+    Opt. Express \textbf{21}, 13351-13367 (2013).
 \end{itemize}

### 2013-06-04 thesis/acknowledgement.tex
Added bibliography and fixed citations.
Removed preface section.
achnowledgement and DABM's corrections.

@@
-\prefacesection{Acknowledgement}
-body 
+\prefacesection{Acknowledgements}
+\begin{quote}
+In the beginning was the Word, and the Word was with God, and the Word was God.
+He was in the beginning with God.
+All things were made through him, and without him was not any thing made that was made.
+In him was life, and the life was the light of men.
+The light shines in the darkness, and the darkness has not overcome it.
+(John 1:1-4)
+\end{quote}
+
+\begin{quote}This is the message we have heard from him and proclaim to you, that God is light, and in him is no darkness at all. (1 John 1:1) \end{quote}
+
+I have had the privilege, 
+    over the course of my studies,
+    to become intimately familiar with the study of light 
+    both from a \emph{physical} and \emph{spiritual} perspective.
+This thesis, not surprisingly, 
+    features the equations which describe light.
+And when properly considered,
+    naturally lead one's mind to the origin of that light, Jesus Christ.
+
+It is the Lord Jesus Christ that I want to acknowledge in this thesis.
+I acknowledge Him as my Creator,
+    and the One who, in the beginning, said, 
+    ```Let there be light', and there was light.'' (Genesis 1:3)
+I acknowledge Him as my Savior, the Light of the world,
+    who has brought me to God by the forgiveness of my sins in His blood.
+He is the ultimate light, 
+    apart from which we cannot do or know anything---whether
+    we acknowledge Him or not.
+And far more significant than any of the progress presented here
+    is the work that He promises to do in every willing and submissive heart,
+\begin{quote}
+For God, who said, ``Let light shine out of darkness,'' has shone in our hearts to give the light of the knowledge of the glory of God in the face of Jesus Christ.
+(2 Corinthians 4:6)
+\end{quote}
+
 \afterpreface

### 2013-06-04 thesis/chapter2.tex
achnowledgement and DABM's corrections.

@@
     but in the improper selection of a target field. 
-In fact, we realized thtat it is very difficult to select a suitable target field 
+In fact, we realized that it is very difficult to select a suitable target field 
     because not every field even has a manufacturable dielectric structure 
@@
     \eq{iterative problem} is only modified in the
-    definition of its constituent vectors and matrices,
+    definition of its constituent vectors and matrices;
     the formulation remains the same.
@@
     as seen in fig.~\ref{bounded comp pic}\cite{Lu10}.
-Note that the the directly discreteness of $z$ was not enforced (since that would make the problem non-convex); 
+Note that the discreteness of $z$ was not enforced (since that would make the problem non-convex); 
     however, a discrete, binary-valued structure arose fortuitously. 
